### 2020-02-10 draft_sub_con.tex
Initial committ

% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

% This is a simple template for a LaTeX document using the "article" class.
% See "book", "report", "letter" for other types of document.
\documentclass[12pt]{article}
\usepackage[round, sort , authoryear]{natbib}

%required by R
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage[normalem]{ulem}
\usepackage[normalem]{ulem}
\usepackage[utf8]{inputenc}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{dcolumn}
\usepackage{mathtools}% http://ctan.org/pkg/mathtools

%Fort title position
\usepackage{titling}

%For new line in table
\usepackage{array}
\usepackage{makecell}

\renewcommand\theadalign{bc}
\renewcommand\theadgape{\Gape[4pt]}
\renewcommand\cellgape{\Gape[4pt]}

%New environments
\newtheorem{lemma}{Lemma}
\newtheorem{assumption}{Assumption}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newenvironment{proof}[1][Proof]{\noindent \textbf{#1.} }{\  \rule{0.5em}{0.5em}}

%For tables position
\usepackage{float}
\restylefloat{table}

%%% PAGE DIMENSIONS
\usepackage[margin=2.5 cm]{geometry}
\usepackage{blindtext} % to change the page dimensions
\geometry{a4paper} % or letterpaper (US) or a5paper or....
% \geometry{margin=2in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information

\usepackage[utf8]{inputenc} 
\usepackage{graphicx} % support the \includegraphics command and options
\usepackage{epstopdf}
\usepackage[hang]{footmisc}
\usepackage{lipsum}
\usepackage{setspace}
% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{pgfplots}
\pgfplotsset{compat=1.13}
\usepackage{caption}
\usepackage{threeparttablex}
\usepackage{color, colortbl}
\definecolor{Gray}{gray}{0.9}
%%% PACKAGES
\usepackage{placeins}
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
% These packages are all incorporated in the memoir class to one degree or another...
\usepackage{amsmath}
\numberwithin{table}{section}
\usepackage{cases}
\usepackage{graphicx}
%
\usepackage{float}
\usepackage{authblk}
\usepackage{pgfplots}
\usepackage{pdfpages}
\linespread{1.5}
\setlength{\footnotemargin}{4mm}
\usepackage{amssymb} 
\usepackage{tabularx}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\addtolength{\footnotesep}{2mm} % change to 1mm

%For Counting Figures in the Appendix
\usepackage{chngcntr}

%For subtables
\usepackage{subcaption}

%For having the catption above tables
\usepackage{float}
\floatstyle{plaintop}
\restylefloat{table}

%Math stuff
\DeclareMathOperator*{\argmax}{arg\,max}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2960}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=BibTeX}
%TCIDATA{LastRevised=Monday, August 27, 2018 20:06:51}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\restylefloat{table}
\oddsidemargin  +0.18in
\evensidemargin +0.18in
\topmargin 40pt \textheight 8.1in \textwidth 6.5in
\linespread{1.5}\parskip .05in

%Nice Figure and table headers
\captionsetup[figure]{labelfont={sc},name={Figure},labelsep=period}
%\captionsetup[table]{labelfont={sc},name={Table},labelsep=period,justification=centering}

\usepackage{booktabs}   % for nice tables
\usepackage[colorlinks=false, linktocpage=true]{hyperref}
%\usepackage[flushmargin]{footmisc}
%\addtolength{\footnotesep}{3mm} % change to 1mm
\hypersetup{
	colorlinks,
	linkcolor={blue!50!black},
	citecolor={blue!50!black},
	urlcolor={blue!80!black}
}
% use for hypertext
\usepackage[colorinlistoftodos]{todonotes}
\setlength{\marginparwidth}{2cm}
\newenvironment{customlegend}[1][]{%
	\begingroup
	% inits/clears the lists (which might be populated from previous
	% axes):
	\pgfplots@init@cleared@structures
	\pgfplotsset{#1}%
}{%
	% draws the legend:
	\pgfplots@createlegend
	\endgroup
}%
%For Figures, below

\usepackage{tikz}
\usetikzlibrary{shapes}
\usepgflibrary{arrows} % LATEX and plain TEX and pure pgf
\usepgflibrary[arrows] % ConTEXt and pure pgf
\usetikzlibrary{arrows} % LATEX and plain TEX when using Tik Z
\usetikzlibrary[arrows] % ConTEXt when using Tik Z
\usepackage{hyperref}

%%% The "real" document content comes below...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\parskip3mm\parindent0cm
\setlength{\droptitle}{-10em}   % This is your set screw

\title{Unilateral Divorce and the Rise of Informal Cohabitation	\thanks{The authors wishe to thank Matthias Doepke, Alessandra Voena and the Norhtwestern Macro group for their useful comments. Blasutto acknowledges financial support from the French speaking community of Belgium (ARC project 15/19-063 on "family transformations").}}
\author{Fabio Blasutto$^1$ \quad Egor Kozlov$^2$}

\begin{document}
	 	\tikzstyle{block} = [draw, fill=white, rectangle, 
	minimum height=3em, minimum width=6em]
	\tikzstyle{sum} = [draw, fill=white, circle, node distance=1cm]
	\tikzstyle{input} = [coordinate]
	\tikzstyle{output} = [coordinate]
	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]

	%Gauss distribution
	\pgfmathdeclarefunction{gauss}{2}{%
		\pgfmathparse{1/(#2*sqrt(2*pi))*exp(-((x-#1)^2)/(2*#2^2))}%
	}
	% Bibliography style, important for biblatex functioning	
	\bibliographystyle{apa}

	\maketitle

	\footnotetext[1]{IRES, UCLouvain \& National Fund for Scientific Research (Belgium). Email:  \tt{fabio.blasutto@uclouvain.be}}
	\footnotetext[2]{Northwestern Univrsity. Email:  \tt{egorkozlov2020@u.northwestern.edu}.\\}

\begin{abstract}
	Does unilateral divorce eroded the gains of marrying with respect to cohabiting? Exploiting the staggered introduction of unilateral divorce across U.S. states, we show that newly formed relationships after the reform are more likely to be cohabitations instead of marriages, and that cohabitation spells last longer. To understand the mechanisms underlying the law changes, we build and estimate a structural life cycle model with partnership choice, where the gains from marriage with respect to cohabitation comes from a better cooperation within the household, enforced through a costly divorce, which acts as a commitment technology. Unilateral divorces increases the risk of separation, making cohabitation preferred to couples that would have had the highest risk of divorce. Since the couples switching relationship are on average better matched than the average cohabitants, the average length of cohabitations increases.
\end{abstract}
\textbf{Keywords}: Marriage, Cohabitation, Unilateral Divorce, Structural Estimation\\
\textbf{JEL-Code}: D83 - J12
%\clearpage
%\noindent \medskip{}
\section{Introduction}
Why do people marry? According to the seminal work of \citet{becker1981}, people marry both for non-economic (i.e. love and companionship) and economic reasons, among which the sharing of public goods, the division of labor to exploit comparative advantages, as in \cite{chiappori1997}, and risk pooling, as \cite{voena2015} and \cite{rigas2015}, points out.
All these reasons are able to explain why couples decide to live together, but they are silent about the choice between different types of partnership contracts, such as marriage and informal cohabitation. Economic incentives might an important determinant of this choice, but also because married and cohabiting couples display a different economics behavior. For example, female labor supply is higher for cohabiting couples, while married couples are wealthier, as \cite{gemici2014} and \cite{lafortune2019} respectively point out. Moreover, cohabitation display a much higher separation rate than marriages, which might be a cause of the high share of single mothers living in the US nowadays, which is the single strongest predictor for upward mobility\footnote{While the share of single mothers is the strongest predictor of differences in upward mobility across counties on top of segregation, residential segregation, income inequality, social capital, school quality, and racial shares, \cite{chetty2018} points out that half of this effect is due to self selection.} according to \cite{chetty2018}. A striking fact about cohabitation is its fast rise in the recent decades: according to \cite{manning2013} the share of women that ever cohabited moved from 33\% in 1987 to 60\% in 2010. Why did this happen?

In this paper we address this question, focusing on the role of the unilateral divorce on the share of people that decides to cohabit. Our main contribution is to show the rate of cohabitation increased after the changes in US law and that the underlying mechanism is that the increased risk of divorce makes marriage less attractive, and as a consequence cohabitation becomes the preferred choice to couples that would have experienced the highest risk of divorce.

We first use data from the National Survey of Family and the Household and of the National Survey of Family growth to build a sample of first and second relationships\footnote{A relationship is defined as an interruption of the state of singleness, which can either be marriage or cohabitation.}. Then, exploiting the exogenous variation coming from the staggered introduction of unilateral divorce over time across US states, we show that cohabitation becomes 5\% more likely  to be chosen as result of the reform. Interestingly,  the effect is heterogeneous across property rights regimes within marriage, being insignificant in title based states and the strongest in community property states. This result suggest that the idea that the surplus of marriage comes from commitment, enforced through the equal division of assets\footnote{This mechanism is highlighted by \cite{lafortune2019}, where the equal division of assets within marriage makes possible to efficiently invest in children even after the rise of unilateral divorce.}, cannot be the only reason why some people started cohabiting instead. Moreover, we analyze how unilateral divorced affected the length of newly formed cohabitation spells, showing that they last longer both because of a reduced risk of marriage and of separation.
To understand the mechanisms that lead to these changes we build a dynamic model of intra household decision making, where cohabitation and marriage differs in the cost of separation and divorce as well as in law that govern the property rights upon divorce, which can vary for marriage while it is always title based for cohabitation. Moreover, separation can always be initiated unilaterally, as opposed to divorce, that would need the consensus of both partner under a mutual divorce regime. Individuals are initially single, and with some probability in each period they meet a potential partner, which they can decide to marry or start cohabiting with. Couples make decisions about consumption, savings and female labor supply and they are subject to idiosyncratic income shocks.  We model the decision making in the couple building on the literature of limited commitment (see for example \cite{kk1996},  \cite{ligon2002}, \cite{marcet2019} and \cite{pavoni2018}), which has been applied to dynamic collective models in the household by \cite{voena2015}, \cite{mazzocco2007}, \cite{foerster2019} and \cite{lise2018} among others. Couples also receive time varying match quality shocks, which might drive the couple to change their partnership status (i.e. from cohabitation to marriage) or to separate. When one member of the couple wishes to split, the bargaining powers are rebargained such that the binding member is made indifferent between separation and staying in a couple\footnote{For particularly bad draws in the match quality or productivity shock this might not be possible and hence the couple would split.}. The gains of marriage with respect to cohabitation derive from a better risk sharing and a more efficient specialization in the production of a public good\footnote{We assume that a public good is produced with money an female time. When females stop working for producing such good their potential productivity in the labor market decreases.}, which arise from a better commitment within the couple, enforced by the treat of a costly divorce, which acts as a commitment device. On the other hand, couples that would face a high risk of divorce if married (i.e. because of a low match quality draw) are more likely to choose cohabitation instead, since it implies a lower cost of separation while allowing to enjoy the gains from being in a couple. In the model, a switch from mutual consent to unilateral divorce causes couples to start cohabiting more, since the higher risk of divorce makes the expected value of divorce with respect to cohabitation lower. The effect would be particularly pronounced under community property division of assets upon divorce, since the richest part of the couple  would risk to lose most of its wealth. This mechanism implies that couples that would have previously married now start cohabiting: since those have on average a higher match quality than cohabiting couples, this selection drives down the risk of separation for cohabiting couples, as observed in the data.

We then estimate the model using the simulated method of moments, using as targets an array of moments regarding the mating market and the differential female labor supply for cohabiting and married couples. We find that the model is able to reproduce the results from our empirical evidence, thus validating our mechanism. We run a series of counterfactual experiments that shrinks the gender wage gap and the relative price of public versus public goods, which tell us the importance of this factors in explaining the rise in cohabitation over time.

This contribution of this paper is threefold. First, we are the first to document and explain how divorce laws affected the choice between marriage and cohabitation. This contribution adds to the existing literature that documented the effects of divorce laws on the rate of divorce (\cite{friedberg1998}, \cite{wolfers2006}), female labor supply (\cite{stevenson2008}, \cite{voena2015}), savings (\cite{voena2015}), assortative mating \cite{reynoso2019} and prostitution (\cite{ciacci2017}) among the others. As in \cite{reynoso2019}, we study not only the effect of unilateral divorce on married couples, but also on sorting. While her focus is on who marries whom and concludes that unilateral divorced raised the share of singles, we abstract from modeling the mating market and we focus on partnership choice, which allow us to conclude that the rate of singleness declined less than previously thought, since some people that were believed not to be in a couple were actually cohabiting. Our paper build on \cite{voena2015}, that studies how unilateral divorce interacted with property rights upon divorce affected household behavior of married couples. We extend her work both considering cohabitation as an alternative relationship and in analyzing the effects of these laws on sorting.
Second, our paper expands the literature on cohabitation, showing how the risk of splitting and its interaction with divorce laws is essential for understanding partnership choices. Different papers in the literature highlighted various gains of marriage with respect cohabitation: commitment (\cite{matouschek2008}), labor specialization within the couple \cite{gemici2014}, learning about match quality \cite{brien2006}, the interaction between commitment and learning \cite{blasutto2020} and  investment in children \cite{lafortune2019}. A paper close to ours is \cite{lafortune2019} who highlights the role of assets as a collateral that enforces commitment and hence allows for optimal investment in children. In their model, a switch from mutual consent to unilateral divorce causes people without wealth to start cohabiting because they are left without a commitment technology. While we think that thei mechinsim is important, it cannot be the whole story since we observe that the switch toward cohabitation was the weakest in title based state, while their model would predict the opposite. In this paper we will quanity how much of the shift is due to this mechanism versus the role of the increased risk of divorce. We extend the work of \cite{gemici2014} and \cite{blasutto2020}, who develop collective dynamic models with limited commitment, introducing saving decisions, which are shown to play an important for commitment and hence for partnership choice, especially when interacted with propoerty rights upon divorce.\\
Third, our paper speaks to the literature studying the canges of the family in recent decades. Recent works have investigated various channels through which the structure of families might have changed over time. \cite{albanesi2009} show the role of imporved maternal health on the rise of female labor force participation, \cite{greenwood2016} instead study the role that technology and the wage structure played in the rise in assortative mating, female labor force participation, the share of divorced and the increas in married people. Our paper extends this work, studying the effect of wage structure, gender wage gap and changes in the home production technology on the rise of cohabitation. Through a series of counterfactual experiments we are able to inspected which were the main forces behind the rise in cohabitation. Intuitively, as wages grow and the price of home appliances decreases, household can buy on the the market goods that were once produced at home. Since one of the gain of marriage with respect to cohabitation lies in the better specialization of production within the household, we might expect that those forces imply a reduction in the share of couples choosing marriage over cohabitation.

The paper is organized as follows: section 2 offers an overview of US divorce laws, section 3 presents the empirical results, while section 4 describes in detail the theoretical model. Section 5 explain the procedure used for the estimation as well as the results. Section 6 report the results from a series of counter-factual experiments , while section 7 performs a welfare analysis. Section 8 draws the conclusions of the paper.

\section{US Divorce Laws: an Overview}
\section{Data and Empirical Evidence}
\subsection{The Dataset}
\subsection{Empirical Evidence}
\section{The Model}
This section describes a dynamic life cycle structural model of partnership formation, savings, female labor supply and  home prduction. Couples act cooperatively subject to limited commitment, which means that rebargaining might happen in response of changes in the outside options, which are assumed to be divorce or separation.

In the model time is discrete, and in each period men and women draw their productivities. If single, with some probability they meet a potential partner that comes with a couple specific match quality shock, and they decide whether to marry, cohabit or to stay single. If they are in a couples, they observe a realization of the match quality shock as well as of their productivity, and according to those they decide whether to stay together or to split. Both singles and couples make consumption and savings decisions, using their money for private or public good expenditure. Couples also make female labor supply decisions\footnote{We assume that single females and all men work full time.} and female time can be used to produce the public good, but this comes at the cost of a loss in productivity. The gains of being in a couple comes from love, risk sharing and labor market specialization. Instead, the gains of marriage with respect to cohabitation comes from a more functioning risk sharing and a better specialization in time use, which derives from the high cost of divorce serving as a commitment device. These gains of marriage deteriorates when the love shock is low enough to cause a high risk of divorce and frequent renegotiations: in this case cohabitation might be the better option, since we assume that the cost of separation will be lower than the cost of marriage.
	   		\begin{figure}[H]\centering
	\begin{tikzpicture}[domain=0:1,scale=4]
	\node [block, name=input,align=center] (sum) {Single\\ 7348};
	\node [block, above right of=sum, node distance=6cm] (controller) {Separation};
	\node [block, below right of=controller,
	node distance=6cm,align=center] (system) {Cohabitation \\ 5308};
	\draw [<-,  thick, latex-] (controller) -| node[below left]{47,8\%}(system);
	\node [output, right of=system] (output) {fe};
	\node [block, below left of=system,  node distance=6cm,align=center] (measurements) {Marriage \\ 2814};
	\node [block, left of=measurements, node distance=4.2cm,align=left] (divorce) {Divorce};
	\draw [<-,  thick, latex-] (sum) |- node[below right]{100\%} (controller);
	\draw [->,  thick, -latex] (sum) -- node[above]{72,4\%} (system);
	\draw [->,  thick, -latex] (system) |-node[above left]{33,8\%} (measurements);
	\draw [->,  thick, -latex] (measurements) --node[above]{23,5\%} (divorce);
	\draw [->,  thick, -latex] (sum) --node[above right]{12,9\%} (measurements);
	\draw [->,  thick, -latex] (divorce) --node[right]{100\%} (sum);
	node [near end] {$$} (sum);
	\end{tikzpicture}
	\label{fig:scheme}
	\caption*{\footnotesize \textsc{Notes}: Number of spells and transitions as arising from the data in our sample.}
	\caption{}
	\end{figure}
\subsection{Preferences}
Women $f$ and men $m$ derive utility consuming a private good  $c$ and a household public good $Q$. The public good can be interpreted in terms of both the quantity and quality of children, as well as the goods and services produced within the household, as washing clothes  or home cooked meals. Preferences are separable in the two goods and across time.
Agents derives utility from a couple specific love shock $\psi$ which evolves over time and it can be interpreted as  can be interpreted as the value of love and companionship in a couples. The intra period utility of a single agent $s\in(f,m)$ is:
\[u(c^s_t,Q^s_t)=\frac{{c^s_t}^{1-\sigma}}{1-\sigma}+\alpha\frac{{Q^s_t}^{1-\xi}}{1-\xi},\]
where the superscript $s$ on $Q$ accounts for the fact that there is no partner to share the public good. Instead, the utility for  agent $s\in(f,m)$ in a couple is:
\[u^{C}(c^s_t,Q_t)=\frac{{c_t^s}^{1-\sigma}}{1-\sigma}+\alpha\frac{Q_t^{1-\xi}}{1-\xi}+\psi_t,\]
where the match quality evolves over time according to the following law of motion:
\[\psi_t=\psi_{t-1}+\epsilon_t,\text{ where }\epsilon_t \sim\mathcal{N}(0,\sigma^2_{\psi})\text{ and }\epsilon_1\sim\mathcal{N}(0,\sigma_{\psi,1}^{2}). \]
\subsection{Home Production}
In our model each agent in embodied with one unit of time. While singles and married men are assumed to supply inelastically one unit of market labor, females in a couple can be out of the labor force to devote their time producing the home good $Q$. The public good can be produced buying $d$ goods in the market. Following \cite{greenwood2016} we define the production function of home good as:
\begin{equation}\label{eq:pfunction}
Q_t=[d_t^\lambda+\kappa {(1-P^f_t)}^\lambda]^{\frac{1}{\lambda}}, \text{ where }0<\lambda<1.
\end{equation}
The parameter $\lambda$ captures the degree of  substitutability between female time and the use of durables in the production of the home good. This structure implies that when the relative price of durables decreases and when wages goes up, households will use less female time for its production, and hence female employment will increase. The variable  $P^f_t$ is a dummy variable that that takes value $1$ when the women is participating in the labor market.

\subsection{Wages}
The labor income for agents $s\in\{f,m\}$ depends on their age $t$ and on a permanent income component $z^s_t$:
\[\ln(w^s_t)=f^s(t)+z^s_t,\]
where $f^s()$ is a gender specific function that captures the evolution of productivity over age. The permanent income component  $z^s_t$ evolves over time as:
\begin{equation}\label{eq:pcomp}
z^s_t=z^s_{t-1}-(1-P_t^s) \mu+\zeta^s_{t}\text{, where }\zeta^s_{t}\sim^{iid}\mathcal{N}(0,\sigma^\zeta)\text{, and }\zeta^s_{1}=z^s_{1}.
\end{equation}
Note that $\mu$ is the loss in productivity that affects women\footnote{As we anticipated men always participate in the labor market, hence $P^m_t=1$ $\forall$ $t$.} that are not participating in the labor market. It can be be interpreted as a reduced form way of capturing both the missed opportunity to accumulate human capital while working as wells as the skill atrophy deriving from interruptions, a phenomenon described by \cite{adda2017}. Modeling the loss in productivity for not working is an important feature of our model as it creates an incentive to join the labor force for women that expect to divorce or separate soon. 
\subsection{Budget Constraints}
The budget constraint of single agents  $s\in\{f,m\}$ is:
\begin{equation}\label{eq:bcs}
a^s_{t+1}=R a^s_t+w^s_t-c^s_t-d^s_t, \text{ with }a^s_{t+1}\geq0,
\end{equation}
where $a^s$ are agent's savings, $w^s$ is the wage and $c^s$ and $d^s$ are consumption in the private good and the expenditure used to produce the public good.
The budget constraint for a couple instead is:
\begin{equation}\label{eq:bcm}
a_{t+1}=R a_t+w^m_t+P^f_t w^f_t-c^f_t-c^m_t-d_t, \text{ with }a_{t+1}\geq0,
\end{equation}
where $P^F_t$ is a dummy of female labor force participation.
When a couple divorces in $t$, we assume 
\[a^m_t+a^f_t=\delta a_t,\]
where $\delta$ is the fraction of total assets $a_t$ left\footnote{The assumption that divorce erodes a fracction of wealth is common to \cite{cubeddu2003}.} after divorce. Separation instead comes with no monetary costs\footnote{In reality the monetary cost of separation is likely to be positive. We assumed it to be zero because of the difficulties that arises when it comes to identify it. In fact, the gap in divorce and separation cost is what is actually needed to match the data.}.
An important feature of our model is the role of property rights upon divorce, which define how assets are divided. We distinguish three cases which define the share of assets $\chi$ going to the women:
\begin{enumerate}
\item \textit{Community Property}. Assets are split exactly in half: $\chi=0.5$
\item \textit{Equitable Distribution}. $\chi\sim\mathcal{U}(1/3,2/3)$.[WHAT I WISH WE HAD]
\item \textit{Title Based Regime}. $\chi$ is proportional to the productivity of the women compared to the one of the men, formally
\[\chi=\frac{\exp{z^f}}{\exp{z^f}+\exp{z^m}}.\]
\end{enumerate}
It is worth noting that we depart from \cite{voena2015} in the way title based regime is modeled: she assumes that assets are split following a couple decision, while for us the sharing rule depends only on $z^F$ and $z^M$. Since in our model relative productivities are the only source of disagreement,if we took the modeling assumption of \cite{voena2015} we would still get that the sharing rule is mainly determined by productivities\footnote{If we had individual specific love shocks, our reduced from modeling assumption would give different results instead.}. Moreover, making the sharing rule endogenous would give cohabitation a strong advantage with respect to a community property or equitable distribution marriage\footnote{This would happen because separation would have more degrees of freedom that divorce, where it is the court that decides the sharing rule.}, which makes hard to match the data.

\subsection{Problems of the Single}
We start by by describing the problem for a single agent $i\in\{f,m\}$ in $t$. The agent have to make consumption and saving decisions, and she is also determining the share of expenditures going to durables $d^i_t$. In $t+1$ she meets a potential partner $j$ of the opposite sex with probability $\lambda_{t+1}$ and she can decide to enter a partnership, which also depend on whether the potential partner will agree. If the two decides to marry, the variable $Ma_{t+1}$ will take value 1, while $CO_{t+1}=1$ if the couple decides to cohabit. Otherwise, $Ma_{t+1}$ and $CO_{t+1}$ will be equal to 0.  Note we assume singles to always participate in the labor market. The state variable of a single then is $\omega^i_t=\{a^i_t,z^i_t\}$, while her choices are represented by the vector $\mathbf{q}^i_t=\{a^i_{t+1},c^i_t,d^i_t\}$. We denote by $V_t^{i,S}(\Omega^i_t)$ the value function of agent $s$, which we define as
\begin{equation}\label{eq:v_single}
\begin{split}
V_t^{iS}(\omega^i_t)=&\max_{\mathbf{q}^i_t} u(c^i_t,Q^i_t)+\beta E_t \bigg\{(1-\lambda_t)V^{iS}_{t+1}(\omega^i_{t+1})+\\ & \quad\quad \lambda_t\big\{(1-Ma_{t+1})(1-CO_{t+1})	V^{i,S}_{t+1}(\omega_{t+1})+\\ &\quad\quad\quad\quad M_{t+1} V^{i,M}_{t+1}(\Omega_{t+1})+ CO_{t+1} V^{i,C}_{t+1}(\Omega_{t+1}) \big\}\bigg\},
\\ &\text{s.t. \eqref{eq:bcs} and \eqref{eq:pfunction}.} 
\end{split}
\end{equation}

\subsection{Household Planning Problem}
The problem of the couple depends both on the type of relationship, cohabitation or marriage, and on the divorce regime, which can be either \textit{mutual consent} or \textit{unilateral}. Separation is always unilateral. Under the unilateral regime, one partner can initiate the separation/divorce process alone, while under mutual consent the agreement of both is needed.
\subsubsection*{Mutual Consent Regime}
Under mutual consent marriage $\hat{M}$, couples solve a pareto problem where the pareto weight\footnote{Refer to \autoref{ssec:marriage_market} for a description about how pareto weight are initially set.} of the wife is $\theta^f$, while the one of the husband is $1-\theta^f$. The state vector is $\Omega^{\hat{M}}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^M_t=\{a_{t+1},d_{t},c^m_{t},c^f_{t},P^f_t,D_t\}$, where $D_t$ is a dummy variable that takes value $1$ is divorce happens and $0$ otherwise. The formal probelm that a couple married is $t$ solve is:
\begin{equation}\label{eq:v_mutual}
\begin{split}
V_t^{\hat{M}}(\Omega^{\hat{M}}_t)=&\max_{\mathbf{q}^M_t} (1-D_t)\{\theta^f u(c^f_t,Q_t)+(1-\theta^f)u(c^m_t,Q_t)+\psi_t+\beta E_t V^{\hat{M}}_{t+1}(\Omega^{\hat{M}}_{t+1})\}\\ &\quad\quad+D_t \{\theta^fV^{fS}_{t}(\omega^{f}_{t+1})+\theta^m  V^{mS}_{t}(\omega^{m}_{t}))\}
\\ &\text{if $D_t=0$:}\hspace{35pt}\text{s.t. \eqref{eq:bcm} and \eqref{eq:pfunction}
}
\\ &\text{if $D_t=1$:}\hspace{35pt}\text{s.t. \eqref{eq:bcs}, \eqref{eq:pfunction} for $i\in\{f,m\}$,}\\ &
\hspace{80pt}a_t^m+a_t^f=\delta a_t,	\\ &
\hspace{80pt}a_t^m,a_t^f\text{ determined according to property right regime,}	\\ &\hspace{80pt}
V_{t}^{fS}(\omega^F_{t})> W^{f\hat{M}}_{t}(\Omega^{\hat{M}}_{t}),\\ &\hspace{80pt}
V_{t+1}^{mS}(\omega^M_{t})> W^{m\hat{M}}_{t}(\Omega^{\hat{M}}_{t}).
\end{split}
\end{equation}
$W_{t}^{i\hat{M}}$ for $i\in\{F,M\}$ is defined as 
\begin{equation}
W_{t}^{i\hat{M}}=u(\tilde{c}_t^{i},\tilde{Q}_t^{i})+\psi_t+\beta E_t V_{t}^{i\hat{M}}(\Omega^{\hat{M}}_{t+1}),
\end{equation}
where $\mathbf{\tilde{q}}^{\hat{M}}_t=\{\tilde{a}_{t+1},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$ is the $\argmax$ of problem \eqref{eq:v_mutual} conditionally on having chosen $D_t=0$. $V_{t+1}^{i\hat{M}}(\Omega^{\hat{M}}_{t+1})$ instead can be obtained by the expectation of the sum of the time utilities that the agent get from $t+1$ to $T$, where the variables entering the utility function derive derive from the the pareto problem if the agent is in a relationship, otherwise they are the solution of \eqref{eq:v_single}.
\subsubsection*{Unilateral Divorce Regime}
Under the unilateral divorce regime, denoted by $\overline{M}$, couple solve a pareto problem where the pareto weight of the wife is $\theta^f_t$ and the one of the husband is $\theta^m_t$.The state vector is $\Omega^{\overline{M}}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^M_t$. The formal probelm that a couple married is $t$ solve is:
\begin{equation}\label{eq:v_uni}
\begin{split}
V_t^{\overline{M}}(\Omega^{\overline{M}}_t)=&\max_{\mathbf{q}^M_t} (1-D_t)\{\theta^f_{t+1} u(c^f_t,Q_t)+\theta^m_{t+1} u(c^m_t,Q_t)+\psi_t+\beta E_t V^{\overline{M}}_{t+1}(\Omega^{\overline{M}}_{t+1})\}\\ &\quad\quad+D_t \{\theta^f_{t}V^{fS}_{t}(\omega^{f}_{t+1})+\theta^m_{t} V^{mS}_{t}(\omega^{m}_{t}))\}
\\ &\text{if $D_t=0$:}\hspace{35pt}\text{s.t. \eqref{eq:bcm} and \eqref{eq:pfunction},}\\ &\hspace{80pt}
\theta^f_{t+1}=\theta^f_{t}+\mu^f_t,\\ &\hspace{80pt}
\theta^m_{t+1}=\theta^m_{t}+\mu^m_t,
\\ &\text{if $D_t=1$:}\hspace{35pt}\text{s.t. \eqref{eq:bcs}, \eqref{eq:pfunction} for $i\in\{f,m\}$,}\\ &
\hspace{80pt}a_t^m+a_t^f=\delta a_t,	\\ &
\hspace{80pt}a_t^m,a_t^f\text{ determined according to property right regime},
\end{split}
\end{equation}
where $\theta^f_{t+1}$ and $\theta^m_{t+1}$ adjust such that the following participation constraints are satisfied:
\begin{equation}\label{eq:p_cons_mar}
\begin{split}
&
W^{f\overline{M}}_{t}(\Omega^{\overline{M}}_{t})\geq V_{t}^{fS}(\omega^f_{t}),\\ &
W^{m\overline{M}}_{t}(\Omega^{\overline{M}}_{t})\geq V_{t}^{mS}(\omega^m_{t}). 
\end{split}
\end{equation}
Note that $\mu^i_t$ are the langrange multipliers associated with spouses' participation constraints.

$W_{t}^{i\overline{M}}$ for $i\in\{f,m\}$ is defined as 
\begin{equation}
W_{t}^{i\overline{M}}=u^M(\tilde{c}_t^{i},\tilde{Q}_t^{i})+\beta E_t V_{t+1}^{i\overline{M}}(\Omega^{\overline{M}}_{t+1}),
\end{equation}
\subsubsection*{Cohabitation}
Under cohabitation, denoted by $C$, couple solve a pareto problem where the pareto weight of the wife is $\theta^f_t$ and the one of the husband is $\theta^m_t$.The state vector is $\Omega^{C}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^C_t=\{a_{t+1},d_t,c^m_t,c^f_t,P^f_t,S_t,MA_t\}$. $S_t$ and ${MA}_t$ are dummy variable that take value $1$ is the couple respectively separate of marry and 0 otherwise. The formal probelm that a cohabiting couple is $t$ solve is:
\begin{equation}\label{eq:v_coh}
\begin{split}
V_t^{C}(\Omega^{C}_t)=&\max_{\mathbf{q}^C_t} (1-S_t)\{\theta^f_{t+1} u(c^f_t,Q_t)+\theta^m_{t+1} u(c^m_t,Q_t)+\psi_t+\beta E_t V^{C}_{t+1}(\Omega^{C}_{t+1})\}
\\ &\quad\quad+MA_t\{\theta^f_{t+1} u(c^f_t,Q_t)+\theta^m_{t+1} u(c^m_t,Q_t)+\psi_t+\beta E_t V^{M}_{t+1}(\Omega^{M}_{t+1})\}\\ &\quad\quad\quad\quad+S_t \{\theta^f_{t}V^{fS}_{t}(\omega^{f}_{t+1})+\theta^m_{t} V^{mS}_{t}(\omega^{m}_{t}))\}
\\ &\text{if $S_t=0$:}\hspace{35pt}\text{s.t. \eqref{eq:bcm} and \eqref{eq:pfunction},}\\ &\hspace{80pt}
\theta^f_{t+1}=\theta^f_{t}+\mu^f_t,\\ &\hspace{80pt}
\theta^m_{t+1}=\theta^m_{t}+\mu^m_t,
\\ &\text{if $S_t=1$:}\hspace{35pt}\text{s.t. \eqref{eq:bcs}, \eqref{eq:pfunction} for $i\in\{f,m\}$,}\\ &
\hspace{80pt}a_t^m+a_t^f= a_t,	\\ &
\hspace{80pt}a_t^m,a_t^f\text{ determined as in the title based regime},
\end{split}
\end{equation}
where $\theta^f_{t+1}$ and $\theta^m_{t+1}$ adjust such that the following participation constraints are satisfied:
\begin{equation}\label{eq:p_cons_coh}
\begin{split}
&
W^{fC}_{t}(\Omega^{C}_{t})\geq V_{t}^{fS}(\omega^f_{t}),\\ &
W^{mC}_{t}(\Omega^{C}_{t})\geq V_{t}^{mS}(\omega^m_{t}). 
\end{split}
\end{equation}
Note that $\mu^i_t$ are the langrange multipliers associated with spouses' participation constraints.

$W_{t}^{iC}$ for $i\in\{f,m\}$ is defined as 
\begin{equation}
W_{t}^{iC}=u(\tilde{c}_t^{i},\tilde{Q}_t^{i})+\psi_t+\beta E_t V_{t+1}^{iC}(\Omega^{C}_{t+1}),
\end{equation}
\subsection{Partnership Choice and the Mating Market}\label{ssec:marriage_market}
In each period $t$ singles have a probability $\lambda_t$ to meet a potential partner of their same age and with a productivity and wealth that depends on their productivity $z_t$ and assets $a_{t}$. Formally:
\begin{equation}\label{mma}
\ln(a^p_t)=\ln(a_{t})+\hat{\epsilon}\text{, where }\hat{\epsilon}\sim\mathcal{N}(0,\sigma^2_{\hat{p}}),
\end{equation}
\begin{equation}\label{mmz}
z^p_t=z_{t}+\tilde{\epsilon}\text{, where }\tilde{\epsilon}\sim\mathcal{N}(0,\sigma^2_{\tilde{p}}).
\end{equation}
These assumptions allow us to capture in a reduced from fashion that people are mating assortatively\footnote{In the life cycle models featured in \cite{ciscato2019}, \cite{shephard2019} and \cite{reynoso2019} assortative mating arise in marriage markets through the interactions of preferences, incentives, supply and demand forces.} both within marriage and cohabitation, as \cite{gemici2014} point out.
Once the meeting happened, agents have to decide whether to stay in a couple and eventually decide which partnership contract to choose. Note that for the rest of this section we will refer to marriage as $M$, but depending on property rights upon divorce we have$M \ \in\{\hat{M},\overline{M}\}$. We model their choices in three steps. 
\begin{enumerate}
\item The couple consider marriage $M$ (cohabitation $C$) as a viable alternative if the set of pareto weights\footnote{Without loss of generality, we impose $\theta^f+\theta^m=1$ at first meeting.} $\theta^f$ such that the couple prefers to marry (cohabit) is non-empty. Formally, for relationship $J\in\{M,C\}$ the set is
\begin{equation}\label{eq:set_couple}
\Theta^J_t(\Omega^J_t,\omega^f_t,\omega^m_t)=\big\{\theta_t: V_t^{fJ}(\Omega^J_t)\geq V_t^{fS}(\omega^f_t), V_t^{mJ}(\Omega^J_t)\geq V_t^{mS}(\omega^m_t)\big\}.
\end{equation}
\item If the set for marriage (cohabitation) is non-empty, the pareto weight for the potential marriage $\theta^{m,f}$ (cohabitation $\theta^{c,f}$) is set through symmetric Nash Bargaining.\footnote{The assumption that the initial pareto weight is pinned down by Nash Bargaining can be found in \cite{low2018}.} Formally\footnote{For consistency with the rest of the paper we define $\Omega^{J,-1}_t$ as the state vector for the couple excluding pareto weights.}, for $J\in\{M,C\}$ $\theta^{J,f}$ is set to :
\begin{equation}\label{nash_couple}
\theta^{J,f}= \argmax_{\theta\in\Theta^J_t} \Upsilon^J(\theta,\Omega^{J,-1}_t,\omega^f_t,\omega^m_t),
\end{equation}
where
\begin{equation}
\Upsilon^J(\theta,\Omega^{J,-1}_t,\omega^f_t,\omega^m_t)=\big[V_t^{fJ}(\Omega^{J,-1}_t)- V_t^{fS}(\omega^f_t)\big]\times\big[ V_t^{mJ}(\Omega^{J,-1}_t)- V_t^{mS}(\omega^m_t)\big].
\end{equation}
\item Four possible situation can arise:
\begin{itemize}
\item $\Theta^M_t=\O\text{ and }\Theta^C_t=\O \Rightarrow$ stay single.
\item $\Theta^M_t\neq\O\text{ and }\Theta^C_t=\O \Rightarrow$ marry.
\item $\Theta^M_t=\O\text{ and }\Theta^C_t\neq\O \Rightarrow$ cohabit.
\item $\Theta^M_t\neq\O\text{ and }\Theta^C_t\neq\O \Rightarrow$ marry if $ \Upsilon^M(\Omega^M_t,\omega^f_t,\omega^m_t)\geq\Upsilon^C(\Omega^C_t,\omega^f_t,\omega^m_t)$, otherwise cohabit.
\end{itemize}
This framework is a natural extension of the nash bargaining problem\footnote{Note that we could have chosen a different protocol for determining the choice between marriage and cohabitation. For example, we could have decided to impose a sequential structure to the problem, assuming that first agents compare cohabitation to singleness, obtaining the envelop of the two, where the pareto weight is set as above. Then, the agents make their final choice solving a pareto problem where the outside option is the outcome of the first step. We tried applying this methodology: results were indistinguishable from our main strategy.} to discrete choices [CITATION OF RELEVANT PAPER HERE].
\end{enumerate}
\section{Estimation}
\section{Counterfactual Experiments}
\section{Welfare Analysis}
\section{Conclusion}

\bibliographystyle{achicago}
\bibliography{mybibliography}

\appendix
\counterwithin{figure}{section}
\counterwithin{table}{section}
\section*{Appendix}
\section{Computational Appendix}
\cite{arnoud2019}+\cite{cartis2019}
\section{Estimation of Income Processes}

\end{document}

### 2020-02-10 eabstract.tex
Initial committ

% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

% This is a simple template for a LaTeX document using the "article" class.
% See "book", "report", "letter" for other types of document.
\documentclass[12pt]{article}
\usepackage[round, sort , authoryear]{natbib}

%required by R
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage[normalem]{ulem}
\usepackage[normalem]{ulem}
\usepackage[utf8]{inputenc}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{dcolumn}
\usepackage{mathtools}% http://ctan.org/pkg/mathtools

%For new line in table
\usepackage{array}
\usepackage{makecell}

\renewcommand\theadalign{bc}
\renewcommand\theadgape{\Gape[4pt]}
\renewcommand\cellgape{\Gape[4pt]}

%New environments
\newtheorem{lemma}{Lemma}
\newtheorem{assumption}{Assumption}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newenvironment{proof}[1][Proof]{\noindent \textbf{#1.} }{\  \rule{0.5em}{0.5em}}

%For tables position
\usepackage{float}
\restylefloat{table}

%%% PAGE DIMENSIONS
\usepackage[margin=2.5 cm]{geometry}
\usepackage{blindtext} % to change the page dimensions
\geometry{a4paper} % or letterpaper (US) or a5paper or....
% \geometry{margin=2in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information

\usepackage[utf8]{inputenc} 
\usepackage{graphicx} % support the \includegraphics command and options
\usepackage{epstopdf}
\usepackage[hang]{footmisc}
\usepackage{lipsum}
\usepackage{setspace}
% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{pgfplots}
\pgfplotsset{compat=1.13}
\usepackage{caption}
\usepackage{threeparttablex}
\usepackage{color, colortbl}
\definecolor{Gray}{gray}{0.9}
%%% PACKAGES
\usepackage{placeins}
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
% These packages are all incorporated in the memoir class to one degree or another...
\usepackage{amsmath}
\numberwithin{table}{section}
\usepackage{cases}
\usepackage{graphicx}
%
\usepackage{float}
\usepackage{authblk}
\usepackage{pgfplots}
\usepackage{pdfpages}
\linespread{1.5}
\setlength{\footnotemargin}{4mm}
\usepackage{amssymb} 
\usepackage{tabularx}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\addtolength{\footnotesep}{2mm} % change to 1mm

%For Counting Figures in the Appendix
\usepackage{chngcntr}

%For subtables
\usepackage{subcaption}

%For having the catption above tables
\usepackage{float}
\floatstyle{plaintop}
\restylefloat{table}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2960}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=BibTeX}
%TCIDATA{LastRevised=Monday, August 27, 2018 20:06:51}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\restylefloat{table}
\oddsidemargin  +0.18in
\evensidemargin +0.18in
\topmargin 40pt \textheight 8.1in \textwidth 6.5in
\linespread{1.5}\parskip .05in

%Nice Figure and table headers
\captionsetup[figure]{labelfont={sc},name={Figure},labelsep=period}
%\captionsetup[table]{labelfont={sc},name={Table},labelsep=period,justification=centering}

\usepackage{booktabs}   % for nice tables
\usepackage[colorlinks=false, linktocpage=true]{hyperref}
%\usepackage[flushmargin]{footmisc}
%\addtolength{\footnotesep}{3mm} % change to 1mm
\hypersetup{
	colorlinks,
	linkcolor={blue!50!black},
	citecolor={blue!50!black},
	urlcolor={blue!80!black}
}
% use for hypertext
\usepackage[colorinlistoftodos]{todonotes}
\setlength{\marginparwidth}{2cm}
\newenvironment{customlegend}[1][]{%
	\begingroup
	% inits/clears the lists (which might be populated from previous
	% axes):
	\pgfplots@init@cleared@structures
	\pgfplotsset{#1}%
}{%
	% draws the legend:
	\pgfplots@createlegend
	\endgroup
}%
%For Figures, below

\usepackage{tikz}
\usetikzlibrary{shapes}
\usepgflibrary{arrows} % LATEX and plain TEX and pure pgf
\usepgflibrary[arrows] % ConTEXt and pure pgf
\usetikzlibrary{arrows} % LATEX and plain TEX when using Tik Z
\usetikzlibrary[arrows] % ConTEXt when using Tik Z
\usepackage{hyperref}

%%% The "real" document content comes below...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\parskip3mm\parindent0cm

\title{Unilateral Divorce and the Rise of Informal Cohabitation}
\author{Fabio Blasutto$^1$ \quad Egor Kozlov$^2$}

\begin{document}
	% Bibliography style, important for biblatex functioning	
	\bibliographystyle{apa}

	\maketitle

	\footnotetext[1]{IRES, UCLouvain \& National Fund for Scientific Research (Belgium). Email: fabio.blasutto@uclouvain.be}
	\footnotetext[2]{Northwestern Univrsity. Email: egorkozlov2020@u.northwestern.edu.\\}

\textbf{Keywords}: Marriage, Cohabitation, Unilateral Divorce, Structural Estimation\\
\textbf{JEL-Code}: D83 - J12

\section{Extended Abstract}
Why do people marry? According to the seminal work of \citet{becker1981}, people marry both for non-economic (i.e. love and companionship) and economic reasons, among which the sharing of public goods, the division of labor to exploit comparative advantages, as in \cite{chiappori1997}, and risk pooling, as the literature on limited commitment, among which \cite{voena2015} and \cite{rigas2015}, points out.
All these reasons are able to explain why couples decide to live together, but they are silent about the choice between just living "under the same roof in a love relationship", henceforth cohabitation, and marrying. More in particular, it is unclear why does cohabitation started being a frequently chosen type of relationship only in the recent decades in most developed countries and whether economics has something to say about this.

In this paper we address these questions, exploiting the variation in US divorce laws\footnote{During this period most states moved from a mutual consent regime, where divorce could happen only if both spouse agreed on that, to a unilateral regime, where the process could be initiated by just one of the two parts.} that took place in the 1970s and 1980s to learn about how individuals choose between different types of partnership. We show that the drop in marriage rates observed after those reforms is driven by the fact that some newly formed couples chose to cohabit instead of marrying. Further, the drop in marriage rates is magnified by the fact that cohabiting couples that were formed after the reform experienced a lower hazard of separation. We argue that these changes are driven by an increased risk of divorce, which made cohabitation a relatively more appealing choice to couples that would have the highest probability of divorcing. Consistently, the observed lower hazard of separation after the reform is due to a composition effect: couples choosing to cohabit because of the reform have on average a better relationship quality than the whole pool of cohabitants. Our mechanism is consistent with the fact that the effects of the policy change are the strongest in states that has a community or equitable distribution property regime within marriage. In fact, in those states the richest one in the couple becomes more willing to cohabit than to marry after the reform: the increased risk of divorced makes her more likely that she looses most of her assets, while this would not happen within a cohabitation, where the property rights upon separation are title based.

As a first step of our research, we show that the introduction of unilateral divorce caused a behavioral response about how couples choose their relationship. Using data from the 1988 survey of the National Survey of Family Growth and from Wave 1 of the National Survey of Family and the Household, we construct a sample of first and second relationship experienced by primary respondents. Using a generalized difference in differences strategy which exploits the variation over time and across states in the adoption of unilateral divorce laws, we find that the relationship is between 5\% and 10\% more likely to be a cohabitation. The results are robust to the introduction of a state specific linear time trends and a range of socio-demographic characteristics. We also show that this effects is heterogeneous across property rights regimes within marriage, being insignificant in title based states and the strongest in community property states. Then, we explore how the introduction of unilateral divorce affected the risk of separation and marriage of couples that started cohabiting after the reform. Exploiting the same type of variation, we use  a multinomial probit model with month-relationship observations to analyze the duration of cohabitation spells, and we find that both the hazard of marriage and of cohabitation decreases between 10\% and 30\% because of the reform.\\
To understand the mechanisms that lead to these changes we build a dynamic model of intra household decision making with limited commitment, where cohabitation and marriage differs in the cost of separation and divorce as well as in law that govern the property rights upon divorce, which can vary for marriage while it is always title based for cohabitation. Moreover, separation can always be initiated unilaterally. Individuals are initially single, and with some probability in each period they meet a potential partner, which they can decide to marry or start cohabiting with. Agents take consumption and saving decisions, which depends on their idiosyncratic income shocks and on couple specific love shocks if they are in a relationship. The couple decides collectively how much to consume and save, as wells as the level of female labor supply. Women time can also be used to produce a public good within the household, but this affects negatively future female labor market prospects. Under a bilateral divorce regime the couple behaves as if it was perfectly commited, while in the unilateral scenario allocation rules might change if one part prefers to split with the current allocation, in line with \citet{voena2015}. In this model people choose to marry rather than to cohabit because the high cost of divorce allows for a stronger commitment, which strengthen risk sharing and leads to efficient female labor supply. Cohabitation instead is chosen when couple surplus is low, which imply a high risk of splitting: in this case cohabitation becomes more attractive since separation cost is lower than divorce cost. Since choosing cohabitation versus marriage crucially depends on the hazard that the couple breaks up, the introduction of unilateral divorce makes cohabitation relatively more attractive, which is consistent with the results of our empirical analysis. An additional reason for the shift towards cohabitation is that unilateral divorce decreases the commitment within marriage, which in turns makes the production of the public good within marriage suboptimal: if we interpret the public good as investment in the quality of children, this argument follows closely \citet{lafortune2019}. Despite being important, this mechanism is unlikely to be the main reason for partnership choice, as it predicts a larger shift to cohabitation in states with title based property rights within marriage, which contradicts empirical evidence. Instead, the increased risk of divorce type of mechanism predicts, consistently with the data, a larger shit to cohabitation in community property states. In fact, under the assumption of imperfectly transferable utility of our model, the introduction of unilateral divorce makes marriage less attractive to the richest member of the couple, which would become more likely to lose most of her wealth if she marry.\\
We then estimate the model using the method of indirect inference, using as targets the results from our empirical analysis, as well as the share of people married and cohabiting by age, the hazard of divorce and separation by couple duration. The estimated model is then used to perform a welfare analysis of the introduction of unilateral divorce laws, with a particular attention to the differential effect on men and women. Intuitively, welfare effects crucially depends of which is the part that first wants to initiate the divorce, since it would gain from being granted the right of starting the process unilaterally. The recent work of \citet{fernandez2017} shows that the aggregate welfare of women is decreasing because of the reform, while our model suggests the opposite, since in our model women are the most likely to initiate divorce. Intuitively, this happens because men, who are on average wealthier, are less likely to initiate divorce since they would lose a larger share of their assets upon divorce. For the same reason, men are also prefers cohabitation over marriage, but choosing the first type of relationship comes with the cost of allowing the women to access a larger share of couple resources.

\bibliography{mybibliography}
\end{document}

### 2020-02-11 draft_sub_con.tex
other adjustments

@@
 
-\title{Unilateral Divorce and the Rise of Informal Cohabitation	\thanks{The authors wishe to thank Matthias Doepke, Alessandra Voena and the Norhtwestern Macro group for their useful comments.
+\title{Unilateral Divorce and the Rise of Informal Cohabitation	\thanks{The authors wish to thank Matthias Doepke, Alessandra Voena and the Norhtwestern Macro group for their useful comments.
 Blasutto acknowledges financial support from the French speaking community of Belgium (ARC project 15/19-063 on "family transformations").}}
@@
 \begin{abstract}
-	Does unilateral divorce eroded the gains of marrying with respect to cohabiting?
+	Does unilateral divorce eroded the gains of marriage with respect to cohabitation?
 Exploiting the staggered introduction of unilateral divorce across U.S.
@@
 Why do people marry?
-According to the seminal work of \citet{becker1981}, people marry both for non-economic (i.e.
-love and companionship) and economic reasons, among which the sharing of public goods, the division of labor to exploit comparative advantages, as in \cite{chiappori1997}, and risk pooling, as \cite{voena2015} and \cite{rigas2015}, points out.
-All these reasons are able to explain why couples decide to live together, but they are silent about the choice between different types of partnership contracts, such as marriage and informal cohabitation.
-Economic incentives might an important determinant of this choice, but also because married and cohabiting couples display a different economics behavior.
+According to the seminal work of \citet{becker1981}, individuals marry both for non-economic (i.e.
+love and companionship) and economic reasons, among which the sharing of public goods, the division of labor to exploit comparative advantages, as in \cite{chiappori1997}, and risk pooling, as \cite{voena2015} and \cite{rigas2015}, point out.
+These reasons tell us why couples live together, while they are actually silent about the choice between different types of partnership contracts, such as marriage and informal cohabitation.
+Economic incentives might play a role in this choice since married and cohabiting couples display a different economics behavior.
 For example, female labor supply is higher for cohabiting couples, while married couples are wealthier, as \cite{gemici2014} and \cite{lafortune2019} respectively point out.
@@
 
-In this paper we address this question, focusing on the role of the unilateral divorce on the share of people that decides to cohabit.
-Our main contribution is to show the rate of cohabitation increased after the changes in US law and that the underlying mechanism is that the increased risk of divorce makes marriage less attractive, and as a consequence cohabitation becomes the preferred choice to couples that would have experienced the highest risk of divorce.
+In this paper we address this question, focusing on the role of unilateral divorce on the share of people that decides to cohabit.
+Our main contribution is to show that the rate of cohabitation increased after the changes in US law and that the underlying mechanism is that the increased risk of divorce makes marriage less attractive.
+As a consequence, cohabitation becomes the preferred choice to couples that would have experienced the highest risk of divorce.
 
-We first use data from the National Survey of Family and the Household and of the National Survey of Family growth to build a sample of first and second relationships\footnote{A relationship is defined as an interruption of the state of singleness, which can either be marriage or cohabitation.}.
-Then, exploiting the exogenous variation coming from the staggered introduction of unilateral divorce over time across US states, we show that cohabitation becomes 5\% more likely  to be chosen as result of the reform.
+We first use data from the National Survey of Family and the Household and of the National Survey of Family Growth to build a sample of first and second relationships\footnote{A relationship is defined as an interruption of the state of singleness, which can either be marriage or cohabitation.}.
+Then, exploiting the exogenous variation coming from the staggered introduction of unilateral divorce over time across US states, we show that cohabitation becomes around 5\% more likely  to be chosen as result of the reform.
 Interestingly,  the effect is heterogeneous across property rights regimes within marriage, being insignificant in title based states and the strongest in community property states.
-This result suggest that the idea that the surplus of marriage comes from commitment, enforced through the equal division of assets\footnote{This mechanism is highlighted by \cite{lafortune2019}, where the equal division of assets within marriage makes possible to efficiently invest in children even after the rise of unilateral divorce.}, cannot be the only reason why some people started cohabiting instead.
-Moreover, we analyze how unilateral divorced affected the length of newly formed cohabitation spells, showing that they last longer both because of a reduced risk of marriage and of separation.
-To understand the mechanisms that lead to these changes we build a dynamic model of intra household decision making, where cohabitation and marriage differs in the cost of separation and divorce as well as in law that govern the property rights upon divorce, which can vary for marriage while it is always title based for cohabitation.
-Moreover, separation can always be initiated unilaterally, as opposed to divorce, that would need the consensus of both partner under a mutual divorce regime.
+This result suggest that cannot be entirely to a deterioration in its commitment technology\footnote{This mechanism is highlighted by \cite{lafortune2019}, where the equal division of assets within marriage makes possible to efficiently invest in children even after the rise of unilateral divorce.}.
+Moreover, we analyze how unilateral divorced affected the length of newly formed cohabitation spells, showing that they last longer both because of a reduced risk of marriage and separation.
+To understand the mechanisms that lead to these changes we build a dynamic model of intra household decision making, where cohabitation and marriage differs in the cost of separation and divorce as well as in law governing property rights upon divorce, which can vary for marriage while it is always title based for cohabitation.
+Moreover, separation can be initiated unilaterally, as opposed to divorce, that would need the consensus of both partner under a mutual divorce regime.
 Individuals are initially single, and with some probability in each period they meet a potential partner, which they can decide to marry or start cohabiting with.
@@
 because of a low match quality draw) are more likely to choose cohabitation instead, since it implies a lower cost of separation while allowing to enjoy the gains from being in a couple.
-In the model, a switch from mutual consent to unilateral divorce causes couples to start cohabiting more, since the higher risk of divorce makes the expected value of divorce with respect to cohabitation lower.
+In the model, a switch from mutual consent to unilateral divorce causes couples to start cohabiting more, since the higher risk of divorce makes the expected value of marriage with respect to cohabitation lower.
 The effect would be particularly pronounced under community property division of assets upon divorce, since the richest part of the couple  would risk to lose most of its wealth.
-This mechanism implies that couples that would have previously married now start cohabiting: since those have on average a higher match quality than cohabiting couples, this selection drives down the risk of separation for cohabiting couples, as observed in the data.
+This mechanism implies that couples that would have married under the old regime, are cohabiting instead.
+Since those have a higher match quality than the average cohabiting couples, this selection drives down the risk of separation for cohabiting couples, as observed in the data.
 
-We then estimate the model using the simulated method of moments, using as targets an array of moments regarding the mating market and the differential female labor supply for cohabiting and married couples.
+We then estimate the model using the simulated method of moments to learn about the size of our main mechanism.
+We use as targets an array of moments regarding the mating market and the differential female labor supply for cohabiting and married couples.
 We find that the model is able to reproduce the results from our empirical evidence, thus validating our mechanism.
-We run a series of counterfactual experiments that shrinks the gender wage gap and the relative price of public versus public goods, which tell us the importance of this factors in explaining the rise in cohabitation over time.
+We then run a series of counterfactual experiments to gain intuition about forces that might have contributed to the rise of cohabitation in the last decades.
+[In particular, we quantify the role of shrinking the gender wage gap and technological progress in the household sector, which increases the opportunity cost of home production with female time and decreases the gains coming from labor market specialization.]
 
-This contribution of this paper is threefold.
-First, we are the first to document and explain how divorce laws affected the choice between marriage and cohabitation.
-This contribution adds to the existing literature that documented the effects of divorce laws on the rate of divorce (\cite{friedberg1998}, \cite{wolfers2006}), female labor supply (\cite{stevenson2008}, \cite{voena2015}), savings (\cite{voena2015}), assortative mating \cite{reynoso2019} and prostitution (\cite{ciacci2017}) among the others.
+The contribution of this paper is threefold.
+First, we document and explain how divorce laws affected the choice between marriage and cohabitation.
+This adds to the existing literature that documented the effects of divorce laws on the rate of divorce (\cite{friedberg1998}, \cite{wolfers2006}), female labor supply (\cite{stevenson2008}, \cite{voena2015}), savings (\cite{voena2015}), assortative mating \cite{reynoso2019} and prostitution (\cite{ciacci2017}) among the others.
 As in \cite{reynoso2019}, we study not only the effect of unilateral divorce on married couples, but also on sorting.
@@
 Second, our paper expands the literature on cohabitation, showing how the risk of splitting and its interaction with divorce laws is essential for understanding partnership choices.
-Different papers in the literature highlighted various gains of marriage with respect cohabitation: commitment (\cite{matouschek2008}), labor specialization within the couple \cite{gemici2014}, learning about match quality \cite{brien2006}, the interaction between commitment and learning \cite{blasutto2020} and  investment in children \cite{lafortune2019}.
-A paper close to ours is \cite{lafortune2019} who highlights the role of assets as a collateral that enforces commitment and hence allows for optimal investment in children.
+Different papers in the literature highlighted various gains of marriage with respect cohabitation: commitment (\cite{matouschek2008}), labor specialization within the couple \cite{gemici2014}, learning about match quality \cite{brien2006}, the interaction between the cost of divorce and learning \cite{blasutto2020} and  investment in children \cite{lafortune2019}.
+A paper close to ours is \cite{lafortune2019}, who highlights the role of assets as a collateral that enforces commitment and hence allows for optimal investment in children.
 In their model, a switch from mutual consent to unilateral divorce causes people without wealth to start cohabiting because they are left without a commitment technology.
-While we think that thei mechinsim is important, it cannot be the whole story since we observe that the switch toward cohabitation was the weakest in title based state, while their model would predict the opposite.
-In this paper we will quanity how much of the shift is due to this mechanism versus the role of the increased risk of divorce.
-We extend the work of \cite{gemici2014} and \cite{blasutto2020}, who develop collective dynamic models with limited commitment, introducing saving decisions, which are shown to play an important for commitment and hence for partnership choice, especially when interacted with propoerty rights upon divorce.\\
-Third, our paper speaks to the literature studying the canges of the family in recent decades.
+While we think that their mechanism is important, it cannot be the whole story since we observe that the switch toward cohabitation was the weakest in title based state, while their model would predict the opposite.
+In this paper we will quantify how much of the shift is due to this mechanism versus the role of the increased risk of divorce.
+We extend the work of \cite{gemici2014} and \cite{blasutto2020}, who develop collective dynamic models with limited commitment, introducing saving decisions, which are shown to play an important for commitment and hence for partnership choice, especially when interacted with property rights upon divorce.\\
+Third, our paper speaks to the literature studying changes of the family in the last decades.
 Recent works have investigated various channels through which the structure of families might have changed over time.
-\cite{albanesi2009} show the role of imporved maternal health on the rise of female labor force participation, \cite{greenwood2016} instead study the role that technology and the wage structure played in the rise in assortative mating, female labor force participation, the share of divorced and the increas in married people.
+\cite{albanesi2016} show the role of improved maternal health on the rise of female labor force participation, \cite{greenwood2016} instead study the role that technology and the wage structure played in the rise in assortative mating, female labor force participation, the share of divorced and the increase in married people.
 Our paper extends this work, studying the effect of wage structure, gender wage gap and changes in the home production technology on the rise of cohabitation.
@@
 
-\subsection{Problems of the Single}
+\subsection{Problem of the Singles}
 We start by by describing the problem for a single agent $i\in\{f,m\}$ in $t$.
-The agent have to make consumption and saving decisions, and she is also determining the share of expenditures going to durables $d^i_t$.
+The agent have to make consumption and saving decisions, and she is also determining expenditure$d^i_t$.
 In $t+1$ she meets a potential partner $j$ of the opposite sex with probability $\lambda_{t+1}$ and she can decide to enter a partnership, which also depend on whether the potential partner will agree.
-If the two decides to marry, the variable $Ma_{t+1}$ will take value 1, while $CO_{t+1}=1$ if the couple decides to cohabit.
-Otherwise, $Ma_{t+1}$ and $CO_{t+1}$ will be equal to 0.
+If the two decides to marry, the variable $MA_{t+1}$ will take value 1, while $CO_{t+1}=1$ if the couple decides to cohabit.
+Otherwise, $MA_{t+1}$ and $CO_{t+1}$ will be equal to 0.
 Note we assume singles to always participate in the labor market.
@@
 \subsubsection*{Mutual Consent Regime}
-Under mutual consent marriage $\hat{M}$, couples solve a pareto problem where the pareto weight\footnote{Refer to \autoref{ssec:marriage_market} for a description about how pareto weight are initially set.} of the wife is $\theta^f$, while the one of the husband is $1-\theta^f$.
+Under mutual consent marriage $\hat{M}$, couples solve a pareto problem where the weight\footnote{Refer to \autoref{ssec:marriage_market} for a description about how pareto weight are initially set.} of the wife is $\theta^f$, while the one of the husband is $1-\theta^f$.
 The state vector is $\Omega^{\hat{M}}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^M_t=\{a_{t+1},d_{t},c^m_{t},c^f_{t},P^f_t,D_t\}$, where $D_t$ is a dummy variable that takes value $1$ is divorce happens and $0$ otherwise.
@@
 \hspace{80pt}a_t^m,a_t^f\text{ determined according to property right regime,}	\\ &\hspace{80pt}
-V_{t}^{fS}(\omega^F_{t})> W^{f\hat{M}}_{t}(\Omega^{\hat{M}}_{t}),\\ &\hspace{80pt}
-V_{t+1}^{mS}(\omega^M_{t})> W^{m\hat{M}}_{t}(\Omega^{\hat{M}}_{t}).
+V_{t}^{fS}(\omega^f_{t})> W^{f\hat{M}}_{t}(\Omega^{\hat{M}}_{t}),\\ &\hspace{80pt}
+V_{t}^{mS}(\omega^m_{t})> W^{m\hat{M}}_{t}(\Omega^{\hat{M}}_{t}).
 \end{split}
@@
 \begin{equation}
-W_{t}^{i\hat{M}}=u(\tilde{c}_t^{i},\tilde{Q}_t^{i})+\psi_t+\beta E_t V_{t}^{i\hat{M}}(\Omega^{\hat{M}}_{t+1}),
+W_{t}^{i\hat{M}}=u(\tilde{c}_t^{i},\tilde{Q}_t)+\psi_t+\beta E_t V_{t}^{i\hat{M}}(\Omega^{\hat{M}}_{t+1}),
 \end{equation}
@@
 $V_{t+1}^{i\hat{M}}(\Omega^{\hat{M}}_{t+1})$ instead can be obtained by the expectation of the sum of the time utilities that the agent get from $t+1$ to $T$, where the variables entering the utility function derive derive from the the pareto problem if the agent is in a relationship, otherwise they are the solution of \eqref{eq:v_single}.
+Under mutual consent regime the pareto weight is never rebargained, which makes risk sharing efficient.
+It also makes harder a divorce to happen, since the member that after a shock is relatively worse off can exercise her veto power to avoid a divorce: this feature makes labor specialization easier.
 \subsubsection*{Unilateral Divorce Regime}
-Under the unilateral divorce regime, denoted by $\overline{M}$, couple solve a pareto problem where the pareto weight of the wife is $\theta^f_t$ and the one of the husband is $\theta^m_t$.The state vector is $\Omega^{\overline{M}}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^M_t$.
+Under the unilateral divorce regime, denoted by $\overline{M}$, couples solve a pareto problem where the weight of the wife is $\theta^f_t$ and the one of the husband is $\theta^m_t$.
+Note that, in opposition to the mutual consent regime, now pareto weights are allowed to vary over time.
+This happes whenever a member of the couple is better off divorcing: the other member will try to convinve her not to split offering her a larger share of resources.
+The state vector of this proble is $\Omega^{\overline{M}}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^M_t$.
 The formal probelm that a couple married is $t$ solve is:
@@
 Note that $\mu^i_t$ are the langrange multipliers associated with spouses' participation constraints.
-
-$W_{t}^{i\overline{M}}$ for $i\in\{f,m\}$ is defined as 
+Similarly to mutual consent regime, $W_{t}^{i\overline{M}}$ for $i\in\{f,m\}$ is defined as 
 \begin{equation}
-W_{t}^{i\overline{M}}=u^M(\tilde{c}_t^{i},\tilde{Q}_t^{i})+\beta E_t V_{t+1}^{i\overline{M}}(\Omega^{\overline{M}}_{t+1}),
+W_{t}^{i\overline{M}}=u(\tilde{c}_t^{i},\tilde{Q}_t)+\psi+\beta E_t V_{t+1}^{i\overline{M}}(\Omega^{\overline{M}}_{t+1}),
 \end{equation}
+where
+$\mathbf{\tilde{q}}^{\overline{M}}_t=\{\tilde{a}_{t+1},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$ is the $\argmax$ of problem \eqref{eq:v_mutual} conditionally on having chosen $D_t=0$.
+$V_{t+1}^{i\hat{M}}(\Omega^{\overline{M}}_{t+1})$ instead can be obtained by the expectation of the sum of the time utilities that the agent get from $t+1$ to $T$, where the variables entering the utility function derive derive from the the pareto problem if the agent is in a relationship, otherwise they are the solution of \eqref{eq:v_single}.
+Under the unilaral divorce regime pareto weights varies every time one participation constraint is binding, which makes risk sharing worse than in the mutual divorce regime.
+Labor market specialisation is also less functioning, since the higher risk of divorce makes women willing to insure against this event through labor market participation.
+Property rights upon divorce plays a significative role when splitting is unilateral: for example under community propery the least wealthy member can bargain a higher share of resources since the threat of divorce is real.
+This could not happen under a title based regime.
 \subsubsection*{Cohabitation}
-Under cohabitation, denoted by $C$, couple solve a pareto problem where the pareto weight of the wife is $\theta^f_t$ and the one of the husband is $\theta^m_t$.The state vector is $\Omega^{C}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^C_t=\{a_{t+1},d_t,c^m_t,c^f_t,P^f_t,S_t,MA_t\}$.
-$S_t$ and ${MA}_t$ are dummy variable that take value $1$ is the couple respectively separate of marry and 0 otherwise.
+Cohabiting couples, denoted by $C$, solve a pareto problem where the weight of the wife is $\theta^f_t$ and the one of the husband is $\theta^m_t$.The state vector is $\Omega^{C}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^C_t=\{a_{t+1},d_t,c^m_t,c^f_t,P^f_t,S_t,MA_t\}$.
+$S_t$ and ${MA}_t$ are dummy variable that take value $1$ is the couple respectively separate of marry\footnote{We denote marriage by $M$, which might be fall under unilateral divorce regime $\overline{M}$ or mutual consent $\hat{M}$.} and 0 otherwise.
 The formal probelm that a cohabiting couple is $t$ solve is:
@@
 Note that $\mu^i_t$ are the langrange multipliers associated with spouses' participation constraints.
-
 $W_{t}^{iC}$ for $i\in\{f,m\}$ is defined as 
@@
 \end{equation}
+where
+$\mathbf{\tilde{q}}^{C}_t=\{\tilde{a}_{t+1},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$ is the $\argmax$ of problem \eqref{eq:v_mutual} conditionally on having chosen $D_t=0$.
+$V_{t+1}^{iC}(\Omega^{C}_{t+1})$ instead can be obtained by the expectation of the sum of the time utilities that the agent get from $t+1$ to $T$, where the variables entering the utility function derive derive from the the pareto problem if the agent is in a relationship, otherwise they are the solution of \eqref{eq:v_single}.
 \subsection{Partnership Choice and the Mating Market}\label{ssec:marriage_market}
@@
 \begin{equation}\label{nash_couple}
-\theta^{J,f}= \argmax_{\theta\in\Theta^J_t} \Upsilon^J(\theta,\Omega^{J,-1}_t,\omega^f_t,\omega^m_t),
+\theta^{J,f}_t= \argmax_{\theta^f_t\in\Theta^J_t} \Upsilon^J(\theta^f_t,\Omega^{J,-1}_t,\omega^f_t,\omega^m_t),
 \end{equation}
@@
 \begin{equation}
-\Upsilon^J(\theta,\Omega^{J,-1}_t,\omega^f_t,\omega^m_t)=\big[V_t^{fJ}(\Omega^{J,-1}_t)- V_t^{fS}(\omega^f_t)\big]\times\big[ V_t^{mJ}(\Omega^{J,-1}_t)- V_t^{mS}(\omega^m_t)\big].
+\Upsilon^J(\theta^f_t,\Omega^{J,-1}_t,\omega^f_t,\omega^m_t)=\big[V_t^{fJ}(\Omega^{J,-1}_t)- V_t^{fS}(\omega^f_t)\big]\times\big[ V_t^{mJ}(\Omega^{J,-1}_t)- V_t^{mS}(\omega^m_t)\big].
 \end{equation}

### 2020-02-11 draft_sub_con.tex
better first page

@@
 \section{Introduction}
-Why do people marry?
-According to the seminal work of \citet{becker1981}, individuals marry both for non-economic (i.e.
-love and companionship) and economic reasons, among which the sharing of public goods, the division of labor to exploit comparative advantages, as in \cite{chiappori1997}, and risk pooling, as \cite{voena2015} and \cite{rigas2015}, point out.
-These reasons tell us why couples live together, while they are actually silent about the choice between different types of partnership contracts, such as marriage and informal cohabitation.
-Economic incentives might play a role in this choice since married and cohabiting couples display a different economics behavior.
-For example, female labor supply is higher for cohabiting couples, while married couples are wealthier, as \cite{gemici2014} and \cite{lafortune2019} respectively point out.
-Moreover, cohabitation display a much higher separation rate than marriages, which might be a cause of the high share of single mothers living in the US nowadays, which is the single strongest predictor for upward mobility\footnote{While the share of single mothers is the strongest predictor of differences in upward mobility across counties on top of segregation, residential segregation, income inequality, social capital, school quality, and racial shares, \cite{chetty2018} points out that half of this effect is due to self selection.} according to \cite{chetty2018}.
-A striking fact about cohabitation is its fast rise in the recent decades: according to \cite{manning2013} the share of women that ever cohabited moved from 33\% in 1987 to 60\% in 2010.
-Why did this happen?
+Cohabitation is on the rise: according to \cite{manning2013}, the share of women that ever cohabited moved from 33\% in 1987 to 60\% in 2010. Why did this happen?
+Since the seminal work of Becker (\citet{becker1981}), economists studied the incentives behind the decision to marry, among which the sharing of public goods, the division of labor to exploit comparative advantages (\cite{chiappori1997}), and risk sharing (\cite{voena2015} and \cite{rigas2015}).
+These reasons tell us why couples live together, while they are actually silent about the choice between marriage and informal cohabitation, two partnership contracts subject to different rules.
+While the literature often simplifies, avoiding the distinction between these two, they display a different labor supply, wealth accumulation and educational composition.
+It is not surprising that households, the smallest economic unit, can behave differently when the contract ruling them is different, but this can be the key to understand important economic phenomena.
+For example, cohabitation display a much higher separation rate than marriages, which might be a cause of the high share of single mothers living in the US nowadays, which is the single strongest predictor for upward mobility\footnote{While the share of single mothers is the strongest predictor of differences in upward mobility across counties on top of segregation, residential segregation, income inequality, social capital, school quality, and racial shares, \cite{chetty2018} points out that half of this effect is due to self selection.} according to \cite{chetty2018}.
+If we want to understand the behavior of cohabiting households, we first need to understand their formation and why they are growing in number.
 
-In this paper we address this question, focusing on the role of unilateral divorce on the share of people that decides to cohabit.
+In this paper we address the question of the rise of cohabitation, focusing on the role of unilateral divorce on the share of people that decides to cohabit.
 Our main contribution is to show that the rate of cohabitation increased after the changes in US law and that the underlying mechanism is that the increased risk of divorce makes marriage less attractive.

### 2020-02-11 draft_sub_con.tex
actual new first page

@@
 For example, cohabitation display a much higher separation rate than marriages, which might be a cause of the high share of single mothers living in the US nowadays, which is the single strongest predictor for upward mobility\footnote{While the share of single mothers is the strongest predictor of differences in upward mobility across counties on top of segregation, residential segregation, income inequality, social capital, school quality, and racial shares, \cite{chetty2018} points out that half of this effect is due to self selection.} according to \cite{chetty2018}.
-If we want to understand the behavior of cohabiting households, we first need to understand their formation and why they are growing in number.
+If we want to understand the behavior of cohabiting households and the implication of it, we first need to understand their formation and why they are growing in number.
 

### 2020-02-12 draft_sub_con.tex
stop tracking stuff
sample description done

@@
 
-\title{Unilateral Divorce and the Rise of Informal Cohabitation	\thanks{The authors wish to thank Matthias Doepke, Alessandra Voena and the Norhtwestern Macro group for their useful comments.
+\title{Unilateral Divorce and the Rise of Informal Cohabitation\thanks{The authors wish to thank Matthias Doepke, Alessandra Voena and the Norhtwestern Macro group for their useful comments.
 Blasutto acknowledges financial support from the French speaking community of Belgium (ARC project 15/19-063 on "family transformations").}}
@@
 \begin{abstract}
-	Does unilateral divorce eroded the gains of marriage with respect to cohabitation?
+	Does unilateral divorce eroded the gains of marriage with respect to informal cohabitation?
 Exploiting the staggered introduction of unilateral divorce across U.S.
-states, we show that newly formed relationships after the reform are more likely to be cohabitations instead of marriages, and that cohabitation spells last longer.
-To understand the mechanisms underlying the law changes, we build and estimate a structural life cycle model with partnership choice, where the gains from marriage with respect to cohabitation comes from a better cooperation within the household, enforced through a costly divorce, which acts as a commitment technology.
-Unilateral divorces increases the risk of separation, making cohabitation preferred to couples that would have had the highest risk of divorce.
-Since the couples switching relationship are on average better matched than the average cohabitants, the average length of cohabitations increases.
+states, we show that after the reform newly formed relationships are more likely to be cohabitations instead of marriages, and that cohabitation spells last longer.
+To understand the mechanisms underlying the law changes, we build and estimate a structural life cycle model with partnership choice, where the gains from marriage with respect to cohabitation come from a better cooperation within the household, enforced through a costly divorce, which acts as a commitment technology.
+In the model the reform increase the risk of divorce, making cohabitation preferred to couples that would have had the highest risk of divorce.
+Since the couples switching relationship are on average better matched than the average cohabitants, the length of cohabitations increases.
 \end{abstract}
@@
 Cohabitation is on the rise: according to \cite{manning2013}, the share of women that ever cohabited moved from 33\% in 1987 to 60\% in 2010. Why did this happen?
-Since the seminal work of Becker (\citet{becker1981}), economists studied the incentives behind the decision to marry, among which the sharing of public goods, the division of labor to exploit comparative advantages (\cite{chiappori1997}), and risk sharing (\cite{voena2015} and \cite{rigas2015}).
+Since the seminal work of Becker (\citealp{becker1981}), economists studied the incentives behind the decision to marry, among which the sharing of public goods, the division of labor to exploit comparative advantages (\citealp{chiappori1997}), and risk sharing (\citealp{voena2015} and \citealp{rigas2015}).
 These reasons tell us why couples live together, while they are actually silent about the choice between marriage and informal cohabitation, two partnership contracts subject to different rules.
@@
 In this paper we address the question of the rise of cohabitation, focusing on the role of unilateral divorce on the share of people that decides to cohabit.
-Our main contribution is to show that the rate of cohabitation increased after the changes in US law and that the underlying mechanism is that the increased risk of divorce makes marriage less attractive.
+Our main contribution is to show that the rate of cohabitation increased after the changes in the US law and that the underlying mechanism is that the increased risk of divorce makes marriage less attractive.
 As a consequence, cohabitation becomes the preferred choice to couples that would have experienced the highest risk of divorce.
+As a consequence, the average match quality of cohabiting couples increase, which increases the length of cohabitation spells.
 
 We first use data from the National Survey of Family and the Household and of the National Survey of Family Growth to build a sample of first and second relationships\footnote{A relationship is defined as an interruption of the state of singleness, which can either be marriage or cohabitation.}.
-Then, exploiting the exogenous variation coming from the staggered introduction of unilateral divorce over time across US states, we show that cohabitation becomes around 5\% more likely  to be chosen as result of the reform.
-Interestingly,  the effect is heterogeneous across property rights regimes within marriage, being insignificant in title based states and the strongest in community property states.
-This result suggest that cannot be entirely to a deterioration in its commitment technology\footnote{This mechanism is highlighted by \cite{lafortune2019}, where the equal division of assets within marriage makes possible to efficiently invest in children even after the rise of unilateral divorce.}.
-Moreover, we analyze how unilateral divorced affected the length of newly formed cohabitation spells, showing that they last longer both because of a reduced risk of marriage and separation.
-To understand the mechanisms that lead to these changes we build a dynamic model of intra household decision making, where cohabitation and marriage differs in the cost of separation and divorce as well as in law governing property rights upon divorce, which can vary for marriage while it is always title based for cohabitation.
+Then, exploiting the exogenous variation coming from the staggered introduction of unilateral divorce over time across US states, we show that cohabitation becomes around 5\% more likely  to be chosen compared to the pre-reform period.
+Interestingly,  the effect is heterogeneous on how property is divided upon divorce, being strongest in states where each spouse gets half of the wealth.
+This suggest that the result cannot be entirely due to a deterioration of divorce as a commitment technology\footnote{This mechanism is highlighted by \cite{lafortune2019}, where the equal division of assets within marriage makes possible to efficiently invest in children even after the rise of unilateral divorce.}, since the egalitarian property division rule can act as a substitute of the mutual consent regime.
+Moreover, we analyze how unilateral divorce affected the length of newly formed cohabitation spells, showing that they last longer both because of a reduced risk of marriage and separation.
+To understand the mechanisms that lead to these changes we build a dynamic model of intrahousehold decision making, where cohabitation and marriage differ in their splitting cost as well as in the way property is divided.
+While in the case of separation assets are always split as an agreement between spouses, in the case of divorce in some states it is the judge to decide.
 Moreover, separation can be initiated unilaterally, as opposed to divorce, that would need the consensus of both partner under a mutual divorce regime.
@@
 Couples make decisions about consumption, savings and female labor supply and they are subject to idiosyncratic income shocks.
-We model the decision making in the couple building on the literature of limited commitment (see for example \cite{kk1996},  \cite{ligon2002}, \cite{marcet2019} and \cite{pavoni2018}), which has been applied to dynamic collective models in the household by \cite{voena2015}, \cite{mazzocco2007}, \cite{foerster2019} and \cite{lise2018} among others.
 Couples also receive time varying match quality shocks, which might drive the couple to change their partnership status (i.e.
 from cohabitation to marriage) or to separate.
-When one member of the couple wishes to split, the bargaining powers are rebargained such that the binding member is made indifferent between separation and staying in a couple\footnote{For particularly bad draws in the match quality or productivity shock this might not be possible and hence the couple would split.}.
-The gains of marriage with respect to cohabitation derive from a better risk sharing and a more efficient specialization in the production of a public good\footnote{We assume that a public good is produced with money an female time.
-When females stop working for producing such good their potential productivity in the labor market decreases.}, which arise from a better commitment within the couple, enforced by the treat of a costly divorce, which acts as a commitment device.
+We model the decision making in the couple building on the literature of limited commitment (see for example \cite{kk1996},  \cite{ligon2002}, \cite{marcet2019} and \cite{pavoni2018}), which has been applied to dynamic collective models in the household by \cite{voena2015}, \cite{mazzocco2007}, \cite{foerster2019} and \cite{lise2018} among others.
+In this framework, when one member of the couple wishes to split, the couple rebargains such that the binding member is made indifferent between separation and staying in a couple\footnote{For particularly bad draws in the match quality or productivity shock this might not be possible and hence the couple would split.}.
+The gains of marriage with respect to cohabitation come from a better risk sharing and a more efficient specialization in the production of a public good\footnote{We assume that a public good is produced with money an female time.
+When females stop working for producing such good their potential productivity in the labor market decreases.}, which arise from a better commitment within the couple, enforced by the threat of a costly divorce, which acts as a commitment device.
 On the other hand, couples that would face a high risk of divorce if married (i.e.
@@
 We then run a series of counterfactual experiments to gain intuition about forces that might have contributed to the rise of cohabitation in the last decades.
-[In particular, we quantify the role of shrinking the gender wage gap and technological progress in the household sector, which increases the opportunity cost of home production with female time and decreases the gains coming from labor market specialization.]
+[In particular, we quantify the role of the wage structure and technological progress in the household sector, which increases the opportunity cost of home production with female time and decreases the gains coming from labor market specialization.]
 
@@
 First, we document and explain how divorce laws affected the choice between marriage and cohabitation.
-This adds to the existing literature that documented the effects of divorce laws on the rate of divorce (\cite{friedberg1998}, \cite{wolfers2006}), female labor supply (\cite{stevenson2008}, \cite{voena2015}), savings (\cite{voena2015}), assortative mating \cite{reynoso2019} and prostitution (\cite{ciacci2017}) among the others.
-As in \cite{reynoso2019}, we study not only the effect of unilateral divorce on married couples, but also on sorting.
+This adds to the existing literature that documented the effects of divorce laws on the rate of divorce (\citealp{friedberg1998}, \citealp{wolfers2006}), female labor supply (\citealp{stevenson2008}, \citealp{voena2015}), savings (\citealp{voena2015}), assortative mating (\citealp{reynoso2019}) and prostitution (\citealp{ciacci2017}) among the others.
+As in \cite{reynoso2019}, we study not only the effect of unilateral divorce on married couples, but also on partnership choice.
 While her focus is on who marries whom and concludes that unilateral divorced raised the share of singles, we abstract from modeling the mating market and we focus on partnership choice, which allow us to conclude that the rate of singleness declined less than previously thought, since some people that were believed not to be in a couple were actually cohabiting.
@@
 We extend her work both considering cohabitation as an alternative relationship and in analyzing the effects of these laws on sorting.
-Second, our paper expands the literature on cohabitation, showing how the risk of splitting and its interaction with divorce laws is essential for understanding partnership choices.
-Different papers in the literature highlighted various gains of marriage with respect cohabitation: commitment (\cite{matouschek2008}), labor specialization within the couple \cite{gemici2014}, learning about match quality \cite{brien2006}, the interaction between the cost of divorce and learning \cite{blasutto2020} and  investment in children \cite{lafortune2019}.
-A paper close to ours is \cite{lafortune2019}, who highlights the role of assets as a collateral that enforces commitment and hence allows for optimal investment in children.
+Second, our paper expands the literature on cohabitation, showing how the risk of divorce is essential for understanding partnership choices.
+Different papers in the literature highlighted various gains of marriage with respect cohabitation: commitment (\citealp{matouschek2008}), labor specialization within the couple \cite{gemici2014}, learning about match quality \cite{brien2006}, the interaction between the cost of divorce and learning \cite{blasutto2020} and  investment in children \cite{lafortune2019}.
+A paper close to ours is \cite{lafortune2019}, who highlight the role of assets as a collateral that enforces commitment and hence allows for optimal investment in children.
 In their model, a switch from mutual consent to unilateral divorce causes people without wealth to start cohabiting because they are left without a commitment technology.
 While we think that their mechanism is important, it cannot be the whole story since we observe that the switch toward cohabitation was the weakest in title based state, while their model would predict the opposite.
-In this paper we will quantify how much of the shift is due to this mechanism versus the role of the increased risk of divorce.
-We extend the work of \cite{gemici2014} and \cite{blasutto2020}, who develop collective dynamic models with limited commitment, introducing saving decisions, which are shown to play an important for commitment and hence for partnership choice, especially when interacted with property rights upon divorce.\\
-Third, our paper speaks to the literature studying changes of the family in the last decades.
+In this paper we will quantify how much of the shift is due to the erosion of marriage's collateral versus the role of the increased risk of divorce.
+We extend the work of \cite{gemici2014} and \cite{blasutto2020}, who develop collective dynamic models with limited commitment, introducing asset accumulation decisions, which are shown to play an important role for commitment and hence for partnership choice, especially when interacted with property rights upon divorce.\\
+Third, our paper speaks to the literature studying the changes of the family in the last decades.
 Recent works have investigated various channels through which the structure of families might have changed over time.
-\cite{albanesi2016} show the role of improved maternal health on the rise of female labor force participation, \cite{greenwood2016} instead study the role that technology and the wage structure played in the rise in assortative mating, female labor force participation, the share of divorced and the increase in married people.
+\cite{albanesi2016} show the role of improved maternal health on the rise of female labor force participation, \cite{greenwood2016} instead study the role that technology and the wage structure played in the rise in assortative mating, female labor force participation, the share of divorced and the increase in the share of singles.
 Our paper extends this work, studying the effect of wage structure, gender wage gap and changes in the home production technology on the rise of cohabitation.
@@
 Section 5 explain the procedure used for the estimation as well as the results.
-Section 6 report the results from a series of counter-factual experiments , while section 7 performs a welfare analysis.
+Section 6 report the results from a series of counter-factual experiments, while section 7 performs a welfare analysis.
 Section 8 draws the conclusions of the paper.
@@
 \subsection{The Dataset}
+We begin by describing our data.
+We use the the National Survey of Family and the Household (NSFH) wave I, and the National survey of Family Growth, 1988 wave.
+Both surveys were designed to study the causes and consequences of changes happening in families and households within the United States.
+This is reflected in detailed question regarding the retrospective family history of respondents, which includes information both about marriage and cohabitation.
+Moreover, primary respondents\footnote{One adult per household was randomly selected as the primary respondent, while in the NSFG respondents are all women of 15-44 years of age.} are asked a large set of questions regarding their socio economic background and the demographics of the household.
+While the NSFH I is the first of three longitudinal waves, NSFG is made of several repeated cross sectional samples.
+We decided not to use the other two other waves of the NSFH because in the second wave all currently cohabiting households were dropped from the survey, while the 1988 wave of NSFG is the only one with publicly available information about the residence of the respondents.
+A drawback of using this data\footnote{We do not have the choice of using other surveys for our analysis, since they either lack the State of residence variable, or they miss information about cohabitation history, or they do not cover people that were in a relationship age at the time the law changed.} is that we know the state of residence of the respondents only at age 16 for the NSFH and at birth for the NSFG.
+Since we also know whether people lived all their life in the same State we are able to perform our empirical analysis both on the universe and of the subsample of never movers.
+We will show that point estimates turn out to be statistically not distinguishable between the two samples.
+Further details regarding those two surveys can be found in \cite{bumpass2017} and \cite{mosher1996}.
+We use this dataset to build two samples, the one of \textit{first and second relationships} and the one of \textit{first cohabitations}, that are described below.
+\subsubsection*{First and Second Relationships Sample}
+We want to build a sample to analyze the type of relationship, which can be either marriage or cohabitation,\footnote{Dating is not considered, since we cannot observe this state.
+Hence, people dating will fall under the category of singles.} that respondents decided to have.
+The sample is made of first and second relationships.
+One first relationship is defined observing the first time (if ever) a certain person started cohabiting or married.
+This observation is associated to the date at which the relationship starts, to the characteristics of the respondent member of the formed couple, and with a \textit{type}, which can either marriage or cohabitation.
+Note the type of couples that cohabited before marriage is "cohabitation": the transition from cohabitation to marriage is analyzed using the sample of \textit{first cohabitations}.
+Second relationships  are defined in a similar fashion, but they include only respondents that ended the relationship with their first partner and started a new one with a different person.
+The way this sample is built implies that for some respondents we will have zero corresponding observations in this sample, while for other we will have other, and for others we will have two.
+We did not consider third or higher order relationships for our analysis since these individuals would be further away from the age at which we knew their state of residence.
+In [FIGURE********] we report the descriptive statistics of this sample.
+\subsubsection*{First Cohabitation Sample}
+This sample is built to analyze the decisions of cohabiting couples to separate or to marry.
+It is composed of the first non marital cohabitation experienced by respondents.
+This sample includes couples that cohabited before marriage, but it also includes cohabitations experienced by people with the following marital history: marriage without premarital cohabitation, divorce, cohabitation with a different person.
+Each observation of this sample is associated with a starting date, a possible ending date, and an outcome, which can be: still cohabiting, married or separated.
+In [FIGURE********] we report the descriptive statistics of this sample.
 \subsection{Empirical Evidence}
 \section{The Model}
-This section describes a dynamic life cycle structural model of partnership formation, savings, female labor supply and  home prduction.
-Couples act cooperatively subject to limited commitment, which means that rebargaining might happen in response of changes in the outside options, which are assumed to be divorce or separation.
+This section describes a dynamic life cycle structural model of partnership formation, savings, female labor supply and  home production.
+Couples act cooperatively subject to limited commitment, which means that rebargaining might happen in response to changes in the outside options, which are assumed to be divorce or separation.
 
 In the model time is discrete, and in each period men and women draw their productivities.
-If single, with some probability they meet a potential partner that comes with a couple specific match quality shock, and they decide whether to marry, cohabit or to stay single.
-If they are in a couples, they observe a realization of the match quality shock as well as of their productivity, and according to those they decide whether to stay together or to split.
+If single, with some probability they meet a potential partner: after drawing a match quality shock they decide whether to marry, cohabit or to stay single.
+Couples observe realization of the match quality shock as well as of their productivity, and according to those they decide whether to stay together or to split.
 Both singles and couples make consumption and savings decisions, using their money for private or public good expenditure.
@@
 where the match quality evolves over time according to the following law of motion:
-\[\psi_t=\psi_{t-1}+\epsilon_t,\text{ where }\epsilon_t \sim\mathcal{N}(0,\sigma^2_{\psi})\text{ and }\epsilon_1\sim\mathcal{N}(0,\sigma_{\psi,1}^{2}). \]
+\[\psi_t=\psi_{t-1}+\epsilon_t,\text{ where }\epsilon_t \sim\mathcal{N}(0,\sigma^2_{\psi}), \]
+while the love shock at first meeting is allowed to have a different variance $\sigma^2_{\psi,I}$
 \subsection{Home Production}
@@
 The labor income for agents $s\in\{f,m\}$ depends on their age $t$ and on a permanent income component $z^s_t$:
-\[\ln(w^s_t)=f^s(t)+z^s_t,\]
-where $f^s()$ is a gender specific function that captures the evolution of productivity over age. The permanent income component  $z^s_t$ evolves over time as:
+\[\ln(w^s_t)=f^s_t+z^s_t,\]
+where $f^s_t$ is a gender specific function that captures the evolution of productivity over age. The permanent income component  $z^s_t$ evolves over time as:
 \begin{equation}\label{eq:pcomp}
@@
 It is worth noting that we depart from \cite{voena2015} in the way title based regime is modeled: she assumes that assets are split following a couple decision, while for us the sharing rule depends only on $z^F$ and $z^M$.
-Since in our model relative productivities are the only source of disagreement,if we took the modeling assumption of \cite{voena2015} we would still get that the sharing rule is mainly determined by productivities\footnote{If we had individual specific love shocks, our reduced from modeling assumption would give different results instead.}.
-Moreover, making the sharing rule endogenous would give cohabitation a strong advantage with respect to a community property or equitable distribution marriage\footnote{This would happen because separation would have more degrees of freedom that divorce, where it is the court that decides the sharing rule.}, which makes hard to match the data.
+Since in our model relative productivities are the only source of disagreement.
+If we took the modeling assumption of \cite{voena2015} we would still get that the sharing rule is mainly determined by productivities\footnote{If we had individual specific love shocks, our reduced form modeling assumption would give different results instead.}.
+Moreover, if the sharing rule was endogenous, couples would always choose cohabitation over community property or equitable distribution marriage,\footnote{This would happen because separation would have more degrees of freedom that divorce, where it is the court that decides the sharing rule.} which would make matching the data impossible.
 
@@
 \subsubsection*{Mutual Consent Regime}
-Under mutual consent marriage $\hat{M}$, couples solve a pareto problem where the weight\footnote{Refer to \autoref{ssec:marriage_market} for a description about how pareto weight are initially set.} of the wife is $\theta^f$, while the one of the husband is $1-\theta^f$.
+Under mutual consent marriage $\hat{M}$, couples solve a Pareto problem where the weight\footnote{Refer to \autoref{ssec:marriage_market} for a description about how pareto weight are initially set.} of the wife is $\theta^f$, while the one of the husband is $1-\theta^f$.
 The state vector is $\Omega^{\hat{M}}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^M_t=\{a_{t+1},d_{t},c^m_{t},c^f_{t},P^f_t,D_t\}$, where $D_t$ is a dummy variable that takes value $1$ is divorce happens and $0$ otherwise.
-The formal probelm that a couple married is $t$ solve is:
+The formal problem that a couple married is $t$ solve is:
 \begin{equation}\label{eq:v_mutual}
 \begin{split}
-V_t^{\hat{M}}(\Omega^{\hat{M}}_t)=&\max_{\mathbf{q}^M_t} (1-D_t)\{\theta^f u(c^f_t,Q_t)+(1-\theta^f)u(c^m_t,Q_t)+\psi_t+\beta E_t V^{\hat{M}}_{t+1}(\Omega^{\hat{M}}_{t+1})\}\\ &\quad\quad+D_t \{\theta^fV^{fS}_{t}(\omega^{f}_{t+1})+\theta^m  V^{mS}_{t}(\omega^{m}_{t}))\}
+V_t^{\hat{M}}(\Omega^{\hat{M}}_t)=&\max_{\mathbf{q}^M_t} (1-D_t)\{\theta^f u(c^f_t,Q_t)+(1-\theta^f)u(c^m_t,Q_t)+\psi_t+\beta E_t V^{\hat{M}}_{t+1}(\Omega^{\hat{M}}_{t+1})\}\\ &\quad\quad+D_t \{\theta^fV^{fS}_{t}(\omega^{f}_{t+1})+(1-\theta^m)  V^{mS}_{t}(\omega^{m}_{t}))\}
 \\ &\text{if $D_t=0$:}\hspace{35pt}\text{s.t. \eqref{eq:bcm} and \eqref{eq:pfunction}
@@
 \end{equation}
-$W_{t}^{i\hat{M}}$ for $i\in\{F,M\}$ is defined as 
+The individual value of marriage conditional on $D_t=0$ is $W_{t}^{i\hat{M}}$ for $i\in\{F,M\}$, and it is defined as 
 \begin{equation}
@@
 \subsubsection*{Unilateral Divorce Regime}
-Under the unilateral divorce regime, denoted by $\overline{M}$, couples solve a pareto problem where the weight of the wife is $\theta^f_t$ and the one of the husband is $\theta^m_t$.
+Under the unilateral divorce regime, denoted by $\overline{M}$, couples solve a Pareto problem where the weight of the wife is $\theta^f_t$ and the one of the husband is $\theta^m_t$.
 Note that, in opposition to the mutual consent regime, now pareto weights are allowed to vary over time.
@@
 The state vector of this proble is $\Omega^{\overline{M}}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^M_t$.
-The formal probelm that a couple married is $t$ solve is:
+The formal problem that a couple married at $t$ solves is:
 \begin{equation}\label{eq:v_uni}
@@
 Note that $\mu^i_t$ are the langrange multipliers associated with spouses' participation constraints.
-Similarly to mutual consent regime, $W_{t}^{i\overline{M}}$ for $i\in\{f,m\}$ is defined as 
+Similarly to mutual consent regime, the individual value of marriage conditional on $D_t=0$ is  $W_{t}^{i\overline{M}}$ for $i\in\{f,m\}$, and it is defined as 
 \begin{equation}
@@
 $V_{t+1}^{i\hat{M}}(\Omega^{\overline{M}}_{t+1})$ instead can be obtained by the expectation of the sum of the time utilities that the agent get from $t+1$ to $T$, where the variables entering the utility function derive derive from the the pareto problem if the agent is in a relationship, otherwise they are the solution of \eqref{eq:v_single}.
+Note that we follow the literature assuming that the planner evaluates the welfare of the two members of the couple if a divorce happens with the current Pareto weights.
 Under the unilaral divorce regime pareto weights varies every time one participation constraint is binding, which makes risk sharing worse than in the mutual divorce regime.
@@
 $S_t$ and ${MA}_t$ are dummy variable that take value $1$ is the couple respectively separate of marry\footnote{We denote marriage by $M$, which might be fall under unilateral divorce regime $\overline{M}$ or mutual consent $\hat{M}$.} and 0 otherwise.
-The formal probelm that a cohabiting couple is $t$ solve is:
+The formal problem that a cohabiting couple at $t$ solves is:
 \begin{equation}\label{eq:v_coh}
@@
 Note that $\mu^i_t$ are the langrange multipliers associated with spouses' participation constraints.
-$W_{t}^{iC}$ for $i\in\{f,m\}$ is defined as 
+The individual value of cohabitation conditional on $S_t=$ is  $W_{t}^{iC}$ for $i\in\{f,m\}$, and it is defined as 
 \begin{equation}
@@
 where
-$\mathbf{\tilde{q}}^{C}_t=\{\tilde{a}_{t+1},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$ is the $\argmax$ of problem \eqref{eq:v_mutual} conditionally on having chosen $D_t=0$.
+$\mathbf{\tilde{q}}^{C}_t=\{\tilde{a}_{t+1},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$ is the $\argmax$ of problem \eqref{eq:v_mutual} conditionally on having chosen $S_t=0$.
 $V_{t+1}^{iC}(\Omega^{C}_{t+1})$ instead can be obtained by the expectation of the sum of the time utilities that the agent get from $t+1$ to $T$, where the variables entering the utility function derive derive from the the pareto problem if the agent is in a relationship, otherwise they are the solution of \eqref{eq:v_single}.
+Similarly to the unilateral divorce regime, we assume that the planner evaluates the welfare of the two members of the couple if a separation happens with the current Pareto weights.
+
+The cohabitation problem is similar to the one of marriage under the unilateral divorce regime, but two main features are different.
+First, the way assets are split within cohabitation might not be the same, and total assets are not eroded when separation happens.
+On the one hand this makes risk sharing and cooperation less functioning than in marriage with unilateral divorce, since the couple is left without a commitment-enhancing technology.
+On the other hand, assuming no cost of separation makes cohabitation more appealing to couples with a low surplus of being in a couple.
+Since for them splitting if very likely, they prefer the relationship that allow them to do it in a cheaper way.
+
 \subsection{Partnership Choice and the Mating Market}\label{ssec:marriage_market}
@@
 Once the meeting happened, agents have to decide whether to stay in a couple and eventually decide which partnership contract to choose.
-Note that for the rest of this section we will refer to marriage as $M$, but depending on property rights upon divorce we have$M \ \in\{\hat{M},\overline{M}\}$.
+Note that for the rest of this section we will refer to marriage as $M$, but depending on property rights upon divorce we have $M \ \in\{\hat{M},\overline{M}\}$.
 We model their choices in three steps.
 \begin{enumerate}
-\item The couple consider marriage $M$ (cohabitation $C$) as a viable alternative if the set of pareto weights\footnote{Without loss of generality, we impose $\theta^f+\theta^m=1$ at first meeting.} $\theta^f$ such that the couple prefers to marry (cohabit) is non-empty.
+\item The couple considers marriage $M$ (cohabitation $C$) as a viable alternative if the set of pareto weights\footnote{Without loss of generality, we impose $\theta^f+\theta^m=1$ at first meeting.} $\theta^f$ such that the couple prefers to marry (cohabit) is non-empty.
 Formally, for relationship $J\in\{M,C\}$ the set is
@@
 \item $\Theta^M_t=\O\text{ and }\Theta^C_t\neq\O \Rightarrow$ cohabit.
-\item $\Theta^M_t\neq\O\text{ and }\Theta^C_t\neq\O \Rightarrow$ marry if $ \Upsilon^M(\Omega^M_t,\omega^f_t,\omega^m_t)\geq\Upsilon^C(\Omega^C_t,\omega^f_t,\omega^m_t)$, otherwise cohabit.
+\item $\Theta^M_t\neq\O\text{ and }\Theta^C_t\neq\O \Rightarrow$ The couple chooses the partnership that gives the largest Nash product.
+Formally, if $ \Upsilon^M(\Omega^M_t,\omega^f_t,\omega^m_t)\geq\Upsilon^C(\Omega^C_t,\omega^f_t,\omega^m_t)$, otherwise cohabit.
 \end{itemize}

### 2020-02-14 draft_sub_con.tex
law review plus some estimation done

@@
 \renewcommand\cellgape{\Gape[4pt]}
+
+%Write a vecor
+\newcommand{\myvec}[1]{\ensuremath{\begin{pmatrix}#1\end{pmatrix}}}
 
@@
 
+%No Counting within section
+\DeclareCaptionLabelSeparator{none}{}
+\captionsetup{labelsep=none}
+\counterwithout{figure}{section}
+\counterwithout{table}{section}
+
+%Nice Figure and table headers
+\captionsetup[figure]{labelfont={sc},name={Figure},labelsep=period}
+\captionsetup[table]{labelfont={sc},name={Table},labelsep=period,justification=centering}
+
 %For subtables
@@
 %Nice Figure and table headers
-\captionsetup[figure]{labelfont={sc},name={Figure},labelsep=period}
-%\captionsetup[table]{labelfont={sc},name={Table},labelsep=period,justification=centering}
+\captionsetup[figure]{labelfont={sc},name={Figure},labelsep=none}
+\captionsetup[table]{labelfont={sc},name={Table},labelsep=none,justification=centering}
 
@@
 In the model the reform increase the risk of divorce, making cohabitation preferred to couples that would have had the highest risk of divorce.
-Since the couples switching relationship are on average better matched than the average cohabitants, the length of cohabitations increases.
+Since the couples switching relationship are on average better matched than the average cohabitants, the duration of cohabitations increases.
 \end{abstract}
@@
 As a consequence, cohabitation becomes the preferred choice to couples that would have experienced the highest risk of divorce.
-As a consequence, the average match quality of cohabiting couples increase, which increases the length of cohabitation spells.
+As a consequence, the average match quality of cohabiting couples increase, which increases the duration of cohabitation spells.
 
@@
 This suggest that the result cannot be entirely due to a deterioration of divorce as a commitment technology\footnote{This mechanism is highlighted by \cite{lafortune2019}, where the equal division of assets within marriage makes possible to efficiently invest in children even after the rise of unilateral divorce.}, since the egalitarian property division rule can act as a substitute of the mutual consent regime.
-Moreover, we analyze how unilateral divorce affected the length of newly formed cohabitation spells, showing that they last longer both because of a reduced risk of marriage and separation.
+Moreover, we analyze how unilateral divorce affected the duration of newly formed cohabitation spells, showing that they last longer both because of a reduced risk of marriage and separation.
 To understand the mechanisms that lead to these changes we build a dynamic model of intrahousehold decision making, where cohabitation and marriage differ in their splitting cost as well as in the way property is divided.
@@
 \section{US Divorce Laws: an Overview}
+Between late 1960s and early 1980s most U.S.
+states experienced fundamental changes in the divorce law, both regarding the right to initiate a divorce without the consent of the other spouse and about the laws that govern the division of assets upon divorce.
+
+Before the 1960s the vast majority of US states had a mutual consent divorce regime\footnote{All the states apart from New Mexico, Oklahoma and Alaska.}, where the agreement of both spouses was needed to obtain a divorce for mundane reasons (i.e.
+without misconduct by any spouse).
+Moreover, divorce was permitted for grounds showing guilt of misconduct\footnote{Examples of guilt or misconduct are adultery or abandonment.} by any of the two spouses: for those cases the agreement of the innocent party alone was enough for having a divorce granted.
+From the late 1960s and early 1980s most U.S.
+states\footnote{A list of the years at which unilateral divorce was introduced in different states can be found in table 1 of \cite{ciacci2017}.} switched to a unilateral divorce regime.
+Under this regime divorce can be filed by one spouse without the consent of the other.
+
+Another dimension along which divorce laws differs across states is the one about property division regimes. In the United States there are three types of those:
+\begin{enumerate}
+\item \textit{Community Property}.
+Under this regime the couple are jointly owning family wealth, both those obtained during marriage and before.
+This implies that when divorce occurs each spouse gets exactly half of the total family wealth.
+\item \textit{Equitable distribution}.
+Under this regime, it is the court that decides how to split family wealth between the two spouses.
+This decision is driven by the principle of equity, which is ambiguous: in some cases the wealth is divided exactly in half, while in others a larger share reserved to the party that contributed the most to its accumulation.
+\item \textit{Title Based Regime}. Under this regime wealth is split according to the title of ownership.	
+\end{enumerate}
+
+The comparison between marriage and cohabitation is worth a final remark.
+Separation can be initiated unilaterally and it falls under the title based property.
+Another importance difference is that while divorce requires the couple to undergo a legal process, which implies monetary and time costs, separation from cohabitation just requires one member of the couple to leave.
 \section{Data and Empirical Evidence}
-\subsection{The Dataset}
+\subsection{The Dataset}\label{dataset}
 We begin by describing our data.
@@
 We did not consider third or higher order relationships for our analysis since these individuals would be further away from the age at which we knew their state of residence.
-In [FIGURE********] we report the descriptive statistics of this sample.
+Finally, we consider only relationship that started when the respondent was 20 years old or older.
+In table \ref{table:sum_rel} we report the descriptive statistics of this sample.
+
+\begin{table}[!htbp]\centering
+	\caption{\\Descriptive Statistics, Cohabitation Sample}
+	\label{table:sum_rel}
+\input{sum_sing.tex}
+\end{table}
+\FloatBarrier
 \subsubsection*{First Cohabitation Sample}
@@
 Each observation of this sample is associated with a starting date, a possible ending date, and an outcome, which can be: still cohabiting, married or separated.
-In [FIGURE********] we report the descriptive statistics of this sample.
+In \ref{table:sum_coh} we report the descriptive statistics of this sample.
+
+\begin{table}[!htbp]\centering
+	\caption{\\Descriptive Statistics, Relationship Sample}
+	\label{table:sum_coh}
+	\input{sum_coh.tex}
+\end{table}
+\FloatBarrier
+
 \subsection{Empirical Evidence}
+Do unilateral divorce affects the partnership choice of couples?
+We exploit the timing\footnote{See table 1 in \cite{ciacci2017} for the timing of adoption of unilateral divorce.} in the adoption of unilateral divorce as a source of exogenous variation in the right to divorce.
+This strategy has already been used several times by the literature\footnote{Among the others, see \cite{wolfers2006}, \cite{stevenson2008}, \cite{voena2015}, \cite{reynoso2019} and \cite{ciacci2017}.} to study the non-neutrality of of the rights to divorce on various economic and demographic outcomes.
+According to \cite{gruber2004}, who reviews the legal literature about the topic, the introduction of unilateral divorce was not view as a tool of social policy, but rather a way to reduce the legal burden of divorce processes.
+This reasoning is consistent with the fact that this change was not initiated by the most liberal states: New York was the last state to introduce unilateral divorce in October 2010, almost 40 years later than Kentucky.
+Moreover, \cite{reynoso2019} shows that there is no geographic correlation in adoption.
+\subsubsection*{Relationship Choice}
+What is the effect of unilateral divorce on the partnerships that couples choose?
+To answer this question we estimate equation \ref{table:ols_rel_standard}, where $i$ are the newly formed couples, $t$ is the calendar time, and $s$ is the state:
+\begin{equation}\label{eq:ols_baseline}
+\text{married}_{i,t,s}=\beta_0+\beta_1*\text{Unilatearal}_{t,s}+\mathbf{\gamma'}\mathbf{X}_i+\delta_s+\nu_t+\epsilon_{i,t,s}.
+\end{equation}
+The dependent variable is a dummy take takes value $1$ if the couple $i$, started at time $t$ is state $s$ is a marriage, and 0 if it is cohabitation.
+The vector $\mathbf{X}_i$ instead includes a set of socio demographic controls, while $\delta_s$ are the state fixed effects and  $\nu_t$ are the time fixed effects.
+The variable $\text{Unilateral}_{t,s}$ instead is a dummy that takes value $1$ if unilateral divorce wave in place in state $s$ at time $t$: $\beta_1$ instead is the coefficient that is informative about the effect of unilateral divorce on partnership choice.
+The results of the estimation are reported in table \ref{table:ols_rel_standard} for different samples.
+Column (1) reports the results for the full sample described in section \ref{dataset}, while column (2) is restricted the observation for which we know that the person lived all its life in the reported states, which ensures that they did not migrate.
+Finally, columns (3) and (4) restrict the sample to respectively the NSFH and NSFG surveys only .
+%MARRUAGE TO DIVORCE
+
+	\begin{table}[htbp]\centering
+		\caption{\\OLS Regression. Observation: first and second relationships}
+		\label{table:ols_rel_standard}
+		\begin{threeparttable}[t]\centering
+			\input{wmar.tex}
+	\begin{tablenotes}[flushleft]
+		\footnotesize{\item \textsc{Notes}: standard errors are clustered at the state level.
+			Coefficients that are significantly different from zero are denoted by the following system: *10\%, **5\%  and ***1\%.}
+	\end{tablenotes}
+\end{threeparttable}
+\end{table}
+\FloatBarrier
+The results reported in table \ref{table:ols_rel_standard} suggest that the effect of unilateral divorced decreased the share of couples that are married by $-5\%/-6\%$.
+This results are robust to an alternative specification that includes state specific fixed effects, whose results are reported in  table \ref{table:wmarlin}, and to the use of a logistic regression, reported in table \ref{table:wmar_logit}.
+
+We then move on to better understand the heterogeneity hidden behind the effect of unilateral divorce.
+Since in some states assets are split in the same way within separation and divorce, which is the case of \textit{title based regime} states, in others this rule is different in others, which is the case of \textit{community property} and \textit{equitable distribution} states.
+Analyzing this heterogeneity is then interesting to understand how much the asset sharing rule is important in understanding relationship choices.
+We hence estimate equation
+
+\begin{equation}\label{eq:ols_by_prop}
+\begin{split}
+\text{married}_{i,t,s}=\beta_0+&\beta_1*\text{Unilatearal*No Title Based}_{t,s}\\&+\beta_2*\text{Unilatearal*Title Based}_{t,s}+\\&\quad\quad\beta_3*\text{Title Based}_{t,s}+\mathbf{\gamma'}\mathbf{X_i}+\delta_s+\nu_t+\epsilon_{i,t,s},
+\end{split}
+\end{equation}
+whose  indexes and controls are the same of equation \ref{eq:ols_by_prop}, with the difference that know we capture the interaction of unilateral divorce with asset division regimes interacting $\text{Unilateral}_{t,s}$ with  $\text{Title Based}_{t,s}$ and $\text{No Title Based}_{t,s}$, which indicates whether state $s$ at time $t$ had or not a title based regime.
+In table \ref{table:wmarc} the report the results of the estimation of equation \ref{eq:ols_by_prop}.
+Similarly to table \ref{table:ols_rel_standard}, column (1) reports the results for the full sample described in section \ref{dataset}, while column (2) is restricted the observation for which we know that the person lived all its life in the reported states, which ensures that they did not migrate.
+Finally, columns (3) and (4) restrict the sample to respectively the NSFH and NSFG surveys only.
+
+	\begin{table}[htbp]\centering
+		\caption{\\OLS Regression. Observation: first and second relationships}
+		\label{table:wmarc}
+		\begin{threeparttable}[t]\centering
+			\input{wmarc.tex}
+			\begin{tablenotes}[flushleft]
+				\footnotesize{\item \textsc{Notes}: standard errors are clustered at the state level.
+					Coefficients that are significantly different from zero are denoted by the following system: *10\%, **5\%  and ***1\%.}
+			\end{tablenotes}
+		\end{threeparttable}
+	\end{table}
+\FloatBarrier
+The results show that the effect of unilateral divorce on the likelihood that a couples chooses marriage over cohabitation is significant and around $-5\%/-6\%$ in non title based states, while it is non significant and much smaller in title based states.
+This results suggests that the fact of having a sharing rule decided by the law is not enough to replace the mutual consent regime as an alternative commitment technology.
+Instead, this results are consistent with the view that the richest partner start disliking marriage when divorce becomes unilateral, since she would risk to lose most of his wealth upon divorce.
+This was not happening in mutual consent regime, since she could have exercised her right to veto divorce.
+In title based state this threat for the richest member of the couple does not exist, hence marriage surplus with respect to cohabitation does not vary significantly.
+Table \ref{table:wmarlinc} shows that results are robust to the inclusion of state specific linear trends.
+\subsubsection*{Cohabitation Duration}
+What is the effect of unilateral divorce on cohabitation duration?
+How much of the change is due to a variation in the risk of separation versus the risk of marriage?
+In order to answer these question, we construct a model of cohabitation duration with multiple risks, namely separation and marriage.
+Our model builds on \cite{jenkins1995}, who shows how that a logistic regression can be used for studying duration of events, expanding the the dataset of relevant spells to make unit of time per spells observations, where the dependent variable takes value $1$ whenever the event of interest occurs.
+The natural extension of this model to a multiple risk environment would be to use a multinomial logit.
+However, the problem with this model is that it assumes independence of irrelevant alternatives, which is particularly unappealing for our problem, since it would imply that the relative probability of choosing marriage over separation stays the same after cohabitation is no longer an option.
+Hence, we chose to model cohabitation duration with a multinomial probit, where the independence of irrelevant alternatives does not need to be satisfied.
+We then study the choice of cohabiting couple $i$, at calendar time $t$ in state $s$ and at duration $d$ estimating the following model:
+\begin{equation}\label{eq:probit_1}
+\begin{split}
+&Y_{i,s,t,d}^\text{Marry}=\beta^\text{Marry}*\text{Unilatearal}_{s,t}+\mathbf{\gamma^{\text{Marry'}}}\mathbf{X_i}+\alpha_d+\delta_s+\nu_t+\epsilon^{\text{Marry}}_{i,s,t,d},\\&
+Y_{i,s,t,d}^\text{Cohabit}=\beta^\text{Cohabit}*\text{Unilatearal}_{s,t}+\mathbf{\gamma^{\text{Cohabit'}}}\mathbf{X_i}+\alpha_d+\delta_s+\nu_t+\epsilon^{\text{Cohabit}}_{i,s,t,d},\\&
+Y_{i,s,t,d}^\text{Separate}=\beta^\text{Separate}*\text{Unilatearal}_{s,t}+\mathbf{\gamma^{\text{Separate'}}}\mathbf{X_i}+\alpha_d+\delta_s+\nu_t+\epsilon^{\text{Separate}}_{i,s,t,d},
+\end{split}
+\end{equation}
+where
+\begin{equation}\label{eq:probit_error}
+\myvec{\epsilon_{i,s,t,d}^{\text{Marry}}\\\epsilon_{i,s,t,d}^{\text{Cohabit}}\\\epsilon_{i,s,t,d}^{\text{Separate}}}\sim\mathcal{N}(\mathbf{0},\mathbf{\Sigma}),
+\end{equation}
+and
+\begin{equation}\label{eq:probit_outcome}
+Y_{i,s,t,d}=
+\begin{cases}  	
+\text{Marry}\hspace{30pt}       \text{if}\hspace{10pt}Y_{i,s,t,d}^\text{Marry}>Y_{i,s,t,d}^\text{Cohabit}\hspace{5pt}\text{and}\hspace{5pt}\hspace{5pt}Y_{i,s,t,d}^\text{Marry}>Y_{i,s,t,d}^\text{Separate}\\
+\text{Cohabit}\hspace{23pt}   \text{if}\hspace{10pt}Y_{i,s,t,d}^\text{Cohabit}>Y_{i,s,t,d}^\text{Marry}\hspace{5pt}\text{and}\hspace{5pt}\hspace{5pt}Y_{i,s,t,d}^\text{Cohabit}>Y_{i,s,t,d}^\text{Separate}\\
+\text{Separate}\hspace{22pt}     \text{otherwise.}
+\end{cases}
+\end{equation}
+The model described above is estimated with bayesian techniques via Markov chain Monte Carlo following the procedure of \cite{imai2005a}, which is implemented using the standard options provided by the $R$ package \textit{MNP} developed by \cite{imai2005b}.
+The estimation results are reported in table \ref{table:mpc}, where we report results from the full sample in column (1), from the resident only sample in column (2) and from the observations coming from the NSFH and NSFG surveys alone respectively in column (3) and (4).
+Note that to gain intuition about the size of the results, in  table \ref{table:mpc} we computed the average risk of the event of interest relatively of continue cohabiting.The results shows that unilateral divorce caused an increase in the duration of cohabitation, which comes from both a reduced hazard of marriage and of separation.
+While the result about the risk of marriage is not unexpected in light of the estimation results described above, the reduced risk of separation brings new insights about the possible mechanisms underlying partnership choices.
+In fact, the decrease in the risk of separation is consistent with a selection effect: some cohabiting couples would have married if mutual consent divorce was still in place.
+If the match quality of cohabitations is lower than the one of marriages\footnote{This seems plausible in light of the fact that the risk of divorce is much lower than the risk of separation.}, unilateral divorce drives down the risk of separation because of a selection effect.
+%Cohabitation Length4
+
+	\begin{table}[htbp]\centering
+		\caption{\\Multinomial Probit. Observation: person-month of cohabitation}
+		\label{table:mpc}
+		\begin{threeparttable}[t]\centering
+			\input{mpc.tex}
+			\begin{tablenotes}[flushleft]
+				\footnotesize{\item \textsc{Notes}: standard errors are obtained through the distribution of parameter obtained using the markov chain monte carlo estimation descibed by \cite{imai2005a}.
+					Coefficients that are significantly different from zero are denoted by the following system: *10\%, **5\%  and ***1\%.}
+			\end{tablenotes}
+		\end{threeparttable}
+	\end{table}
+
+\FloatBarrier
+\FloatBarrier
 \section{The Model}
@@
 	\begin{tikzpicture}[domain=0:1,scale=4]
-	\node [block, name=input,align=center] (sum) {Single\\ 7348};
+	\node [block, name=input,align=center] (sum) {Single};
 	\node [block, above right of=sum, node distance=6cm] (controller) {Separation};
 	\node [block, below right of=controller,
-	node distance=6cm,align=center] (system) {Cohabitation \\ 5308};
-	\draw [<-,  thick, latex-] (controller) -| node[below left]{47,8\%}(system);
+	node distance=6cm,align=center] (system) {Cohabitation };
+	\draw [<-,  thick, latex-] (controller) -| node[below left]{}(system);
 	\node [output, right of=system] (output) {fe};
-	\node [block, below left of=system,  node distance=6cm,align=center] (measurements) {Marriage \\ 2814};
+	\node [block, below left of=system,  node distance=6cm,align=center] (measurements) {Marriage };
 	\node [block, left of=measurements, node distance=4.2cm,align=left] (divorce) {Divorce};
-	\draw [<-,  thick, latex-] (sum) |- node[below right]{100\%} (controller);
-	\draw [->,  thick, -latex] (sum) -- node[above]{72,4\%} (system);
-	\draw [->,  thick, -latex] (system) |-node[above left]{33,8\%} (measurements);
-	\draw [->,  thick, -latex] (measurements) --node[above]{23,5\%} (divorce);
-	\draw [->,  thick, -latex] (sum) --node[above right]{12,9\%} (measurements);
-	\draw [->,  thick, -latex] (divorce) --node[right]{100\%} (sum);
+	\draw [<-,  thick, latex-] (sum) |- node[below right]{} (controller);
+	\draw [->,  thick, -latex] (sum) -- node[above]{} (system);
+	\draw [->,  thick, -latex] (system) |-node[above left]{} (measurements);
+	\draw [->,  thick, -latex] (measurements) --node[above]{} (divorce);
+	\draw [->,  thick, -latex] (sum) --node[above right]{} (measurements);
+	\draw [->,  thick, -latex] (divorce) --node[right]{} (sum);
 	node [near end] {$$} (sum);
@@
 \begin{equation}\label{eq:pfunction}
-Q_t=[d_t^\lambda+\kappa {(1-P^f_t)}^\lambda]^{\frac{1}{\lambda}}, \text{ where }0<\lambda<1.
+Q_t=[d_t^\nu+\kappa {(1-P^f_t)}^\nu]^{\frac{1}{\nu}}, \text{ where }0<\nu<1.
 \end{equation}
-The parameter $\lambda$ captures the degree of  substitutability between female time and the use of durables in the production of the home good.
+The parameter $\nu$ captures the degree of  substitutability between female time and the use of durables in the production of the home good.
 This structure implies that when the relative price of durables decreases and when wages goes up, households will use less female time for its production, and hence female employment will increase.
@@
 \begin{equation}\label{eq:pcomp}
-z^s_t=z^s_{t-1}-(1-P_t^s) \mu+\zeta^s_{t}\text{, where }\zeta^s_{t}\sim^{iid}\mathcal{N}(0,\sigma^\zeta)\text{, and }\zeta^s_{1}=z^s_{1}.
+z^s_t=z^s_{t-1}-(1-P_t^s) \mu+\zeta^s_{t}\text{, where }\zeta^s_{t}\sim^{iid}\mathcal{N}(0,\sigma_\zeta^{2_s})\text{, and }\zeta^s_{1}=z^s_{1}.
 \end{equation}
@@
 Then, the agents make their final choice solving a pareto problem where the outside option is the outcome of the first step.
-We tried applying this methodology: results were indistinguishable from our main strategy.} to discrete choices [CITATION OF RELEVANT PAPER HERE].
+We tried applying this methodology: results were indistinguishable from our main strategy.} to discrete choices.
 \end{enumerate}
 \section{Estimation}
+We estimate our model following a two step procedure.
+In a first step, we set some parameters outside the model.
+This can be done for parameters that can be directly linked to the data and for parameters that our data does not directly identifies, and that are hence fixed according to findings coming from the existing literature.
+Moreover, we also estimate the labor income processes of men and women outside the model: this procedure is common in the literature\footnote{See for example \cite{voena2015}, \cite{reynoso2019} and \cite{gourinchas2002}.} and it has been used to reduce the burden of structural estimation.
+ In the second step we use the simulated method of mooments to estimate the deep parameters of the model.
+In this section we described in detailed every step of the estimation, we discuss the identification of the structural parameters and the results.
+\subsection{Income Processes}
+\begin{table}[H]
+\label{table:income_params}
+\caption{\\Parameters of the Income Processes} % title of Table
+\centering % used for centering table
+\begin{threeparttable}
+\begin{tabular}{@{\extracolsep{5pt}}lcccc}   % centered columns (4 columns)
+\hline \hline%inserts single line
+\ Parameter & Symbol  & Value &   Standard Error\\ [0.45ex] % inserts table
+\hline
+\ $f$'s age return (constant)         & $\iota^f_0$  & -0.383 & MSM & \\[0.45ex]
+\ $f$'s age return (linear component) & $\iota^f_1$         & 0.0244  & MSM & \\[0.45ex]
+\ $f$'s age return (squared component)               & $\iota^f_2$       & -0.0005 & MSM & \\[0.45ex]
+\ Variance of $f$'s permanent income shock                                 & $\sigma_\zeta^{2_f}$             & 0.0399  & MSM & \\[0.45ex]
+\ $m$'s age return (constant)         & $\iota^m_0$  & -0.342 & MSM & \\[0.45ex]
+\ $m$'s age return (linear component) & $\iota^m_1$         & 0.0495  & MSM & \\[0.45ex]
+\ $m$'s age return (squared component)               & $\iota^m_2$       & -0.0009 & MSM & \\[0.45ex]
+\ Variance of $m$'s permanent income shock                                 & $\sigma_\zeta^{2_m}$             & 0.0417  & MSM & \\[0.45ex]
+\hline
+\end{tabular}
+\begin{tablenotes}[flushleft]
+\footnotesize{\item \textsc{Notes}: The parameters are estimated using nonlinear least squares using single, cohabiting and married males and females from the PSID.
+Standard errors are computed by bootstrap.}
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+\FloatBarrier
+\subsection{Preset Parameters}
+This section describes how we choose the parameters that set externally from the model.
+In the model we assume agents to start making decisions at age $20$, while they retire at 65 and die with probability $1$ at age $82$.
+Each period in the model lasts $1$ year: we chose this length balancing the benefits of having a short period, which fits the fact that cohabitation spells are particularly short, and the computational burden associated with having too many periods.
+We chose the relative risk aversion $\gamma$ of private goods and the discount factor $\beta$ to be those in \cite{attanasio2008}, while the relative risk aversion of public goods $\xi$ is taken from \cite{greenwood2016}.
+Instead the parameters relative to the production of public goods, $\nu$ and $\kappa$ are those in \cite{mcgrattan1997}.
+The annual interest rate is set to $3\%$.
+The unexplained variance of male and female's earnings at age $20$ $\sigma_{\zeta,1}^{2_m}$ and $\sigma_{\zeta,1}^{2_f}$ are taken directly from the PSID data, as well as the variance in the labor earning of the partner at meeting, which is denoted by $\sigma^2_{\tilde{p}}$.
+Instead, the variance in the assets owned by the partner at meeting $\sigma^2_{\hat{p}}$ is taken from the ACS.
+
+\begin{table}[H]
+\caption{\\Preset Parameters} % title of Table
+\label{table:preset_params}
+\centering % used for centering table
+\begin{threeparttable}
+\begin{tabular}{@{\extracolsep{5pt}}lccc}   % centered columns (4 columns)
+\hline \hline 
+ Estimated Parameters & Symbol & Value & Source  \\ [0.45ex] % inserts table
+\hline
+ Initial age              &          & 20  &  \\[0.45ex]
+ Retirement age           &    $T_R$      & 65  &  \\[0.45ex]
+ Age at death             &     $T$     & 82  &  \\[0.45ex]
+ Years per period         &          & 1  &  \\[0.45ex]
+% Retirement income        &          & 0.61 &  \\[0.45ex]
+ Interest rate            &$R-1$       & 0.03 &  \\[0.45ex]
+ $m'$s average earnings in $t=1$      &       & 1 & Normalization \\[0.45ex]
+ Var. partner's asset at meeting             &$\sigma^2_{\hat{p}}$       & 0.01 & ACS\\ [0.45ex]
+ Var. partner's productivity    at meeting        &$\sigma^2_{\tilde{p}}$       & 0.16 & PSID \\[0.45ex]
+  Var. $f$'s productivity in $t=1$&$\sigma_{\zeta,1}^{2_f}$       & 0.41 & PSID \\[0.45ex]
+   Var. $m$'s productivity   $t=1$  &$\sigma_{\zeta,1}^{2_m}$       & 0.40 & PSID \\[0.45ex]
+ Relarive Risk Aversion private good   &$\gamma$  & 1.5 &\cite{attanasio2008}  \\[0.45ex]
+ Discount factor          &$\beta$   & 0.98&\cite{attanasio2008}  \\[0.45ex]
+ Relarive Risk Aversion public good          &$\xi$   & 3.11& \cite{greenwood2016}  \\[0.45ex]
+\hline \hline
+ Function &Symbol & Value & Source  \\ [0.45ex] % inserts table
+ \hline 
+$Q_t=[d_t^\nu+\kappa {(1-P^f_t)}^\nu]^{\frac{1}{\nu}}$& 
+\begin{tabular}{@{}c@{}}$\kappa$ \\[0.25ex] $\nu$\end{tabular} &\begin{tabular}{@{}c@{}}3.76 \\[0.25ex] 0.19\end{tabular}  &  \begin{tabular}{@{}c@{}} \cite{mcgrattan1997} \\[0.25ex] \cite{mcgrattan1997}\end{tabular}  \\[0.95ex]
+\hline
+\end{tabular}
+\end{threeparttable}
+\end{table}
+\FloatBarrier
+
+\subsection{Method of Simulated Moments}
+\subsection{Identification}
+\subsection{Results}
+
+%Table of deep parameters
+\begin{table}[H]
+\caption{\\Estimated Structural Parameters} % title of Table
+\label{table:structural_params}
+\centering % used for centering table
+\begin{threeparttable}
+\begin{tabular}{@{\extracolsep{5pt}}lccc}   % centered columns (4 columns)
+\hline \hline%inserts single line
+\ Estimated Parameters &  & Value &  \\ [0.45ex] % inserts table
+\hline
+\ Standard deviation of match quality shock         & $\sigma_{\psi}$  & 0.18 & MSM \\[0.45ex]
+\ Standard deviation of initial match quality shock & $\sigma_{\psi,I}$         & 0.21  & MSM \\[0.45ex]
+\ Probability of meeting a partner               & $\lambda$       & -3.55 & MSM \\[0.45ex]
+\ Divorce cost                                 & $\sigma$             & 0.20  & MSM \\[0.45ex]
+\ Weight of public good               & $\alpha$             & 0.18 & MSM \\[0.45ex]
+\ Loss in productivity while not working               & $\mu$             & 0.21 & MSM \\[0.45ex]
+\hline
+\end{tabular}
+\begin{tablenotes}[flushleft]
+\footnotesize{\item \textsc{Notes}: The parameters in the table are estimated using the method of simulated moments.}
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+\FloatBarrier
+
 \section{Counterfactual Experiments}
@@
 \appendix
+
+\section*{Appendix}
 \counterwithin{figure}{section}
 \counterwithin{table}{section}
-\section*{Appendix}
 \section{Computational Appendix}
@@
 \section{Estimation of Income Processes}
+\section{Robustness Checks - Empircal Analysis}
+\subsubsection*{Relationship Choice - Linear State Trends}
+
+%RELATIONSHIP CHOICE
+	\begin{table}[htbp]\centering
+	\caption{\\OLS Regression. Observation: first and second relationships}
+	\label{table:wmarlin}
+	\begin{threeparttable}[t]\centering
+	\input{wmarlin.tex}
+	\begin{tablenotes}[flushleft]
+	\footnotesize{\item \textsc{Notes}: standard errors are clustered at the state level.
+		Coefficients that are significantly different from zero are denoted by the following system: *10\%, **5\%  and ***1\%.}
+	\end{tablenotes}
+	\end{threeparttable}
+	\end{table}
+
+\subsubsection*{Relationship Choice - Heterogeneity by Propoerty regime and linear state trends}
+
+%RELATIONSHIP CHOICE
+
+	\begin{table}[htbp]\centering
+	\caption{\\OLS Regression. Observation: first and second relationships}
+	\label{table:wmarlinc}
+	\begin{threeparttable}[t]\centering
+	\input{wmarlinc.tex}
+	\begin{tablenotes}[flushleft]
+	\footnotesize{\item \textsc{Notes}: standard errors are clustered at the state level.
+		Coefficients that are significantly different from zero are denoted by the following system: *10\%, **5\%  and ***1\%.}
+	\end{tablenotes}
+	\end{threeparttable}
+	\end{table}
+
+\FloatBarrier
+\subsubsection*{Relationship Choice - Logit}
+
+%RELATIONSHIP CHOICE
+	\begin{table}[htbp]\centering
+	\caption{\\Logitstic regression. Observation: first and second relationships}
+	\label{table:wmar_logit}
+	\begin{threeparttable}[t]\centering
+	\input{wmar_logit.tex}
+	\begin{tablenotes}[flushleft]
+	\footnotesize{\item \textsc{Notes}: standard errors are clustered at the state level.
+		Coefficients that are significantly different from zero are denoted by the following system: *10\%, **5\%  and ***1\%.}
+	\end{tablenotes}
+	\end{threeparttable}
+	\end{table}
 

### 2020-02-14 mpc.Rnw
law review plus some estimation done

\footnotesize 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline 
\\[-1.8ex] & \multicolumn{1}{c}{Full Sample} & \multicolumn{1}{c}{Resident}& \multicolumn{1}{c}{NSFH}& \multicolumn{1}{c}{NSFG} \Writing to file mpc.tex
Processing code chunks with options ...

You can now run (pdf)latex on ‘mpc.tex’
}{c}{(4)}\\ 
\hline \\[-1.8ex] 
\\[-2.2ex] & \multicolumn{4}{c}{Risk of Marriage relative to Cohabitation} \\  
 \hline \\[-1.8ex]
 Unilateral Divorce &  -0.09  &  -0.07  &  -0.12  &  -0.13  \\ 
  & ( 0.04 ) & ( 0.04 ) & ( 0.04 ) & ( 0.11 ) \\  
 \hline \\[-1.8ex]
 Average Relative Risk &  -0.12  &  -0.08  &  -0.2  &  -0.14  \\ 
 \hline \\[-1.8ex]
 \\[-2.2ex] & \multicolumn{4}{c}{Risk of Separation relative to Cohabitation} \\  
 \hline \\[-1.8ex]
 Unilateral Divorce &  -0.04  &  -0.09  &  -0.05  &  -0.06  \\ 
  & ( 0.02 ) & ( 0.02 ) & ( 0.02 ) & ( 0.1 ) \\  
 \hline \\[-1.8ex]
 Average Relative Risk &  -0.06  &  -0.18  &  -0.1  &  -0.06  \\ 
 \hline \\[-1.8ex]
State Fixed effects & Yes & Yes & Yes & Yes \\ 
Year Fixed effects & Yes & Yes & Yes & Yes \\ 
Age Polynomial & Yes & Yes & Yes & Yes \\
Picewise Duration & Yes & Yes & Yes & Yes \\ 
\hline
Observations & \multicolumn{1}{c}{ 138012 } & \multicolumn{1}{c}{ 81920 } & \multicolumn{1}{c}{ 77826 } & \multicolumn{1}{c}{ 60186 } \\ 
\hline
Censored spells(\%) & \multicolumn{1}{c}{ 10.18 } & \multicolumn{1}{c}{ 10.98 } & \multicolumn{1}{c}{ 11.6 } & \multicolumn{1}{c}{ 8.38 } \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}

### 2020-02-14 mpc.tex
law review plus some estimation done

--- 2020-02-14 mpc.Rnw
@@
 \hline 
-\\[-1.8ex] & \multicolumn{1}{c}{Full Sample} & \multicolumn{1}{c}{Resident}& \multicolumn{1}{c}{NSFH}& \multicolumn{1}{c}{NSFG} \Writing to file mpc.tex
-Processing code chunks with options ...
-
-You can now run (pdf)latex on ‘mpc.tex’
-}{c}{(4)}\\ 
+\\[-1.8ex] & \multicolumn{1}{c}{Full Sample} & \multicolumn{1}{c}{Resident}& \multicolumn{1}{c}{NSFH}& \multicolumn{1}{c}{NSFG} \\ 
+\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
 \hline \\[-1.8ex] 

### 2020-02-14 draft_sub_con.tex
only results left

@@
 In a first step, we set some parameters outside the model.
-This can be done for parameters that can be directly linked to the data and for parameters that our data does not directly identifies, and that are hence fixed according to findings coming from the existing literature.
+This can be done for parameters that can be directly linked to the data and for parameters that our data does not directly identifies: those are fixed according to findings coming from the existing literature.
 Moreover, we also estimate the labor income processes of men and women outside the model: this procedure is common in the literature\footnote{See for example \cite{voena2015}, \cite{reynoso2019} and \cite{gourinchas2002}.} and it has been used to reduce the burden of structural estimation.
- In the second step we use the simulated method of mooments to estimate the deep parameters of the model.
-In this section we described in detailed every step of the estimation, we discuss the identification of the structural parameters and the results.
+ In the second step we use the simulated method of moments to estimate the deep parameters of the model.
+In this section we described in detailed every step of the estimation and we discuss the identification of the structural parameters as well as the results.
 \subsection{Income Processes}
+For both men and women we model the hourly wage rate using PSID, dividing the annual labor income by the number of yearly working hours supplied.
+In this way we avoid considering a variation in working hours as a productivity shock.
+This correction is particularly relevant for the estimation of women's income process, as the variance of hours worked per year is considerably higher than for men.
+For our estimation we consider the $1968$-$1993$ waves of the PSID, including men and women between age 20 and 65.
+
+For the estimation of men's processes we proceed estimating the following model for man $i$, of age $t$, from state $s$  in survey year $sur$:
+\begin{equation}\label{eq:male_earn}
+\ln(w^m_{i,t,s,sur})=\iota^m_0+\iota^m_1*t+\iota^m_2*t^2+\delta_s+\nu_{sur}+u_{i,t,s,sur}^m,
+\end{equation}
+where $u_{i,t,s,sur}^m=z_t^m+e^m_{i,t,s,sur}$.
+$z_t^m$ follows equation $\ref{eq:pcomp}$, while $e^m_{i,t,s,sur}$ is the measurment error.
+Instead, $\delta_s$ are state fixed effects and $\nu_{sur}$ are year of the survey fixed effects.
+We then estimate equation \ref{eq:male_earn}, whose results are reported in table \ref{table:inc_men}: this allow us to obtain the residuals  $\hat{u}_{t}^m$.
+We then use the regression residuals to estimate through GMM the variance of the permanent component of income $\sigma_\zeta^{2_m}$ and the one of the measurment error $\sigma_e^{2_m}$ using the following conditions:
+\begin{equation}\label{eq:male_gmm}
+\begin{split}
+E(\Delta\hat{u}_{t}^m)&=\sigma_\zeta^{2_m}+2\sigma_e^{2_m}\\
+E(\Delta\hat{u}_{t}^m\Delta\hat{u}_{t-1}^m)&=-\sigma_e^{2_m}
+\end{split}
+\end{equation}
+Results are reported in table \ref{table:income_params}.
+
+The estimation of female's labor earning differs from the men's one since we need to take into account the endogeneity of female labor participation.
+We do so using a Heckman selection correction procedure.
+Female labor earnings of female $i$, of age $t$, from state $s$  in survey year $sur$:
+\begin{equation}\label{eq:femae_earn}
+\ln(w^f_{i,t,s,sur})=\iota^f_0+\iota^f_1*t+\iota^f_2*t^2+\delta_s+\nu_{sur}+u_{i,t,s,sur}^f,
+\end{equation}
+where $u_{i,t,s,sur}^f=z_t^f+e^f_{i,t,s,sur}$.
+$z_t^f$ follows equation $\ref{eq:pcomp}$, while $e^f_{i,t,s,sur}$ is the measurment error.
+Instead, $\delta_s$ are state fixed effects and $\nu_{sur}$ are year of the survey fixed effects.
+We observe female wages only if
+\begin{equation}\label{eq:femae_part}
+\gamma'\mathbf{Z}_{i,t,s,sur}+\pi_{i,t,s,sur}>0,
+\end{equation}
+where $\mathbf{Z}_{i,t,s,sur}$ includes all the regressors in \ref{eq:femae_earn} plus the interaction of unilateral divorce\footnote{This strategy has been used by \cite{voena2015} and \cite{reynoso2019}} with property rights regimes upon divorce.
+The estimation results of the two steps are reported in tables \ref{table:prb_wom} and \ref{table:inc_wom}.
+Finally, we use the regression residuals from the second step $\hat{u}_{t}^m$  to estimate through GMM the variance of the permanent component of income $\sigma_\zeta^{2_f}$ and the one of the measurment error $\sigma_e^{2_f}$ using the following conditions\footnote{The conditions are those used by \cite{low2018}.}:
+\begin{equation}\label{eq:female_gmm}
+\begin{split}
+E(\Delta\hat{u}_{t}^f | P^f_t=1,P^f_{t-1}=1)&=\sigma_\pi^{f}\frac{\phi(\tau_t)}{1-\Phi(\tau_t)},\\
+E(\Delta(\hat{u}_{t}^{f})^2 | P^f_t=1,P^f_{t-1}=1)&=\sigma_\zeta^{2_f}+\sigma_\pi^{2_f}+2\sigma_e^{2_f}+\tau_t\frac{\phi(\tau_t)}{1-\Phi(\tau_t)},\\
+E(\Delta\hat{u}_{t}^f\Delta\hat{u}_{t-1}^f | P^f_t=1,P^f_{t-1}=1,P^f_{t-2}=1))&=-\sigma_e^{2_f}.
+\end{split}
+\end{equation}
+Results are displayed in table \ref{table:income_params}.
+
 \begin{table}[H]
-\label{table:income_params}
 \caption{\\Parameters of the Income Processes} % title of Table
@@
 \end{threeparttable}
+\label{table:income_params}
 \end{table}
@@
 \subsection{Method of Simulated Moments}
+We use the method of simulated moments (\citealp{mcfadden1989} and \citealp{pakes1989}) to pin down the vector $\vartheta=(\alpha, \lambda, \sigma_\psi, \sigma_{\psi,I}, \delta, \mu)$ of the 6 remaining parameters of the model.
+We use 38 moments for the structural estimation, which capture the process of marriage cohabitation creation and dissolution, as well the labor supply behavior of women.
+More precisely, we include moments about the hazard of divorce (12), the hazard of separation (6), the hazard of marriage (6), the share of people everm married over time (6), the share of people that ever cohabited over time (6), female labor force participation (1), and differences in female labor force participation between marriage and cohabitation (1).
+We use the retrospective marital hisotry data from the NSFH wave III to construct\footnote{NSFH wave III is conducted in 2001/2003 following the original respondents of wave 1.
+This sample does not include respondents under age 45 as of January 2000 unless some particular conditions are met, but this is not an issue for us since the youngest person in our estimating sample was 44 in 2000.
+One possible issue with this data is that by mistake during NSFH wave II  all cohabiting couples were dropped by the sample.
+We can circumvent this issue simulating the same "mistake" dropping some observation from the fictional samples.} moments about marriage and cohabitation, while we use the PSID for female labor supply.
+We include in the sample for the data moment construction male and females born in 1945-1955, which allow us to follow them unitl a late age, and also to observe how their behavior react to changes in divorce laws.
+The first step for the estimation is to solve the model for a vecto of paramters $\vartheta$, then simulating income and love shocks, we obtain the simulated behavior for the given parametrization.
+This allow us to compare the simulated and the data moments: the objective is to obtain $\vartheta$ such that this difference is the smallest possible.
+Formally, the problem that we solve is
+\begin{equation}
+\hat{\vartheta}=\arg\min_\theta \quad\quad (\mathbf{m}-\mathbf{m}_\vartheta)'\mathbf{W}(\mathbf{m}-\mathbf{m}_\vartheta),
+\end{equation}
+where $\mathbf{m}$ is the vector of empirical moments, as described in the section about target moments, while $\mathbf{m}_\vartheta$ is the vector of the moments simulated by the model parametrized with $\vartheta$.
+$\mathbf{W}$ is a matrix where the diagonal contains the inverse of the variance of the data moments, while all the other entries are zeros.
+The minimization of this object function is performed using a global minimization algorithm called TikTak, which is described in detail in appendix \ref{section:computation}.
+
 \subsection{Identification}
+This section provides a description of how, heuristically, the structural parameters of the model are identified.
+The parameter $\alpha$ is identified by total female labor force participation: when this parameter is large the household want to produce more of public good which require female time.
+Instead $\mu$ affects the gap in female labor force participation for married and cohabiting couples: when this parameter is large, specialization within cohabitation becomes harder, which increases the gap.
+$\lambda$ is intuitively identified by the share of people in a relationship, while $\delta$ is informative about the gains of marriage with respect to cohabitation.
+The parameter $\sigma_{\psi,I}$ is identified by the hazard of separation and marriage: when this parameter is small compared to the variance of the transitory shocks, agents are not \textit{picky} about sorting into cohabtitation, but they move fast to a new relationship or they separate within the first periods of the relationship.
+Finally, $\sigma_{\psi}$ identifies the hazard of divorce: the larger the variance in the shocks, the more higher would be the likelihood that marriage surplus becomes negative.
+We did not use the results from the empirical part as targets as we think that would provide rendundant information about the identification.
+More in particular, as the risk of divorce is the main driver of the reaction to divorce laws, $\sigma_{\psi}$  is also identifying the parameters of the quasi experiment regression.
 \subsection{Results}
@@
 \ Probability of meeting a partner               & $\lambda$       & -3.55 & MSM \\[0.45ex]
-\ Divorce cost                                 & $\sigma$             & 0.20  & MSM \\[0.45ex]
+\ Share assets left upon divorce                                 & $\delta$             & 0.80  & MSM \\[0.45ex]
 \ Weight of public good               & $\alpha$             & 0.18 & MSM \\[0.45ex]
@@
 \counterwithin{table}{section}
-\section{Computational Appendix}
+\section{Computational Appendix}\label{section:computation}
 \cite{arnoud2019}+\cite{cartis2019}
 \section{Estimation of Income Processes}
+
+%MARRUAGE TO DIVORCE
+{	
+	\def\onepc{$^{\ast\ast}$} \def\fivepc{$^{\ast}$}
+	\def\tenpc{$^{\dag}$}
+	\def\legend{\multicolumn{1}{l}{\footnotesize{Significance levels
+				:\hspace{1em} $\ast$ : 10\% \hspace{1em}
+				$\ast\ast$ : 5\% \hspace{1em} $\ast\ast\ast$ : 1\% \normalsize}}}
+	\begin{table}[htbp]\centering
+	\caption{\\OLS Regression. Observation: Males in Year $t$.}
+	\label{table:inc_men}
+	\begin{threeparttable}[t]\centering
+	\input{inc_men}
+	\end{tabular}}
+\begin{tablenotes}[flushleft]
+\footnotesize{\item \textsc{Notes}: Standard errors are obtained through bootstrapping and they are reported in summary table \ref{table:income_params}.}
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+}
+\FloatBarrier
+%MARRUAGE TO DIVORCE
+{	
+	\def\onepc{$^{\ast\ast}$} \def\fivepc{$^{\ast}$}
+	\def\tenpc{$^{\dag}$}
+	\def\legend{\multicolumn{1}{l}{\footnotesize{Significance levels
+				:\hspace{1em} $\ast$ : 10\% \hspace{1em}
+				$\ast\ast$ : 5\% \hspace{1em} $\ast\ast\ast$ : 1\% \normalsize}}}
+	\begin{table}[htbp]\centering
+	\caption{\\OLS Regression. Observation: Females in Year $t$.}
+	\label{table:inc_wom}
+	\begin{threeparttable}[t]\centering
+	\input{inc_wom}
+	\end{tabular}}
+\begin{tablenotes}[flushleft]
+\footnotesize{\item \textsc{Notes}: Standard errors are obtained through bootstrapping and they are reported in summary table \ref{table:income_params}.}
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+}
+\FloatBarrier
+
+%MARRUAGE TO DIVORCE
+{	
+	\def\onepc{$^{\ast\ast}$} \def\fivepc{$^{\ast}$}
+	\def\tenpc{$^{\dag}$}
+	\def\legend{\multicolumn{1}{l}{\footnotesize{Significance levels
+				:\hspace{1em} $\ast$ : 10\% \hspace{1em}
+				$\ast\ast$ : 5\% \hspace{1em} $\ast\ast\ast$ : 1\% \normalsize}}}
+	\begin{table}[htbp]\centering
+	\caption{\\Probit Regression. Observation: Females in Year $t$.}
+	\label{table:prb_wom}
+	\begin{threeparttable}[t]\centering
+	\input{prb_wom}
+	\end{tabular}}
+\begin{tablenotes}[flushleft]
+\footnotesize{\item \textsc{Notes}: standard errors are clustered at the state level.
+	Coefficients that are significantly different from zero are denoted by the following system: *10\%, **5\%  and ***1\%. \ref{table:income_params}.}
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+}
+\FloatBarrier
 \section{Robustness Checks - Empircal Analysis}
@@
 	\end{table}
-
+\FloatBarrier
 \subsubsection*{Relationship Choice - Heterogeneity by Propoerty regime and linear state trends}
@@
 	\end{table}
+\FloatBarrier
 

### 2020-02-14 inc_men.tex
only results left

{\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}              \begin{tabular}{l*{1}{c}}                          \toprule             &\multicolumn{1}{c}{(1)}       \\             \midrule             \textsc{Dep. Variable:} &  \\\textsc{Male Log Earnings} & \\ & \\
$\iota^m_1$         &        0.05\\
$\iota^m_2$         &       -0.00\\
$\iota^m_0$           &       -0.34\\
Survey Year Fixed Effects  & \checkmark   \\         State Fixed Effects  & \checkmark  \\                         \hline
Observations        &       98118\\
\(R^{2}\)           &       0.152\\
\hline

### 2020-02-14 inc_wom.tex
only results left

{\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}              \begin{tabular}{l*{1}{c}}                          \toprule             &\multicolumn{1}{c}{(1)}       \\             \midrule             \textsc{Dep. Variable:} &  \\\textsc{Female Labor Earnings} & \\ & \\
$\iota^f_1$         &        0.02\\
$\iota^f_2$         &       -0.00\\
$\iota^f_0$            &       -0.38\\
Survey Year Fixed Effects  & \checkmark   \\         State Fixed Effects  & \checkmark  \\                         \hline
Observations        &       86891\\
\(R^{2}\)           &       0.085\\
\hline

### 2020-02-14 prb_wom.tex
only results left

{\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}              \begin{tabular}{l*{1}{c}}                          \toprule             &\multicolumn{1}{c}{(1)}       \\             \midrule             \textsc{Dep. Variable:} &  \\\textsc{Female Labor Force Participation} & \\ & \\
Unilateral Divorce$*$Community Property&       -0.18\sym{***}\\
Unilateral Divorce$*$Title Based&       -0.08         \\
Unilateral Divorce$*$Equitable Distribution&       -0.06         \\
Equitable Distribution&       -0.00         \\
$\iota^f_1$         &        0.01\sym{***}\\
$\iota^f_2$         &       -0.00\sym{***}\\
$\iota^f_0$            &        1.95         \\
Survey Year Fixed Effects  & \checkmark   \\         State Fixed Effects  & \checkmark  \\                         \hline
Observations        &      127728         \\
\hline

### 2020-09-28 abstract.tex
latest

--- 2020-02-12 draft_sub_con.tex
@@
 \restylefloat{table}
+
+%For bar charts in table
+\newlength\MAX  \setlength\MAX{40mm}
+\newcommand*\Chart[1]{#1~\rlap{\textcolor{blue!20}{\rule{#1\MAX}{2ex}}}}
+%\newcommand*\Chartguys[1]{\rlap{\textcolor{blue!30}{\rule{6ex}{\MAX}}}{\textcolor{white!30}{\rule{6ex}{#1\MAX}}}}
+%\newcommand*\Chartgirls[1]{\rlap{\textcolor{red!30}{\rule{6ex}{\MAX}}}{\textcolor{white!30}{\rule{6ex}{#1\MAX}}}}
+\newcommand*\Chartguys[1]{{\textcolor{blue!30}{\rule{6ex}{#1\MAX}}}}
+\newcommand*\Chartgirls[1]{{\textcolor{red!30}{\rule{6ex}{#1\MAX}}}}
 
@@
 Blasutto acknowledges financial support from the French speaking community of Belgium (ARC project 15/19-063 on "family transformations").}}
-\author{Fabio Blasutto$^1$ \quad Egor Kozlov$^2$}
+\author{Fabio Blasutto$^1$ (Presenter) \quad Egor Kozlov$^2$}
 
@@
 
-	\footnotetext[1]{IRES, UCLouvain \& National Fund for Scientific Research (Belgium). Email:  \tt{fabio.blasutto@uclouvain.be}}
+	\footnotetext[1]{IRES, UCLouvain \& National Fund for Scientific Research (Belgium).
+Email:  \tt{fabio.blasutto@uclouvain.be}, Phone:\tt{+32 489545996}, Address: \tt{Chaussee de Wavre 561/2, Etterbeek, Belgium.}}
 	\footnotetext[2]{Northwestern Univrsity. Email:  \tt{egorkozlov2020@u.northwestern.edu}.\\}
@@
 Exploiting the staggered introduction of unilateral divorce across U.S.
-states, we show that after the reform newly formed relationships are more likely to be cohabitations instead of marriages, and that cohabitation spells last longer.
-To understand the mechanisms underlying the law changes, we build and estimate a structural life cycle model with partnership choice, where the gains from marriage with respect to cohabitation come from a better cooperation within the household, enforced through a costly divorce, which acts as a commitment technology.
-In the model the reform increase the risk of divorce, making cohabitation preferred to couples that would have had the highest risk of divorce.
-Since the couples switching relationship are on average better matched than the average cohabitants, the length of cohabitations increases.
+states, we show that after the reform newly formed relationships are 5\% more likely to be cohabitations instead of marriages, and that cohabitation spells last longer.
+To understand the mechanisms underlying the law changes, we build and estimate a structural life cycle model with partnership choice, female labor supply and savings decisions, where the gains of marriage with respect to cohabitation come from a better risk sharing and specialization within the household, enforced through a costly divorce.
+In the model the reform increases the risk of divorce, making cohabitation preferred to couples that would have had the highest risk of divorce.
+Since the couples switching relationship are on average better matched than the average cohabitants, the duration of cohabitations increases.
 \end{abstract}
@@
 \textbf{JEL-Code}: D83 - J12
-%\clearpage
-%\noindent \medskip{}
-\section{Introduction}
-Cohabitation is on the rise: according to \cite{manning2013}, the share of women that ever cohabited moved from 33\% in 1987 to 60\% in 2010. Why did this happen?
-Since the seminal work of Becker (\citealp{becker1981}), economists studied the incentives behind the decision to marry, among which the sharing of public goods, the division of labor to exploit comparative advantages (\citealp{chiappori1997}), and risk sharing (\citealp{voena2015} and \citealp{rigas2015}).
-These reasons tell us why couples live together, while they are actually silent about the choice between marriage and informal cohabitation, two partnership contracts subject to different rules.
-While the literature often simplifies, avoiding the distinction between these two, they display a different labor supply, wealth accumulation and educational composition.
-It is not surprising that households, the smallest economic unit, can behave differently when the contract ruling them is different, but this can be the key to understand important economic phenomena.
-For example, cohabitation display a much higher separation rate than marriages, which might be a cause of the high share of single mothers living in the US nowadays, which is the single strongest predictor for upward mobility\footnote{While the share of single mothers is the strongest predictor of differences in upward mobility across counties on top of segregation, residential segregation, income inequality, social capital, school quality, and racial shares, \cite{chetty2018} points out that half of this effect is due to self selection.} according to \cite{chetty2018}.
-If we want to understand the behavior of cohabiting households and the implication of it, we first need to understand their formation and why they are growing in number.
-
-In this paper we address the question of the rise of cohabitation, focusing on the role of unilateral divorce on the share of people that decides to cohabit.
-Our main contribution is to show that the rate of cohabitation increased after the changes in the US law and that the underlying mechanism is that the increased risk of divorce makes marriage less attractive.
-As a consequence, cohabitation becomes the preferred choice to couples that would have experienced the highest risk of divorce.
-As a consequence, the average match quality of cohabiting couples increase, which increases the length of cohabitation spells.
-
-We first use data from the National Survey of Family and the Household and of the National Survey of Family Growth to build a sample of first and second relationships\footnote{A relationship is defined as an interruption of the state of singleness, which can either be marriage or cohabitation.}.
-Then, exploiting the exogenous variation coming from the staggered introduction of unilateral divorce over time across US states, we show that cohabitation becomes around 5\% more likely  to be chosen compared to the pre-reform period.
-Interestingly,  the effect is heterogeneous on how property is divided upon divorce, being strongest in states where each spouse gets half of the wealth.
-This suggest that the result cannot be entirely due to a deterioration of divorce as a commitment technology\footnote{This mechanism is highlighted by \cite{lafortune2019}, where the equal division of assets within marriage makes possible to efficiently invest in children even after the rise of unilateral divorce.}, since the egalitarian property division rule can act as a substitute of the mutual consent regime.
-Moreover, we analyze how unilateral divorce affected the length of newly formed cohabitation spells, showing that they last longer both because of a reduced risk of marriage and separation.
-To understand the mechanisms that lead to these changes we build a dynamic model of intrahousehold decision making, where cohabitation and marriage differ in their splitting cost as well as in the way property is divided.
-While in the case of separation assets are always split as an agreement between spouses, in the case of divorce in some states it is the judge to decide.
-Moreover, separation can be initiated unilaterally, as opposed to divorce, that would need the consensus of both partner under a mutual divorce regime.
-Individuals are initially single, and with some probability in each period they meet a potential partner, which they can decide to marry or start cohabiting with.
-Couples make decisions about consumption, savings and female labor supply and they are subject to idiosyncratic income shocks.
-Couples also receive time varying match quality shocks, which might drive the couple to change their partnership status (i.e.
-from cohabitation to marriage) or to separate.
-We model the decision making in the couple building on the literature of limited commitment (see for example \cite{kk1996},  \cite{ligon2002}, \cite{marcet2019} and \cite{pavoni2018}), which has been applied to dynamic collective models in the household by \cite{voena2015}, \cite{mazzocco2007}, \cite{foerster2019} and \cite{lise2018} among others.
-In this framework, when one member of the couple wishes to split, the couple rebargains such that the binding member is made indifferent between separation and staying in a couple\footnote{For particularly bad draws in the match quality or productivity shock this might not be possible and hence the couple would split.}.
-The gains of marriage with respect to cohabitation come from a better risk sharing and a more efficient specialization in the production of a public good\footnote{We assume that a public good is produced with money an female time.
-When females stop working for producing such good their potential productivity in the labor market decreases.}, which arise from a better commitment within the couple, enforced by the threat of a costly divorce, which acts as a commitment device.
-On the other hand, couples that would face a high risk of divorce if married (i.e.
-because of a low match quality draw) are more likely to choose cohabitation instead, since it implies a lower cost of separation while allowing to enjoy the gains from being in a couple.
-In the model, a switch from mutual consent to unilateral divorce causes couples to start cohabiting more, since the higher risk of divorce makes the expected value of marriage with respect to cohabitation lower.
-The effect would be particularly pronounced under community property division of assets upon divorce, since the richest part of the couple  would risk to lose most of its wealth.
-This mechanism implies that couples that would have married under the old regime, are cohabiting instead.
-Since those have a higher match quality than the average cohabiting couples, this selection drives down the risk of separation for cohabiting couples, as observed in the data.
-
-We then estimate the model using the simulated method of moments to learn about the size of our main mechanism.
-We use as targets an array of moments regarding the mating market and the differential female labor supply for cohabiting and married couples.
-We find that the model is able to reproduce the results from our empirical evidence, thus validating our mechanism.
-We then run a series of counterfactual experiments to gain intuition about forces that might have contributed to the rise of cohabitation in the last decades.
-[In particular, we quantify the role of the wage structure and technological progress in the household sector, which increases the opportunity cost of home production with female time and decreases the gains coming from labor market specialization.]
-
-The contribution of this paper is threefold.
-First, we document and explain how divorce laws affected the choice between marriage and cohabitation.
-This adds to the existing literature that documented the effects of divorce laws on the rate of divorce (\citealp{friedberg1998}, \citealp{wolfers2006}), female labor supply (\citealp{stevenson2008}, \citealp{voena2015}), savings (\citealp{voena2015}), assortative mating (\citealp{reynoso2019}) and prostitution (\citealp{ciacci2017}) among the others.
-As in \cite{reynoso2019}, we study not only the effect of unilateral divorce on married couples, but also on partnership choice.
-While her focus is on who marries whom and concludes that unilateral divorced raised the share of singles, we abstract from modeling the mating market and we focus on partnership choice, which allow us to conclude that the rate of singleness declined less than previously thought, since some people that were believed not to be in a couple were actually cohabiting.
-Our paper build on \cite{voena2015}, that studies how unilateral divorce interacted with property rights upon divorce affected household behavior of married couples.
-We extend her work both considering cohabitation as an alternative relationship and in analyzing the effects of these laws on sorting.
-Second, our paper expands the literature on cohabitation, showing how the risk of divorce is essential for understanding partnership choices.
-Different papers in the literature highlighted various gains of marriage with respect cohabitation: commitment (\citealp{matouschek2008}), labor specialization within the couple \cite{gemici2014}, learning about match quality \cite{brien2006}, the interaction between the cost of divorce and learning \cite{blasutto2020} and  investment in children \cite{lafortune2019}.
-A paper close to ours is \cite{lafortune2019}, who highlight the role of assets as a collateral that enforces commitment and hence allows for optimal investment in children.
-In their model, a switch from mutual consent to unilateral divorce causes people without wealth to start cohabiting because they are left without a commitment technology.
-While we think that their mechanism is important, it cannot be the whole story since we observe that the switch toward cohabitation was the weakest in title based state, while their model would predict the opposite.
-In this paper we will quantify how much of the shift is due to the erosion of marriage's collateral versus the role of the increased risk of divorce.
-We extend the work of \cite{gemici2014} and \cite{blasutto2020}, who develop collective dynamic models with limited commitment, introducing asset accumulation decisions, which are shown to play an important role for commitment and hence for partnership choice, especially when interacted with property rights upon divorce.\\
-Third, our paper speaks to the literature studying the changes of the family in the last decades.
-Recent works have investigated various channels through which the structure of families might have changed over time.
-\cite{albanesi2016} show the role of improved maternal health on the rise of female labor force participation, \cite{greenwood2016} instead study the role that technology and the wage structure played in the rise in assortative mating, female labor force participation, the share of divorced and the increase in the share of singles.
-Our paper extends this work, studying the effect of wage structure, gender wage gap and changes in the home production technology on the rise of cohabitation.
-Through a series of counterfactual experiments we are able to inspected which were the main forces behind the rise in cohabitation.
-Intuitively, as wages grow and the price of home appliances decreases, household can buy on the the market goods that were once produced at home.
-Since one of the gain of marriage with respect to cohabitation lies in the better specialization of production within the household, we might expect that those forces imply a reduction in the share of couples choosing marriage over cohabitation.
-
-The paper is organized as follows: section 2 offers an overview of US divorce laws, section 3 presents the empirical results, while section 4 describes in detail the theoretical model.
-Section 5 explain the procedure used for the estimation as well as the results.
-Section 6 report the results from a series of counter-factual experiments, while section 7 performs a welfare analysis.
-Section 8 draws the conclusions of the paper.
-
-\section{US Divorce Laws: an Overview}
-\section{Data and Empirical Evidence}
-\subsection{The Dataset}
-We begin by describing our data.
-We use the the National Survey of Family and the Household (NSFH) wave I, and the National survey of Family Growth, 1988 wave.
-Both surveys were designed to study the causes and consequences of changes happening in families and households within the United States.
-This is reflected in detailed question regarding the retrospective family history of respondents, which includes information both about marriage and cohabitation.
-Moreover, primary respondents\footnote{One adult per household was randomly selected as the primary respondent, while in the NSFG respondents are all women of 15-44 years of age.} are asked a large set of questions regarding their socio economic background and the demographics of the household.
-While the NSFH I is the first of three longitudinal waves, NSFG is made of several repeated cross sectional samples.
-We decided not to use the other two other waves of the NSFH because in the second wave all currently cohabiting households were dropped from the survey, while the 1988 wave of NSFG is the only one with publicly available information about the residence of the respondents.
-A drawback of using this data\footnote{We do not have the choice of using other surveys for our analysis, since they either lack the State of residence variable, or they miss information about cohabitation history, or they do not cover people that were in a relationship age at the time the law changed.} is that we know the state of residence of the respondents only at age 16 for the NSFH and at birth for the NSFG.
-Since we also know whether people lived all their life in the same State we are able to perform our empirical analysis both on the universe and of the subsample of never movers.
-We will show that point estimates turn out to be statistically not distinguishable between the two samples.
-Further details regarding those two surveys can be found in \cite{bumpass2017} and \cite{mosher1996}.
-We use this dataset to build two samples, the one of \textit{first and second relationships} and the one of \textit{first cohabitations}, that are described below.
-\subsubsection*{First and Second Relationships Sample}
-We want to build a sample to analyze the type of relationship, which can be either marriage or cohabitation,\footnote{Dating is not considered, since we cannot observe this state.
-Hence, people dating will fall under the category of singles.} that respondents decided to have.
-The sample is made of first and second relationships.
-One first relationship is defined observing the first time (if ever) a certain person started cohabiting or married.
-This observation is associated to the date at which the relationship starts, to the characteristics of the respondent member of the formed couple, and with a \textit{type}, which can either marriage or cohabitation.
-Note the type of couples that cohabited before marriage is "cohabitation": the transition from cohabitation to marriage is analyzed using the sample of \textit{first cohabitations}.
-Second relationships  are defined in a similar fashion, but they include only respondents that ended the relationship with their first partner and started a new one with a different person.
-The way this sample is built implies that for some respondents we will have zero corresponding observations in this sample, while for other we will have other, and for others we will have two.
-We did not consider third or higher order relationships for our analysis since these individuals would be further away from the age at which we knew their state of residence.
-In [FIGURE********] we report the descriptive statistics of this sample.
-\subsubsection*{First Cohabitation Sample}
-This sample is built to analyze the decisions of cohabiting couples to separate or to marry.
-It is composed of the first non marital cohabitation experienced by respondents.
-This sample includes couples that cohabited before marriage, but it also includes cohabitations experienced by people with the following marital history: marriage without premarital cohabitation, divorce, cohabitation with a different person.
-Each observation of this sample is associated with a starting date, a possible ending date, and an outcome, which can be: still cohabiting, married or separated.
-In [FIGURE********] we report the descriptive statistics of this sample.
-\subsection{Empirical Evidence}
-\section{The Model}
-This section describes a dynamic life cycle structural model of partnership formation, savings, female labor supply and  home production.
-Couples act cooperatively subject to limited commitment, which means that rebargaining might happen in response to changes in the outside options, which are assumed to be divorce or separation.
-
-In the model time is discrete, and in each period men and women draw their productivities.
-If single, with some probability they meet a potential partner: after drawing a match quality shock they decide whether to marry, cohabit or to stay single.
-Couples observe realization of the match quality shock as well as of their productivity, and according to those they decide whether to stay together or to split.
-Both singles and couples make consumption and savings decisions, using their money for private or public good expenditure.
-Couples also make female labor supply decisions\footnote{We assume that single females and all men work full time.} and female time can be used to produce the public good, but this comes at the cost of a loss in productivity.
-The gains of being in a couple comes from love, risk sharing and labor market specialization.
-Instead, the gains of marriage with respect to cohabitation comes from a more functioning risk sharing and a better specialization in time use, which derives from the high cost of divorce serving as a commitment device.
-These gains of marriage deteriorates when the love shock is low enough to cause a high risk of divorce and frequent renegotiations: in this case cohabitation might be the better option, since we assume that the cost of separation will be lower than the cost of marriage.
-	   		\begin{figure}[H]\centering
-	\begin{tikzpicture}[domain=0:1,scale=4]
-	\node [block, name=input,align=center] (sum) {Single\\ 7348};
-	\node [block, above right of=sum, node distance=6cm] (controller) {Separation};
-	\node [block, below right of=controller,
-	node distance=6cm,align=center] (system) {Cohabitation \\ 5308};
-	\draw [<-,  thick, latex-] (controller) -| node[below left]{47,8\%}(system);
-	\node [output, right of=system] (output) {fe};
-	\node [block, below left of=system,  node distance=6cm,align=center] (measurements) {Marriage \\ 2814};
-	\node [block, left of=measurements, node distance=4.2cm,align=left] (divorce) {Divorce};
-	\draw [<-,  thick, latex-] (sum) |- node[below right]{100\%} (controller);
-	\draw [->,  thick, -latex] (sum) -- node[above]{72,4\%} (system);
-	\draw [->,  thick, -latex] (system) |-node[above left]{33,8\%} (measurements);
-	\draw [->,  thick, -latex] (measurements) --node[above]{23,5\%} (divorce);
-	\draw [->,  thick, -latex] (sum) --node[above right]{12,9\%} (measurements);
-	\draw [->,  thick, -latex] (divorce) --node[right]{100\%} (sum);
-	node [near end] {$$} (sum);
-	\end{tikzpicture}
-	\label{fig:scheme}
-	\caption*{\footnotesize \textsc{Notes}: Number of spells and transitions as arising from the data in our sample.}
-	\caption{}
-	\end{figure}
-\subsection{Preferences}
-Women $f$ and men $m$ derive utility consuming a private good  $c$ and a household public good $Q$.
-The public good can be interpreted in terms of both the quantity and quality of children, as well as the goods and services produced within the household, as washing clothes  or home cooked meals.
-Preferences are separable in the two goods and across time.
-Agents derives utility from a couple specific love shock $\psi$ which evolves over time and it can be interpreted as  can be interpreted as the value of love and companionship in a couples.
-The intra period utility of a single agent $s\in(f,m)$ is:
-\[u(c^s_t,Q^s_t)=\frac{{c^s_t}^{1-\sigma}}{1-\sigma}+\alpha\frac{{Q^s_t}^{1-\xi}}{1-\xi},\]
-where the superscript $s$ on $Q$ accounts for the fact that there is no partner to share the public good. Instead, the utility for  agent $s\in(f,m)$ in a couple is:
-\[u^{C}(c^s_t,Q_t)=\frac{{c_t^s}^{1-\sigma}}{1-\sigma}+\alpha\frac{Q_t^{1-\xi}}{1-\xi}+\psi_t,\]
-where the match quality evolves over time according to the following law of motion:
-\[\psi_t=\psi_{t-1}+\epsilon_t,\text{ where }\epsilon_t \sim\mathcal{N}(0,\sigma^2_{\psi}), \]
-while the love shock at first meeting is allowed to have a different variance $\sigma^2_{\psi,I}$
-\subsection{Home Production}
-In our model each agent in embodied with one unit of time.
-While singles and married men are assumed to supply inelastically one unit of market labor, females in a couple can be out of the labor force to devote their time producing the home good $Q$.
-The public good can be produced buying $d$ goods in the market.
-Following \cite{greenwood2016} we define the production function of home good as:
-\begin{equation}\label{eq:pfunction}
-Q_t=[d_t^\lambda+\kappa {(1-P^f_t)}^\lambda]^{\frac{1}{\lambda}}, \text{ where }0<\lambda<1.
-\end{equation}
-The parameter $\lambda$ captures the degree of  substitutability between female time and the use of durables in the production of the home good.
-This structure implies that when the relative price of durables decreases and when wages goes up, households will use less female time for its production, and hence female employment will increase.
-The variable  $P^f_t$ is a dummy variable that that takes value $1$ when the women is participating in the labor market.
-
-\subsection{Wages}
-The labor income for agents $s\in\{f,m\}$ depends on their age $t$ and on a permanent income component $z^s_t$:
-\[\ln(w^s_t)=f^s_t+z^s_t,\]
-where $f^s_t$ is a gender specific function that captures the evolution of productivity over age. The permanent income component  $z^s_t$ evolves over time as:
-\begin{equation}\label{eq:pcomp}
-z^s_t=z^s_{t-1}-(1-P_t^s) \mu+\zeta^s_{t}\text{, where }\zeta^s_{t}\sim^{iid}\mathcal{N}(0,\sigma^\zeta)\text{, and }\zeta^s_{1}=z^s_{1}.
-\end{equation}
-Note that $\mu$ is the loss in productivity that affects women\footnote{As we anticipated men always participate in the labor market, hence $P^m_t=1$ $\forall$ $t$.} that are not participating in the labor market.
-It can be be interpreted as a reduced form way of capturing both the missed opportunity to accumulate human capital while working as wells as the skill atrophy deriving from interruptions, a phenomenon described by \cite{adda2017}.
-Modeling the loss in productivity for not working is an important feature of our model as it creates an incentive to join the labor force for women that expect to divorce or separate soon.
-\subsection{Budget Constraints}
-The budget constraint of single agents  $s\in\{f,m\}$ is:
-\begin{equation}\label{eq:bcs}
-a^s_{t+1}=R a^s_t+w^s_t-c^s_t-d^s_t, \text{ with }a^s_{t+1}\geq0,
-\end{equation}
-where $a^s$ are agent's savings, $w^s$ is the wage and $c^s$ and $d^s$ are consumption in the private good and the expenditure used to produce the public good.
-The budget constraint for a couple instead is:
-\begin{equation}\label{eq:bcm}
-a_{t+1}=R a_t+w^m_t+P^f_t w^f_t-c^f_t-c^m_t-d_t, \text{ with }a_{t+1}\geq0,
-\end{equation}
-where $P^F_t$ is a dummy of female labor force participation.
-When a couple divorces in $t$, we assume 
-\[a^m_t+a^f_t=\delta a_t,\]
-where $\delta$ is the fraction of total assets $a_t$ left\footnote{The assumption that divorce erodes a fracction of wealth is common to \cite{cubeddu2003}.} after divorce.
-Separation instead comes with no monetary costs\footnote{In reality the monetary cost of separation is likely to be positive.
-We assumed it to be zero because of the difficulties that arises when it comes to identify it.
-In fact, the gap in divorce and separation cost is what is actually needed to match the data.}.
-An important feature of our model is the role of property rights upon divorce, which define how assets are divided.
-We distinguish three cases which define the share of assets $\chi$ going to the women:
-\begin{enumerate}
-\item \textit{Community Property}. Assets are split exactly in half: $\chi=0.5$
-\item \textit{Equitable Distribution}. $\chi\sim\mathcal{U}(1/3,2/3)$.[WHAT I WISH WE HAD]
-\item \textit{Title Based Regime}. $\chi$ is proportional to the productivity of the women compared to the one of the men, formally
-\[\chi=\frac{\exp{z^f}}{\exp{z^f}+\exp{z^m}}.\]
-\end{enumerate}
-It is worth noting that we depart from \cite{voena2015} in the way title based regime is modeled: she assumes that assets are split following a couple decision, while for us the sharing rule depends only on $z^F$ and $z^M$.
-Since in our model relative productivities are the only source of disagreement.
-If we took the modeling assumption of \cite{voena2015} we would still get that the sharing rule is mainly determined by productivities\footnote{If we had individual specific love shocks, our reduced form modeling assumption would give different results instead.}.
-Moreover, if the sharing rule was endogenous, couples would always choose cohabitation over community property or equitable distribution marriage,\footnote{This would happen because separation would have more degrees of freedom that divorce, where it is the court that decides the sharing rule.} which would make matching the data impossible.
-
-\subsection{Problem of the Singles}
-We start by by describing the problem for a single agent $i\in\{f,m\}$ in $t$.
-The agent have to make consumption and saving decisions, and she is also determining expenditure$d^i_t$.
-In $t+1$ she meets a potential partner $j$ of the opposite sex with probability $\lambda_{t+1}$ and she can decide to enter a partnership, which also depend on whether the potential partner will agree.
-If the two decides to marry, the variable $MA_{t+1}$ will take value 1, while $CO_{t+1}=1$ if the couple decides to cohabit.
-Otherwise, $MA_{t+1}$ and $CO_{t+1}$ will be equal to 0.
-Note we assume singles to always participate in the labor market.
-The state variable of a single then is $\omega^i_t=\{a^i_t,z^i_t\}$, while her choices are represented by the vector $\mathbf{q}^i_t=\{a^i_{t+1},c^i_t,d^i_t\}$.
-We denote by $V_t^{i,S}(\Omega^i_t)$ the value function of agent $s$, which we define as
-\begin{equation}\label{eq:v_single}
-\begin{split}
-V_t^{iS}(\omega^i_t)=&\max_{\mathbf{q}^i_t} u(c^i_t,Q^i_t)+\beta E_t \bigg\{(1-\lambda_t)V^{iS}_{t+1}(\omega^i_{t+1})+\\ & \quad\quad \lambda_t\big\{(1-Ma_{t+1})(1-CO_{t+1})	V^{i,S}_{t+1}(\omega_{t+1})+\\ &\quad\quad\quad\quad M_{t+1} V^{i,M}_{t+1}(\Omega_{t+1})+ CO_{t+1} V^{i,C}_{t+1}(\Omega_{t+1}) \big\}\bigg\},
-\\ &\text{s.t. \eqref{eq:bcs} and \eqref{eq:pfunction}.} 
-\end{split}
-\end{equation}
-
-\subsection{Household Planning Problem}
-The problem of the couple depends both on the type of relationship, cohabitation or marriage, and on the divorce regime, which can be either \textit{mutual consent} or \textit{unilateral}.
-Separation is always unilateral.
-Under the unilateral regime, one partner can initiate the separation/divorce process alone, while under mutual consent the agreement of both is needed.
-\subsubsection*{Mutual Consent Regime}
-Under mutual consent marriage $\hat{M}$, couples solve a Pareto problem where the weight\footnote{Refer to \autoref{ssec:marriage_market} for a description about how pareto weight are initially set.} of the wife is $\theta^f$, while the one of the husband is $1-\theta^f$.
-The state vector is $\Omega^{\hat{M}}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^M_t=\{a_{t+1},d_{t},c^m_{t},c^f_{t},P^f_t,D_t\}$, where $D_t$ is a dummy variable that takes value $1$ is divorce happens and $0$ otherwise.
-The formal problem that a couple married is $t$ solve is:
-\begin{equation}\label{eq:v_mutual}
-\begin{split}
-V_t^{\hat{M}}(\Omega^{\hat{M}}_t)=&\max_{\mathbf{q}^M_t} (1-D_t)\{\theta^f u(c^f_t,Q_t)+(1-\theta^f)u(c^m_t,Q_t)+\psi_t+\beta E_t V^{\hat{M}}_{t+1}(\Omega^{\hat{M}}_{t+1})\}\\ &\quad\quad+D_t \{\theta^fV^{fS}_{t}(\omega^{f}_{t+1})+(1-\theta^m)  V^{mS}_{t}(\omega^{m}_{t}))\}
-\\ &\text{if $D_t=0$:}\hspace{35pt}\text{s.t. \eqref{eq:bcm} and \eqref{eq:pfunction}
-}
-\\ &\text{if $D_t=1$:}\hspace{35pt}\text{s.t. \eqref{eq:bcs}, \eqref{eq:pfunction} for $i\in\{f,m\}$,}\\ &
-\hspace{80pt}a_t^m+a_t^f=\delta a_t,	\\ &
-\hspace{80pt}a_t^m,a_t^f\text{ determined according to property right regime,}	\\ &\hspace{80pt}
-V_{t}^{fS}(\omega^f_{t})> W^{f\hat{M}}_{t}(\Omega^{\hat{M}}_{t}),\\ &\hspace{80pt}
-V_{t}^{mS}(\omega^m_{t})> W^{m\hat{M}}_{t}(\Omega^{\hat{M}}_{t}).
-\end{split}
-\end{equation}
-The individual value of marriage conditional on $D_t=0$ is $W_{t}^{i\hat{M}}$ for $i\in\{F,M\}$, and it is defined as 
-\begin{equation}
-W_{t}^{i\hat{M}}=u(\tilde{c}_t^{i},\tilde{Q}_t)+\psi_t+\beta E_t V_{t}^{i\hat{M}}(\Omega^{\hat{M}}_{t+1}),
-\end{equation}
-where $\mathbf{\tilde{q}}^{\hat{M}}_t=\{\tilde{a}_{t+1},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$ is the $\argmax$ of problem \eqref{eq:v_mutual} conditionally on having chosen $D_t=0$.
-$V_{t+1}^{i\hat{M}}(\Omega^{\hat{M}}_{t+1})$ instead can be obtained by the expectation of the sum of the time utilities that the agent get from $t+1$ to $T$, where the variables entering the utility function derive derive from the the pareto problem if the agent is in a relationship, otherwise they are the solution of \eqref{eq:v_single}.
-Under mutual consent regime the pareto weight is never rebargained, which makes risk sharing efficient.
-It also makes harder a divorce to happen, since the member that after a shock is relatively worse off can exercise her veto power to avoid a divorce: this feature makes labor specialization easier.
-\subsubsection*{Unilateral Divorce Regime}
-Under the unilateral divorce regime, denoted by $\overline{M}$, couples solve a Pareto problem where the weight of the wife is $\theta^f_t$ and the one of the husband is $\theta^m_t$.
-Note that, in opposition to the mutual consent regime, now pareto weights are allowed to vary over time.
-This happes whenever a member of the couple is better off divorcing: the other member will try to convinve her not to split offering her a larger share of resources.
-The state vector of this proble is $\Omega^{\overline{M}}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^M_t$.
-The formal problem that a couple married at $t$ solves is:
-\begin{equation}\label{eq:v_uni}
-\begin{split}
-V_t^{\overline{M}}(\Omega^{\overline{M}}_t)=&\max_{\mathbf{q}^M_t} (1-D_t)\{\theta^f_{t+1} u(c^f_t,Q_t)+\theta^m_{t+1} u(c^m_t,Q_t)+\psi_t+\beta E_t V^{\overline{M}}_{t+1}(\Omega^{\overline{M}}_{t+1})\}\\ &\quad\quad+D_t \{\theta^f_{t}V^{fS}_{t}(\omega^{f}_{t+1})+\theta^m_{t} V^{mS}_{t}(\omega^{m}_{t}))\}
-\\ &\text{if $D_t=0$:}\hspace{35pt}\text{s.t. \eqref{eq:bcm} and \eqref{eq:pfunction},}\\ &\hspace{80pt}
-\theta^f_{t+1}=\theta^f_{t}+\mu^f_t,\\ &\hspace{80pt}
-\theta^m_{t+1}=\theta^m_{t}+\mu^m_t,
-\\ &\text{if $D_t=1$:}\hspace{35pt}\text{s.t. \eqref{eq:bcs}, \eqref{eq:pfunction} for $i\in\{f,m\}$,}\\ &
-\hspace{80pt}a_t^m+a_t^f=\delta a_t,	\\ &
-\hspace{80pt}a_t^m,a_t^f\text{ determined according to property right regime},
-\end{split}
-\end{equation}
-where $\theta^f_{t+1}$ and $\theta^m_{t+1}$ adjust such that the following participation constraints are satisfied:
-\begin{equation}\label{eq:p_cons_mar}
-\begin{split}
-&
-W^{f\overline{M}}_{t}(\Omega^{\overline{M}}_{t})\geq V_{t}^{fS}(\omega^f_{t}),\\ &
-W^{m\overline{M}}_{t}(\Omega^{\overline{M}}_{t})\geq V_{t}^{mS}(\omega^m_{t}). 
-\end{split}
-\end{equation}
-Note that $\mu^i_t$ are the langrange multipliers associated with spouses' participation constraints.
-Similarly to mutual consent regime, the individual value of marriage conditional on $D_t=0$ is  $W_{t}^{i\overline{M}}$ for $i\in\{f,m\}$, and it is defined as 
-\begin{equation}
-W_{t}^{i\overline{M}}=u(\tilde{c}_t^{i},\tilde{Q}_t)+\psi+\beta E_t V_{t+1}^{i\overline{M}}(\Omega^{\overline{M}}_{t+1}),
-\end{equation}
-where
-$\mathbf{\tilde{q}}^{\overline{M}}_t=\{\tilde{a}_{t+1},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$ is the $\argmax$ of problem \eqref{eq:v_mutual} conditionally on having chosen $D_t=0$.
-$V_{t+1}^{i\hat{M}}(\Omega^{\overline{M}}_{t+1})$ instead can be obtained by the expectation of the sum of the time utilities that the agent get from $t+1$ to $T$, where the variables entering the utility function derive derive from the the pareto problem if the agent is in a relationship, otherwise they are the solution of \eqref{eq:v_single}.
-Note that we follow the literature assuming that the planner evaluates the welfare of the two members of the couple if a divorce happens with the current Pareto weights.
-Under the unilaral divorce regime pareto weights varies every time one participation constraint is binding, which makes risk sharing worse than in the mutual divorce regime.
-Labor market specialisation is also less functioning, since the higher risk of divorce makes women willing to insure against this event through labor market participation.
-Property rights upon divorce plays a significative role when splitting is unilateral: for example under community propery the least wealthy member can bargain a higher share of resources since the threat of divorce is real.
-This could not happen under a title based regime.
-\subsubsection*{Cohabitation}
-Cohabiting couples, denoted by $C$, solve a pareto problem where the weight of the wife is $\theta^f_t$ and the one of the husband is $\theta^m_t$.The state vector is $\Omega^{C}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^C_t=\{a_{t+1},d_t,c^m_t,c^f_t,P^f_t,S_t,MA_t\}$.
-$S_t$ and ${MA}_t$ are dummy variable that take value $1$ is the couple respectively separate of marry\footnote{We denote marriage by $M$, which might be fall under unilateral divorce regime $\overline{M}$ or mutual consent $\hat{M}$.} and 0 otherwise.
-The formal problem that a cohabiting couple at $t$ solves is:
-\begin{equation}\label{eq:v_coh}
-\begin{split}
-V_t^{C}(\Omega^{C}_t)=&\max_{\mathbf{q}^C_t} (1-S_t)\{\theta^f_{t+1} u(c^f_t,Q_t)+\theta^m_{t+1} u(c^m_t,Q_t)+\psi_t+\beta E_t V^{C}_{t+1}(\Omega^{C}_{t+1})\}
-\\ &\quad\quad+MA_t\{\theta^f_{t+1} u(c^f_t,Q_t)+\theta^m_{t+1} u(c^m_t,Q_t)+\psi_t+\beta E_t V^{M}_{t+1}(\Omega^{M}_{t+1})\}\\ &\quad\quad\quad\quad+S_t \{\theta^f_{t}V^{fS}_{t}(\omega^{f}_{t+1})+\theta^m_{t} V^{mS}_{t}(\omega^{m}_{t}))\}
-\\ &\text{if $S_t=0$:}\hspace{35pt}\text{s.t. \eqref{eq:bcm} and \eqref{eq:pfunction},}\\ &\hspace{80pt}
-\theta^f_{t+1}=\theta^f_{t}+\mu^f_t,\\ &\hspace{80pt}
-\theta^m_{t+1}=\theta^m_{t}+\mu^m_t,
-\\ &\text{if $S_t=1$:}\hspace{35pt}\text{s.t. \eqref{eq:bcs}, \eqref{eq:pfunction} for $i\in\{f,m\}$,}\\ &
-\hspace{80pt}a_t^m+a_t^f= a_t,	\\ &
-\hspace{80pt}a_t^m,a_t^f\text{ determined as in the title based regime},
-\end{split}
-\end{equation}
-where $\theta^f_{t+1}$ and $\theta^m_{t+1}$ adjust such that the following participation constraints are satisfied:
-\begin{equation}\label{eq:p_cons_coh}
-\begin{split}
-&
-W^{fC}_{t}(\Omega^{C}_{t})\geq V_{t}^{fS}(\omega^f_{t}),\\ &
-W^{mC}_{t}(\Omega^{C}_{t})\geq V_{t}^{mS}(\omega^m_{t}). 
-\end{split}
-\end{equation}
-Note that $\mu^i_t$ are the langrange multipliers associated with spouses' participation constraints.
-The individual value of cohabitation conditional on $S_t=$ is  $W_{t}^{iC}$ for $i\in\{f,m\}$, and it is defined as 
-\begin{equation}
-W_{t}^{iC}=u(\tilde{c}_t^{i},\tilde{Q}_t^{i})+\psi_t+\beta E_t V_{t+1}^{iC}(\Omega^{C}_{t+1}),
-\end{equation}
-where
-$\mathbf{\tilde{q}}^{C}_t=\{\tilde{a}_{t+1},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$ is the $\argmax$ of problem \eqref{eq:v_mutual} conditionally on having chosen $S_t=0$.
-$V_{t+1}^{iC}(\Omega^{C}_{t+1})$ instead can be obtained by the expectation of the sum of the time utilities that the agent get from $t+1$ to $T$, where the variables entering the utility function derive derive from the the pareto problem if the agent is in a relationship, otherwise they are the solution of \eqref{eq:v_single}.
-Similarly to the unilateral divorce regime, we assume that the planner evaluates the welfare of the two members of the couple if a separation happens with the current Pareto weights.
-
-The cohabitation problem is similar to the one of marriage under the unilateral divorce regime, but two main features are different.
-First, the way assets are split within cohabitation might not be the same, and total assets are not eroded when separation happens.
-On the one hand this makes risk sharing and cooperation less functioning than in marriage with unilateral divorce, since the couple is left without a commitment-enhancing technology.
-On the other hand, assuming no cost of separation makes cohabitation more appealing to couples with a low surplus of being in a couple.
-Since for them splitting if very likely, they prefer the relationship that allow them to do it in a cheaper way.
-
-\subsection{Partnership Choice and the Mating Market}\label{ssec:marriage_market}
-In each period $t$ singles have a probability $\lambda_t$ to meet a potential partner of their same age and with a productivity and wealth that depends on their productivity $z_t$ and assets $a_{t}$.
-Formally:
-\begin{equation}\label{mma}
-\ln(a^p_t)=\ln(a_{t})+\hat{\epsilon}\text{, where }\hat{\epsilon}\sim\mathcal{N}(0,\sigma^2_{\hat{p}}),
-\end{equation}
-\begin{equation}\label{mmz}
-z^p_t=z_{t}+\tilde{\epsilon}\text{, where }\tilde{\epsilon}\sim\mathcal{N}(0,\sigma^2_{\tilde{p}}).
-\end{equation}
-These assumptions allow us to capture in a reduced from fashion that people are mating assortatively\footnote{In the life cycle models featured in \cite{ciscato2019}, \cite{shephard2019} and \cite{reynoso2019} assortative mating arise in marriage markets through the interactions of preferences, incentives, supply and demand forces.} both within marriage and cohabitation, as \cite{gemici2014} point out.
-Once the meeting happened, agents have to decide whether to stay in a couple and eventually decide which partnership contract to choose.
-Note that for the rest of this section we will refer to marriage as $M$, but depending on property rights upon divorce we have $M \ \in\{\hat{M},\overline{M}\}$.
-We model their choices in three steps.
-\begin{enumerate}
-\item The couple considers marriage $M$ (cohabitation $C$) as a viable alternative if the set of pareto weights\footnote{Without loss of generality, we impose $\theta^f+\theta^m=1$ at first meeting.} $\theta^f$ such that the couple prefers to marry (cohabit) is non-empty.
-Formally, for relationship $J\in\{M,C\}$ the set is
-\begin{equation}\label{eq:set_couple}
-\Theta^J_t(\Omega^J_t,\omega^f_t,\omega^m_t)=\big\{\theta_t: V_t^{fJ}(\Omega^J_t)\geq V_t^{fS}(\omega^f_t), V_t^{mJ}(\Omega^J_t)\geq V_t^{mS}(\omega^m_t)\big\}.
-\end{equation}
-\item If the set for marriage (cohabitation) is non-empty, the pareto weight for the potential marriage $\theta^{m,f}$ (cohabitation $\theta^{c,f}$) is set through symmetric Nash Bargaining.\footnote{The assumption that the initial pareto weight is pinned down by Nash Bargaining can be found in \cite{low2018}.} Formally\footnote{For consistency with the rest of the paper we define $\Omega^{J,-1}_t$ as the state vector for the couple excluding pareto weights.}, for $J\in\{M,C\}$ $\theta^{J,f}$ is set to :
-\begin{equation}\label{nash_couple}
-\theta^{J,f}_t= \argmax_{\theta^f_t\in\Theta^J_t} \Upsilon^J(\theta^f_t,\Omega^{J,-1}_t,\omega^f_t,\omega^m_t),
-\end{equation}
-where
-\begin{equation}
-\Upsilon^J(\theta^f_t,\Omega^{J,-1}_t,\omega^f_t,\omega^m_t)=\big[V_t^{fJ}(\Omega^{J,-1}_t)- V_t^{fS}(\omega^f_t)\big]\times\big[ V_t^{mJ}(\Omega^{J,-1}_t)- V_t^{mS}(\omega^m_t)\big].
-\end{equation}
-\item Four possible situation can arise:
-\begin{itemize}
-\item $\Theta^M_t=\O\text{ and }\Theta^C_t=\O \Rightarrow$ stay single.
-\item $\Theta^M_t\neq\O\text{ and }\Theta^C_t=\O \Rightarrow$ marry.
-\item $\Theta^M_t=\O\text{ and }\Theta^C_t\neq\O \Rightarrow$ cohabit.
-\item $\Theta^M_t\neq\O\text{ and }\Theta^C_t\neq\O \Rightarrow$ The couple chooses the partnership that gives the largest Nash product.
-Formally, if $ \Upsilon^M(\Omega^M_t,\omega^f_t,\omega^m_t)\geq\Upsilon^C(\Omega^C_t,\omega^f_t,\omega^m_t)$, otherwise cohabit.
-\end{itemize}
-This framework is a natural extension of the nash bargaining problem\footnote{Note that we could have chosen a different protocol for determining the choice between marriage and cohabitation.
-For example, we could have decided to impose a sequential structure to the problem, assuming that first agents compare cohabitation to singleness, obtaining the envelop of the two, where the pareto weight is set as above.
-Then, the agents make their final choice solving a pareto problem where the outside option is the outcome of the first step.
-We tried applying this methodology: results were indistinguishable from our main strategy.} to discrete choices [CITATION OF RELEVANT PAPER HERE].
-\end{enumerate}
-\section{Estimation}
-\section{Counterfactual Experiments}
-\section{Welfare Analysis}
-\section{Conclusion}
-
-\bibliographystyle{achicago}
-\bibliography{mybibliography}
-
-\appendix
-\counterwithin{figure}{section}
-\counterwithin{table}{section}
-\section*{Appendix}
-\section{Computational Appendix}
-\cite{arnoud2019}+\cite{cartis2019}
-\section{Estimation of Income Processes}
 

### 2020-09-28 draft_sub_con.tex
latest

--- 2020-02-12 draft_sub_con.tex
@@
-% !TEX TS-program = pdflatex
-% !TEX encoding = UTF-8 Unicode
-
-% This is a simple template for a LaTeX document using the "article" class.
-% See "book", "report", "letter" for other types of document.
 \documentclass[12pt]{article}
+%\documentclass[AEJ]{AEA}
 \usepackage[round, sort , authoryear]{natbib}
+
+\usepackage{pgf}
+%%% PAGE DIMENSIONS
+\usepackage[margin=2cm]{geometry}
+%\usepackage[top=1.5in, bottom=1.5in, left=1.5in, right=1.5in]{geometry}
+\usepackage{blindtext} % to change the page dimensions
+%\geometry{a4paper} % or letterpaper (US) or a5paper or....
+%\geometry{margin=1.5in} % for example, change the margins to 2 inches all round
+% \geometry{landscape} % set up the page for landscape
+%   read geometry.pdf for detailed page layout information
 
@@
 
-\renewcommand\theadalign{bc}
-\renewcommand\theadgape{\Gape[4pt]}
-\renewcommand\cellgape{\Gape[4pt]}
+%Write a vecor
+\newcommand{\myvec}[1]{\ensuremath{\begin{pmatrix}#1\end{pmatrix}}}
 
@@
 %%% PAGE DIMENSIONS
-\usepackage[margin=2.5 cm]{geometry}
-\usepackage{blindtext} % to change the page dimensions
-\geometry{a4paper} % or letterpaper (US) or a5paper or....
-% \geometry{margin=2in} % for example, change the margins to 2 inches all round
+%\usepackage[margin=2.5 cm]{geometry}
+%\usepackage{blindtext} % to change the page dimensions
+%\geometry{a4paper} % or letterpaper (US) or a5paper or....
+%\geometry{margin=1.5cm} % for example, change the margins to 2 inches all round
 % \geometry{landscape} % set up the page for landscape
@@
 \usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
+
 % These packages are all incorporated in the memoir class to one degree or another...
-\usepackage{amsmath}
+%\usepackage{amsmath}
 \numberwithin{table}{section}
@@
 
+%No Counting within section
+\DeclareCaptionLabelSeparator{none}{}
+\captionsetup{labelsep=none}
+\counterwithout{figure}{section}
+\counterwithout{table}{section}
+
+%footnote space
+\setlength{\footnotesep}{0.35cm}
+\interfootnotelinepenalty=10000
+
+%Nice Figure and table headers
+\captionsetup[figure]{labelfont={sc},name={Figure},labelsep=period}
+\captionsetup[table]{labelfont={sc},name={Table},labelsep=period,justification=centering}
+
 %For subtables
 \usepackage{subcaption}
-
+\usepackage[justification=centering]{caption}
 %For having the catption above tables
@@
 
+%For bar charts in table
+\newlength\MAX  \setlength\MAX{20mm}
+\newcommand*\Chart[1]{#1~\rlap{\textcolor{blue!20}{\rule{#1\MAX}{2ex}}}}
+%\newcommand*\Chartguys[1]{\rlap{\textcolor{blue!30}{\rule{6ex}{\MAX}}}{\textcolor{white!30}{\rule{6ex}{#1\MAX}}}}
+%\newcommand*\Chartgirls[1]{\rlap{\textcolor{red!30}{\rule{6ex}{\MAX}}}{\textcolor{white!30}{\rule{6ex}{#1\MAX}}}}
+\newcommand*\Chartguys[1]{{\textcolor{blue!30}{\rule{6ex}{#1\MAX}}}}
+\newcommand*\Chartgirls[1]{{\textcolor{red!30}{\rule{6ex}{#1\MAX}}}}
+
+\renewcommand{\thesubfigure}{ (\alph{subfigure})}
+\captionsetup[sub]{labelformat=simple}
 %Math stuff
@@
 
-\restylefloat{table}
-\oddsidemargin  +0.18in
-\evensidemargin +0.18in
-\topmargin 40pt \textheight 8.1in \textwidth 6.5in
-\linespread{1.5}\parskip .05in
+%\restylefloat{table}
+%\oddsidemargin  +0.18in
+%\evensidemargin +0.18in
+%\topmargin 40pt \textheight 8.1in \textwidth 6.5in
+%\linespread{1.5}\parskip .05in
 
 %Nice Figure and table headers
-\captionsetup[figure]{labelfont={sc},name={Figure},labelsep=period}
-%\captionsetup[table]{labelfont={sc},name={Table},labelsep=period,justification=centering}
+\captionsetup[figure]{labelfont={sc},name={Figure},labelsep=none}
+\captionsetup[table]{labelfont={sc},name={Table},labelsep=none,justification=centering}
 
@@
 %\parskip3mm\parindent0cm
-\setlength{\droptitle}{-10em}   % This is your set screw
-
-\title{Unilateral Divorce and the Rise of Informal Cohabitation\thanks{The authors wish to thank Matthias Doepke, Alessandra Voena and the Norhtwestern Macro group for their useful comments.
-Blasutto acknowledges financial support from the French speaking community of Belgium (ARC project 15/19-063 on "family transformations").}}
-\author{Fabio Blasutto$^1$ \quad Egor Kozlov$^2$}
+
+\title{The Rise of Cohabitation and Unilateral Divorce\thanks{The authors wish to thank David de la Croix, Matthias Doepke, Fabio Mariani, Jesús Fernández-Villaverde, Alessandra Voena and the Norhtwestern Macro group for their useful comments.
+Computational resources were provided by the supercomputing facilities of the Université catholique de Louvain (CISM/UCL) and Northwestern University.
+Blasutto acknowledges financial support from the French speaking community of Belgium (ARC project 15/19-063 on \textit{family transformations} and \textit{mandat d' aspirant} FC 23613).}}
+\author{\large Fabio Blasutto$^1$ \quad Egor Kozlov$^2$}
+\date{}
 
@@
 
-	\footnotetext[1]{IRES, UCLouvain \& National Fund for Scientific Research (Belgium). Email:  \tt{fabio.blasutto@uclouvain.be}}
+\vspace{-2cm}
+\begin{center}\large	
+	Job Market Paper\\
+	\href{https://drive.google.com/file/d/1utFkMPdUR5yb07oyJI7Vx1BJDLfYgMHi/view?usp=sharing}{Latest version available here}
+\end{center}
+\begin{center}\large
+	\today
+\end{center}
+
+	\footnotetext[1]{IRES/LIDAM, UCLouvain \& FNRS (Belgium). Email:  \tt{fabio.blasutto@uclouvain.be}}
 	\footnotetext[2]{Northwestern Univrsity. Email:  \tt{egorkozlov2020@u.northwestern.edu}.\\}
 
+%\begin{abstract}
+%	Marriage differs from informal cohabitation for its higher cost of breaking up.
+Moving from a mutual to a unilateral divorce regime drastically increases the risk of dissolution.
+We explore how this change affects partnership choice and the relative power within the couple.
+Exploiting the staggered introduction of unilateral divorce across the US states, we show that after the reform newly formed relationships are significantly more likely to be cohabitations instead of marriages, and that cohabitation spells last longer.
+To understand the drivers of these changes, we build and estimate a structural life cycle model with partnership choice, female labor supply and savings decisions, where the gains of marriage with respect to cohabitation come from a better risk sharing and specialization within the household, enforced through a costly divorce.
+In the model, the reform increases the risk of divorce, making cohabitation preferred by couples that would have had the highest risk of divorce under the mutual consent regime.
+Since the match quality of cohabitations is on average lower than that of marriages, the reform increases their length: we estimate that time spent cohabiting would have been four times lower if the law had never changed.
+In states where assets upon divorce are split equally, men would lose most of their wealth upon divorce: at equilibrium, many women accept to cohabit in exchange for a higher bargaining power.
+%\end{abstract}
+
+%\begin{abstract}
+%	This paper analyzes the role of unilateral divorce for the rise in cohabitation.
+Exploiting the staggered introduction of unilateral divorce across the US states, we show that after the reform singles become more likely to cohabit than to marry, and that newly formed cohabitation spells last longer.
+We then provide a theoretical rationale for these facts, building a life-cycle model with partnership choice, female labor supply and saving decisions.
+A structural estimation of the model suggests that the decline in marriage is due to an increased risk of divorce, while new cohabitation spells last longer for a selection effect.
+A counterfactual experiment reveals that time spent cohabiting would have been four times lower if divorce law had never changed.
+%\end{abstract}
+
+%\begin{abstract}
+%	This paper analyzes the role of unilateral divorce for the rise of cohabitation.
+Exploiting the staggered introduction of unilateral divorce across the US states, we show that after the reform singles become more likely to cohabit than to marry, and that newly formed cohabitation spells last longer.
+We then provide a theoretical rationale for these facts, building a life-cycle model with partnership choice, female labor supply and saving decisions.
+A structural estimation of the model suggests that unilateral divorce reduces the gains from marriage, making cohabitation preferred to couples that would have had the highest risk of divorce.
+Since married couples are on average better matched, the reform increases the length of newly formed cohabitations because of a selection effect.
+A counterfactual experiment reveals that time spent cohabiting would have been four times lower if divorce law had never changed.
+%\end{abstract}
+
 \begin{abstract}
-	Does unilateral divorce eroded the gains of marriage with respect to informal cohabitation?
-Exploiting the staggered introduction of unilateral divorce across U.S.
-states, we show that after the reform newly formed relationships are more likely to be cohabitations instead of marriages, and that cohabitation spells last longer.
-To understand the mechanisms underlying the law changes, we build and estimate a structural life cycle model with partnership choice, where the gains from marriage with respect to cohabitation come from a better cooperation within the household, enforced through a costly divorce, which acts as a commitment technology.
-In the model the reform increase the risk of divorce, making cohabitation preferred to couples that would have had the highest risk of divorce.
-Since the couples switching relationship are on average better matched than the average cohabitants, the length of cohabitations increases.
+	This paper analyzes the role of unilateral divorce for the rise of cohabitation.
+Exploiting the staggered introduction of unilateral divorce across the US states, we show that after the reform singles become more likely to cohabit than to marry, and that newly formed cohabitations last longer.
+We then provide a theoretical rationale for these facts, building a life-cycle model with partnership choice, female labor force participation and saving decisions.
+A structural estimation of the model suggests that unilateral divorce decreases couples' stability, which makes cohabitation preferred to couples that would have been at high risk of divorce.
+Since cohabiting couples formed after the reform are better matched, the average length of cohabitations increases.
+A counterfactual experiment reveals that the time spent cohabiting would have been halved if divorce laws had never changed.
 \end{abstract}
-\textbf{Keywords}: Marriage, Cohabitation, Unilateral Divorce, Structural Estimation\\
-\textbf{JEL-Code}: D83 - J12
+
 %\clearpage
 %\noindent \medskip{}
+\clearpage
 \section{Introduction}
-Cohabitation is on the rise: according to \cite{manning2013}, the share of women that ever cohabited moved from 33\% in 1987 to 60\% in 2010. Why did this happen?
-Since the seminal work of Becker (\citealp{becker1981}), economists studied the incentives behind the decision to marry, among which the sharing of public goods, the division of labor to exploit comparative advantages (\citealp{chiappori1997}), and risk sharing (\citealp{voena2015} and \citealp{rigas2015}).
-These reasons tell us why couples live together, while they are actually silent about the choice between marriage and informal cohabitation, two partnership contracts subject to different rules.
-While the literature often simplifies, avoiding the distinction between these two, they display a different labor supply, wealth accumulation and educational composition.
-It is not surprising that households, the smallest economic unit, can behave differently when the contract ruling them is different, but this can be the key to understand important economic phenomena.
-For example, cohabitation display a much higher separation rate than marriages, which might be a cause of the high share of single mothers living in the US nowadays, which is the single strongest predictor for upward mobility\footnote{While the share of single mothers is the strongest predictor of differences in upward mobility across counties on top of segregation, residential segregation, income inequality, social capital, school quality, and racial shares, \cite{chetty2018} points out that half of this effect is due to self selection.} according to \cite{chetty2018}.
-If we want to understand the behavior of cohabiting households and the implication of it, we first need to understand their formation and why they are growing in number.
-
-In this paper we address the question of the rise of cohabitation, focusing on the role of unilateral divorce on the share of people that decides to cohabit.
-Our main contribution is to show that the rate of cohabitation increased after the changes in the US law and that the underlying mechanism is that the increased risk of divorce makes marriage less attractive.
-As a consequence, cohabitation becomes the preferred choice to couples that would have experienced the highest risk of divorce.
-As a consequence, the average match quality of cohabiting couples increase, which increases the length of cohabitation spells.
-
-We first use data from the National Survey of Family and the Household and of the National Survey of Family Growth to build a sample of first and second relationships\footnote{A relationship is defined as an interruption of the state of singleness, which can either be marriage or cohabitation.}.
-Then, exploiting the exogenous variation coming from the staggered introduction of unilateral divorce over time across US states, we show that cohabitation becomes around 5\% more likely  to be chosen compared to the pre-reform period.
-Interestingly,  the effect is heterogeneous on how property is divided upon divorce, being strongest in states where each spouse gets half of the wealth.
-This suggest that the result cannot be entirely due to a deterioration of divorce as a commitment technology\footnote{This mechanism is highlighted by \cite{lafortune2019}, where the equal division of assets within marriage makes possible to efficiently invest in children even after the rise of unilateral divorce.}, since the egalitarian property division rule can act as a substitute of the mutual consent regime.
-Moreover, we analyze how unilateral divorce affected the length of newly formed cohabitation spells, showing that they last longer both because of a reduced risk of marriage and separation.
-To understand the mechanisms that lead to these changes we build a dynamic model of intrahousehold decision making, where cohabitation and marriage differ in their splitting cost as well as in the way property is divided.
-While in the case of separation assets are always split as an agreement between spouses, in the case of divorce in some states it is the judge to decide.
-Moreover, separation can be initiated unilaterally, as opposed to divorce, that would need the consensus of both partner under a mutual divorce regime.
-Individuals are initially single, and with some probability in each period they meet a potential partner, which they can decide to marry or start cohabiting with.
-Couples make decisions about consumption, savings and female labor supply and they are subject to idiosyncratic income shocks.
-Couples also receive time varying match quality shocks, which might drive the couple to change their partnership status (i.e.
-from cohabitation to marriage) or to separate.
-We model the decision making in the couple building on the literature of limited commitment (see for example \cite{kk1996},  \cite{ligon2002}, \cite{marcet2019} and \cite{pavoni2018}), which has been applied to dynamic collective models in the household by \cite{voena2015}, \cite{mazzocco2007}, \cite{foerster2019} and \cite{lise2018} among others.
-In this framework, when one member of the couple wishes to split, the couple rebargains such that the binding member is made indifferent between separation and staying in a couple\footnote{For particularly bad draws in the match quality or productivity shock this might not be possible and hence the couple would split.}.
-The gains of marriage with respect to cohabitation come from a better risk sharing and a more efficient specialization in the production of a public good\footnote{We assume that a public good is produced with money an female time.
-When females stop working for producing such good their potential productivity in the labor market decreases.}, which arise from a better commitment within the couple, enforced by the threat of a costly divorce, which acts as a commitment device.
-On the other hand, couples that would face a high risk of divorce if married (i.e.
-because of a low match quality draw) are more likely to choose cohabitation instead, since it implies a lower cost of separation while allowing to enjoy the gains from being in a couple.
-In the model, a switch from mutual consent to unilateral divorce causes couples to start cohabiting more, since the higher risk of divorce makes the expected value of marriage with respect to cohabitation lower.
-The effect would be particularly pronounced under community property division of assets upon divorce, since the richest part of the couple  would risk to lose most of its wealth.
-This mechanism implies that couples that would have married under the old regime, are cohabiting instead.
-Since those have a higher match quality than the average cohabiting couples, this selection drives down the risk of separation for cohabiting couples, as observed in the data.
-
-We then estimate the model using the simulated method of moments to learn about the size of our main mechanism.
-We use as targets an array of moments regarding the mating market and the differential female labor supply for cohabiting and married couples.
-We find that the model is able to reproduce the results from our empirical evidence, thus validating our mechanism.
-We then run a series of counterfactual experiments to gain intuition about forces that might have contributed to the rise of cohabitation in the last decades.
-[In particular, we quantify the role of the wage structure and technological progress in the household sector, which increases the opportunity cost of home production with female time and decreases the gains coming from labor market specialization.]
-
-The contribution of this paper is threefold.
-First, we document and explain how divorce laws affected the choice between marriage and cohabitation.
-This adds to the existing literature that documented the effects of divorce laws on the rate of divorce (\citealp{friedberg1998}, \citealp{wolfers2006}), female labor supply (\citealp{stevenson2008}, \citealp{voena2015}), savings (\citealp{voena2015}), assortative mating (\citealp{reynoso2019}) and prostitution (\citealp{ciacci2017}) among the others.
-As in \cite{reynoso2019}, we study not only the effect of unilateral divorce on married couples, but also on partnership choice.
-While her focus is on who marries whom and concludes that unilateral divorced raised the share of singles, we abstract from modeling the mating market and we focus on partnership choice, which allow us to conclude that the rate of singleness declined less than previously thought, since some people that were believed not to be in a couple were actually cohabiting.
-Our paper build on \cite{voena2015}, that studies how unilateral divorce interacted with property rights upon divorce affected household behavior of married couples.
-We extend her work both considering cohabitation as an alternative relationship and in analyzing the effects of these laws on sorting.
-Second, our paper expands the literature on cohabitation, showing how the risk of divorce is essential for understanding partnership choices.
-Different papers in the literature highlighted various gains of marriage with respect cohabitation: commitment (\citealp{matouschek2008}), labor specialization within the couple \cite{gemici2014}, learning about match quality \cite{brien2006}, the interaction between the cost of divorce and learning \cite{blasutto2020} and  investment in children \cite{lafortune2019}.
-A paper close to ours is \cite{lafortune2019}, who highlight the role of assets as a collateral that enforces commitment and hence allows for optimal investment in children.
-In their model, a switch from mutual consent to unilateral divorce causes people without wealth to start cohabiting because they are left without a commitment technology.
-While we think that their mechanism is important, it cannot be the whole story since we observe that the switch toward cohabitation was the weakest in title based state, while their model would predict the opposite.
-In this paper we will quantify how much of the shift is due to the erosion of marriage's collateral versus the role of the increased risk of divorce.
-We extend the work of \cite{gemici2014} and \cite{blasutto2020}, who develop collective dynamic models with limited commitment, introducing asset accumulation decisions, which are shown to play an important role for commitment and hence for partnership choice, especially when interacted with property rights upon divorce.\\
-Third, our paper speaks to the literature studying the changes of the family in the last decades.
-Recent works have investigated various channels through which the structure of families might have changed over time.
-\cite{albanesi2016} show the role of improved maternal health on the rise of female labor force participation, \cite{greenwood2016} instead study the role that technology and the wage structure played in the rise in assortative mating, female labor force participation, the share of divorced and the increase in the share of singles.
-Our paper extends this work, studying the effect of wage structure, gender wage gap and changes in the home production technology on the rise of cohabitation.
-Through a series of counterfactual experiments we are able to inspected which were the main forces behind the rise in cohabitation.
-Intuitively, as wages grow and the price of home appliances decreases, household can buy on the the market goods that were once produced at home.
-Since one of the gain of marriage with respect to cohabitation lies in the better specialization of production within the household, we might expect that those forces imply a reduction in the share of couples choosing marriage over cohabitation.
-
-The paper is organized as follows: section 2 offers an overview of US divorce laws, section 3 presents the empirical results, while section 4 describes in detail the theoretical model.
-Section 5 explain the procedure used for the estimation as well as the results.
-Section 6 report the results from a series of counter-factual experiments, while section 7 performs a welfare analysis.
-Section 8 draws the conclusions of the paper.
-
-\section{US Divorce Laws: an Overview}
+
+%Informal cohabitation is on the rise: the share of women that ever cohabited in the United States moved from 33\% in 1987 to 60\% in 2010 \citep{manning2013}.
+Since cohabiting couples display different outcomes than married ones, this rise definitely contributes to the overall changes in the structure and behavior of the American family.
+For example, \cite{bumpass2000} claim that the higher instability of cohabitation is responsible for the rise in the number of single mothers, which is linked to worse children's outcomes \citep{chetty2018}.
+The first step to find out why cohabitation is surging and why its outcomes differs from marriage is to better understand partnership choice, selection and cohabiting couples behavior.
+
+%Moreover, \cite{poortman2012} point out that couple specific investments of those who cohabit are lower than those who are married.
+%Since disadvantaged social classes are those who are more likely to cohabit instead of marrying, partnership choice can be an engine of economic inequality
+
+Informal cohabitation is on the rise: the share of women that ever cohabited in the United States moved from 33\% in 1987 to 60\% in 2010 \citep{manning2013}.
+This increase contributed to the overall changes in the structure and behavior of the American family.
+For example, \cite{bumpass2000} claim that the higher instability of cohabitation is responsible for the rise in the number of single mothers, which is associated with poor outcomes of children \citep{chetty2018,mclanahan2013}.
+Moreover, compared to married couples, the relationship-specific investments of cohabitants are lower \citep{poortman2012} and their children's well-being is worse \citep{brown2004}, even after controlling for parental resources.
+However, it is not clear to which extent the outcomes of cohabiting families are due to selection versus the direct effect of partnership's rights on couple's behavior.
+Quantifying the relative importance of these two mechanisms can be done only by understanding the rational for partnership's choices.
+Why do people cohabit instead of marrying?
+Why did cohabitation become more common over time?
+
+This paper addresses these questions by asking what role does unilateral divorce have for the rise of cohabitation.
+Since marriage and cohabitation can be viewed as contracts whose attractiveness depend on their termination rights and costs, the switch from mutual consent to unilateral divorce represents a unique opportunity to learn about partnership choices.
+This paper answers to this question with four contributions.
+First, we offer empirical evidence that unilateral divorce made cohabitation more likely to be chosen and that newly formed cohabitations last longer.
+Second, we propose a theory of partnership choice and endogenous breakup/divorce.
+In particular, in our model the policy makes cohabitation the preferred choice to couples that would have experienced the highest risk of a costly divorce.
+Therefore, the average match quality of cohabiting couples increases, which cause cohabitation spells to last longer.
+Third we structurally estimate our model to reflect the empirical findings.
+Fourth, we perform a counterfactual experiment to assess the overall role of unilateral divorce on the rise of cohabitation and we quantify the welfare gains and losses of the reform for men and women.
+This paper thus consists of four parts, one for each contribution, which we now describe in more detail.
+
+%Since the seminal work of \cite{becker1981}, economists studied the incentives behind the decision to marry, among which the sharing of public goods, the division of labor to exploit comparative advantages (\citealp{chiappori1997}), and risk sharing (\citealp{voena2015} and \citealp{rigas2015}).
+These reasons tell us why couples live together, while they are actually silent about the choice between marriage and informal cohabitation.
+Those two partnerships can be viewed as contracts subject to different rules, which in particular regulate costs and rights to end these agreements.
+While the cost of divorce is higher than the one of just breaking up,\footnote{Henceforth we will refer to the separation from cohabitation as breakup to avoid confusion with the legal separation.}, the introduction of unilateral divorce during the 1970s shifted the property rights from the spouse who wished to stay married to the one who wished to divorce.
+Hence, the switch from mutual consent to unilateral divorce represents a unique opportunity to learn how people choose between marriage and cohabitation.
+%In particular, unilateral divorce might have eroded the gains from marriage, both increasing the likelihood of a costly divorce and hampering couples' ability to commit, thus making some couples willing to cohabit instead of marrying.
+In addition, shifting to a less committed relationship hampers couples' ability to specialize and it might affect the relative bargaining  power of partners.
+
+%In this paper, we study the role of unilateral divorce on the rise of cohabitation.
+Our main contribution is to show that the rate of cohabitation surged after the changes in the US law because the increased risk of divorce made marriage less attractive.
+In particular, cohabitation becomes the preferred choice to couples that would have experienced the highest risk of divorce.
+As a consequence, the average match quality of cohabiting couples increases, which cause cohabitation spells to last longer.
+Interestingly, men are those who wish to cohabit the most after the reform because they would lose a relatively higher share of their wealth upon divorce.
+This increases the bargaining power of women entering cohabitation.
+
+In the first part of the paper we document the effect of unilateral divorce on the choice between marriage and cohabitation and on the duration of newly formed cohabitations.
+We use data from the National Survey of Family and the Household (NSFH) and from the National Survey of Family Growth (NSFG) to study the choice between marrying and cohabiting.
+Then, exploiting the exogenous variation coming from the staggered introduction of unilateral divorce over time across the US states, we estimate that newly formed couples are 5-7\% more likely to choose cohabitation over marriage compared to the pre-reform period.
+Interestingly, the effect's size depends on how property is divided upon divorce, being strongest in states where each spouse gets half of the wealth and where the assets shares are decided by the judge.
+This suggest that divorce allocations affect partnership choices.
+%This suggests that the result cannot be entirely driven by divorce being a less binding commitment technology,\footnote{This mechanism is highlighted by \cite{lafortune2020}, where the equal division of assets within marriage makes it possible to efficiently invest in children even after the rise of unilateral divorce.} since the egalitarian property division rule can act as a substitute for the mutual consent regime.
+Moreover, we analyze how unilateral divorce affected the duration of cohabitation spells: our estimates from a multinomial probit show that cohabitations formed after the reform last longer both because of a reduced risk of marriage and of breakup.\footnote{Henceforth we will refer to the separation from cohabitation as breakup to avoid confusion with legal separation.}
+
+In the second part of the paper we propose a theory to understand the mechanisms underlying the facts documented in the empirical part.
+We build a dynamic model of intra-household decision making and search in the mating market, where agents makes decisions according to the realization of idiosyncratic income shocks, their amount of wealth and a couple-specific match quality.
+Single agents meet, with some probability, a potential partner with a match quality, productivity and wealth.
+After the draw, they decide whether to marry, cohabit or stay single.
+Couples make decisions about consumption, savings and female labor force participation.
+Women receive a productivity penalty for not working and women's time can be used to produce a public good which captures utility gains from children, durable goods and services.
+Cohabitation and marriage differ in their splitting costs as well as in the way property is divided when the couple dissolves.
+Moreover, cohabitation is subjected to stigma, which is modeled as an exogenous utility flow.\footnote{The stigma towards cohabitation is to be interpreted considering the shame towards out-out-wedlock births, premarital sex and premarital cohabitation at time of the divorce revolution.} In the case of breakup, assets are split according to individual property rights, while in the case of divorce they are divided in half.\footnote{We made this assumption because the model will be estimated using community property states data.} Breakup (unilateral divorce) can be initiated unilaterally, as opposed to mutual consent divorce, which requires the consensus of both partners.
+Following \cite{voena2015}, under mutual consent the couple always cooperates while married, which implies that the allocation of resources corresponds to the Pareto-efficient inter-temporal allocation.
+Instead, unilateral divorce (breakup) results in a lack of commitment within marriage (cohabitation),\footnote{We model the decision making in the couple building on the literature on limited commitment (see for example \cite{kk1996},  \cite{ligon2002}, \cite{marcet2019} and \cite{pavoni2018}), which has been applied to dynamic collective models in the household by \cite{mazzocco2007}, \cite{mazzocco2013}, \cite{bayot2015}, \cite{rigas2015}, \cite{voena2015}, \cite{abraham2018}, \cite{lise2018}, \cite{low2018}, \cite{foerster2019} and \cite{reynoso2019} among others.} in fact the intra-household allocation can change in response to shocks, as spouses (cohabitants) can credibly exercise the threat of divorce (breakup).
+The fact that couples cannot commit ex-ante to any possible division of marital surplus contributes to the creation of an imperfectly transferable utility environment, under which the Becker-Coase theorem does not hold.\footnote{For an application of an imperfectly transferable utility environment to matching and collective models see \cite{galichon2019} and \cite{weber2018}.} Hence, abandoning the mutual consent regime affects the risk of divorce and in turn the surplus of marriage.\footnote{According to \cite{becker1977}, divorce laws should not affect separation decisions \textit{``if all compensations between spouses were feasible and costless"}.
+The assumptions underlying the Becker-Coase theorem are discussed by \cite{chiappori2015} and \cite{fella2004}.} More precisely, the barriers to divorce---represented by its costs and rights---affect the gains of marriage with respect to cohabitation through three main channels.
+First, by acting as commitment technologies, they enforce a better risk sharing and a more efficient specialization in the production of public goods within marriage.\footnote{We assume that public goods are produced with money and women's time.
+When women stop working for producing such a good their potential productivity in the labor market decreases.} Second, they increase the risk of being ``trapped" in a bad marriage.
+Third, they affect the expected value of marriage by modifying the risk and value of divorce.
+The effects of tightening or relaxing the barriers to divorce depends on which channel prevails: for example, the introduction of unilateral divorce has an uncertain impact on the share of couples that cohabit and marry.
+Interestingly, in our framework  the outcomes of cohabitation and marriage not only depend on the rules underlying these contracts, but also on sorting on match quality.
+In fact, a cheap breakup is most attractive to couples whose match quality is low and couples' ability to cooperate depends on the match quality itself through its effect on the couples' stability.\footnote{It's easier to make partnership-specific investments when the risk of splitting is low, which is the case when the match quality is high.}
+
+%
+%In our framework marriage gains depend on the quality of the match: for couples whose value is low cohabitation is the best choice because breaking up is cheaper and their risk of splitting is high.
+Interestingly, the ability of the couple to cooperate is directly affected by the quality of the match.
+For this reason, the outcomes of cohabitation and marriage depend not only of the rules underlying these contracts, but the ability of the couple to cooperate is directly affected by the quality of the match.
+
+%The gains of marriage with respect to cohabitation come from a better risk sharing and a more efficient specialization in the production of public goods,\footnote{We assume that public goods are produced with money and women's time.
+When women stop working for producing such a good their potential productivity in the labor market decreases.} which arise from a stronger commitment, enforced through the threat of a costly divorce and the mutual consent regime.
+On the other hand, couples facing the highest risk of splitting (i.e.
+because of a low match quality draw) are more likely to choose cohabitation, since breaking up is cheaper.
+Interestingly, the ability of the couple to cooperate is directly affected by the quality of the match.
+For this reason, the outcomes of cohabitation and marriage depend not only of the rules underlying these contracts, but also on sorting on match quality.
+
+% After unilateral divorce is introduced, the dissolution of marriage can be initiated by one spouse without the other spouse's consent.
+We model the decision making in the couple building on the literature on limited commitment (see for example \cite{kk1996},  \cite{ligon2002}, \cite{marcet2019} and \cite{pavoni2018}), which has been applied to dynamic collective models in the household by \cite{voena2015}, \cite{mazzocco2007}, \cite{foerster2019} and \cite{lise2018} among others.
+In this framework, when one member of the couple wishes to split, the couple rebargains such that the binding member is made indifferent between breakup and staying in a couple.\footnote{For particularly bad draws in the match quality or productivity shock this might not be possible and hence the couple would split.}
+
+In the third part of the paper we structurally estimate the model to understand the quantitative relevance of the mechanisms that drive partnership choice.
+The model is estimated by indirect inference using as targets the regression results from our empirical analysis, mating market moments (NSFH), and female labor supply moments (PSID).
+The introduction of unilateral divorce is modeled as an unexpected policy.
+The estimated model closely replicates the targeted moments, and over-identification checks support the estimation results by highlighting that the model can match a number of non-targeted moments, among which the impact of unilateral divorce on cohabitation duration.
+According to the estimated model, a switch from mutual consent to unilateral divorce causes couples to start cohabiting more by reducing married couple's ability to cooperate and by increasing the likelihood of a costly divorce.\footnote{An increased likelihood of divorce can reduce the ability of the couple to cooperate by itself.
+Yet it also has a direct effect on the marriage surplus by reducing the likelihood of losing assets upon divorce.
+For example, if there was no wage uncertainty and women were always participating in the labor market, unilateral divorce would affect the gains of marriage via the direct effect only.} Since cohabiting couples that would have married under the older regime are better matched than the average cohabiting couple, the reform increases the stability and the duration on newly formed cohabitations.
+To further deepen our understanding of the mechanisms, we analyze the changes in intra-household bargaining that followed the policy change in the model.
+We find that the average Pareto weight of cohabiting women increases because men, fearing to lose most of their assets because of divorce, convince women to cohabit instead of marrying in exchange for more power in the couple.
+This mechanism is specific to community property regime: under a title-based regime men would not need to choose cohabitation to insure their assets.
+Consistently with empirical evidence, the impact of unilateral divorce on the likelihood to cohabit is lower in the model under a title-based regime.
+
+The fourth and last part of the paper conducts a series of counterfactual experiments to understand the quantitative importance of the forces that contributed to the rise of cohabitation.
+To assess the role of unilateral divorce we perform a counterfactual experiment where unilateral divorce was never introduced.
+We find that people on average would have spent 1.35 years cohabiting instead of 2.26, while only 26.7\% of people would have ever cohabited instead of 34.8\%.
+In a second series of counterfactual experiments we find that a 20\% increase in women wages and a 20\% drop in market prices of goods increase respectively by 1\% and 2\% the share of people that ever cohabited at age 39.
+Both effects are driven by a reduced scope for household specialization, which is better exploited within marriage.
+We also perform a welfare analysis of the introduction of unilateral divorce: the possibility to cohabit limits the welfare losses for men who can secure their assets, while women suffer more because couple-specific investments like children deteriorate their value of divorcing more that for men.
+
+\textbf{Literature.} This paper adds to three strands of the literature.
+First, by documenting how divorce laws influence the choice between marriage and cohabitation, we add to the existing literature that studies the effects of unilateral divorce.
+This policy change has been shown to affect the rate of divorce (\citealp{friedberg1998}, \citealp{wolfers2006}), female labor supply (\citealp{stevenson2008}, \citealp{voena2015}), savings (\citealp{voena2015}), marriage rates (\citealp{rasul2003,rasul2006}), children's well-being (\citealp{gruber2004}), family violence (\citealp{stevenson2006}), marriage-specific capital (\citealp{stevenson2007}), assortative mating (\citealp{reynoso2019}) and prostitution (\citealp{ciacci2017}), among the others.
+We complement the findings of \cite{rasul2003,rasul2006} by showing that the decrease in marriage rates after the introduction of unilateral divorce is not only driven by more people staying singles, but also by more people that choose to cohabit.
+This suggest that marriage and cohabitation are substitutes.\footnote{Cohabitation can also be a substitute for being single or dating, as \cite{rindfuss1990} point out.
+Moreover, \cite{blasutto2020} and \cite{brien2006} claim that cohabitation can also be a complement for marriage, which allows the couple to learn about its match quality before making the binding decision of getting married.} Our paper builds on \cite{voena2015}, that studies how the interaction of unilateral divorce with property rights upon divorce affected household behavior of married couples.
+We extend her work both by considering cohabitation as an alternative relationship and by analyzing selection into partnership.
+This paper also extends the work of \cite{fernandez2017} by showing that not considering cohabitation as an alternative to marriage biases upwards the negative impact of unilateral divorce on men's welfare.
+The intuition is that men can limit the losses stemming from the increased risk of divorce by choosing to cohabit.
+
+Second, our paper adds to the literature that studies the choice between marriage and cohabitation.
+A first subset thereof has focused on identifying the gains of marriage and cohabitation, highlighting the role of commitment \citep{matouschek2008}, specialization within the couple \citep{gemici2014}, learning about match quality \citep{brien2006}, income dynamics \citep{blasutto2020}, assets \citep{lafortune2017, lafortune2020} and investment in children \citep{lundberg2015}.
+We extend these works by showing how an increase in the easiness of divorce not only decreases the ability of the couple to cooperate, but it also makes divorce allocations more relevant for partnership choices, since the likelihood of divorce increases.
+Consequently, the relative power of potential partners and the rules about division of assets upon divorce become crucial.
+These results highlight a new role of partners' relative power and assets for partnership choices, which is analyzed within a framework that extends the theory of \cite{blasutto2020} and \cite{gemici2014} by including saving decisions.\footnote{\cite{lafortune2020} also highlight the role of assets: our model features their intuition that assets can act as act as a commitment technology, but our framework also allows assets to influence partnership choices via a direct effect of divorce's risk.
+Thanks to this mechanism we can explain why unilateral divorce caused cohabitation to increase more in community property states than in title-based ones.} A second set of papers studies the effect of changes in cohabitants' rights on partnership choices and cohabiting couples' behavior, highlighting the role of alimony rights (\citealp{chiappori2017,gousse2018}), taxation \cite{leturcq2012} and division of assets at breakup (\citealp{fisher2012,gousse2018,chigavazira2019}).
+We extend this literature by showing that the introduction of unilateral divorce impacts both the choice to cohabit and cohabitation's stability, even though cohabitant's rights are not directly affected.\footnote{\cite{matouschek2008} study the effect of unilateral divorce on marriage rates using a framework where the choice between marriage and cohabitation is considered.
+Their framework does not predict changes to the propensity to cohabit.} Further, the effects on the choice to cohabit depends on property division rights, which indicates that partnership choices depend on divorce allocations.
+This evidence suggests that changes in family law should be designed considering that marriage and cohabitation are substitutes.
+%\cite{chiappori2017},\cite{persson2020}, \cite{leturcq2012}, \cite{gousse2018}
+%Second, our paper expands the literature on cohabitation, showing how the risk of divorce is essential for understanding partnership choices.
+Different papers in the literature highlighted various gains of marriage with respect cohabitation: commitment \citep{matouschek2008}, labor specialization within the couple \citep{gemici2014}, learning about match quality \citep{brien2006}, income dynamics \citep{blasutto2020} and investment in children \citep{lafortune2020}.
+A paper closely related to ours is \cite{lafortune2020}, who highlight the role of assets as a collateral that enforces commitment and hence allows for optimal investment in children.
+While we think that their mechanism is important, it cannot be the whole story since we observe that the switch towards cohabitation is the strongest in states where assets are divided more equally, where their model would predict that the effect is the weakest.
+In this paper, we quantify how much of the shift is due to the erosion of marriage's collateral versus the role of the increased risk of divorce.
+We extend the work of \cite{gemici2014} and \cite{blasutto2020}, who develop collective dynamic models with limited commitment, introducing asset accumulation decisions, which are shown to play an important role for commitment and hence for partnership choice, especially when interacted with property rights upon divorce.
+Other papers highlighted how
+
+Finally, this paper is tied to the large literature that studies the changes in the character of the American household over the last decades.
+Various studies explored the role of health improvements, wage distribution and dynamics, norms and technology on the rise in female labor force participation \citep{fernandez2004,greenwood2005,albanesi2016,greenwood2016}, the changes in household formation and dissolution \citep{greenwood2016,ciscato2019}, the rise in positive assortative mating \citep{fernandez2005,greenwood2016,ciscato2019} and the increase in the age at marriage \citep{santos2016}.
+We extend this literature by showing that the introduction of unilateral divorce implied an increase in cohabitation and that advances in the home production technology and the reduction in the gender wage gap also contributed to the rise in cohabitation.
+
+The paper is organized as follows.
+Section 2 offers an overview of US divorce laws.
+Section 3 documents the effect of introducing unilateral divorce on partnership choices.
+Section 4 presents and develop the theoretical model.
+Section 5 describes the estimation of the model, while section 6 discusses the main mechanisms of the model.
+Section 7 reports the results of the welfare analysis.
+Section 8 performs a series of counterfactual experiments, while section 9 contains the conclusion.
+
+%\begin{enumerate}
+%\item \cite{chigavazira2019}: What: extending  equitable  property  division  divorce  laws  to  unmarried cohabiting couples in Australia.
+Findings: men increase their employment and women increase time spent on housework.
+Couples have more children and are more likely  to  become  home  owners.
+Strategy: triple Diff-in-Diff: state-time-relationship(coh/mar).
+They select a sample of marriages and cohabitation that stays intact at the end of the time span[this seems wrong to me].
+Then they claim that the effect is not due to selection, even tought they check that in a sloppy way without a duration model, which seems the thing to do.
+%\item \cite{chiappori2017}: what:  granting alimony rights to cohabiting couples in Canada.
+Finsings: Among couples united before the reform, obtaining the right to petition for alimony led women to lower their labor force participation but not among newly formed cohabiting couples.
+Cool difference lead by selection+commitment
+%\item \cite{persson2020}: VERY IMPORTANT PAPER.
+Exploiting Sweden’ s elimin ation of s ur v ivors insur ance, I demon strate that severin g this link (1) affected entry into marriage up to 50 years before expected payout, (2) raised the divorce rate by 10pp, and (3) raised the assortativeness of matching (4) increased rate of cohabitation and of separation, consistent with selection along match quality
+%
+%\end{enumerate}
+\section{US Divorce and Cohabitation Laws: an Overview}
+\textbf{Divorce Laws.} Between late 1960s and early 1980s most U.S.
+states experienced fundamental changes in the divorce law, both regarding the right to initiate a divorce without the consent of the other spouse and about the laws that govern the division of assets upon divorce.
+
+Before the 1960s the vast majority of US states had a mutual consent divorce regime,\footnote{All the states apart from New Mexico, Oklahoma and Alaska.} where the agreement of both spouses was needed to obtain a divorce for mundane reasons (i.e.
+without misconduct by any spouse).
+Moreover, divorce was permitted for grounds showing guilt of misconduct by any of the two spouses: for those cases the agreement of the innocent party alone was enough for having a divorce granted.\footnote{Examples of guilt or misconduct are adultery or abandonment.}
+From the late 1960s and early 1980s most U.S.
+states switched to a unilateral divorce regime.\footnote{A list of the years at which unilateral divorce was introduced in different states can be found in table 1 of \cite{ciacci2017}.} Under this regime divorce can be filed by one spouse without the consent of the other.
+
+Another dimension along which divorce laws differs across states and over time is the one about property division regimes. In the United States there are three types of those:
+\begin{enumerate}
+\item \textit{Community Property}.
+Under this regime the couple are jointly owning family wealth, both that obtained during marriage and before.
+This implies that when divorce occurs, each spouse gets exactly half of the total family wealth.
+\item \textit{Equitable distribution}.
+Under this regime, it is the court that decides how to split family wealth between the two spouses.
+This decision is driven by the principle of equity, which is ambiguous: in some cases the wealth is divided exactly in half, while in others a larger share reserved to the party that contributed the most to its accumulation.
+\item \textit{Title Based Regime}. Under this regime wealth is split according to the title of ownership.	
+\end{enumerate}
+%Rights of cohabitors,literature
+%\begin{enumerate}
+%	\item \cite{garrison2008} cohabitation was never regulated because it lasts for a too short time.
+In a nutshell, Cohabitation created no rights or obligations+ Cohabitants could not agree to create rights or obligations based on their intimate relationship.
+Instead, cohabitors can call for other equitable	doctrine for relief purchase money resulting trust, quantum meruit.
+These various forms of equitable relief ensured that, in many cases, one cohabitant who had been	cheated by the other could obtain recovery for some or all of his losses.
+Anyway, cohabitant claims for financial relief have not flooded the courts, partially because they are poorer and more disadvantaged
+%	\item \cite{katz2008} , in a state that makes a	meaningful distinction between the legal status of legitimate and illegitimate children, children born to a non-marital cohabiting couple are illegitimate, requiring some affirmative action by the birth father if he wishes to have any legal control over his child.
+%	\item \cite{starnes2016} Cohabitation might cause the alimony rights to terminate in some States.
+%	\item \cite{waggoner2016} Textual words:\textit{As far as the law is concerned, the partners are complete strangers to each other}.
+He means short term relationship because longer-term cohabitations have already found their way into the legal system, even tough Contracts are unenforceable in some jurisdictions and, even if they are, the plaintiff cannot always prove the	existence of a contract.
+Other English-speaking jurisdictions have already enacted or introduced	legislation granting marital rights to cohabiting couples if their relationship meets specific criteria (Australia, Canada, Ireland,1 New Zealand,101 and Scotland1 and introduced in the United Kingdom for England and Wales.
+Other that the anglsphere,many european contries also does have that).
+%	
+%	\item \cite{strasser2001} Definition of Domestic Partners two persons of the same or  opposite sex, not married to one another, who for a significant period of time share a  primary residence and a life together as a couple.” Whether a couple has shared a life together will be determined in light of a number of factors including the parties’“oral or written statements,” the extent to which their finances were intermingled,“ the extent to  which their relationship fostered...[either] inter-dependence” or one party’s dependence on the other, the extent to which the members of the couple acted or assumed roles in furtherance of their life together, the extent to which the relationship wrought change in the life” of either party, the emotional or physical intimacy of the relationship, and the reputation of the couple in the community
+%		
+%	\item \cite{mayeri2015} Enforcement of financial responsibilities for non-marital fathers was increased rapidly during the welfare reform in the 1990s, and made the income sharing guaranteed through marriage and non-marital fertility much more similar.
+%	
+%	\item \cite{rossin2017} in-hospital voluntary paternity establishment enable all unmarried parents to voluntarily establish paternity by filing out a simple one-page form at the hospital at the time of childbirth, and provide information to all new fathers about their rights and obligations.
+Before IHVPE, paternity establishment was a costly and complicated process involving the court system and	DNA testing; less than a third of children born out of wedlock had fathers who	established paternity in the late 1980s.
+This was a way to enforce child support
+%\item \cite{goran2008} Common-Law Marriage requires cohabitation (relevant factors=sexual relationship, exclusive relationship, mutual children, mutual house, economic support, emotional support, shared recreation,length of cohabitation might play a role, only because cohabitation has to be permanent.) and reputation as spouses (outwardly represent themselves as spouses with respect to third parties) as continuing factors to be considered as-if-married.
+Inferred agreements might also play a role: couple could cohabit for years without being considered as being in a marriage agreement, with marital right and obligations.
+The burden of the proof is on the party alleging the existence common-law marriage, in which case it is presumed and the burden shifts: the other party has to prove that no informal marital contract has been formed.
+%\item \cite{bowman2004} similar to garrison up to a certain point.
+then she says that in some states there exist some status-based rights.
+In washington the meretricious relationship implies community property but it applies to couples with common law marraige characteristics, which are rare for cohabitors and also hard to prove.
+it has been introduced in 1984 (does not matter much for us.) In Vermont and Massachussets only same-sex couples recive status-based cohabitation rights, apporved by most of other us states.
+Domestic partnerships are available in Hawaii (1997-some benefits as cara at hoispital of insurance for partners of employees), new Jeersey (2004-stringent rights for entering and exiting with few benefits) adn California (2001-2004 as marriage for same sex and hetero above age of 62.) Many of the most significant government benefits are universallyunavailable to cohabitants, however, because they derive from federal law.Social Security survivors’ benefits are available only to those who qualify as spouses as defined by state law.
+Some exception (california) applies for state related benefits.
+Concerning children, what matters is mostly biology and not the relationship status.
+%
+%\end{enumerate}
+\textbf{Breakup/Divorce laws compared.} The regulation of cohabitation in the US is limited, and small changes have been done since the 1960s, when “Cohabitation created no rights or obligations” \citep{garrison2008}.\footnote{\cite{garrison2008} explains that in to 1960s \textit{“Cohabitants could not agree to create rights or obligations based on their intimate relationship”}.
+She continues analyzing the effect of the \textit{Marvin vs.
+Marvin} case (year 1976), where a palimony---a compensation from one member of an unmarried couple to another after breakup--- was awarded to the female partner: \textit{“[the case] has not produced results markedly different from those permissible under pre-Marvin case law.”} Finally, she argues that claims for financial relief has rarely reached the courts because 1) cohabitation are usually very short and no committed 2) cohabitants are younger and poorer than marrieds and 3) cohabitants do not usually adopt sharing behavior, unlike in the Marvin cases.
+Similarly, \cite{bowman2004} claims that remedies based of contract had a limited application.} Hence, breakup resembles unilateral divorce because cohabitation can be ended by one partner without the consent of the other partner.
+Concerning property division rights, breakup de facto falls under the title-based property regime.
+One important difference between divorce and breakup is that the former requires the couple to undergo a legal process, which implies monetary and time costs, while the latter does not requires this procedure.\footnote{While \cite{garrison2008} argues that claims for financial reliefs after breakup are rare, breakup is treated like divorce under the doctrine of common-law marriage, a legal framework under which a couple is considered as married without having formally registered their relationship.
+\cite{goran2008} explains that the existence of the implied contract is presumed once continuous cohabitation and reputation (holding out as husband and wife) are proven, but it is still possible that the couple---even if cohabiting for many years---is not considered as being in a marriage agreement, with marital right and obligations.
+These rules creates uncertainty regarding the recognition of common-law marriage for some couples, especially those close to a breakdown, where the two partners might disagree about the existence of an implied marital agreement.} This fact is consistent with the findings of \cite{avellar2005}, who show that for women the drop in income following couple's breakdown is larger for divorce than breakup.
+To further support the claim that divorce is more costly than breakup, in appendix \ref{section:eventsa} we select from the PSID a sample of couples that divorced/broke up to study how their net-worth evolves after splitting.
+The point estimates of two event-studies indicates that the divorce of richer couples results in a loss of assets, while we could not observe the same pattern for the divorce of poorer couples and breakups.
+%When a child is born in the unmarried couple, where the situation started changing in the 1990s, when establishing paternity and the enforcement of child support became easier.\footnote{\cite{rossin2017} explains that in-hospital voluntary paternity establishments enabled all unmarried parents to voluntarily establish paternity.}
+
 \section{Data and Empirical Evidence}
-\subsection{The Dataset}
+\subsection{Dataset}\label{dataset}
 We begin by describing our data.
-We use the the National Survey of Family and the Household (NSFH) wave I, and the National survey of Family Growth, 1988 wave.
+We use the National Survey of Family and the Household (NSFH) wave I, and the National survey of Family Growth, 1988 wave.
 Both surveys were designed to study the causes and consequences of changes happening in families and households within the United States.
-This is reflected in detailed question regarding the retrospective family history of respondents, which includes information both about marriage and cohabitation.
-Moreover, primary respondents\footnote{One adult per household was randomly selected as the primary respondent, while in the NSFG respondents are all women of 15-44 years of age.} are asked a large set of questions regarding their socio economic background and the demographics of the household.
-While the NSFH I is the first of three longitudinal waves, NSFG is made of several repeated cross sectional samples.
-We decided not to use the other two other waves of the NSFH because in the second wave all currently cohabiting households were dropped from the survey, while the 1988 wave of NSFG is the only one with publicly available information about the residence of the respondents.
-A drawback of using this data\footnote{We do not have the choice of using other surveys for our analysis, since they either lack the State of residence variable, or they miss information about cohabitation history, or they do not cover people that were in a relationship age at the time the law changed.} is that we know the state of residence of the respondents only at age 16 for the NSFH and at birth for the NSFG.
-Since we also know whether people lived all their life in the same State we are able to perform our empirical analysis both on the universe and of the subsample of never movers.
+This is reflected in detailed questions regarding the retrospective family history of respondents, including information both about marriage and cohabitation.
+Moreover, primary respondents are asked a large set of questions regarding their socio economic background and the demographics of the household.\footnote{One adult per household was randomly selected as the primary respondent, while in the NSFG respondents are all women of 15-44 years of age.} While the NSFH I is the first of three longitudinal waves, NSFG is made of several repeated cross sectional samples.\footnote{We decided not to use the other two other waves of the NSFH because in the second wave all currently cohabiting households were dropped from the survey.
+Moreover, the 1988 wave of NSFG is the only one with publicly available information about the residence of the respondents, which is crucial to identify the divorce regime that applies to the respondent.} A drawback of using this data is that we know the state of residence of the respondents only at age 16 for the NSFH and at birth for the NSFG.\footnote{We do not have the choice of using other surveys for our analysis, since they either lack the State of residence variable, or they miss information about cohabitation history, or they do not cover people that were in a relationship age at the time the law changed.} Since we also know whether people lived all their life in the same state, we can overcome it and perform our empirical analysis both on the universe and of the subsample of never movers.
 We will show that point estimates turn out to be statistically not distinguishable between the two samples.
@@
 We use this dataset to build two samples, the one of \textit{first and second relationships} and the one of \textit{first cohabitations}, that are described below.
-\subsubsection*{First and Second Relationships Sample}
-We want to build a sample to analyze the type of relationship, which can be either marriage or cohabitation,\footnote{Dating is not considered, since we cannot observe this state.
-Hence, people dating will fall under the category of singles.} that respondents decided to have.
-The sample is made of first and second relationships.
-One first relationship is defined observing the first time (if ever) a certain person started cohabiting or married.
+
+\textbf{First and Second Relationships Sample.} We build a sample to analyze the type of relationship that respondents decided to have, which can be either marriage or cohabitation.
+The sample is made of first and second relationships.\footnote{Dating is not considered, since we cannot observe this state.
+Hence, people dating will fall under the category of singles.} One first relationship is defined observing the first time (if ever) a certain person started cohabiting or married.
 This observation is associated to the date at which the relationship starts, to the characteristics of the respondent member of the formed couple, and with a \textit{type}, which can either marriage or cohabitation.
-Note the type of couples that cohabited before marriage is "cohabitation": the transition from cohabitation to marriage is analyzed using the sample of \textit{first cohabitations}.
+Note that the type of relationship of couples that cohabited before marriage is ``cohabitation": the transition from cohabitation to marriage is analyzed using the sample of \textit{first cohabitations}.
 Second relationships are defined in a similar fashion, but they include only respondents that ended the relationship with their first partner and started a new one with a different person.
-The way this sample is built implies that for some respondents we will have zero corresponding observations in this sample, while for other we will have other, and for others we will have two.
+The way this sample is built implies that for some respondents we will have zero corresponding observations in this sample, while for others we will have one, and for others we will have two.
 We did not consider third or higher order relationships for our analysis since these individuals would be further away from the age at which we knew their state of residence.
-In [FIGURE********] we report the descriptive statistics of this sample.
-\subsubsection*{First Cohabitation Sample}
-This sample is built to analyze the decisions of cohabiting couples to separate or to marry.
-It is composed of the first non marital cohabitation experienced by respondents.
+Finally, we consider only relationships that started when the respondent was 20 years old or older.
+In table \ref{table:sum_rel} we report the descriptive statistics of this sample.
+
+\begin{table}[!htbp]\centering
+	\caption{\\Descriptive statistics, cohabitation sample}
+	\label{table:sum_rel}
+\input{sum_sing.tex}
+\end{table}
+\FloatBarrier
+\textbf{First Cohabitation Sample.} This sample is built to analyze the decisions of cohabiting couples to breakup or to marry.
+It is composed of the first non-marital cohabitation experienced by respondents.
 This sample includes couples that cohabited before marriage, but it also includes cohabitations experienced by people with the following marital history: marriage without premarital cohabitation, divorce, cohabitation with a different person.
-Each observation of this sample is associated with a starting date, a possible ending date, and an outcome, which can be: still cohabiting, married or separated.
-In [FIGURE********] we report the descriptive statistics of this sample.
-\subsection{Empirical Evidence}
-\section{The Model}
-This section describes a dynamic life cycle structural model of partnership formation, savings, female labor supply and  home production.
-Couples act cooperatively subject to limited commitment, which means that rebargaining might happen in response to changes in the outside options, which are assumed to be divorce or separation.
-
-In the model time is discrete, and in each period men and women draw their productivities.
+Each observation of this sample is associated with a starting date, a possible ending date, and an outcome, which can be still cohabiting, married or breakup.
+In table \ref{table:sum_coh} we report the descriptive statistics of this sample.
+
+\begin{table}[!htbp]\centering
+	\caption{\\Descriptive statistics, relationship sample}
+	\label{table:sum_coh}
+	\input{sum_coh.tex}
+\end{table}
+\FloatBarrier
+
+\subsection{Empirical Evidence}\label{empirics}
+Does unilateral divorce affect the partnership choice of couples?
+We exploit the timing in the adoption of unilateral divorce as a source of exogenous variation in the right to divorce.\footnote{See table 1 in \cite{ciacci2017} for the timing of adoption of unilateral divorce.} This strategy has already been used several times by the literature\footnote{Among the others, see \cite{wolfers2006}, \cite{stevenson2008}, \cite{voena2015}, \cite{reynoso2019} and \cite{ciacci2017}.} to study the non-neutrality of the rights to divorce on various economic and demographic outcomes.
+According to \cite{gruber2004}, who reviews the legal literature about the topic, the introduction of unilateral divorce was not view as a tool of social policy, but rather a way to reduce the legal burden of divorce trials.
+This reasoning is consistent with the fact that this change was not initiated by the most liberal states: New York was the last state to introduce unilateral divorce in October 2010, almost 40 years later than Kentucky.
+Moreover, \cite{reynoso2019} shows that there is no geographic correlation in adoption.
+\subsubsection*{Relationship Choice}
+What is the effect of unilateral divorce on the partnerships that couples choose?
+To answer this question, we estimate equation (\ref{eq:ols_baseline}), where $i$ are the newly formed couples, $t$ is the calendar time, and $s$ is the state:
+\begin{equation}\label{eq:ols_baseline}
+\text{married}_{i,t,s}=\beta_0+\beta_1*\text{Unilatearal}_{t,s}+\mathbf{\gamma'}\mathbf{X}_i+\delta_s+\nu_t+\epsilon_{i,t,s}.
+\end{equation}
+The dependent variable is a dummy take takes value $1$ if the couple $i$, started at time $t$ if state $s$ is a marriage, and 0 if it is cohabitation.
+The vector $\mathbf{X}_i$ instead includes a set of socio demographic controls, while $\delta_s$ are the state fixed effects and  $\nu_t$ are the time fixed effects.
+The variable $\text{Unilateral}_{t,s}$ instead is a dummy that takes value $1$ if unilateral divorce wave in place in state $s$ at time $t$: $\beta_1$ instead is the coefficient that is informative about the effect of unilateral divorce on partnership choice.
+The results of the estimation are reported in table \ref{table:ols_rel_standard} for different samples.
+Column (1) reports the results for the full sample described in section \ref{dataset}, while column (2) is restricted to observations for which we know that the person lived all its life in the reported states, ensuring that they did not migrate.
+Finally, columns (3) and (4) restrict the sample to respectively the NSFH and NSFG surveys only.
+%MARRUAGE TO DIVORCE
+
+	\begin{table}[H]\centering
+		\caption{\\OLS Regression. Observation: first and second relationships}
+		\label{table:ols_rel_standard}
+		\begin{threeparttable}[t]\centering
+			\input{wmar.tex}
+	\begin{tablenotes}[flushleft]
+		\footnotesize{\item \textsc{Notes}: standard errors are clustered at the state level.
+			Coefficients that are significantly different from zero are denoted by the following system: *10\%, **5\%  and ***1\%.}
+	\end{tablenotes}
+\end{threeparttable}
+\end{table}
+\FloatBarrier
+The results reported in table \ref{table:ols_rel_standard} suggest that unilateral divorce decreased the share of couples that are married by $-5\%(6\%)$ depending on the specification.
+These results are robust to an alternative specification that includes state specific linear trends, whose results are reported in table \ref{table:wmarlin}, and to the use of a logistic regression, reported in table \ref{table:wmar_logit}.
+
+We then move on to better understand the heterogeneity hidden behind the effect of unilateral divorce.
+While in some states assets are split in the same way in both breakup and divorce, which is the case of \textit{title-based regime} states, in others this rule is different, which is the case of \textit{community property} and \textit{equitable distribution} states.
+Analyzing this heterogeneity is then interesting to understand how much the asset sharing rule is important for understanding relationship choices.
+We hence estimate equation (\ref{eq:ols_by_prop})
+
+\begin{equation}\label{eq:ols_by_prop}
+\begin{split}
+\text{married}_{i,t,s}=\beta_0+&\beta_1*\text{Unilatearal*No Title Based}_{t,s}\\&+\beta_2*\text{Unilatearal*Title Based}_{t,s}+\\&\quad\quad\beta_3*\text{Title Based}_{t,s}+\mathbf{\gamma'}\mathbf{X_i}+\delta_s+\nu_t+\epsilon_{i,t,s},
+\end{split}
+\end{equation}
+whose  indexes and controls are the same of equation (\ref{eq:ols_baseline}), with the difference that now we capture the interaction of unilateral divorce with asset division regimes interacting $\text{Unilateral}_{t,s}$ with  $\text{Title Based}_{t,s}$ and $\text{No Title Based}_{t,s}$, which indicates whether state $s$ at time $t$ had or not a title-based regime.
+In table \ref{table:wmarc} we report the results of the estimation of equation \ref{eq:ols_by_prop}.
+Similarly to table \ref{table:ols_rel_standard}, column (1) reports the results for the full sample described in section \ref{dataset}, while column (2) is restricted to the observations for which we know that the person lived all her life in the reported states, which ensures that they did not migrate.
+Finally, columns (3) and (4) restrict the sample to respectively the NSFH and NSFG surveys only.
+
+	\begin{table}[H]\centering
+		\caption{\\OLS Regression. Observation: first and second relationships}
+		\label{table:wmarc}
+		\begin{threeparttable}[t]\centering
+			\input{wmarc.tex}
+			\begin{tablenotes}[flushleft]
+				\footnotesize{\item \textsc{Notes}: standard errors are clustered at the state level.
+					Coefficients that are significantly different from zero are denoted by the following system: *10\%, **5\%  and ***1\%.}
+			\end{tablenotes}
+		\end{threeparttable}
+	\end{table}
+\FloatBarrier
+The results show that the effect of unilateral divorce on the likelihood that a couples chooses marriage over cohabitation in non-title-based states is significant with a magnitude of $-6\%(-7\%)$ depending on specification, while it is non significant and much smaller in title-based states.
+These results suggest that having a sharing rule decided by the law is not enough to replace the mutual consent regime as an alternative commitment technology.
+Instead, these results are consistent with the view that the richest partner starts disliking marriage when divorce becomes unilateral, since she would risk losing most of her wealth upon divorce.
+This was not happening in mutual consent regime, since she could have exercised her right to veto divorce.
+In title-based state this threat for the richest member of the couple does not exist, hence marriage surplus with respect to cohabitation does not vary significantly.
+Table \ref{table:wmarlinc} shows that results are robust to the inclusion of state specific linear trends.
+\subsubsection*{Cohabitation Duration}
+What is the effect of unilateral divorce on cohabitation duration?
+How much of the change is due to a variation in the risk of breakup versus the risk of marriage?
+In order to answer this question, we construct a model of cohabitation duration with multiple risks, namely breakup and marriage.
+Our model builds on \cite{jenkins1995}, who shows how that a logistic regression can be used for studying duration of events by reshaping the dataset to obtain unit of time per spells observations, where the dependent variable takes value $1$ whenever the event of interest occurs.
+The natural extension of this model to a multiple risk environment would be to use a multinomial logit.
+However, the problem with this model is that it assumes independence of irrelevant alternatives, which is particularly unappealing for our problem, since it would imply that the relative probability of choosing marriage over breakup stays the same after cohabitation is no longer an option.
+Hence, we chose to model cohabitation duration with a multinomial probit, where the independence of irrelevant alternatives does not need to be satisfied.
+We then study the choice of cohabiting couple $i$, at calendar time $t$ in state $s$ and at duration $d$ estimating the following model:
+\begin{equation}\label{eq:probit_1}
+\begin{split}
+&Y_{i,s,t,d}^\text{Marry}=\beta^\text{Marry}*\text{Unilatearal}_{s,t}+\mathbf{\gamma^{\text{Marry'}}}\mathbf{X_i}+\alpha_d+\delta_s+\nu_t+\epsilon^{\text{Marry}}_{i,s,t,d},\\&
+Y_{i,s,t,d}^\text{Cohabit}=\beta^\text{Cohabit}*\text{Unilatearal}_{s,t}+\mathbf{\gamma^{\text{Cohabit'}}}\mathbf{X_i}+\alpha_d+\delta_s+\nu_t+\epsilon^{\text{Cohabit}}_{i,s,t,d},\\&
+Y_{i,s,t,d}^\text{Separate}=\beta^\text{Separate}*\text{Unilatearal}_{s,t}+\mathbf{\gamma^{\text{Separate'}}}\mathbf{X_i}+\alpha_d+\delta_s+\nu_t+\epsilon^{\text{Separate}}_{i,s,t,d},
+\end{split}
+\end{equation}
+where
+\begin{equation}\label{eq:probit_error}
+\myvec{\epsilon_{i,s,t,d}^{\text{Marry}}\\\epsilon_{i,s,t,d}^{\text{Cohabit}}\\\epsilon_{i,s,t,d}^{\text{Separate}}}\sim\mathcal{N}(\mathbf{0},\mathbf{\Sigma}),
+\end{equation}
+and
+\begin{equation}\label{eq:probit_outcome}
+Y_{i,s,t,d}=
+\begin{cases}  	
+\text{Marry}\hspace{30pt}       \text{if}\hspace{10pt}Y_{i,s,t,d}^\text{Marry}>Y_{i,s,t,d}^\text{Cohabit}\hspace{5pt}\text{and}\hspace{5pt}\hspace{5pt}Y_{i,s,t,d}^\text{Marry}>Y_{i,s,t,d}^\text{Separate}\\
+\text{Cohabit}\hspace{23pt}   \text{if}\hspace{10pt}Y_{i,s,t,d}^\text{Cohabit}>Y_{i,s,t,d}^\text{Marry}\hspace{5pt}\text{and}\hspace{5pt}\hspace{5pt}Y_{i,s,t,d}^\text{Cohabit}>Y_{i,s,t,d}^\text{Separate}\\
+\text{Separate}\hspace{22pt}     \text{otherwise.}
+\end{cases}
+\end{equation}
+The model described above is estimated with bayesian techniques via Markov chain Monte Carlo following the procedure of \cite{imai2005a}, which is implemented using the standard options provided by the $R$ package \textit{MNP} developed by \cite{imai2005b}.
+In table \ref{table:mpc} we report results from the full sample in column (1), from the resident only sample in column (2) and from the observations coming from the NSFH and NSFG surveys alone respectively in column (3) and (4).
+Note that to gain intuition about the size of the results, in  table \ref{table:mpc} we computed the average risk of the event of interest relatively of continue cohabiting.
+The results show that unilateral divorce caused an increase in the duration of cohabitation, which comes from both a reduced hazard of marriage and of breakup.
+While the result about the risk of marriage is not unexpected in light of the estimation results described above, the reduced risk of breakup brings new insights about the possible mechanisms underlying partnership choices.
+In fact, the decrease in the risk of breakup is consistent with a selection effect: some cohabiting couples would have married if mutual consent divorce was still in place.
+If the match quality of cohabitations is lower than the one of marriages,\footnote{This seems plausible because the risk of divorce is much lower than the risk of breakup.} unilateral divorce drives down the risk of breakup because of a selection effect.
+%Cohabitation Length4
+
+	\begin{table}[htbp]\centering
+		\caption{\\Multinomial Probit. Observation: person-month of cohabitation}
+		\label{table:mpc}
+		\begin{threeparttable}[t]\centering
+			\input{mpc.tex}
+			\begin{tablenotes}[flushleft]
+				\footnotesize{\item \textsc{Notes}: the values reported in the table are the mean and the standard deviation (in parenthesis) of the posterior distribution of parameters obtained using the markov chain monte carlo estimation described by \cite{imai2005a}.
+				Coefficients' distributions whose interpercentile range do not contain 0 are denoted by the following system: *90\%, **95\%  and ***99\%.}
+			\end{tablenotes}
+		\end{threeparttable}
+	\end{table}
+
+\FloatBarrier
+\FloatBarrier
+\section{Theory}
+To identify the channels through which unilateral divorce impact partnership choice, we develop a dynamic life-cycle model of partnership formation and dissolution, savings, female labor force participation and home production.
+Couples act cooperatively, and according to the divorce regime they can be subject to limited commitment, which means that there might be renegotiations in response to changes in the outside options, which are assumed to be divorce or breakup.
+Time is discrete and in each period men and women draw their productivities.
 If single, with some probability they meet a potential partner: after drawing a match quality shock they decide whether to marry, cohabit or to stay single.
-Couples observe realization of the match quality shock as well as of their productivity, and according to those they decide whether to stay together or to split.
-Both singles and couples make consumption and savings decisions, using their money for private or public good expenditure.
-Couples also make female labor supply decisions\footnote{We assume that single females and all men work full time.} and female time can be used to produce the public good, but this comes at the cost of a loss in productivity.
-The gains of being in a couple comes from love, risk sharing and labor market specialization.
+Couples observe the match quality shock, their productivity and assets, and according to those they decide whether to stay together or to split.
+Cohabiting couples can also decide whether to marry.
+Both singles and couples make consumption and saving decisions, using their money for private or public good expenditure.
+Couples also make female labor participation decisions and women's time can be used to produce public goods, but this comes at the cost of a loss in productivity.
+%The gains of being in a couple come from love, risk sharing and labor market specialization.
 Instead, the gains of marriage with respect to cohabitation comes from a more functioning risk sharing and a better specialization in time use, which derives from the high cost of divorce serving as a commitment device.
-These gains of marriage deteriorates when the love shock is low enough to cause a high risk of divorce and frequent renegotiations: in this case cohabitation might be the better option, since we assume that the cost of separation will be lower than the cost of marriage.
-	   		\begin{figure}[H]\centering
-	\begin{tikzpicture}[domain=0:1,scale=4]
-	\node [block, name=input,align=center] (sum) {Single\\ 7348};
-	\node [block, above right of=sum, node distance=6cm] (controller) {Separation};
-	\node [block, below right of=controller,
-	node distance=6cm,align=center] (system) {Cohabitation \\ 5308};
-	\draw [<-,  thick, latex-] (controller) -| node[below left]{47,8\%}(system);
-	\node [output, right of=system] (output) {fe};
-	\node [block, below left of=system,  node distance=6cm,align=center] (measurements) {Marriage \\ 2814};
-	\node [block, left of=measurements, node distance=4.2cm,align=left] (divorce) {Divorce};
-	\draw [<-,  thick, latex-] (sum) |- node[below right]{100\%} (controller);
-	\draw [->,  thick, -latex] (sum) -- node[above]{72,4\%} (system);
-	\draw [->,  thick, -latex] (system) |-node[above left]{33,8\%} (measurements);
-	\draw [->,  thick, -latex] (measurements) --node[above]{23,5\%} (divorce);
-	\draw [->,  thick, -latex] (sum) --node[above right]{12,9\%} (measurements);
-	\draw [->,  thick, -latex] (divorce) --node[right]{100\%} (sum);
-	node [near end] {$$} (sum);
-	\end{tikzpicture}
+These gains of marriage deteriorate when the love shock is low enough to cause a high risk of divorce and frequent renegotiations: in this case cohabitation might be the better option, since we assume that the cost of breakup will be lower than the cost of marriage.
+\begin{figure}[h!]
 	\label{fig:scheme}
-	\caption*{\footnotesize \textsc{Notes}: Number of spells and transitions as arising from the data in our sample.}
 	\caption{}
+	\hspace{0.3cm}
+	\resizebox{0.99\textwidth}{!}{\input{graph_transitions2.tex}}
+	\begin{minipage}{0.99\textwidth} % choose width suitably
+		\hspace{3em}
+		{\footnotesize .\par}
+	\end{minipage}
 \end{figure}
 \subsection{Preferences}
-Women $f$ and men $m$ derive utility consuming a private good  $c$ and a household public good $Q$.
-The public good can be interpreted in terms of both the quantity and quality of children, as well as the goods and services produced within the household, as washing clothes  or home cooked meals.
+Women $f$ and men $m$ derive utility from consuming a private good  $c$ and a household public good $Q$.
+The public good can be interpreted in terms of both the quantity and quality of children, as well as the goods and services produced within the household, such as washing clothes or preparing meals.
 Preferences are separable in the two goods and across time.
-Agents derives utility from a couple specific love shock $\psi$ which evolves over time and it can be interpreted as  can be interpreted as the value of love and companionship in a couples.
-The intra period utility of a single agent $s\in(f,m)$ is:
+Agents derives utility from a couple specific love shock $\psi$, which evolves over time and it can be interpreted as the value of love and companionship in a couple.
+The intra-period utility of a single agent $s\in(f,m)$ is:
 \[u(c^s_t,Q^s_t)=\frac{{c^s_t}^{1-\sigma}}{1-\sigma}+\alpha\frac{{Q^s_t}^{1-\xi}}{1-\xi},\]
-where the superscript $s$ on $Q$ accounts for the fact that there is no partner to share the public good. Instead, the utility for  agent $s\in(f,m)$ in a couple is:
+where the superscript $s$ on $Q$ accounts for the fact that there is no partner to share the public good. The utility for an agent $s\in(f,m)$ in a couple is:
 \[u^{C}(c^s_t,Q_t)=\frac{{c_t^s}^{1-\sigma}}{1-\sigma}+\alpha\frac{Q_t^{1-\xi}}{1-\xi}+\psi_t,\]
-where the match quality evolves over time according to the following law of motion:
-\[\psi_t=\psi_{t-1}+\epsilon_t,\text{ where }\epsilon_t \sim\mathcal{N}(0,\sigma^2_{\psi}), \]
-while the love shock at first meeting is allowed to have a different variance $\sigma^2_{\psi,I}$
-\subsection{Home Production}
-In our model each agent in embodied with one unit of time.
-While singles and married men are assumed to supply inelastically one unit of market labor, females in a couple can be out of the labor force to devote their time producing the home good $Q$.
-The public good can be produced buying $d$ goods in the market.
-Following \cite{greenwood2016} we define the production function of home good as:
-\begin{equation}\label{eq:pfunction}
-Q_t=[d_t^\lambda+\kappa {(1-P^f_t)}^\lambda]^{\frac{1}{\lambda}}, \text{ where }0<\lambda<1.
-\end{equation}
-The parameter $\lambda$ captures the degree of  substitutability between female time and the use of durables in the production of the home good.
-This structure implies that when the relative price of durables decreases and when wages goes up, households will use less female time for its production, and hence female employment will increase.
-The variable  $P^f_t$ is a dummy variable that that takes value $1$ when the women is participating in the labor market.
+where the match quality $\psi$ evolves according to the following law of motion:
+\[\psi_t=\psi_{t-1}+\epsilon_t,\text{ where }\epsilon_t \overset{\text{i.i.d.}}{\sim}\mathcal{N}(0,\sigma^2_{\psi}). \]
+The love shock at first meeting can have a different variance, denoted by $\sigma^2_{\psi,I}$.
+Note that if the couple is cohabiting, the utility of the two partners is decreased by $\gamma$, which captures the stigma associated with premarital sex, premarital cohabitation and out-of-wedlock births.
+This assumption fits the fact that for people born in 1940-1955 (whose behavior will be used to build the target moments for the structural estimation) conservative attitudes towards premarital sex were common.\footnote{The shame associated with an out-of-wedlock birth, whose interaction with technology is studied by \cite{fernandez2014}, can be a factor leading young women to prefer marriage over cohabitation even if the rules governing these two partnerships were identical.
+\cite{blasutto2020} can match closely marriage and cohabitation choices using a theoretical framework close to ours, without the need of introducing a stigma component towards cohabitation.
+This is possible because he analyzes the behavior of people born in 1980-1984, for whom the stigma towards premarital sex and premarital cohabitation was low.}
 
@@
 \begin{equation}\label{eq:pcomp}
-z^s_t=z^s_{t-1}-(1-P_t^s) \mu+\zeta^s_{t}\text{, where }\zeta^s_{t}\sim^{iid}\mathcal{N}(0,\sigma^\zeta)\text{, and }\zeta^s_{1}=z^s_{1}.
-\end{equation}
-Note that $\mu$ is the loss in productivity that affects women\footnote{As we anticipated men always participate in the labor market, hence $P^m_t=1$ $\forall$ $t$.} that are not participating in the labor market.
-It can be be interpreted as a reduced form way of capturing both the missed opportunity to accumulate human capital while working as wells as the skill atrophy deriving from interruptions, a phenomenon described by \cite{adda2017}.
-Modeling the loss in productivity for not working is an important feature of our model as it creates an incentive to join the labor force for women that expect to divorce or separate soon.
+z^s_t=z^s_{t-1}-(1-P_t^s) \mu+\zeta^s_{t}\text{, where }\zeta^s_{t}\overset{\text{i.i.d.}}{\sim}\mathcal{N}(0,\sigma_\zeta^{2_s})\text{, and }\zeta^s_{1}=z^s_{1}.
+\end{equation}
+Parameter $\mu$ is the loss in productivity that affects women that are not participating in the labor market.
+Men and single women are always assumed to participate in the labor market, hence $P^m_t=1$.\footnote{The assumption that men, as opposed to women, always participate in the labor market is rather common in the literature (\citealp{ciscato2019,low2018,voena2015}) and it is in line with the gender roles typically observed in the period under analysis.
+In our PSID sample only 5\% of men between 20 and 60 do not supply working hours in the market.} It can be interpreted as a reduced form way of capturing both the missed opportunity to accumulate human capital while working and the skill atrophy from interruptions \citep{adda2017}.
+Modeling the loss in productivity for not working is an important feature of our model as it creates an incentive to join the labor force for women that expect to divorce or breakup soon.
+\subsection{Home Production}
+In our model each agent has one unit of time.
+Singles and men in a couple supply inelastically a fraction $1-\phi$ of their time to the labor market, while women in a couple can be out of the labor force to devote their time producing the home good $Q$.
+The public good can also be produced buying $d$ goods in the market.
+Following \cite{greenwood2016} we define the production function of home goods for couples as:
+\begin{equation}\label{eq:pfunction}
+Q_t=[d_t^\nu+\kappa ({2\phi+(1-P^f_t)(1-\phi))}^\nu]^{\frac{1}{\nu}}, \text{ where }0<\nu<1,
+\end{equation}
+while for singles of gender $s\in\{f,m\}$
+\begin{equation}\label{eq:pfunctions}
+Q^s_t=[(d^s_t)^\nu+\kappa \phi^\nu]^{\frac{1}{\nu}}.
+\end{equation}
+The parameter $\nu$ captures the degree of substitutability between women's time and the use of durables in the production of home goods.
+This structure implies that when the relative price of $d_t$ decreases and when wages goes up,\footnote{The relative price of $d_t$ is normalized to 1 in equations (\ref{eq:pfunction}) and (\ref{eq:pfunctions})} women spend less time producing household goods and their employment outside the home increases.
 \subsection{Budget Constraints}
-The budget constraint of single agents  $s\in\{f,m\}$ is:
+The budget constraint of a single agent of gender  $s\in\{f,m\}$ is:
 \begin{equation}\label{eq:bcs}
-a^s_{t+1}=R a^s_t+w^s_t-c^s_t-d^s_t, \text{ with }a^s_{t+1}\geq0,
-\end{equation}
-where $a^s$ are agent's savings, $w^s$ is the wage and $c^s$ and $d^s$ are consumption in the private good and the expenditure used to produce the public good.
-The budget constraint for a couple instead is:
+a^s_{t+1}=R a^s_t+w^s_t(1-\phi)-c^s_t-d^s_t, \text{ with }a^s_{t+1}\geq0,
+\end{equation}
+where $a^s$ are agent's savings and $w^s$ is the wage. $c^s$ and $d^s$ are the private good consumption and the expenditure used to produce the public good.
+The budget constraint for a couple is:
 \begin{equation}\label{eq:bcm}
-a_{t+1}=R a_t+w^m_t+P^f_t w^f_t-c^f_t-c^m_t-d_t, \text{ with }a_{t+1}\geq0,
-\end{equation}
-where $P^F_t$ is a dummy of female labor force participation.
+a_{t+1}=R a_t+w^m_t(1-\phi)+P^f_t w^f_t(1-\phi)-c^f_t-c^m_t-d_t, \text{ with }a_{t+1}\geq0,
+\end{equation}
+where $P^f_t$ is a dummy of female labor force participation.
 When a couple divorces in $t$, we assume 
 \[a^m_t+a^f_t=\delta a_t,\]
-where $\delta$ is the fraction of total assets $a_t$ left\footnote{The assumption that divorce erodes a fracction of wealth is common to \cite{cubeddu2003}.} after divorce.
-Separation instead comes with no monetary costs\footnote{In reality the monetary cost of separation is likely to be positive.
-We assumed it to be zero because of the difficulties that arises when it comes to identify it.
-In fact, the gap in divorce and separation cost is what is actually needed to match the data.}.
-An important feature of our model is the role of property rights upon divorce, which define how assets are divided.
-We distinguish three cases which define the share of assets $\chi$ going to the women:
-\begin{enumerate}
-\item \textit{Community Property}. Assets are split exactly in half: $\chi=0.5$
-\item \textit{Equitable Distribution}. $\chi\sim\mathcal{U}(1/3,2/3)$.[WHAT I WISH WE HAD]
-\item \textit{Title Based Regime}. $\chi$ is proportional to the productivity of the women compared to the one of the men, formally
-\[\chi=\frac{\exp{z^f}}{\exp{z^f}+\exp{z^m}}.\]
-\end{enumerate}
-It is worth noting that we depart from \cite{voena2015} in the way title based regime is modeled: she assumes that assets are split following a couple decision, while for us the sharing rule depends only on $z^F$ and $z^M$.
-Since in our model relative productivities are the only source of disagreement.
-If we took the modeling assumption of \cite{voena2015} we would still get that the sharing rule is mainly determined by productivities\footnote{If we had individual specific love shocks, our reduced form modeling assumption would give different results instead.}.
-Moreover, if the sharing rule was endogenous, couples would always choose cohabitation over community property or equitable distribution marriage,\footnote{This would happen because separation would have more degrees of freedom that divorce, where it is the court that decides the sharing rule.} which would make matching the data impossible.
+where $\delta$ is the fraction of total assets $a_t$ left after divorce.
+We assume $\delta=0$ for breakup.\footnote{The assumption that divorce erodes a fraction of wealth is common to \cite{cubeddu2003}.
+In appendix \ref{section:eventsa} we provide evidence that divorce results in a loss of net worth for rich but not for poor households.
+Moreover, we do not find evidence for a loss of net worth following breakup for rich and poor households.
+In practice the cost of breakup is positive because of psychological distress associated with a separation and because looking for a new accommodation requires time.
+However, these costs are common with divorce and hence they do not help explaining why couples should choose one partnership over the others.
+This reasoning is confirmed by the fact that when we tried estimating the model allowing for a positive cost of breakup, these parameters was not identified.}
+An important feature of our model is the role of property rights, which defines how assets are divided upon divorce/breakup.
+Since we use data from community property states to estimate the model, this regime applies to divorce.
+Accordingly, upon divorce each spouse keeps half of the assets, while the division of asset upon breakup is a couple decision.
+We describe the details of this choice in this section, where the problem of the cohabiting couple is presented.
 
 \subsection{Problem of the Singles}
-We start by by describing the problem for a single agent $i\in\{f,m\}$ in $t$.
-The agent have to make consumption and saving decisions, and she is also determining expenditure$d^i_t$.
+We start by describing the problem for a single agent $i\in\{f,m\}$ in $t$.
+The agent makes consumption, saving and expenditure decisions.
 In $t+1$ she meets a potential partner $j$ of the opposite sex with probability $\lambda_{t+1}$ and she can decide to enter a partnership, which also depend on whether the potential partner will agree.
-If the two decides to marry, the variable $MA_{t+1}$ will take value 1, while $CO_{t+1}=1$ if the couple decides to cohabit.
-Otherwise, $MA_{t+1}$ and $CO_{t+1}$ will be equal to 0.
-Note we assume singles to always participate in the labor market.
-The state variable of a single then is $\omega^i_t=\{a^i_t,z^i_t\}$, while her choices are represented by the vector $\mathbf{q}^i_t=\{a^i_{t+1},c^i_t,d^i_t\}$.
-We denote by $V_t^{i,S}(\Omega^i_t)$ the value function of agent $s$, which we define as
+If the two decide to marry, the variable $M_{t+1}$ will take value 1, while $C_{t+1}=1$ if the couple decides to cohabit.
+Otherwise, $M_{t+1}$ and $C_{t+1}$ will be equal to 0.
+The state variable of a single is $\omega^i_t=\{a^i_t,z^i_t\}$, while her choices are represented by the vector $\mathbf{q}^i_t=\{a^i_{t+1},c^i_t,d^i_t\}$.
+We denote by $V_t^{i,S}(\omega^i_t)$ the value function of agent $i$, which we define as
 \begin{equation}\label{eq:v_single}
 \begin{split}
-V_t^{iS}(\omega^i_t)=&\max_{\mathbf{q}^i_t} u(c^i_t,Q^i_t)+\beta E_t \bigg\{(1-\lambda_t)V^{iS}_{t+1}(\omega^i_{t+1})+\\ & \quad\quad \lambda_t\big\{(1-Ma_{t+1})(1-CO_{t+1})	V^{i,S}_{t+1}(\omega_{t+1})+\\ &\quad\quad\quad\quad M_{t+1} V^{i,M}_{t+1}(\Omega_{t+1})+ CO_{t+1} V^{i,C}_{t+1}(\Omega_{t+1}) \big\}\bigg\},
-\\ &\text{s.t. \eqref{eq:bcs} and \eqref{eq:pfunction}.} 
+V_t^{iS}(\omega^i_t)=&\max_{\mathbf{q}^i_t} u(c^i_t,Q^i_t)+\beta E_t \bigg\{(1-\lambda_{t+1})V^{iS}_{t+1}(\omega^i_{t+1})+\\ & \quad\quad \lambda_{t+1}\big\{(1-M_{t+1})(1-C_{t+1})	V^{i,S}_{t+1}(\omega_{t+1})+\\ &\quad\quad\quad\quad M_{t+1} V^{i,M}_{t+1}(\Omega_{t+1})+ C_{t+1} V^{i,C}_{t+1}(\Omega_{t+1}) \big\}\bigg\},
+\\ &\text{s.t. \eqref{eq:bcs} and \eqref{eq:pfunctions},} 
 \end{split}
 \end{equation}
+where $V^{i,M}$ and $V^{i,C}$ are the individual values of being married and cohabiting.
 
 \subsection{Household Planning Problem}
-The problem of the couple depends both on the type of relationship, cohabitation or marriage, and on the divorce regime, which can be either \textit{mutual consent} or \textit{unilateral}.
-Separation is always unilateral.
-Under the unilateral regime, one partner can initiate the separation/divorce process alone, while under mutual consent the agreement of both is needed.
+The problem of the couple depends both on the type of relationship---cohabitation or marriage----and on the divorce regime, which can be either \textit{mutual consent} or \textit{unilateral divorce}.
+Breakup is always unilateral.
+Under the unilateral regime, one partner can initiate the breakup/divorce process alone, while under mutual consent the agreement of both partners is needed.
 \subsubsection*{Mutual Consent Regime}
-Under mutual consent marriage $\hat{M}$, couples solve a Pareto problem where the weight\footnote{Refer to \autoref{ssec:marriage_market} for a description about how pareto weight are initially set.} of the wife is $\theta^f$, while the one of the husband is $1-\theta^f$.
-The state vector is $\Omega^{\hat{M}}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^M_t=\{a_{t+1},d_{t},c^m_{t},c^f_{t},P^f_t,D_t\}$, where $D_t$ is a dummy variable that takes value $1$ is divorce happens and $0$ otherwise.
-The formal problem that a couple married is $t$ solve is:
+Under mutual consent regime, marriage is denoted by $\hat{M}$.
+Couples solve a Pareto problem where the weight of the wife is $\theta^f$ and the one of the husband is $1-\theta^f$.\footnote{Later in this section we describe how initial Pareto weight are set.} The state vector is $\Omega^{\hat{M}}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f\}$, while the variables over which the couple maximizes are summarized by the vector $\mathbf{q}^M_t=\{a_{t+1},d_{t},c^m_{t},c^f_{t},P^f_t,D_t\}$, where $D_t$ is a dummy variable that takes value $1$ is divorce happens and $0$ otherwise.
+The formal problem solved by a couple who enters period $t$ as married is:
 \begin{equation}\label{eq:v_mutual}
 \begin{split}
-V_t^{\hat{M}}(\Omega^{\hat{M}}_t)=&\max_{\mathbf{q}^M_t} (1-D_t)\{\theta^f u(c^f_t,Q_t)+(1-\theta^f)u(c^m_t,Q_t)+\psi_t+\beta E_t V^{\hat{M}}_{t+1}(\Omega^{\hat{M}}_{t+1})\}\\ &\quad\quad+D_t \{\theta^fV^{fS}_{t}(\omega^{f}_{t+1})+(1-\theta^m)  V^{mS}_{t}(\omega^{m}_{t}))\}
+V_t^{\hat{M}}(\Omega^{\hat{M}}_t)=&\max_{\mathbf{q}^M_t} (1-D_t)\{\theta^f u(c^f_t,Q_t)+(1-\theta^f)u(c^m_t,Q_t)+\psi_t+\beta E_t V^{\hat{M}}_{t+1}(\Omega^{\hat{M}}_{t+1})\}\\ &\quad\quad+D_t \{\theta^fV^{fS}_{t}(\omega^{f}_{t})+(1-\theta^f)  V^{mS}_{t}(\omega^{m}_{t}))\}
 \\ &\text{if $D_t=0$:}\hspace{35pt}\text{s.t. \eqref{eq:bcm} and \eqref{eq:pfunction}
 }
-\\ &\text{if $D_t=1$:}\hspace{35pt}\text{s.t. \eqref{eq:bcs}, \eqref{eq:pfunction} for $i\in\{f,m\}$,}\\ &
-\hspace{80pt}a_t^m+a_t^f=\delta a_t,	\\ &
-\hspace{80pt}a_t^m,a_t^f\text{ determined according to property right regime,}	\\ &\hspace{80pt}
-V_{t}^{fS}(\omega^f_{t})> W^{f\hat{M}}_{t}(\Omega^{\hat{M}}_{t}),\\ &\hspace{80pt}
-V_{t}^{mS}(\omega^m_{t})> W^{m\hat{M}}_{t}(\Omega^{\hat{M}}_{t}).
+\\ &\text{if $D_t=1$:}\hspace{35pt}\text{s.t. \eqref{eq:bcs}, \eqref{eq:pfunctions} for $i\in\{f,m\}$,}\\ &
+\hspace{80pt}a_t^m+a_t^f=\delta a_t,	\\ &\hspace{80pt}
+V_{t}^{fS}(\omega^f_{t})\ge W^{f\hat{M}}_{t}(\Omega^{\hat{M}}_{t}),\\ &\hspace{80pt}
+V_{t}^{mS}(\omega^m_{t})\ge W^{m\hat{M}}_{t}(\Omega^{\hat{M}}_{t}).
 \end{split}
@@
 \begin{equation}
-W_{t}^{i\hat{M}}=u(\tilde{c}_t^{i},\tilde{Q}_t)+\psi_t+\beta E_t V_{t}^{i\hat{M}}(\Omega^{\hat{M}}_{t+1}),
-\end{equation}
-where $\mathbf{\tilde{q}}^{\hat{M}}_t=\{\tilde{a}_{t+1},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$ is the $\argmax$ of problem \eqref{eq:v_mutual} conditionally on having chosen $D_t=0$.
-$V_{t+1}^{i\hat{M}}(\Omega^{\hat{M}}_{t+1})$ instead can be obtained by the expectation of the sum of the time utilities that the agent get from $t+1$ to $T$, where the variables entering the utility function derive derive from the the pareto problem if the agent is in a relationship, otherwise they are the solution of \eqref{eq:v_single}.
-Under mutual consent regime the pareto weight is never rebargained, which makes risk sharing efficient.
-It also makes harder a divorce to happen, since the member that after a shock is relatively worse off can exercise her veto power to avoid a divorce: this feature makes labor specialization easier.
+W_{t}^{i\hat{M}}=u(\tilde{c}_t^{i},\tilde{Q}_t)+\psi_t+\beta E_t V_{t+1}^{i\hat{M}}(\Omega^{\hat{M}}_{t+1}),
+\end{equation}
+where $\mathbf{q}^{\hat{M}}_t=\{\tilde{a}_{t+1},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$ is the $\argmax$ of problem \eqref{eq:v_mutual} conditionally on having chosen $D_t=0$.
+$V_{t+1}^{i\hat{M}}(\Omega^{\hat{M}}_{t+1})$ instead can be obtained by the expectation of the sum of the time utilities that the agent gets from $t+1$ to $T$, where the variables entering the utility function derive from the Pareto problem if the agent is in a relationship, otherwise they are the solution of \eqref{eq:v_single}, which represent the singles' problem.
+
+ Under the mutual consent regime, the allocation corresponds to the Pareto efficient solution if the couple is intact.
+Intuitively, the fact that Pareto weights stay constant allows for a functioning risk-sharing and the female labor force participation decisions are taken cooperatively, ruling out the possibility that women over-supply labor to increase their bargaining power.
+In this framework, the conditions for divorce are particularly stringent: the couple splits only if both partners are better off divorcing than staying together for a feasible allocation.
+More in particular, if one spouse only wishes to divorce under the divorce allocation dictated by the law where assets are split equally, she will ``bribe'' the other by offering a larger share of assets to make her indifferent between staying married and divorcing.\footnote{Note that if both partners are better off divorcing under the sharing rule dictated by the law, which corresponds to an equal division in community property states, no bribing happens.}
 \subsubsection*{Unilateral Divorce Regime}
-Under the unilateral divorce regime, denoted by $\overline{M}$, couples solve a Pareto problem where the weight of the wife is $\theta^f_t$ and the one of the husband is $\theta^m_t$.
-Note that, in opposition to the mutual consent regime, now pareto weights are allowed to vary over time.
-This happes whenever a member of the couple is better off divorcing: the other member will try to convinve her not to split offering her a larger share of resources.
-The state vector of this proble is $\Omega^{\overline{M}}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^M_t$.
-The formal problem that a couple married at $t$ solves is:
+Under the unilateral divorce regime marriage is denoted by $\overline{M}$.
+Couples solve a Pareto problem where the weight of the wife is $\theta^f_t$ and the one of the husband is $\theta^m_t$.
+Note that, in opposition to the mutual consent regime, Pareto weights can vary over time.
+The state vector of this problem is $\Omega^{\overline{M}}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^M_t$.
+The formal problem of a couple entering $t$ as married is:
 \begin{equation}\label{eq:v_uni}
 \begin{split}
-V_t^{\overline{M}}(\Omega^{\overline{M}}_t)=&\max_{\mathbf{q}^M_t} (1-D_t)\{\theta^f_{t+1} u(c^f_t,Q_t)+\theta^m_{t+1} u(c^m_t,Q_t)+\psi_t+\beta E_t V^{\overline{M}}_{t+1}(\Omega^{\overline{M}}_{t+1})\}\\ &\quad\quad+D_t \{\theta^f_{t}V^{fS}_{t}(\omega^{f}_{t+1})+\theta^m_{t} V^{mS}_{t}(\omega^{m}_{t}))\}
+V_t^{\overline{M}}(\Omega^{\overline{M}}_t)=&\max_{\mathbf{q}^M_t} (1-D_t)\{\theta^f_{t} u(c^f_t,Q_t)+\theta^m_{t} u(c^m_t,Q_t)+\psi_t+\beta E_t V^{\overline{M}}_{t+1}(\Omega^{\overline{M}}_{t+1})\}\\ &\quad\quad+D_t \{\theta^f_{t}V^{fS}_{t}(\omega^{f}_{t+1})+\theta^m_{t} V^{mS}_{t}(\omega^{m}_{t}))\}
 \\ &\text{if $D_t=0$:}\hspace{35pt}\text{s.t. \eqref{eq:bcm} and \eqref{eq:pfunction},}\\ &\hspace{80pt}
@@
 \hspace{80pt}a_t^m+a_t^f=\delta a_t,	\\ &
-\hspace{80pt}a_t^m,a_t^f\text{ determined according to property right regime},
+\hspace{80pt}a_t^m=a_t^f,
 \end{split}
@@
 \end{equation}
-Note that $\mu^i_t$ are the langrange multipliers associated with spouses' participation constraints.
-Similarly to mutual consent regime, the individual value of marriage conditional on $D_t=0$ is  $W_{t}^{i\overline{M}}$ for $i\in\{f,m\}$, and it is defined as 
+Note that $\mu^i_t$ are the Lagrange multipliers associated with spouses' participation constraints.
+The individual value of marriage conditional on $D_t=0$ is denoted by $W_{t}^{i\overline{M}}$ and it can be obtained following the procedure described in the mutual consent regime section.
+
+Under the unilateral divorce regime Pareto weights vary every time one participation constraint is binding.
+Whenever a spouse is better off divorcing, the other member will try to convince her not to split by offering her a larger bargaining power, such that she is indifferent between divorcing and staying married.
+In this framework risk-sharing is less functional than under the mutual consent regime, since variations in the Pareto weight imply less smooth consumption patterns over time.
+Labor market specialization is also less functioning, since conditionally on having the same state variables, the risk of divorce is higher, which makes women willing to insure against this event through labor market participation.
+While cooperation is more effective under mutual consent than unilateral divorce, it is still possible that the individual value of being married under the latter regime is larger.
+This is possible because of the possibility to exit marriage without the consent of the other spouse.
+
+%Property rights upon divorce plays a significant role when splitting is unilateral: for example under community properly the least wealthy member can bargain a higher share of resources since the threat of divorce is real.
+This could not happen under a title-based regime.
+\subsubsection*{Cohabitation}
+The problem of cohabiting couples is like the one of marriage under the unilateral divorce regime, but it differs from it for three crucial reasons.
+First, there is no loss in assets upon breakup.
+Second, the choice set of the cohabiting couple $\mathbf{q}^C_t=\{a_{t+1},d_t,c^m_t,c^f_t,P^f_t,D_t,M_t,\chi_{t+1}\}$ and the state variables $\Omega^{C}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t,\chi_t\}$ are different.
+Note that $M_t$ is dummy that indicates the choice of marrying and $\chi_t$ is the share of assets going to the women in case of breakup.\footnote{Note that while cohabiting couples can decide to marry, married couples cannot decide to cohabit.
+This asymmetry is not relevant because married couples would never decide to divorce and start cohabiting, even if they could.} Third, the time utility of cohabiting couple is decreased by $\gamma$.
+%Cohabiting couples, denoted by $C$, solve a pareto problem where the weight of the wife is $\theta^f_t$ and the one of the husband is $\theta^m_t$.The state vector is $\Omega^{C}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^C_t=\{a_{t+1},d_t,c^m_t,c^f_t,P^f_t,S_t,MA_t\}$.
+$S_t$ and ${M}_t$ are dummy variable that take value $1$ is the couple respectively breackup or marry\footnote{We denote marriage by $M$, which might be fall under unilateral divorce regime $\overline{M}$ or mutual consent $\hat{M}$.} and 0 otherwise.
+The formal problem that a cohabiting couple at $t$ solves is:
+%\begin{equation}\label{eq:v_coh}
+%\begin{split}
+%V_t^{C}(\Omega^{C}_t)=&\max_{\mathbf{q}^C_t} (1-S_t)\{\theta^f_{t+1} u(c^f_t,Q_t)+\theta^m_{t+1} u(c^m_t,Q_t)+\psi_t-\gamma+\beta E_t V^{C}_{t+1}(\Omega^{C}_{t+1})\}
+%\\ &\quad\quad+MA_t\{\theta^f_{t+1} u(c^f_t,Q_t)+\theta^m_{t+1} u(c^m_t,Q_t)+\psi_t+\beta E_t V^{M}_{t+1}(\Omega^{M}_{t+1})\}\\ &\quad\quad\quad\quad+S_t \{\theta^f_{t}V^{fS}_{t}(\omega^{f}_{t+1})+\theta^m_{t} V^{mS}_{t}(\omega^{m}_{t}))\}
+%\\ &\text{if $S_t=0$:}\hspace{35pt}\text{s.t. \eqref{eq:bcm} and \eqref{eq:pfunction},}\\ &\hspace{80pt}
+%\theta^f_{t+1}=\theta^f_{t}+\mu^f_t,\\ &\hspace{80pt}
+%\theta^m_{t+1}=\theta^m_{t}+\mu^m_t,
+%\\ &\text{if $S_t=1$:}\hspace{35pt}\text{s.t. \eqref{eq:bcs}, \eqref{eq:pfunction} for $i\in\{f,m\}$,}\\ &
+%\hspace{80pt}a_t^m+a_t^f= a_t,	\\ &
+%\hspace{80pt}a_t^m,a_t^f\text{ determined as in the title-based regime},
+%\end{split}
+%\end{equation}
+%where $\theta^f_{t+1}$ and $\theta^m_{t+1}$ adjust such that the following participation constraints are satisfied:
+%\begin{equation}\label{eq:p_cons_coh}
+%\begin{split}
+%&
+%W^{fC}_{t}(\Omega^{C}_{t})\geq V_{t}^{fS}(\omega^f_{t}),\\ &
+%W^{mC}_{t}(\Omega^{C}_{t})\geq V_{t}^{mS}(\omega^m_{t}). 
+%\end{split}
+%\end{equation}
+%Note that $\mu^i_t$ are the Lagrange multipliers associated with spouses' participation constraints.
+%The individual value of cohabitation conditional on $S_t=$ is  $W_{t}^{iC}$ for $i\in\{f,m\}$, and it is defined as 
+%\begin{equation}
+%W_{t}^{iC}=u(\tilde{c}_t^{i},\tilde{Q}_t^{i})+\psi_t-\gamma+\beta E_t V_{t+1}^{iC}(\Omega^{C}_{t+1}),
+%\end{equation}
+%where
+%$\mathbf{\tilde{q}}^{C}_t=\{\tilde{a}_{t+1},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$ is the $\argmax$ of problem \eqref{eq:v_mutual} conditionally on having chosen $S_t=0$.
+$V_{t+1}^{iC}(\Omega^{C}_{t+1})$ instead can be obtained by the expectation of the sum of the time utilities that the agent get from $t+1$ to $T$, where the variables entering the utility function derive from the pareto problem if the agent is in a relationship, otherwise they are the solution of \eqref{eq:v_single}.
+Similarly to the unilateral divorce regime, we assume that the planner evaluates the welfare of the two members of the couple if a breakup happens with the current Pareto weights.
+
+The fact that there is not breakup cost makes risk-sharing and cooperation less functional compared to marriage.
+This happens because the couple is left without a commitment-enhancing technology, which would have allowed the couple to improve its ability to commit.\footnote{Under the limit case of an infinite cost of splitting, as long as the couple stays intact the allocation under the mutual consent and unilateral divorce regimes are the same and correspond to the inter-temporal Pareto-efficient allocation.} On the other hand, assuming no cost of breakup makes cohabitation more appealing to couples whose risk of splitting is high.
+For example, this is the case of couples with a low match quality.
+
+ Property rights upon divorce/breakup differ between marriage and cohabitation.
+In the former, assets are divided equally when the couple splits, while in the latter assets are divided according to individual property rights.
+We model property rights at breakup following \cite{bayot2015}, where upon divorce assets are split following the sharing rule decided by the couple in the previous period.\footnote{\cite{bayot2015} study the choice between community and separation of property in Italy.
+Separation of property resembles the American title-based regime, which also applies to cohabitation.} They show that this regime is always preferred to community property if outside options are invariant to property right regimes.
+In our framework this result implies that if the cost of breaking up was the same as the one of divorcing and there was no stigma towards cohabitation, the value of cohabitation would always be higher than the one of marriage.
+The benefits of having a positive cost of divorce and the stigma linked to cohabitation allows us to generate a positive number of marriages and to match the data.
+
+\subsection{Partnership Choice and the Mating Market}\label{ssec:marriage_market}
+In each period $t$ singles have a probability $\lambda_t$ to meet a potential partner.
+The productivity and the assets of the potential partner depends on the single agent's characteristics.
+Formally, the assets of the potential partner are defined as:
+\begin{equation}\label{eq:mma}
+\ln(a^p_t)=\ln(a^s_t)+\overline{a}^{s}+\epsilon^a,
+\end{equation}
+where $a^s_t$ are the assets of the individual, $\overline{a}^{s}_t$ is a number that depends on gender and $\epsilon^a$ is a normally distributed shock.
+Instead, the productivity of the potential partner is defined as:
+\begin{equation}\label{eq:mmz}
+z_t^p=f(\overline{z}^{s^*,i^*}_t,z^r_t,\epsilon^z),
+\end{equation}
+where $\overline{z}^{s^*,i^*}_t$ represents the average productivity of singles of gender $s^*$,  $z^r_t$ is the productivity of the agent net of the gender and education specific trend, while $\epsilon^z$ is a normally distributed shock.
+These assumptions capture in a reduced from fashion that people are mating assortatively both within marriage and cohabitation.
+Once the meeting happened, agents must decide whether to stay in a couple and eventually decide which partnership contract to choose and they must pick a Pareto weight.
+We now describe how these decisions are taken.
+Note that for the rest of this section we will refer to marriage as $M$, where $M \ \in\{\hat{M},\overline{M}\}$ depending on the divorce regime.
+The decisions follow a three-steps procedure.
+\begin{enumerate}
+\item The couple considers marriage $M$ (cohabitation $C$) as a viable alternative if the set of Pareto weights $\theta^f$ such that the couple prefers to marry (cohabit) is non-empty.\footnote{Without loss of generality, we impose $\theta^f_t+\theta^m_t=1$ at first meeting.} Formally, for relationship $J\in\{M,C\}$ the set is
+\begin{equation}\label{eq:set_couple}
+\Theta^J_t(\Omega^J_t,\omega^f_t,\omega^m_t)=\big\{\theta_t^f: V_t^{fJ}(\Omega^J_t)\geq V_t^{fS}(\omega^f_t), V_t^{mJ}(\Omega^J_t)\geq V_t^{mS}(\omega^m_t)\big\}.
+\end{equation}
+\item If the set for marriage (cohabitation) is non-empty, the Pareto weight for the potential marriage $\theta^{M,f}_t$ (cohabitation $\theta^{C,f}_t$) is set through symmetric Nash Bargaining.\footnote{The assumption that the initial Pareto weight is pinned down by Nash Bargaining can be found in \cite{mazzocco2007} and \cite{low2018}.} Formally $\theta^{J,f}_t$ is set to :
+\begin{equation}\label{nash_couple}
+\theta^{J,f}_t= \argmax_{\theta^f_t\in\Theta^J_t} \Upsilon^J(\theta^f_t,\Omega^{J-1}_t,\omega^f_t,\omega^m_t),
+\end{equation}
+where $\Omega^{J-1}_t$ is the state vector of the couple excluding Pareto weights and
 \begin{equation}
-W_{t}^{i\overline{M}}=u(\tilde{c}_t^{i},\tilde{Q}_t)+\psi+\beta E_t V_{t+1}^{i\overline{M}}(\Omega^{\overline{M}}_{t+1}),
-\end{equation}
-where
-$\mathbf{\tilde{q}}^{\overline{M}}_t=\{\tilde{a}_{t+1},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$ is the $\argmax$ of problem \eqref{eq:v_mutual} conditionally on having chosen $D_t=0$.
-$V_{t+1}^{i\hat{M}}(\Omega^{\overline{M}}_{t+1})$ instead can be obtained by the expectation of the sum of the time utilities that the agent get from $t+1$ to $T$, where the variables entering the utility function derive derive from the the pareto problem if the agent is in a relationship, otherwise they are the solution of \eqref{eq:v_single}.
-Note that we follow the literature assuming that the planner evaluates the welfare of the two members of the couple if a divorce happens with the current Pareto weights.
-Under the unilaral divorce regime pareto weights varies every time one participation constraint is binding, which makes risk sharing worse than in the mutual divorce regime.
-Labor market specialisation is also less functioning, since the higher risk of divorce makes women willing to insure against this event through labor market participation.
-Property rights upon divorce plays a significative role when splitting is unilateral: for example under community propery the least wealthy member can bargain a higher share of resources since the threat of divorce is real.
-This could not happen under a title based regime.
-\subsubsection*{Cohabitation}
-Cohabiting couples, denoted by $C$, solve a pareto problem where the weight of the wife is $\theta^f_t$ and the one of the husband is $\theta^m_t$.The state vector is $\Omega^{C}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^C_t=\{a_{t+1},d_t,c^m_t,c^f_t,P^f_t,S_t,MA_t\}$.
-$S_t$ and ${MA}_t$ are dummy variable that take value $1$ is the couple respectively separate of marry\footnote{We denote marriage by $M$, which might be fall under unilateral divorce regime $\overline{M}$ or mutual consent $\hat{M}$.} and 0 otherwise.
-The formal problem that a cohabiting couple at $t$ solves is:
-\begin{equation}\label{eq:v_coh}
-\begin{split}
-V_t^{C}(\Omega^{C}_t)=&\max_{\mathbf{q}^C_t} (1-S_t)\{\theta^f_{t+1} u(c^f_t,Q_t)+\theta^m_{t+1} u(c^m_t,Q_t)+\psi_t+\beta E_t V^{C}_{t+1}(\Omega^{C}_{t+1})\}
-\\ &\quad\quad+MA_t\{\theta^f_{t+1} u(c^f_t,Q_t)+\theta^m_{t+1} u(c^m_t,Q_t)+\psi_t+\beta E_t V^{M}_{t+1}(\Omega^{M}_{t+1})\}\\ &\quad\quad\quad\quad+S_t \{\theta^f_{t}V^{fS}_{t}(\omega^{f}_{t+1})+\theta^m_{t} V^{mS}_{t}(\omega^{m}_{t}))\}
-\\ &\text{if $S_t=0$:}\hspace{35pt}\text{s.t. \eqref{eq:bcm} and \eqref{eq:pfunction},}\\ &\hspace{80pt}
-\theta^f_{t+1}=\theta^f_{t}+\mu^f_t,\\ &\hspace{80pt}
-\theta^m_{t+1}=\theta^m_{t}+\mu^m_t,
-\\ &\text{if $S_t=1$:}\hspace{35pt}\text{s.t. \eqref{eq:bcs}, \eqref{eq:pfunction} for $i\in\{f,m\}$,}\\ &
-\hspace{80pt}a_t^m+a_t^f= a_t,	\\ &
-\hspace{80pt}a_t^m,a_t^f\text{ determined as in the title based regime},
-\end{split}
-\end{equation}
-where $\theta^f_{t+1}$ and $\theta^m_{t+1}$ adjust such that the following participation constraints are satisfied:
-\begin{equation}\label{eq:p_cons_coh}
-\begin{split}
-&
-W^{fC}_{t}(\Omega^{C}_{t})\geq V_{t}^{fS}(\omega^f_{t}),\\ &
-W^{mC}_{t}(\Omega^{C}_{t})\geq V_{t}^{mS}(\omega^m_{t}). 
-\end{split}
-\end{equation}
-Note that $\mu^i_t$ are the langrange multipliers associated with spouses' participation constraints.
-The individual value of cohabitation conditional on $S_t=$ is  $W_{t}^{iC}$ for $i\in\{f,m\}$, and it is defined as 
-\begin{equation}
-W_{t}^{iC}=u(\tilde{c}_t^{i},\tilde{Q}_t^{i})+\psi_t+\beta E_t V_{t+1}^{iC}(\Omega^{C}_{t+1}),
-\end{equation}
-where
-$\mathbf{\tilde{q}}^{C}_t=\{\tilde{a}_{t+1},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$ is the $\argmax$ of problem \eqref{eq:v_mutual} conditionally on having chosen $S_t=0$.
-$V_{t+1}^{iC}(\Omega^{C}_{t+1})$ instead can be obtained by the expectation of the sum of the time utilities that the agent get from $t+1$ to $T$, where the variables entering the utility function derive derive from the the pareto problem if the agent is in a relationship, otherwise they are the solution of \eqref{eq:v_single}.
-Similarly to the unilateral divorce regime, we assume that the planner evaluates the welfare of the two members of the couple if a separation happens with the current Pareto weights.
-
-The cohabitation problem is similar to the one of marriage under the unilateral divorce regime, but two main features are different.
-First, the way assets are split within cohabitation might not be the same, and total assets are not eroded when separation happens.
-On the one hand this makes risk sharing and cooperation less functioning than in marriage with unilateral divorce, since the couple is left without a commitment-enhancing technology.
-On the other hand, assuming no cost of separation makes cohabitation more appealing to couples with a low surplus of being in a couple.
-Since for them splitting if very likely, they prefer the relationship that allow them to do it in a cheaper way.
-
-\subsection{Partnership Choice and the Mating Market}\label{ssec:marriage_market}
-In each period $t$ singles have a probability $\lambda_t$ to meet a potential partner of their same age and with a productivity and wealth that depends on their productivity $z_t$ and assets $a_{t}$.
-Formally:
-\begin{equation}\label{mma}
-\ln(a^p_t)=\ln(a_{t})+\hat{\epsilon}\text{, where }\hat{\epsilon}\sim\mathcal{N}(0,\sigma^2_{\hat{p}}),
-\end{equation}
-\begin{equation}\label{mmz}
-z^p_t=z_{t}+\tilde{\epsilon}\text{, where }\tilde{\epsilon}\sim\mathcal{N}(0,\sigma^2_{\tilde{p}}).
-\end{equation}
-These assumptions allow us to capture in a reduced from fashion that people are mating assortatively\footnote{In the life cycle models featured in \cite{ciscato2019}, \cite{shephard2019} and \cite{reynoso2019} assortative mating arise in marriage markets through the interactions of preferences, incentives, supply and demand forces.} both within marriage and cohabitation, as \cite{gemici2014} point out.
-Once the meeting happened, agents have to decide whether to stay in a couple and eventually decide which partnership contract to choose.
-Note that for the rest of this section we will refer to marriage as $M$, but depending on property rights upon divorce we have $M \ \in\{\hat{M},\overline{M}\}$.
-We model their choices in three steps.
-\begin{enumerate}
-\item The couple considers marriage $M$ (cohabitation $C$) as a viable alternative if the set of pareto weights\footnote{Without loss of generality, we impose $\theta^f+\theta^m=1$ at first meeting.} $\theta^f$ such that the couple prefers to marry (cohabit) is non-empty.
-Formally, for relationship $J\in\{M,C\}$ the set is
-\begin{equation}\label{eq:set_couple}
-\Theta^J_t(\Omega^J_t,\omega^f_t,\omega^m_t)=\big\{\theta_t: V_t^{fJ}(\Omega^J_t)\geq V_t^{fS}(\omega^f_t), V_t^{mJ}(\Omega^J_t)\geq V_t^{mS}(\omega^m_t)\big\}.
-\end{equation}
-\item If the set for marriage (cohabitation) is non-empty, the pareto weight for the potential marriage $\theta^{m,f}$ (cohabitation $\theta^{c,f}$) is set through symmetric Nash Bargaining.\footnote{The assumption that the initial pareto weight is pinned down by Nash Bargaining can be found in \cite{low2018}.} Formally\footnote{For consistency with the rest of the paper we define $\Omega^{J,-1}_t$ as the state vector for the couple excluding pareto weights.}, for $J\in\{M,C\}$ $\theta^{J,f}$ is set to :
-\begin{equation}\label{nash_couple}
-\theta^{J,f}_t= \argmax_{\theta^f_t\in\Theta^J_t} \Upsilon^J(\theta^f_t,\Omega^{J,-1}_t,\omega^f_t,\omega^m_t),
-\end{equation}
-where
-\begin{equation}
-\Upsilon^J(\theta^f_t,\Omega^{J,-1}_t,\omega^f_t,\omega^m_t)=\big[V_t^{fJ}(\Omega^{J,-1}_t)- V_t^{fS}(\omega^f_t)\big]\times\big[ V_t^{mJ}(\Omega^{J,-1}_t)- V_t^{mS}(\omega^m_t)\big].
-\end{equation}
-\item Four possible situation can arise:
+\Upsilon^J(\theta^f_t,\Omega^{J-1}_t,\omega^f_t,\omega^m_t)=\big[V_t^{fJ}(\Omega^{J-1}_t)- V_t^{fS}(\omega^f_t)\big]\times\big[ V_t^{mJ}(\Omega^{J-1}_t)- V_t^{mS}(\omega^m_t)\big].
+\end{equation}
+\item Four possible situations can arise:
 \begin{itemize}
@@
 \item $\Theta^M_t\neq\O\text{ and }\Theta^C_t\neq\O \Rightarrow$ The couple chooses the partnership that gives the largest Nash product.
-Formally, if $ \Upsilon^M(\Omega^M_t,\omega^f_t,\omega^m_t)\geq\Upsilon^C(\Omega^C_t,\omega^f_t,\omega^m_t)$, otherwise cohabit.
+Formally, if $ \Upsilon^M(\Omega^M_t,\omega^f_t,\omega^m_t)\geq\Upsilon^C(\Omega^C_t,\omega^f_t,\omega^m_t)$ the couple chooses marriage, otherwise cohabitation.
 \end{itemize}
-This framework is a natural extension of the nash bargaining problem\footnote{Note that we could have chosen a different protocol for determining the choice between marriage and cohabitation.
-For example, we could have decided to impose a sequential structure to the problem, assuming that first agents compare cohabitation to singleness, obtaining the envelop of the two, where the pareto weight is set as above.
-Then, the agents make their final choice solving a pareto problem where the outside option is the outcome of the first step.
-We tried applying this methodology: results were indistinguishable from our main strategy.} to discrete choices [CITATION OF RELEVANT PAPER HERE].
 \end{enumerate}
 \section{Estimation}
+We estimate the structural model following a two-step procedure.
+The first step is to set some parameters following the literature or by matching some features of the data without the need to simulate the model.
+In particular, we estimate the labor income processes of men and women outside the model: this procedure is common in the literature because it reduces the burden on structural estimation.\footnote{See for example \cite{voena2015}, \cite{reynoso2019} and \cite{gourinchas2002}.}
+The second step is to estimate by indirect inference the remaining parameters of the model.
+In this section we detail the steps of the estimation, we discuss the identification of the structural parameters and we present the results.
+\subsection{Income Processes}
+The income processes of men and women are estimated using the $1968$-$1993$ waves of the PSID, including people between age 20 and 65.
+We further restrict our sample by retaining men who are household heads or men who are married/cohabiting with the household head or who are household heads themselves.
+Similarly to \cite{low2018}, we drop observations where the hourly wage is less than half the minimum wage and where the hourly wage changes by more than 125\% in two subsequent years.
+We compute the hourly wage rate of men and women dividing the annual labor income by the number of yearly working hours supplied.
+This procedure avoids considering a variation in working hours as a productivity shock.
+This correction is particularly relevant for the estimation of the income process of women, because their hours worked vary significantly over the life-cycle.
+
+The income process of men is estimated by fitting the following liner model:
+\begin{equation}\label{eq:male_earn}
+\ln(w^m_{i,t,s,sur})=\iota^m_0+\iota^m_1*t+\iota^m_2*t^2+\delta_s+\nu_{sur}+u_{i,t,s,sur}^m,
+\end{equation}
+where $i$ stands for individual, $t$ for age, $s$ for state and $sur$ for survey year.
+Moreover, $u_{i,t,s,sur}^m=z_t^m+e^m_{i,t,s,sur}$, where $z_t^m$ follows equation $\ref{eq:pcomp}$, while $e^m_{i,t,s,sur}$ is the measurement error.
+Instead, $\delta_s$ are state fixed effects and $\nu_{sur}$ are year of the survey fixed effects.
+The results are reported in table \ref{table:inc_men}.
+Then, using the residuals  $\hat{u}_{t}^m$, we estimate through GMM  1) the variance of the permanent component of income $\sigma_\zeta^{2_m}$, 2) the variance of the measurement error $\sigma_e^{2_m}$ using the following conditions:
+\begin{equation}\label{eq:male_gmm}
+\begin{split}
+E((\Delta\hat{u}_{t}^m)^2)&=\sigma_\zeta^{2_m}+2\sigma_e^{2_m}\\
+E(\Delta\hat{u}_{t}^m\Delta\hat{u}_{t-1}^m)&=-\sigma_e^{2_m}
+\end{split}
+\end{equation}
+Results are reported in table \ref{table:income_params}.
+
+The estimation of women's income process differs from the men's one since we need to consider the endogeneity of female labor force participation.
+We do so by using a two-step Heckman selection correction procedure.
+The first step consists in estimating a probit model where the dependent variable is female labor force participation and the independent variables includes all the regressors in equation (\ref{eq:male_earn}) plus the interaction of a dummy variable for unilateral divorce with the dummy variables for the property rights regimes upon divorce.
+These variables are used as exclusion restriction following the work of \cite{voena2015}, who finds that these affect female labor force participation by influencing intra-household bargaining.\footnote{\cite{voena2015} and \cite{reynoso2019} already used the interaction between grounds of divorce and division of property as an exclusion restriction for female labor force participation.} Women participate in the labor market if
+\begin{equation}\label{eq:femae_part}
+\gamma'\mathbf{Z}_{i,t,s,sur}+\pi_{i,t,s,sur}>0,
+\end{equation}
+where $\pi_{i,t,s,sur}$ is the sum of the measurement error and the permanent component of income and $\mathbf{Z}_{i,t,s,sur}$ contains the regressors.
+The second setup is estimating the following linear model:
+\begin{equation}\label{eq:femae_earn}
+\ln(w^f_{i,t,s,sur})=\iota^f_0+\iota^f_1*t+\iota^f_2*t^2+\delta_s+\nu_{sur}+\varphi_{i,t,s,sur}+u_{i,t,s,sur}^f,
+\end{equation}
+where $i$ stands for individual, $t$ for age, $s$ for state and $sur$ for survey year.
+Moreover, $u_{i,t,s,sur}^f=z_t^f+e^f_{i,t,s,sur}$.
+$z_t^f$ follows equation $\ref{eq:pcomp}$, while $e^f_{i,t,s,sur}$ is the measurement error.
+Instead, $\delta_s$ are state fixed effects and $\nu_{sur}$ are year of the survey fixed effects.
+The endogeneity of female labor force participation is considered by controlling for $\varphi_{i,t,s,sur}$, the inverse of the Mills ratio of the prediction obtained in the first step.
+The estimation results of the two steps are reported in tables \ref{table:prb_wom} and \ref{table:inc_wom}.
+We then use the regression residuals from the second step $\hat{u}_{t}^m$  to estimate through GMM 1) the variance of the permanent component of income $\sigma_\zeta^{2_f}$, 2) the variance of the measurement error $\sigma_e^{2_f}$ using the following conditions:\footnote{The conditions are those used by \cite{low2018}.}
+\begin{equation}\label{eq:female_gmm}
+\begin{split}
+E(\Delta\hat{u}_{t}^f | P^f_t=1,P^f_{t-1}=1)&=\sigma_\pi^{f}\frac{\phi(\tau_t)}{1-\Phi(\tau_t)},\\
+E((\Delta\hat{u}_{t}^{f})^2 | P^f_t=1,P^f_{t-1}=1)&=\sigma_\zeta^{2_f}+\sigma_\pi^{2_f}+2\sigma_e^{2_f}+\tau_t\frac{\phi(\tau_t)}{1-\Phi(\tau_t)},\\
+E(\Delta\hat{u}_{t}^f\Delta\hat{u}_{t-1}^f | P^f_t=1,P^f_{t-1}=1,P^f_{t-2}=1))&=-\sigma_e^{2_f}.
+\end{split}
+\end{equation}
+where $\phi()$ and $\Phi()$ are respectively the density and the distribution function of a standardized normal,  while $\tau_t=-\gamma'\mathbf{Z}_{i,t,s,sur}$.
+Results are displayed in table \ref{table:income_params}.
+
+\begin{table}[H]
+\caption{\\Parameters of the income processes} % title of Table
+\centering % used for centering table
+\begin{threeparttable}
+\begin{tabular}{@{\extracolsep{5pt}}lccc}   % centered columns (4 columns)
+\hline \hline%inserts single line
+\rule{-4pt}{2.5ex}
+Parameter & Symbol  & Value \\ [0.45ex] % inserts table
+\hline
+\rule{-4pt}{2.5ex}
+$f$'s age return (constant)         & $\iota^f_0$  & -0.383 &  \\[0.45ex]
+$f$'s age return (linear component) & $\iota^f_1$         & 0.0244  & \\[0.45ex]
+$f$'s age return (squared component)               & $\iota^f_2$       & -0.0005 &  \\[0.45ex]
+Variance of $f$'s permanent income shock                                 & $\sigma_\zeta^{2_f}$             & 0.0399  &  \\[0.45ex]
+$m$'s age return (constant)         & $\iota^m_0$  & -0.342 &\\[0.45ex]
+$m$'s age return (linear component) & $\iota^m_1$         & 0.0495  &  \\[0.45ex]
+$m$'s age return (squared component)               & $\iota^m_2$       & -0.0009 &  \\[0.45ex]
+Variance of $m$'s permanent income shock                                 & $\sigma_\zeta^{2_m}$             & 0.0417  &  \\[0.45ex]
+\hline
+\end{tabular}
+\begin{tablenotes}[flushleft]
+\footnotesize{\item \textsc{Notes}: The parameters are estimated using nonlinear least squares using single, cohabiting and married males and females from the PSID. }
+\end{tablenotes}
+\end{threeparttable}
+\label{table:income_params}
+\end{table}
+\FloatBarrier
+\subsection{Preset Parameters}
+This section describes how we fix the set of preset parameters.
+Each period in the model lasts $1$ year: we chose this length balancing the benefits of having a short period, which fits the fact that cohabitation spells are particularly short, and the computational burden associated with having too many periods.
+We assume that men (women) start making decisions at age $20$ ($18$).
+Couples are always formed by men who are 2 years older than women.
+Agents retire at the age of 62 and the number of periods in the model if $T=62$.
+The discount factor $\beta$, the annual interest rate and the relative risk aversion $\sigma$ of private goods match those in \cite{attanasio2008}.
+Instead, the parameters relative to the production of public goods, $\nu$ and $\kappa$ match those in \cite{mcgrattan1997}.
+As far as the pensions are concerned, I follow \cite{heathcote2010}: they consider the progressive nature of the US pension system but they simplify it, assuming that only the last period before retirement is relevant for the amount of the pension that a person receives.
+Parameter $\phi$ is set to 0.189 to reflect the relative time that singles spend on house works relative to the time spend on the labor market.\footnote{In the PSID the average yearly time spend on house works by singles is 465.5 hours.
+Assuming that the yearly hours of full-time work in the labor market is 2000, we get $\phi=465.5/(465.5+2000)=0.189$.
+The median number of yearly hours spent in the labor market for single men is 1976, while for single women is 1848.
+We considered the 1940-1955 birth cohorts of the PSID for these computations because the moments that we will use in the structural estimation are based on the behavior of people born in those years.} Wages are normalized such that average log wages of male at age 30 is 0.
+The variance of male and female's earnings at age $20$ $\sigma_{\zeta,1}^{2_m}$ and $\sigma_{\zeta,1}^{2_f}$ are taken directly from the PSID data.
+The parameters regarding the mating market, contained in equations \ref{eq:mma} and \ref{eq:mmz}, are pinned down to obtain a realistic degree of assortative mating with respect to assets and wages.
+In particular, we target the correlation in log wages in the PSID and the share of households with family income above the median whose wealth is also above the median in the Survey of Consumer Finances (SCF).
+The parameters of the mating market are pinned down to respect a second condition, which is \textit{symmetry}.
+For example, married men at age $t$ should have on average the same wage and wealth regardless of being simulated for their life cycle, or being partners of women who are simulated for their whole life cycle.\footnote{The agents who belong to our fictional sample are simulated for their whole life cycle and they marry/cohabit with partners that they randomly meet.
+The behavior of these partners is followed only while they are in a relationship with the person in our fictional sample.
+Figure \ref{fig:symmetry} shows the mean and variance of productivity and wealth by age, both for agents belonging to the “fictional sample” and to their “partners”.
+The variables of interest are similar for the two groups, which means that the two groups are symmetric with respect to these variables.} Since we set these parameters before the structural estimation takes place, we cannot perfectly match the mating market moment that we targeted.
+The correlation in log wages of couples in the PISD is 0.58 versus 0.62 in the simulated sample,\footnote{We obtain this value by simulating the behavior of agents under the parametrization of deep parameters described later in this section.} while the share of people that have a wealth above the median, conditionally on having a family income above the median, is 0.76 in the Survey of Consumer Finances and 0.82 in the model.
+\begin{table}[H]
+\caption{\\Preset parameters} % title of Table
+\label{table:preset_params}
+\centering % used for centering table
+\begin{threeparttable}
+\begin{tabular}{@{\extracolsep{5pt}}lccc}   % centered columns (4 columns)
+\hline \hline 
+\rule{-4pt}{2.5ex}
+ Estimated Parameters & Symbol & Value & Source  \\ [0.45ex] % inserts table
+\hline
+\rule{-4pt}{2.5ex}
+ Initial age              &          & 18-20  &  \\[0.45ex]
+ Retirement age           &          & 62  &  \\[0.45ex]
+ Number of time periods             &     $T$     & 62  &  \\[0.45ex]
+ Years per period         &          & 1  &  \\[0.45ex]
+% Retirement income        &          & 0.61 &  \\[0.45ex]
+ $m'$s average earnings at $30$     &       & 1 & Normalization \\[0.45ex]
+ Mating market---productivities      &       &  & PSID \\[0.45ex]
+ Mating market---assets      &       &  & SCF \\[0.45ex]
+ Pensions      &       &  &  \cite{heathcote2010} \\[0.45ex]
+  Var. $f$'s productivity in $t=1$&$\sigma_{\zeta,1}^{2_f}$       & 0.54 & PSID \\[0.45ex]
+   Var. $m$'s productivity   $t=1$  &$\sigma_{\zeta,1}^{2_m}$       & 0.54 & PSID \\[0.45ex]
+    Interest rate            &$R-1$       & 1.5\% & \cite{attanasio2008}   \\[0.45ex]
+ Relative Risk Aversion private good   &$\gamma$  & 1.5 &\cite{attanasio2008}  \\[0.45ex]
+ Discount factor          &$\beta$   & 0.98&\cite{attanasio2008}  \\[0.45ex]
+\hline \hline
+\rule{-4pt}{2.5ex}
+ Function &Symbol & Value & Source  \\ [0.45ex] % inserts table
+ \hline 
+$Q_t=[d_t^\nu+\kappa {(1-P^f_t)}^\nu]^{\frac{1}{\nu}}$& 
+\begin{tabular}{@{}c@{}}$\kappa$ \\[0.25ex] $\nu$\end{tabular} &\begin{tabular}{@{}c@{}}3.76 \\[0.25ex] 0.19\end{tabular}  &  \begin{tabular}{@{}c@{}} \cite{mcgrattan1997} \\[0.25ex] \cite{mcgrattan1997}\end{tabular}  \\[0.95ex]
+\hline
+\end{tabular}
+\end{threeparttable}
+\end{table}
+\FloatBarrier
+
+\subsection{Indirect Inference}
+We use the method of indirect inference \citep{gourieroux1993} to pin down the vector $\vartheta=(\alpha, \lambda, \sigma_\psi, \sigma_{\psi,I}, \delta, \mu, \xi, \gamma )$ of the 8 remaining parameters of the model.
+We use 32 moments and regression coefficients for the structural estimation, which capture the process of marriage and cohabitation creation and dissolution, as well the female labor force participation.
+More precisely, we include as targets the coefficient of unilateral divorce estimated through equation \ref{eq:ols_baseline},\footnote{Note that the sample used for estimating equation \ref{eq:ols_baseline} in the empirical section and in the structural estimation is different.
+We will describe within this section how the sample used for structural estimation is constructed.} the hazard of divorce (6), the hazard of breakup (3), the hazard of marriage (3), the share of people ever married over time (7), the share of people that ever cohabited over time (7), female labor supply (1),\footnote{Female labor supply in the model is constructed by multiplying the indicator of female labor force participation by 2000 hours.
+The assumption that working full-time corresponds to 2000 hours of work in a year was also used for calibrating $\phi$.
+Alternatively, we could have targeted female labor force participation, picking a number of hours for full-time work such that female labor supply is also matched.
+Since the amount of part-time work is very different according to the status (married, cohabiting or single) of the women, the amount of hours for participating women should have been differed by status.
+The problem with this approach is that women would have chosen their partnership according to the artificially fixed working schedule that partnerships offer, and not only accolading to the mechanisms that our model generates.} differences in female labor force participation between marriage and cohabitation (2), ratio of the rate of divorce between households with male wage above and below the median (1) and differences in log wages between married and cohabiting men (1).
+We use the retrospective marital history data from the NSFH wave III to construct the moments linked to partnership choice, while we all the others are computed using the PSID.\footnote{NSFH wave III is conducted in 2001/2003 following the original respondents of wave 1.
+This sample does not include respondents under age 45 as of January 2000 unless some particular conditions are met, but this is not an issue for us since the youngest person in our estimating sample was 44 in 2000.
+One possible issue with this data is that by mistake during NSFH wave II all cohabiting couples were dropped by the sample.
+We overcome this problem by simulating the same ``mistake" on the sample drawn from the simulated data.} The data moments are constructed selecting men and women born in 1940-1955 in community property states.
+
+The first step for the estimation is to solve the model for a vector of parameters $\vartheta$, then simulating income, love shocks and unexpected divorce policy changes to obtain the simulated behavior for the given parametrization.
+The next step is to perform stratified sampling on the simulated population in order to obtain the same distribution over gender/age/regime of divorce as in the data used to construct the moments.
+This allows us to compare the simulated and data moments: the objective is to obtain $\vartheta$ such that this difference is the smallest possible.
+Formally, the problem that we solve is
+\begin{equation}\label{eq:msm}
+\hat{\vartheta}=\arg\min_\vartheta \quad\quad (\mathbf{m}-\mathbf{m}_\vartheta)'\mathbf{W}(\mathbf{m}-\mathbf{m}_\vartheta),
+\end{equation}
+where $\mathbf{m}$ is the vector of empirical moments, as described in the section about target moments, while $\mathbf{m}_\vartheta$ is the vector of the moments simulated by the model parametrized with $\vartheta$.
+$\mathbf{W}$ is a matrix where the diagonal contains the inverse of the variance of the data moments, while all the other entries are zeros.
+The minimization of this object function is performed using the global optimization algorithm TikTak, which according to \cite{arnoud2019} outperforms an array of global and local optimizers when the target is a difficult objective function.
+In appendix \ref{section:computation} we describe in detail how the algorithm TikTak works and how me modify it to allow for the possibility of running it in parallel.
+
+\subsection{Identification}
+This section provides a description of how the structural parameters of the model are identified  heuristically.
+The parameter $\alpha$ is identified by total female labor supply: when this parameter is large, the household want to produce more of public good which requires women's time.
+Instead $\mu$ affects the gap in female labor supply for married and cohabiting couples.
+When this parameter is large the gap increases, because specialization within cohabitation becomes relatively harder as this relationship lacks a commitment technology $\lambda$ is intuitively identified by the share of people in a relationship.
+The parameter $\sigma_{\psi}$ has a role in identifying the stability of marriage and cohabitation by modifying the likelihood that marriage surplus becomes negative, but it is mostly identified by the share of people that are choosing marriage over cohabitation.
+In fact, as this parameter
+grows larger, money become less important than love for total utility. This means that
+agents care less about insuring against income shocks and labor specialization starts
+binding less, while the risk of breakup and divorce increases.
+The parameter $\sigma_{\psi}$ alone is not able to generate a large enough marriage surplus, such that the number of ever married people is matched.
+For this reason we introduced parameter $\gamma$, thanks to which we can match the share of people ever married and that ever cohabited.
+Also parameter $\delta$ influences the gain of marriage with respect to cohabitation, but it does so in a non-monotone fashion.
+In fact, on the one hand increasing the cost of divorce enhance commitment, while on the other hand it makes more costly to end the relationship.
+Hence, the effect of increasing or decreasing $\delta$ depends on its initial value.
+Since the introduction of unilateral divorce is to a first approximation like a decrease in the cost of divorce, the parameter $\delta$ is mostly identified by the coefficient of unilateral divorce of regression \ref{eq:ols_baseline}.
+Instead, $\sigma_{\psi,I}$ is identified by the hazard of breakup and marriage: when this parameter is small compared to the variance of the transitory shocks, agents are not \textit{picky} about sorting into cohabitation, but they move fast to a marriage or they separate within the first periods of the relationship, according to the evolution of the love and productivity shocks.
+Finally, the parameter $\xi$ influences the surplus of marriage and cohabitation by income.
+In fact, when $\xi$ is small, wealthier agents find the consumption of the public good $Q$ relatively more attractive.
+Since marriage allows to consume a larger quantity of $Q$ because it protects women that devote time to its production, marriage becomes a relatively more interesting option for wealthier families.
+Hence, $\xi$ is identified by the difference in log wages of married and cohabiting men and by the ratio of the rate of divorce between the relatively richer and poorer households.
+\subsection{Model Fit}
+Table \ref{table:structural_params} reports the results of the structural estimation together with asymptotic standard errors, computed following \cite{adda2003}.
+The estimated standard deviation $\sigma_{\psi}$ of the transitory match quality shock is $0.39$, while standard deviation $\sigma_{\psi,I}$ of the love shock at first meeting is higher with a value of $0.85$.
+Instead, the probability of meeting a partner $\lambda$ is $0.51$, while the share of assets left after divorce is $0.75$.
+The weight on the public good $\alpha$ is $1.01$, while the loss in productivity parameter $\mu$ is $0.04$.
+Finally, the penalty of cohabiting is $\gamma$, while the coefficient of relative risk aversion for the public good $\xi$ is $1.18$.
+
+The fit of the model is reported in table \ref{table:fit}.
+The model matches well the hazard of marriage, breakup and divorce over time: model moments rarely lie outside the 95\% confidence interval of data moments.
+One exception is that the hazard of divorce is not hump shaped over duration because our model abstracts from learning, which is necessary to match this pattern of the data \citep{blasutto2020} .
+The share of people that ever cohabited and married over time is well matched, even though in the model the people that cohabited are slightly smaller than in the data.
+The data about female labor supply is well matched and the differences in divorce by wage and the differences in log wages for married and cohabiting men are well matched.
+Finally, the coefficient of unilateral divorce estimated through equation (\ref{eq:ols_baseline}) is slightly too large.
+
+The model is validated according to its ability to reproduce the effects of unilateral divorce on cohabitation duration, the share of income earned by women over time and average wage earned by women over age.
+We run the same econometric models of section \ref{empirics} for cohabitation duration, both with the real data sample and with the simulated sample.
+The results, reported in table \ref{table:fit}, show that the size of the effects is well matched.
+Instead, women wages are a slightly too low in the simulation, as figure \ref{fig:datasimwage} suggest.
+Finally, the average share of income provided by the wife in the household is well matched.
+
+A further test is to check whether the effect of unilateral divorce on the propensity to cohabit is lower under title-based regime than under community property regime, as it is in the data.
+We solve the model assuming a title-based regime and we obtain that the coefficient of unilateral divorce of equation (\ref{eq:ols_baseline}) is -0.04, while it was -0.09 under community property.\footnote{Note that we do not expect to match exactly the empirical coefficient (\ref{eq:ols_baseline}) under the title-based regime because we did not re-estimate the model using a sample of residents in title-based states.
+The parameters used for this exercise are those in table \ref{table:fit}.} This result is consistent with the idea that under community property regime the shift towards cohabitation is larger because men, who are those with most decisional power, start finding cohabitation attractive when the risk of divorce increases.
+This is because upon divorce they would lose most of their assets, leaving a part of them to their ex-wife.
+This mechanism bites less under a title-based regime, because men would keep the assets of their property upon divorce.
+
+%Table of deep parameters
+\begin{table}[H]
+\caption{\\Estimated structural parameters} % title of Table
+\label{table:structural_params}
+\centering % used for centering table
+\begin{threeparttable}
+\begin{tabular}{@{\extracolsep{5pt}}lcccc}   % centered columns (4 columns)
+\hline \hline%inserts single line
+\rule{-4pt}{2.5ex}
+Estimated Parameters &  & Value & Standard error &\\ [0.45ex] % inserts table
+\hline
+\rule{-4pt}{2.5ex}
+Standard deviation of match quality shock         & $\sigma_{\psi}$  & 0.39 &  $0.58\cdot 10^{-3}$&\\[0.45ex]
+Standard deviation of initial match quality shock & $\sigma_{\psi,I}$         & 0.85  &  $1.32\cdot 10^{-3}$&\\[0.45ex]
+Probability of meeting a partner               & $\lambda$       & 0.51 & $1.53\cdot 10^{-3}$ &\\[0.45ex]
+Assets left upon divorce                                 & $\delta$             & 0.75  &  $4.22\cdot 10^{-3}$&\\[0.45ex]
+Weight of public good               & $\alpha$             & 1.01 &  $6.33\cdot 10^{-3}$&\\[0.45ex]
+Loss in productivity while not working               & $\mu$             & 0.04 &  $0.13\cdot 10^{-3}$&\\[0.45ex]
+Relative Risk Aversion public good          &$\xi$   & 1.18& $2.78\cdot 10^{-3}$&\\[0.45ex]
+Penalty of Cohabiting          &$\gamma$   & 0.09&  $0.09\cdot 10^{-3}$&\\[0.45ex]
+\hline
+\end{tabular}
+\begin{tablenotes}[flushleft]
+\footnotesize{\item \textsc{Notes}: The parameters in the table are estimated by Indirect inference. Asymptotic standard errors are computed following \cite{adda2003}.}
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+\FloatBarrier
+
+\begin{table}[H]
+	\caption{\\Model fit and validation} % title of Table
+	\label{table:fit} % is used to refer this table in the text
+	\centering % used for centering table
+\begin{threeparttable}[t]
+\begin{tabular}{@{} l c c c c @{}}  % centered columns (4 columns)
+\hline\hline %inserts double horizontal lines
+\rule{-4pt}{2.5ex}
+Estimated Moments & Model  & Data & 95\% CI \\ [0.05ex] % inserts table
+%heading
+\hline % inserts single horizontal line
+\rule{-4pt}{2.5ex}
+Hazards over Time              & fig. \ref{fig:haz} & fig. \ref{fig:haz} & fig. \ref{fig:haz} \\[0.15ex]
+Share Ever Cohabited and Married         & fig. \ref{fig:erel} &  fig. \ref{fig:erel} & fig. \ref{fig:erel} \\[0.15ex]
+FLS in a Couple (hours)                 & 1075 & 1016& [1001,1031] \\[0.15ex]
+FLS if Married/ FLS if Cohabiting ($<$35 yrs)                 & 0.95 & 0.86 & [0.77,0.95] \\[0.15ex]
+FLS if Married/ FLS if Cohabiting ($\ge$35 yrs)                 & 0.95 & 1.00 & [0.88,1.12] \\[0.15ex]
+Log wages Marriage-Log wages Cohabitation                  & 0.14 & 0.12 & [0.11,0.13] \\[0.15ex]
+Divorce Rate Rich/Divorce Rate Poor                  & 0.78 & 0.79 & [0.71,0.87] \\[0.15ex]
+Unilateral Divorce coefficient equation (\ref{eq:ols_baseline})     & -0.091  & -0.065 & [-0.12,+0.06] \\[0.15ex]
+\hline \hline%inserts single line
+\rule{-4pt}{2.5ex}
+External Moments & Model  & Data       &      95\% CI                      \\ [0.05ex] % inserts table
+\hline 
+\rule{-4pt}{2.5ex}
+Unilateral Divorce on the relative Risk of Marriage      & 0.75 & 0.73 &   [0.60,0.86]\\[0.15ex]
+Unilateral Divorce on the relative Risk of Separation                   & 0.81 & 0.82 & [0.75,0.89] \\[0.15ex]
+Women wages by age           &  fig. \ref{fig:datasimwage} &  fig. \ref{fig:datasimwage} & fig. \ref{fig:datasimwage} \\[0.15ex]
+Share household income earned by women  &  0.34\% &  0.35\% & [0.36-0.38] \\[0.15ex]
+\hline
+\end{tabular}
+	\begin{tablenotes}[flushleft]
+\footnotesize{\item \textsc{Notes}: The coefficients and the relative hazard ratios in the table differs from those obtained with the same econometric model in section \ref{empirics}.
+The reason is that the sample used for the empirical part is different from the one used for structural estimation as explained in the section.}
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+\section{Mechanisms}
+The aim of this section is to better understand the mechanisms underlying the introduction of unilateral divorce and the subsequent rise in cohabitation.
+
+ We start by analyzing how selection and intra-household bargaining change as a result of the reform.
+The estimated structural model allows us to study the evolution of the match quality $\psi$ and women's Pareto weight $\theta_t$ using a standard event study.
+Specifically, we estimate the following regression model on simulated data
+\begin{equation}\label{eq:ev_stud}
+\text{Variable of Interest}_{i,a,t}=\sum_{j=-5}^{5}\beta^{Uni}_j\cdot\mathcal{I}(t=j)+\alpha_{0}+\alpha_{a}+\epsilon_{i,t}
+\end{equation}
+where $a$ is age, $t$ if the year relative to switching to unilateral divorce ($t=-1$ is omitted) and $i$ is a couple.
+We estimate the model for $\psi$ and $\theta$ using as samples 1) cohabiting couples that just met 2) married couples that just met.
+Figure \ref{fig:fis2g} reports the results.
+We normalize the coefficient estimates $\beta^{Uni}_j$ by adding the average of the variable of interest in the year before unilateral divorce is introduced $E[\text{Variable of Interest}|t=-1]$.
+
+\textbf{Match quality $\psi$.} We start by analyzing panel \subref{sf:sub-first}.
+First, note that the average match quality of married couples is higher than for cohabitants.\footnote{A more in depth analysis reveals that the distribution of match quality at meeting of cohabiting couples dominates that of married couples.
+See figure \ref{fig:psidist}.} This fact is consistent with a strong selection on marriage and cohabitation with respect to match quality.
+Marriage guarantees a better commitment and cooperation, but when the match quality is low the best option is to opt for cohabitation because breaking up is cheaper than divorcing.
+The results of the event study show that upon the introduction of unilateral divorce the match quality of newly formed cohabitations increases by a value that is around 30\% percent of its structural standard deviation.\footnote{Note that the observed and structural distributions of the initial match quality are different because couples are not formed when the match quality at meeting is too low.} This result is consistent with selection of relatively high match quality couples into cohabitation after the policy change.
+This happens because unilateral divorce increases the risk of dissolution of marriage and the spouses' ability cooperate.
+This result explains why the hazard of breakup of newly formed cohabiting couples decreases after the policy reform.
+From panel \subref{sf:sub-first} we also observe that the match quality of newly formed marriages goes up, which happens because of the decreased gains from marriage.
+Overall, the match quality threshold for being in a couples increases, which increases the rate of singleness, which is consistent with the empirical evidence provided by \cite{rasul2003,rasul2006} and \cite{reynoso2019} that unilateral divorce increased the rate of singleness.
+
+\textbf{Women's bargaining power $\theta$.} Panel \subref{sf:sub-second} depicts the evolution of the women bargaining power $\theta$ for cohabitation and marriage around unilateral divorce.
+$\theta$ increases with respect to baseline for cohabitation after the policy change, while no detectable differences are observed for marriage.
+Therefore, the reform drastically reduces the differences in average $\theta$ that preceded the policy change.
+Under Mutual consent, marriage was protecting women from ending up divorced and poor, while cohabitation was chosen only by couples where the man was not able to commit for a long term relationship and the woman had little say about the decision.
+After the reform, men prefer cohabitation over marriage because it avoids splitting up assets equally upon divorce, but they have to promise a higher initial $\theta$ to convince women.\footnote{Note that upon breakup men receive on average around 65\% of the couple's wealth.}
+
+%Lastly, panel \subref{sf:sub-third} shows the evolution of female labor force participation around the reform.
+Consistently with \cite{fernandezw2014} we find that female labor force participation increases after the reform, as women seek to have higher productivities through experience and accumulate more wealth to smooth out consumption under the increased possibility of a divorce.
+Note that this effect is weaker within cohabiting couples, as their baseline participation in the labor market is already high.
+
+\begin{figure}[H]
+\begin{center}
+\caption{\\ Event Studies Around the introduction of Unilateral Divorce--Simulated Data}
+\label{fig:fis2g}
+\begin{subfigure}{.49\textwidth}
+\centering
+% include first image
+\caption{Love Shock $\psi$ at meeting}
+\label{sf:sub-first}
+\scalebox{0.5}{\input{e_psi.pgf} } 
+\end{subfigure}
+\begin{subfigure}{.49\textwidth}
+\centering
+% include second image
+\caption{Women Pareto Weight $\theta$ at meeting}
+\label{sf:sub-second}
+\scalebox{0.5}{\input{e_theta.pgf} } 
+\end{subfigure}
+\end{center}
+
+\begin{minipage}{0.99\textwidth} % choose width suitably
+{\footnotesize \textsc{Notes} The figures display the evolution of the love shock $\psi$ and the female Pareto weight $\theta$ around the introduction on Unilateral Divorce.
+The displayed patterns are normalized coefficients from event studies around divorce.
+The graphs are relative to couples that started a relationship.
+\par}
+\end{minipage}
+\end{figure}
+\FloatBarrier
+
+\section{Welfare}
+Previous research already studied the welfare effects of the introduction of unilateral divorce: both \cite{reynoso2019} and \cite{fernandez2017} find that this policy change decreases welfare for both genders, but more so for women.
+While we find a similar effect, in this section we claim that accounting for cohabitation results in an even stronger difference by gender.
+To study well-being under the two divorce regimes we perform an \textit{ex-ante} welfare comparison, where for each gender we compute the expected value of spending the whole life cycle under a certain regime, before the realization of productivity and love shocks.
+Table \ref{table:welf} reports the results, which show that welfare under a unilateral divorce regime is lower than under mutual consent for both genders.
+The difference is larger for women, which would need to be given more than 17,000\$ in assets in $t=0$ to be indifferent between the two regimes, while men would need only \$9,023 to be indifferent between the two.
+To understand the role of cohabitation for the changes in well-being, we repeat the welfare analysis assuming that cohabitation in no longer a choice.\footnote{In practice, we increase the stigma parameter towards cohabitation $\gamma$ such that cohabitation is never chosen.} For ease of exposition, we refer to the model with cohabitation as model $A$, while model $B$ is the one without cohabitation.
+The results in table \ref{table:welf} show that the loss of welfare related to unilateral divorce is similar under models $A$ and $B$ for women, while men lose more under model $B$.
+This result suggests not accounting for cohabitation overestimates the welfare losses for men when unilateral divorce is introduced.
+The intuition is that cohabitation is valuable for men under the unilateral divorce regime, because it avoids the risk of losing most of their assets in favor of their ex-wife upon dissolution.
+\begin{table}[htbp]\centering
+\caption{\\Welfare by gender and divorce regime}
+\label{table:welf}
+\begin{threeparttable}[t]\centering
+\input{welfare.tex}
+\begin{tablenotes}[flushleft]
+\footnotesize{\item Welfare losses are obtained computing the amount of wealth that must be transferred to men and women in $t=0$ such that their lifetime utility under the unilateral divorce regime equals the one under mutual consent.
+The wealth is measured in 1990 dollars.}
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+\FloatBarrier
+
 \section{Counterfactual Experiments}
-\section{Welfare Analysis}
+The aim of this section is to understand the quantitative importance of the economic mechanisms that contributed to the rise of cohabitation during the last decades.
+To do so, we examine the results from a series of counterfactual experiments.
+
+\textbf{Unilateral Divorce.} The qualitative impact of unilateral divorce on the choice between marriage and cohabitation has been largely discussed throughout this paper.
+Here we assess its quantitative relevance by performing an experiment where unilateral divorce is never introduced.
+Table \ref{table:counterfactual_exp} reports the share of people that cohabited at 39 and the average years spent cohabiting\footnote{We consider the number of years spent cohabiting between the age of 20 to the age of 55.} under the baseline scenario and the counterfactual.
+The results show that under the counterfactual only three fourth of the people would have cohabited by the age of 39, while the years spent into cohabitation would have moved from 2.26 to 1.35.
+The latter effect is the strongest because it captures both changes in partnership choices of singles and in the duration of partnerships.
+
+\textbf{Shrinking gender wage gap.} Table \ref{table:counterfactual_exp} reports the results of another scenario where the gender wage gap is reduced, increasing women potential wages by 20\%:\footnote{More specifically, we increase women's productivity, which might not be realized if they decide not to participate in the labor market.} the share of people that ever cohabited increases from 34.8\% to 36.2\%, while the number of years spent cohabiting move from 2.26 to 2.45.
+In the counterfactual there is less room from specialization in the couple when the two partner's wages are more similar and the opportunity cost of not working for women rises.
+Hence, in the counterfactual the couple's need for commitment decreases: cohabitation becomes relatively more interesting as it comes with a lower cost of breakup.
+This result is consistent with the work of \cite{anelli2019}, who find that exposure to robots causes both a decline in market opportunities of men with respect to women and a decrease (increase) in the likelihood of being married (cohabiting).
+
+\textbf{Decreasing the price of home appliances.} In table \ref{table:counterfactual_exp} we report one last counterfactual experiment that explores the effects of reducing by 20\% the relative price of goods $d$, used to produce public goods $Q$.
+This change is to be interpreted as a result of the improvement in home production technologies, such as the dish washer or the washing machine, which freed up women's time.
+Previous research already showed the impact of those changes of female labor supply \citep{greenwood2005}, the decline in marriage, the rise in divorce and assortative mating  \citep{greenwood2016}.
+The counterfactual experiment shows that the share of people that ever cohabited  increases by moved from 34.8\% to 37.1\%, while the years spent cohabiting stays almost identical.
+Similarly to a reduction in the gender wage gap, improvements in the technology of home production decrease the need for labor specialization within the household and for a commitment technology to enforce it.
+Hence, improvements in the technology of home production not only caused a decline of marriage with respect to singleness, as \cite{greenwood2016} claim, but also a change in the relative convenience of partnership contracts.
+
+%Table of deep parameters
+\begin{table}[H]
+\caption{\\Counterfactual experiments} % title of Table
+\label{table:counterfactual_exp}
+\centering % used for centering table
+\begin{threeparttable}
+\begin{tabular}{@{\extracolsep{5pt}}lccc}   % centered columns (4 columns)
+\hline \hline%inserts single line
+\rule{-4pt}{2.5ex}
+Scenario & \% people ever cohabited   & Years spent cohabiting &  \\ [0.45ex] % inserts table
+\hline
+\rule{-4pt}{2.5ex}
+Baseline         &  34.8 & 2.26 &  \\[0.45ex]
+No Unilateral Divorce &  26.7  & 1.35 &  \\[0.45ex]
+$\downarrow$ Wage gap      & 36.2 & 2.45 &  \\[0.45ex]
+$\downarrow$ Price of ``durable" good $d$     & 37.1  & 2.24 &  \\[0.45ex]
+\hline
+\end{tabular}
+\begin{tablenotes}[flushleft]
+\footnotesize{\item \textsc{Notes}.
+The Baseline scenario reports the model output with the parameters reported in the previous section.
+The scenario ``No Unilateral divorce" assumes that all the agents live under a Mutual consent regime during all their life, while in the lower gender gap scenario women wages are increased by 20\%.
+Instead, under the lower price of public good scenario the relative price between goods $d$, used to produce the public good, and private consumption $c$ is reduced by 20\%.
+The share of people that ever cohabited is measured at the simulated age of 39, while years spent cohabiting are computed between ages 20 and 55.}
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+\FloatBarrier
+
 \section{Conclusion}
+In this paper, we show that partnership choices depend on the rights to divorce: the introduction of unilateral divorce in most US states influenced selection into marriage and cohabitation as well as the duration of these relationships and women's bargaining power.
+Using NSFH and NSFG data, we show that the introduction of unilateral divorce is responsible for a 5\% increase in the likelihood that singles choose cohabitation over marriage, and that newly formed cohabitations last longer.
+To understand the mechanisms that underlie those changes, as well its welfare effect for the two genders, we build a dynamic structural model where agents can choose to marry, cohabit and when to end these relationships.
+We use regression results from survey data as well as moments that describe the mating market and female labor supply to estimate our model by indirect inference.
+The structural estimation reveals that couples choosing cohabitation instead of marriage are those that would have had the highest risk of divorce.
+Since cohabiting couples had on average a lower match quality than married ones, this selection effect increases the duration of newly formed cohabitations.
+Moreover, in the US states where assets are split equally, men are those who wish to cohabit after the policy reform, since they would lose relatively more of their assets upon divorce.
+Women are convinced to enter this relationship in exchange for a higher bargaining power, even though this makes them worse off if the couple subsequently breaks up.
+The possibility to switch to cohabitation does not affect much men's welfare, while for women the welfare under unilateral divorce is much lower because.
+Finally, we show that the magnitude of the overall effect of unilateral divorce on cohabitation is large: a counterfactual experiment reveals that if the law never changed, time spent into cohabitation for the birth cohorts used in our estimation would have been 1.35 years instead of 2.26, while the share of people that eve cohabited would have moved from 34.8\% to 26.7\%.
+
+Beyond what is studied in this paper it would be interesting to introduce explicitly fertility in our framework to understand why children born within cohabitation does not perform well later in life.
+A promising approach would be to follow \cite{kozlov2020}, who distinguishes between fertility as a choice and as an unplanned event.
+In fact, children raised by single mothers are likely outcomes of unwanted births that happen within cohabitation.
+This situation might happen less frequently within marriage, since it is a more stable relationship than cohabitation.
+
+%\section{Stuff to be Done}
+%\begin{itemize}
+%\item Check literature of rights of cohabitors in Family Law Quarterly
+%\item Read and Understand well Bayot-Voena, then provide a robustness check that incorporates their view of title-based breakup
+%\item Robustness check on comomn-law marriage: cohabitations with some probability $p$ should turn into marriages.
+Consider p varying with female labor supply, as cohabitation is more likely to be considered as common law marriage if children are present
+%\item Revise the empirical part, making the choice between cohabitation and marriage a duration model---better if a multinomial probit.
+%\item Robustness checks for the empirical part: eliminate california from the sample, do an event study.
+%\end{itemize}
 
@@
 \appendix
+
+\section*{Appendix}
 \counterwithin{figure}{section}
 \counterwithin{table}{section}
-\section*{Appendix}
-\section{Computational Appendix}
-\cite{arnoud2019}+\cite{cartis2019}
+\section{Net worth around divorce/breakup}\label{section:eventsa}
+
+In this section we provide evidence about the evolution of household's net worth around the event of divorce/breakup.
+Using the 1997-2017 waves of the PSID, we build a sample of 1087 divorces and 1187 breakups that respect the following characteristics: 1) household wealth is observed before and after the relationship  breakdown 2) the number of adults in the household move from two to one after the relationship breakdown 3) the net worth of the household is below the 96\% of the relative distribution 4) we exclude household where the head is older than 65 years old.\footnote{We could not distinguish the net worth of the couple/individuals against the other member if we considered households with more adults.} Net worth is constructed using the PSID variables employed by \cite{blundell2016}.
+We analyze the evolution of net worth using a standard event study on our sample.
+Note that, after the relationship breakdown, we report the net worth of the household of the partner that the PSID kept interviewing.
+Specifically, we estimate the following regression model
+\begin{equation}\label{eq:ev_studa}
+\text{Net worth}_{i,a,t,y,ma}=\sum_{j=-6}^{4}\beta^{Split}_j\cdot\mathcal{I}(t=j)+\alpha_{0}+\alpha_{a}+\alpha_{y}+\alpha_{ma}+\epsilon_{i,t},
+\end{equation}
+where $a$ is age of the person observed after the couple chase to exist, $t$ if the year relative to switching to unilateral divorce ($t=-1$ is omitted), and $i$ is the household, $y$ is the year and $ma$ is the number of years since the start of the marriage/cohabitation.
+Note that we included year, years since marriage/cohabitation and age fixed effects.
+We estimate this model separately for formerly married and cohabiting households and we further subdivide our sample considering wealthier/poorer households and men/women.\footnote{A household is considered wealthy if its net worth before couple disruption is above the $75^{th}$ percentile of the distribution and poor otherwise.d} Figure \ref{fig:assdiv} reports the results.
+We normalize the coefficient estimates $\beta^{Split}_j$ by adding the average of net worth at divorce $E[\text{Net worth}|t = -1]$.
+In panel \subref{sf:assdiv1} we can see a decrease in net worth for richer households: the estimates indicate the year after the divorce the household is left with significantly less than half its original net worth, even tough the large standard errors do not allow us to identify clearly the amount of net worth lost because of the divorce.
+Instead, no clear decrease in net worth can be observed for poorer household.
+Panel \subref{sf:assdiv3} shows that there is not clear loss in net worth for poor and rich cohabiting households.
+Finally, panels \subref{sf:assdiv2} and \subref{sf:assdiv4} show that no gender-related difference regarding the evolution of net worth can be detected.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Symmetry in income and assets
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[ht]
+\caption{\\ Event studies of net-worth around divorce}
+\label{fig:assdiv}
+
+\begin{subfigure}{.49\textwidth}
+\centering
+% include second image
+\caption{Net worth---rich and poor households}
+\label{sf:assdiv1}
+\scalebox{0.5}{\input{eventwh_r_p.pgf} } 
+\end{subfigure}
+\begin{subfigure}{.49\textwidth}
+\centering
+% include first image
+\caption{Net worth---men and women}
+\label{sf:assdiv2}
+\scalebox{0.5}{\input{eventwh_r_s.pgf} } 
+\end{subfigure}
+
+\hspace{20em}
+
+\begin{subfigure}{.49\textwidth}
+\centering
+% include second image
+\caption{Net worth---rich and poor households}
+\label{sf:assdiv3}
+\scalebox{0.5}{\input{eventwh_r_p_c.pgf} } 
+\end{subfigure}
+\begin{subfigure}{.49\textwidth}
+\centering
+% include first image
+\caption{Net worth---men and women}
+\label{sf:assdiv4}
+\scalebox{0.5}{\input{eventwh_r_s_c.pgf} } 
+\end{subfigure}
+
+\begin{minipage}{0.99\textwidth} % choose width suitably
+
+\hspace{50em}
+
+{\footnotesize \textsc{Notes.} The figures display the evolution of net-worth (measured in 1997\$).
+The displayed patterns are normalized coefficients from event studies around divorce.
+Rich household are defined as those whose net-worth is above the median in the first period they were observed.
+Poor households are those whose net-worth is below the $75^{th}$ percentile of the distribution.
+Net worth is constructed using the same PSID variables that \cite{blundell2016} use.)\par}
+\end{minipage}
+\end{figure}
+\FloatBarrier
+
+\section{Computational Appendix}\label{section:computation}
+\cite{arnoud2019} compares an array of local and global optimizers, which are given the task of finding the global optimum of difficult objective functions.
+They find that the multi-start algorithm that they propose, called TikTak, outperforms the others in terms of time required to reach the solution and the probability that the algorithm finds the optimum.
+In light of these findings, we decided to use TikTak for solving problem (\ref{eq:msm}).
+A description of the TikTak algorithm follows:
+\begin{enumerate}
+\item Determine the bounds for each parameter and generate a sequence of Sobol points with length $N$. Then evaluate the function value at each Sobol point.
+\item Sort the $N$ Sobol points ($s_1$ ,..., $s_N$), with $f(s_1)\le$ ··· $\le f(s_N)$ and keep the first $N^*$ with $N^*<N$.
+Note that $f()$ is the objective function.
+We set $N^*$ such that $N^*/N=0.15.$ Set the global iteration number $j$ to 1, then run a local minimizer starting from $s_1$.
+Call $z^*_j$ the fit resulting from the local minimization,\footnote{We use the local minimization algorithm provided by \cite{cartis2019}, which is a derivative-free optimization (DFO) for nonlinear Least-Squares (LS) problems.
+This algorithm is robust to noise, which might arise because of the errors coming from the approximation of continuous problems on a discrete grid.} and define the set $Z^*_1=\min \{z^*_1\}=z^*_1 $.
+\item Define a new starting point $\hat{s}_{j+1}$ defined as
+$$\hat{s}_{j+1}=(1-\theta_j)s_{j+1}+\theta_j Z^*_j, $$
+where
+$$\theta_j=\min \big[\max[0,1,(j/N^*)^\frac{1}{2}],0.995\big]. $$
+Run a local minimizer starting from $\hat{s}_{j+1}$ and call the local minimum found $z^*_{j+1}$.
+Then, define $Z^*_{j+1}=\min \{z^*_1,...,z^*_{j+1} \} $.
+Update the global iteration number: $j=j+1$.
+Repeat step 3 until $j=N^*$.
+
+\item  Return $Z^*_{N^*}$.
+\end{enumerate}
+We adapt the original algorithm such that it can be run in parallel using $M$ nodes.
+Other than evaluating more points at the same time on different nodes, the only difference is the step 3.
+In the parallel version of TikTak, $Z^*_{j}$ is defined as the minimum among the outcomes  of the local minimizers  that already converged, while at the end of step 3 the global iteration number is updated to $j^*$, which stands for the number of global minimization that already started, without necessarily having converged already.
 \section{Estimation of Income Processes}
 
+%MARRUAGE TO DIVORCE
+{	
+	\def\onepc{$^{\ast\ast}$} \def\fivepc{$^{\ast}$}
+	\def\tenpc{$^{\dag}$}
+	\def\legend{\multicolumn{1}{l}{\footnotesize{Significance levels
+				:\hspace{1em} $\ast$ : 10\% \hspace{1em}
+				$\ast\ast$ : 5\% \hspace{1em} $\ast\ast\ast$ : 1\% \normalsize}}}
+	\begin{table}[H]\centering
+	\caption{\\OLS Regression. Observation: males in year $t$.}
+	\label{table:inc_men}
+	\begin{threeparttable}[t]\centering
+	\input{inc_men}
+	\end{tabular}}
+\begin{tablenotes}[flushleft]
+\footnotesize{\item \textsc{Notes}: Standard errors are obtained through bootstrapping and they are reported in summary table \ref{table:income_params}.}
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+}
+\FloatBarrier
+%MARRUAGE TO DIVORCE
+{	
+	\def\onepc{$^{\ast\ast}$} \def\fivepc{$^{\ast}$}
+	\def\tenpc{$^{\dag}$}
+	\def\legend{\multicolumn{1}{l}{\footnotesize{Significance levels
+				:\hspace{1em} $\ast$ : 10\% \hspace{1em}
+				$\ast\ast$ : 5\% \hspace{1em} $\ast\ast\ast$ : 1\% \normalsize}}}
+	\begin{table}[H]\centering
+	\caption{\\OLS Regression. Observation: Females in Year $t$.}
+	\label{table:inc_wom}
+	\begin{threeparttable}[t]\centering
+	\input{inc_wom}
+	\end{tabular}}
+\begin{tablenotes}[flushleft]
+\footnotesize{\item \textsc{Notes}: Standard errors are obtained through bootstrapping and they are reported in summary table \ref{table:income_params}.}
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+}
+\FloatBarrier
+
+%MARRUAGE TO DIVORCE
+{	
+	\def\onepc{$^{\ast\ast}$} \def\fivepc{$^{\ast}$}
+	\def\tenpc{$^{\dag}$}
+	\def\legend{\multicolumn{1}{l}{\footnotesize{Significance levels
+				:\hspace{1em} $\ast$ : 10\% \hspace{1em}
+				$\ast\ast$ : 5\% \hspace{1em} $\ast\ast\ast$ : 1\% \normalsize}}}
+	\begin{table}[H]\centering
+	\caption{\\Probit Regression. Observation: Females in Year $t$.}
+	\label{table:prb_wom}
+	\begin{threeparttable}[t]\centering
+	\input{prb_wom}
+	\end{tabular}}
+\begin{tablenotes}[flushleft]
+\footnotesize{\item \textsc{Notes}: standard errors are clustered at the state level.
+	Coefficients that are significantly different from zero are denoted by the following system: *10\%, **5\%  and ***1\%. \ref{table:income_params}.}
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+}
+\FloatBarrier
+\section{Robustness Checks - Empirical Analysis}
+\subsubsection*{Relationship Choice - Linear State Trends}
+
+%RELATIONSHIP CHOICE
+	\begin{table}[H]\centering
+	\caption{\\OLS Regression. Observation: first and second relationships}
+	\label{table:wmarlin}
+	\begin{threeparttable}[t]\centering
+	\input{wmarlin.tex}
+	\begin{tablenotes}[flushleft]
+	\footnotesize{\item \textsc{Notes}: standard errors are clustered at the state level.
+		Coefficients that are significantly different from zero are denoted by the following system: *10\%, **5\%  and ***1\%.}
+	\end{tablenotes}
+	\end{threeparttable}
+	\end{table}
+\FloatBarrier
+\subsubsection*{Relationship Choice - Heterogeneity by Property regime and linear state trends}
+
+%RELATIONSHIP CHOICE
+
+	\begin{table}[H]\centering
+	\caption{\\OLS Regression. Observation: first and second relationships}
+	\label{table:wmarlinc}
+	\begin{threeparttable}[t]\centering
+	\input{wmarlinc.tex}
+	\begin{tablenotes}[flushleft]
+	\footnotesize{\item \textsc{Notes}: standard errors are clustered at the state level.
+		Coefficients that are significantly different from zero are denoted by the following system: *10\%, **5\%  and ***1\%.}
+	\end{tablenotes}
+	\end{threeparttable}
+	\end{table}
+\FloatBarrier
+
+\FloatBarrier
+\subsubsection*{Relationship Choice - Logit}
+
+%RELATIONSHIP CHOICE
+	\begin{table}[H]\centering
+	\caption{\\Logitstic regression. Observation: first and second relationships}
+	\label{table:wmar_logit}
+	\begin{threeparttable}[t]\centering
+	\input{wmar_logit.tex}
+	\begin{tablenotes}[flushleft]
+	\footnotesize{\item \textsc{Notes}: standard errors are clustered at the state level.
+		Coefficients that are significantly different from zero are denoted by the following system: *10\%, **5\%  and ***1\%.}
+	\end{tablenotes}
+	\end{threeparttable}
+	\end{table}
+\FloatBarrier
+
+\newpage
+
+\section{Figures}
+
+%%%%%%%%%%%%%%%%%%%%%%%%5
+% MODE FIT
+%%%%%%%%%%%%%%%%%%%%%%%%5
+
+\subsection{Model Fit}
+
+\FloatBarrier
+\begin{figure}[H]
+\caption{\\Hazards by duration of spells: data and simulations}
+\label{fig:haz}
+\begin{center}
+\begin{subfigure}{.49\textwidth}
+\centering
+\caption{Hazard of Divorce}
+\label{fig:hazd}
+\scalebox{0.49}{\input{hazd.pgf}} 
+\end{subfigure}
+\begin{subfigure}{.49\textwidth}
+\centering
+\caption{Hazard of Separation}
+\label{fig:hazs}
+\scalebox{0.49}{\input{hazs.pgf}} 
+\end{subfigure}
+\end{center}
+
+\hspace{20em}
+
+\begin{center}
+\begin{subfigure}{.49\textwidth}
+\centering
+\caption{Hazard of Marriage}
+\label{fig:hazm}
+\scalebox{0.49}{\input{hazm.pgf}} 
+\end{subfigure}
+\end{center}
+\end{figure}
+\FloatBarrier
+
+\begin{figure}
+\begin{center}
+\caption{\\Share ever cohabited and married: data and simulations}
+\label{fig:erel}
+%\begin{subfigure}
+\hspace*{-1.3cm} 
+\scalebox{0.99}{\input{erel.pgf}} 
+%\end{subfigure}
+\end{center}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Symmetry in income and assets
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[ht]
+	\begin{center}
+		\caption{---Low wages over the life cycle: simulations and data}
+		\label{fig:datasimwage}
+
+		\begin{subfigure}{.49\textwidth}
+			\centering
+			% include first image
+			\caption{Women}
+			\label{fig:em}
+			\scalebox{0.5}{\input{ef.pgf} } 
+		\end{subfigure}
+		\begin{subfigure}{.49\textwidth}
+			\centering
+			% include second image
+			\caption{Men}
+			\label{fig:ef}
+			\scalebox{0.5}{\input{em.pgf} } 
+		\end{subfigure}
+	\end{center}	
+	\begin{minipage}{0.99\textwidth} % choose width suitably
+		{\footnotesize \textsc{Notes.} This figure depicts simulated and empirical low wages over the life cycle.
+Data on wages are constructed dividing the annual labor income by the total number of hours.
+\par}
+	\end{minipage}
+\end{figure}
+\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%
+%MECHANISM
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Mechanisms}
+\begin{figure}[h!]
+\centering
+\caption{\\Cumulative distribution of love shock $\psi$ at meeting}
+\hspace*{-1.3cm} 
+\label{fig:psidist}
+\resizebox{0.8\textwidth}{!}{\input{psidist.pgf}}
+
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\caption{\\Distribution of women Pareto weight $\theta$---marriage and cohabitation}
+\label{fig:thetadist}
+\hspace*{-1.1cm} 
+\resizebox{0.8\textwidth}{!}{\input{thtdist.pgf}}
+\begin{minipage}{0.99\textwidth} % choose width suitably
+
+\hspace{30em}
+
+{\footnotesize \textsc{Notes.} This figure depicts the distribution women Pareto weight for married and cohabiting couples.
+The thick solid lines represent the distribution of this variable in the period the couple decides to get together, while the lighter areas depict the distribution of $\theta$ considering every relationship duration.\par}
+\end{minipage}
+\end{figure}
+\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Symmetry in income and assets
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Simulations-Symmetry}
+\begin{figure}[ht]
+\begin{center}
+\caption{\\ Log Income and assets mean and variances by age---simulated data}
+\label{fig:symmetry}
+
+\begin{subfigure}{.49\textwidth}
+\centering
+% include first image
+\caption{Average productivity}
+\label{fig:sub-firs1t}
+\scalebox{0.5}{\input{sy_minc.pgf} } 
+\end{subfigure}
+\begin{subfigure}{.49\textwidth}
+\centering
+% include second image
+\caption{Variance productivity}
+\label{fig:sub-second1}
+\scalebox{0.5}{\input{sy_vinc.pgf} } 
+\end{subfigure}
+\end{center}
+
+\hspace{20em}
+
+\begin{center}
+\begin{subfigure}{.49\textwidth}
+\centering
+% include second image
+\caption{Average assets}
+\label{fig:sub-third12}
+\scalebox{0.5}{\input{sy_mass.pgf} } 
+\end{subfigure}
+\begin{subfigure}{.49\textwidth}
+\centering
+% include second image
+\caption{Variance assets}
+\label{fig:sub-third13}
+\scalebox{0.5}{\input{sy_vass.pgf} } 
+\end{subfigure}
+\end{center}
+
+\begin{minipage}{0.99\textwidth} % choose width suitably
+{\footnotesize \textsc{Notes.} The figures display mean and variances of simulated log wages and assets of men and women in a couple over their age.
+We label as ``main person" the variables that are computed from agents that are simulated and followed through their whole life-cycle, while we label as ``met person" the variables constructed using the partners met by the people whose behavior is simulated for their whole life-cycle.
+Wage variables are constructed using couples at any point of their relationship, while for assets we use only the period the couple met, where we can still distinguish the title of ownership of assets.
+\par}
+\end{minipage}
+\end{figure}
+\FloatBarrier
+
 \end{document}

### 2020-09-28 graph_transitions2.tex
latest

\begin{tikzpicture}[domain=0:1,scale=1]
\node [block, name=input,align=center] (sum) {\large Single};
\node [block, above right=1.5cm and 7.449cm of sum ] (controller) {\large Separation};
\node [block, below right=1.5cm and 7.449cm of controller,align=center] (system) {\large Cohabitation};
\draw [<-,  thick, latex-] (controller) -- node[above left,yshift=0.3cm]{\large }(system);
\node [output, right of=system] (output) {fe};
\node [block, below left=1.5cm and 7.449cm of system,align=center] (measurements) {\large Marriage };
\node [block, left of=measurements, node distance=10.05cm,align=left] (divorce) {\large Divorces};
\draw [<-,  thick, latex-] (sum) -- node[above right,yshift=0.3cm]{\large } (controller);
\draw [->,  thick, -latex] (sum) -- node[above]{\large} (system);
\draw [->,  thick, -latex] (system) --node[above left]{\large } (measurements);
\draw [->,  thick, -latex] (measurements) --node[above]{\large } (divorce);
\draw [->,  thick, -latex] (sum) --node[above right]{\large } (measurements);
\draw [->,  thick, -latex] (divorce) --node[right]{\large } (sum);
node [near end] {$$} (sum);
\end{tikzpicture}

### 2020-09-28 mpc.Rnw
latest

@@
  \hline \\[-1.8ex]
- Unilateral Divorce &  -0.09  &  -0.07  &  -0.12  &  -0.13  \\ 
-  & ( 0.04 ) & ( 0.04 ) & ( 0.04 ) & ( 0.11 ) \\  
+ Unilateral Divorce &  -0.24  &  -0.25  &  -0.28  &  -0.28  \\ 
+  & ( 0.06 ) & ( 0.08 ) & ( 0.09 ) & ( 0.09 ) \\  
  \hline \\[-1.8ex]
- Average Relative Risk &  -0.12  &  -0.08  &  -0.2  &  -0.14  \\ 
+ Average Relative Risk &  0.64  &  0.63  &  0.59  &  0.6  \\ 
  \hline \\[-1.8ex]
@@
  \hline \\[-1.8ex]
- Unilateral Divorce &  -0.04  &  -0.09  &  -0.05  &  -0.06  \\ 
-  & ( 0.02 ) & ( 0.02 ) & ( 0.02 ) & ( 0.1 ) \\  
+ Unilateral Divorce &  -0.19  &  -0.16  &  -0.08  &  -0.24  \\ 
+  & ( 0.07 ) & ( 0.06 ) & ( 0.05 ) & ( 0.14 ) \\  
  \hline \\[-1.8ex]
- Average Relative Risk &  -0.06  &  -0.18  &  -0.1  &  -0.06  \\ 
+ Average Relative Risk &  0.67  &  0.71  &  0.83  &  0.62  \\ 
  \hline \\[-1.8ex]

### 2020-09-28 tiktak.tex
latest

--- 2020-09-28 abstract.tex
@@
 \usepackage[round, sort , authoryear]{natbib}
+
+\usepackage{pgf}
 
@@
 \usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
+
 % These packages are all incorporated in the memoir class to one degree or another...
@@
 
+\renewcommand{\thesubfigure}{ (\alph{subfigure})}
+\captionsetup[sub]{labelformat=simple}
 %Math stuff
@@
 %\parskip3mm\parindent0cm
-\setlength{\droptitle}{-10em}   % This is your set screw
 
-\title{Unilateral Divorce and the Rise of Informal Cohabitation\thanks{The authors wish to thank Matthias Doepke, Alessandra Voena and the Norhtwestern Macro group for their useful comments.
-Blasutto acknowledges financial support from the French speaking community of Belgium (ARC project 15/19-063 on "family transformations").}}
-\author{Fabio Blasutto$^1$ (Presenter) \quad Egor Kozlov$^2$}
+\title{The Rise of Cohabitation and Unilateral Divorce\thanks{The authors wish to thank David de la Croix, Matthias Doepke, Fabio Mariani, Alessandra Voena and the Norhtwestern Macro group for their useful comments.
+Blasutto acknowledges financial support from the French speaking community of Belgium (ARC project 15/19-063 on \textit{family transformations} and \textit{mandat d' aspirant} FC 23613).}}
+\author{Fabio Blasutto$^1$ \quad Egor Kozlov$^2$}
 
 \begin{document}
-	 	\tikzstyle{block} = [draw, fill=white, rectangle, 
-	minimum height=3em, minimum width=6em]
-	\tikzstyle{sum} = [draw, fill=white, circle, node distance=1cm]
-	\tikzstyle{input} = [coordinate]
-	\tikzstyle{output} = [coordinate]
-	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
+	\bibliographystyle{apa}
+	\section*{TikTak: an efficient Global Optimizer}
+	Research by \cite{arnoud2019} compares an array of local and global optimizers, which are given the task of finding the global optimum of non well-behaved functions.
+They find that a multistart algorithm that they propose, called TikTak, outperforms the others regarding in terms of time required to reach the solution and the probability that the algorithm actually find the right point.
+TikTak is implemented following the following steps:
+	\begin{enumerate}
+		\item Determine bounds for each parameter, then draw and evaluate $N$ Sobol points.
+		\item Sort the $N$ Sobol points ($s_1$ ,..., $s_N$), with $f(s_1)\le$ ··· $\le f(s_N)$ and keep the first $N^*$ with $N^*<N$.
+Note that $f()$ is the objective function.
+We set those numbers such that $N^*/N=0.15.$ Then, set $j=1$.
+		\item Set £Then run local searches ($\hat{s}_1$ ,..., $\hat{s}_N$).
+Call $z^*_j$ the point resulting from the local minimization\footnote{We use the local minimization algorithm provided by \cite{cartis2019}, which is a derivative-free optimization (DFO) for nonlinear Least-Squares (LS) problems.
+This algorithm is robust to noise, which might arise because of the errors coming from the approximation of continuous problems on a discrete grid.} starting from $\hat{s}_j$.
+Then, the next starting point will be a convex combination between $\hat{s}_{j+1}$ and the most fit point computed so far through local minimizations $Z_j^*$, defined as $Z^*_j=\min \{z^*_1,...,z^*_j \} $.
+Formally:
+		$$\hat{s}_{j+1}=(1-\theta_j)s_{j+1}+\theta_j Z^*_j, $$
+		where
+		$$\theta_j=\min \big[\max[0,1,(j/N^*)^\frac{1}{2}],0.995\big]. $$
+		\item The global minimum is $Z^*_{N^*}$.
+	\end{enumerate}
 
-	%Gauss distribution
-	\pgfmathdeclarefunction{gauss}{2}{%
-		\pgfmathparse{1/(#2*sqrt(2*pi))*exp(-((x-#1)^2)/(2*#2^2))}%
-	}
-	% Bibliography style, important for biblatex functioning	
-	\bibliographystyle{apa}
-
-	\maketitle
-
-	\footnotetext[1]{IRES, UCLouvain \& National Fund for Scientific Research (Belgium).
-Email:  \tt{fabio.blasutto@uclouvain.be}, Phone:\tt{+32 489545996}, Address: \tt{Chaussee de Wavre 561/2, Etterbeek, Belgium.}}
-	\footnotetext[2]{Northwestern Univrsity. Email:  \tt{egorkozlov2020@u.northwestern.edu}.\\}
-
-\begin{abstract}
-	Does unilateral divorce eroded the gains of marriage with respect to informal cohabitation?
-Exploiting the staggered introduction of unilateral divorce across U.S.
-states, we show that after the reform newly formed relationships are 5\% more likely to be cohabitations instead of marriages, and that cohabitation spells last longer.
-To understand the mechanisms underlying the law changes, we build and estimate a structural life cycle model with partnership choice, female labor supply and savings decisions, where the gains of marriage with respect to cohabitation come from a better risk sharing and specialization within the household, enforced through a costly divorce.
-In the model the reform increases the risk of divorce, making cohabitation preferred to couples that would have had the highest risk of divorce.
-Since the couples switching relationship are on average better matched than the average cohabitants, the duration of cohabitations increases.
-\end{abstract}
-\textbf{Keywords}: Marriage, Cohabitation, Unilateral Divorce, Structural Estimation\\
-\textbf{JEL-Code}: D83 - J12
+\bibliographystyle{achicago}
+\bibliography{mybibliography}
 

### 2020-09-28 welfare.tex
latest

\begin{tabular}{cccc}
    \hline\midrule
    \multicolumn{2}{c}{\textbf{Female}}& \multicolumn{2}{c}{\textbf{Male}}\\
    \cmidrule(l){1-2}\cmidrule(l){3-4}
     Mutual Consent & Unilateral Divorce & Mutual Consent & Unilateral Divorce\\
     \cmidrule(l){1-4}
    \multicolumn{4}{c}{\textit{Life-Time utilities in $t=0$}}\\[3ex]
-352.16 &-355.06 &-338.88 &-340.62 \\
\cmidrule(l){1-4}
\multicolumn{4}{c}{\textit{Welfare Losses with Unilateral Divorce}}\\[3ex]
\multicolumn{2}{c}{\Chartgirls{1.0}}& \multicolumn{2}{c}{\Chartguys{0.4307177814029403}}\\[-0.15ex]
\multicolumn{2}{c}{17531.97 \$}& \multicolumn{2}{c}{9023.81 \$}\\
    \hline\midrule
    \multicolumn{4}{c}{\textit{Life-Time utilities in $t=0$ when cohabitation is not an option}}\\[3ex]
-351.47 &-354.68 &-339.59 &-340.74 \\
\cmidrule(l){1-4}
\multicolumn{4}{c}{\textit{Welfare Losses with Unilateral Divorce when cohabitation is not an option}}\\[3ex]
\multicolumn{2}{c}{\Chartgirls{1.0}}& \multicolumn{2}{c}{\Chartguys{0.6304128902316224}}\\[-0.15ex]
\multicolumn{2}{c}{18287.03 \$}& \multicolumn{2}{c}{11528.38 \$}\\
\hline\hline
    \end{tabular}

### 2020-09-29 draft_sub_con.tex
Edited the bibliography so it compiles on mine + temp remove "achicago" style
Edits to Sections 1 and 2

@@
 \begin{abstract}
-	This paper analyzes the role of unilateral divorce for the rise of cohabitation.
-Exploiting the staggered introduction of unilateral divorce across the US states, we show that after the reform singles become more likely to cohabit than to marry, and that newly formed cohabitations last longer.
-We then provide a theoretical rationale for these facts, building a life-cycle model with partnership choice, female labor force participation and saving decisions.
-A structural estimation of the model suggests that unilateral divorce decreases couples' stability, which makes cohabitation preferred to couples that would have been at high risk of divorce.
-Since cohabiting couples formed after the reform are better matched, the average length of cohabitations increases.
-A counterfactual experiment reveals that the time spent cohabiting would have been halved if divorce laws had never changed.
+This paper analyzes the role of unilateral divorce for the rise of unmarried cohabitation.
+Exploiting the staggered introduction of unilateral divorce across the US states, we show that after the reform singles become more likely to cohabit than to marry, and newly formed cohabitations last longer.
+We then provide a theoretical rationale for these facts, building a life-cycle model with partnership choice, female labor force participation, and saving decisions.
+A structural estimation of the model suggests that unilateral divorce decreases couples’ stability, making cohabitation preferred to couples that would have been at high risk of divorce if they marry.
+As cohabiting couples formed after the reform are better matched, the average length of cohabitations increases.
+A counterfactual experiment reveals that the time spent cohabiting would have been halved if the divorce laws had never changed.
 \end{abstract}
@@
 
-Informal cohabitation is on the rise: the share of women that ever cohabited in the United States moved from 33\% in 1987 to 60\% in 2010 \citep{manning2013}.
+Unmarried cohabitation is on the rise: the share of women that ever cohabited in the United States moved from 33\% in 1987 to 60\% in 2010 \citep{manning2013}.
 This increase contributed to the overall changes in the structure and behavior of the American family.
-For example, \cite{bumpass2000} claim that the higher instability of cohabitation is responsible for the rise in the number of single mothers, which is associated with poor outcomes of children \citep{chetty2018,mclanahan2013}.
-Moreover, compared to married couples, the relationship-specific investments of cohabitants are lower \citep{poortman2012} and their children's well-being is worse \citep{brown2004}, even after controlling for parental resources.
-However, it is not clear to which extent the outcomes of cohabiting families are due to selection versus the direct effect of partnership's rights on couple's behavior.
-Quantifying the relative importance of these two mechanisms can be done only by understanding the rational for partnership's choices.
+The higher instability of cohabitation plausibly contributes to the rise in the number of single mothers (\cite{bumpass2000}), which is associated with poor outcomes for children \citep{chetty2018,mclanahan2013}.
+Cohabiting people spend less money on relationship-specific investments % maybe any examples here?
+\citep{poortman2012}.
+Finally, their children's well-being is worse even after controlling for parental resources \citep{brown2004}.
+However, it is not clear to what extent cohabitants' outcomes are due to selection % elaborate what kind of?
+versus the direct effect of the form of partnership on the couple's behavior.
+Quantifying these two mechanisms' relative importance can be done only by understanding the rationale for the partnerships choices.
 Why do people cohabit instead of marrying?
@@
 
-This paper addresses these questions by asking what role does unilateral divorce have for the rise of cohabitation.
-Since marriage and cohabitation can be viewed as contracts whose attractiveness depend on their termination rights and costs, the switch from mutual consent to unilateral divorce represents a unique opportunity to learn about partnership choices.
-This paper answers to this question with four contributions.
-First, we offer empirical evidence that unilateral divorce made cohabitation more likely to be chosen and that newly formed cohabitations last longer.
+Our paper addresses these questions by focusing on a major US policy change that took place mostly during the 1970s.
+During this period, most of the states have made divorce considerably easier by switching from the mutual consent divorce regime, requiring both spouses to agree to divorce, towards unilateral divorce, in which one spouse's decision was enough to initiate the procedure.
+The paper explores what role does unilateral divorce have for the rise of cohabitation.
+Since marriage and cohabitation can be viewed as contracts whose attractiveness depends on their termination rights and costs, the switch from mutual consent to unilateral divorce represents a unique opportunity to learn about partnership choices.
+
+We answer the questions with four contributions.
+First, we offer a few pieces of empirical evidence.
+We show that under the unilateral divorce people prefer cohabitation to marriage more often.
+We also argue that the newly formed cohabitations last longer.
 Second, we propose a theory of partnership choice and endogenous breakup/divorce.
-In particular, in our model the policy makes cohabitation the preferred choice to couples that would have experienced the highest risk of a costly divorce.
-Therefore, the average match quality of cohabiting couples increases, which cause cohabitation spells to last longer.
-Third we structurally estimate our model to reflect the empirical findings.
-Fourth, we perform a counterfactual experiment to assess the overall role of unilateral divorce on the rise of cohabitation and we quantify the welfare gains and losses of the reform for men and women.
-This paper thus consists of four parts, one for each contribution, which we now describe in more detail.
+In particular, in our model the policy makes cohabitation the preferred option to couples that would have experienced the highest risk of a costly divorce.
+Therefore, the average match quality of cohabiting couples increases, which causes cohabitation spells to last longer.
+% A theory professor asked me once if something I claim to be a result is generic or is it specific to my choice of parameters.
+This may be a useless thing, but maybe the wording can slightly be adjusted top.
+Third, we structurally estimate our model to match the empirical findings about the divorce regimes' transition.
+Fourth, we perform several counterfactual experiments to understand the overall role of unilateral divorce on the rise of cohabitation.
+We then quantify the welfare gains and losses of the reform for men and women.
+Thus, this paper consists of four parts, one for each contribution, which we now describe in more detail.
 
@@
 
-In the first part of the paper we document the effect of unilateral divorce on the choice between marriage and cohabitation and on the duration of newly formed cohabitations.
+In the first part of the paper we document the effect of unilateral divorce on the choice between marriage and cohabitation and the duration of newly formed cohabitations.
 We use data from the National Survey of Family and the Household (NSFH) and from the National Survey of Family Growth (NSFG) to study the choice between marrying and cohabiting.
-Then, exploiting the exogenous variation coming from the staggered introduction of unilateral divorce over time across the US states, we estimate that newly formed couples are 5-7\% more likely to choose cohabitation over marriage compared to the pre-reform period.
-Interestingly, the effect's size depends on how property is divided upon divorce, being strongest in states where each spouse gets half of the wealth and where the assets shares are decided by the judge.
-This suggest that divorce allocations affect partnership choices.
+Then, exploiting the exogenous variation coming from the staggered introduction of unilateral divorce over time across the US states, we estimate that newly formed couples are 5-7\% more likely to choose cohabitation over marriage than in the pre-reform period.
+% Give some baseline numbers here?
+Interestingly, the effect's size depends on how property is divided upon divorce, being strongest in states where each spouse gets half of the wealth and where the judge decides the assets' shares.
+This suggests that divorce allocations affect partnership choices.
 %This suggests that the result cannot be entirely driven by divorce being a less binding commitment technology,\footnote{This mechanism is highlighted by \cite{lafortune2020}, where the equal division of assets within marriage makes it possible to efficiently invest in children even after the rise of unilateral divorce.} since the egalitarian property division rule can act as a substitute for the mutual consent regime.
-Moreover, we analyze how unilateral divorce affected the duration of cohabitation spells: our estimates from a multinomial probit show that cohabitations formed after the reform last longer both because of a reduced risk of marriage and of breakup.\footnote{Henceforth we will refer to the separation from cohabitation as breakup to avoid confusion with legal separation.}
-
-In the second part of the paper we propose a theory to understand the mechanisms underlying the facts documented in the empirical part.
-We build a dynamic model of intra-household decision making and search in the mating market, where agents makes decisions according to the realization of idiosyncratic income shocks, their amount of wealth and a couple-specific match quality.
-Single agents meet, with some probability, a potential partner with a match quality, productivity and wealth.
-After the draw, they decide whether to marry, cohabit or stay single.
-Couples make decisions about consumption, savings and female labor force participation.
-Women receive a productivity penalty for not working and women's time can be used to produce a public good which captures utility gains from children, durable goods and services.
-Cohabitation and marriage differ in their splitting costs as well as in the way property is divided when the couple dissolves.
-Moreover, cohabitation is subjected to stigma, which is modeled as an exogenous utility flow.\footnote{The stigma towards cohabitation is to be interpreted considering the shame towards out-out-wedlock births, premarital sex and premarital cohabitation at time of the divorce revolution.} In the case of breakup, assets are split according to individual property rights, while in the case of divorce they are divided in half.\footnote{We made this assumption because the model will be estimated using community property states data.} Breakup (unilateral divorce) can be initiated unilaterally, as opposed to mutual consent divorce, which requires the consensus of both partners.
+Moreover, we analyze how unilateral divorce affected cohabitation spells duration: our estimates from a multinomial probit show that cohabitations formed after the reform last longer because people both marry less and break up less.\footnote{Hereafter we refer to the separation from cohabitation as a breakup to avoid confusion with legal separation.}
+
+In the second part of the paper, we propose a theory to understand the mechanisms underlying the facts documented in the empirical part.
+We build a dynamic model of intra-household decision making and search in the mating market, where agents make decisions according to the realization of idiosyncratic permanent income shocks, their amount of wealth and couple-specific match quality.
+With some probability, single agents meet a potential partner with a random match quality, productivity, and wealth.
+After the draw, they decide whether to marry, cohabit, or stay single.
+Couples make decisions about consumption, savings, and female labor force participation.
+Women receive a productivity penalty for not working, and women's time can be used to produce a public good that captures utility gains from children, durable goods, and services.
+
+In the model, cohabitation and marriage differ in their splitting costs and the way property is divided when the couple dissolves.
+Moreover, there is a stigma affecting cohabitations, which is modeled as an exogenous disutility flow.
+It can capture the shame towards out-out-wedlock births, premarital sex, and premarital cohabitation at the time of the divorce revolution.
+In the case of a breakup, assets are split according to individual property rights.
+In the case of divorce, we assume they are divided in half.
+We estimate the model using community property states data to be consistent with this assumption.
+Breakup (unilateral divorce) can be initiated unilaterally, as opposed to mutual consent divorce, which requires both partners' agreement.
 Following \cite{voena2015}, under mutual consent the couple always cooperates while married, which implies that the allocation of resources corresponds to the Pareto-efficient inter-temporal allocation.
-Instead, unilateral divorce (breakup) results in a lack of commitment within marriage (cohabitation),\footnote{We model the decision making in the couple building on the literature on limited commitment (see for example \cite{kk1996},  \cite{ligon2002}, \cite{marcet2019} and \cite{pavoni2018}), which has been applied to dynamic collective models in the household by \cite{mazzocco2007}, \cite{mazzocco2013}, \cite{bayot2015}, \cite{rigas2015}, \cite{voena2015}, \cite{abraham2018}, \cite{lise2018}, \cite{low2018}, \cite{foerster2019} and \cite{reynoso2019} among others.} in fact the intra-household allocation can change in response to shocks, as spouses (cohabitants) can credibly exercise the threat of divorce (breakup).
-The fact that couples cannot commit ex-ante to any possible division of marital surplus contributes to the creation of an imperfectly transferable utility environment, under which the Becker-Coase theorem does not hold.\footnote{For an application of an imperfectly transferable utility environment to matching and collective models see \cite{galichon2019} and \cite{weber2018}.} Hence, abandoning the mutual consent regime affects the risk of divorce and in turn the surplus of marriage.\footnote{According to \cite{becker1977}, divorce laws should not affect separation decisions \textit{``if all compensations between spouses were feasible and costless"}.
-The assumptions underlying the Becker-Coase theorem are discussed by \cite{chiappori2015} and \cite{fella2004}.} More precisely, the barriers to divorce---represented by its costs and rights---affect the gains of marriage with respect to cohabitation through three main channels.
-First, by acting as commitment technologies, they enforce a better risk sharing and a more efficient specialization in the production of public goods within marriage.\footnote{We assume that public goods are produced with money and women's time.
-When women stop working for producing such a good their potential productivity in the labor market decreases.} Second, they increase the risk of being ``trapped" in a bad marriage.
+% Wait is this even true???
+Instead, the fact that just one spouse can decide to terminate the relationship results in a lack of commitment, making the intra-household allocation of decision power responsive to shocks.
+Hence, abandoning the mutual consent regime affects the risk of divorce and, in turn, the surplus of marriage.
+
+The divorce costs and rights affect the gains of marriage relative to cohabitation through three main channels.
+First, by acting as commitment technologies, they enforce a better risk sharing and a more efficient specialization in public goods production within marriage.
+We assume that public goods are produced with money and women's time.
+When a woman stops working to produce such a good, her potential productivity in the labor market decreases.
+Second, divorce costs increase the risk of being ``trapped" in a bad marriage.
 Third, they affect the expected value of marriage by modifying the risk and value of divorce.
-The effects of tightening or relaxing the barriers to divorce depends on which channel prevails: for example, the introduction of unilateral divorce has an uncertain impact on the share of couples that cohabit and marry.
-Interestingly, in our framework  the outcomes of cohabitation and marriage not only depend on the rules underlying these contracts, but also on sorting on match quality.
-In fact, a cheap breakup is most attractive to couples whose match quality is low and couples' ability to cooperate depends on the match quality itself through its effect on the couples' stability.\footnote{It's easier to make partnership-specific investments when the risk of splitting is low, which is the case when the match quality is high.}
-
-%
+The effects of tightening or relaxing the barriers to divorce depend on which channel prevails.
+For example, the introduction of unilateral divorce has an uncertain impact on the share of couples that cohabit and marry.
+The outcomes of cohabitation and marriage depend not only on the rules underlying these contracts but also on sorting on unobserved relationship quality.
+A cheap breakup is most attractive to couples whose match quality is low.
+The couples' ability to cooperate depends on the match quality itself through its effect on the couples' stability: making partnership-specific investments is more comfortable when the risk of splitting is low, which is when the match quality is high.
+
 %In our framework marriage gains depend on the quality of the match: for couples whose value is low cohabitation is the best choice because breaking up is cheaper and their risk of splitting is high.
@@
 In the third part of the paper we structurally estimate the model to understand the quantitative relevance of the mechanisms that drive partnership choice.
-The model is estimated by indirect inference using as targets the regression results from our empirical analysis, mating market moments (NSFH), and female labor supply moments (PSID).
-The introduction of unilateral divorce is modeled as an unexpected policy.
-The estimated model closely replicates the targeted moments, and over-identification checks support the estimation results by highlighting that the model can match a number of non-targeted moments, among which the impact of unilateral divorce on cohabitation duration.
-According to the estimated model, a switch from mutual consent to unilateral divorce causes couples to start cohabiting more by reducing married couple's ability to cooperate and by increasing the likelihood of a costly divorce.\footnote{An increased likelihood of divorce can reduce the ability of the couple to cooperate by itself.
-Yet it also has a direct effect on the marriage surplus by reducing the likelihood of losing assets upon divorce.
-For example, if there was no wage uncertainty and women were always participating in the labor market, unilateral divorce would affect the gains of marriage via the direct effect only.} Since cohabiting couples that would have married under the older regime are better matched than the average cohabiting couple, the reform increases the stability and the duration on newly formed cohabitations.
-To further deepen our understanding of the mechanisms, we analyze the changes in intra-household bargaining that followed the policy change in the model.
+The model is estimated by indirect inference using to match the regression results from our empirical analysis, mating market moments (NSFH), and female labor supply moments (PSID).
+The introduction of unilateral divorce is modeled as an unexpected policy change.
+The estimated model closely replicates the targeted moments.
+Our over-identification checks support the estimation results: the model can match several non-targeted moments, for instance, the impact of unilateral divorce on cohabitation duration.
+
+According to the estimates, a switch from mutual consent to unilateral divorce causes couples to start cohabiting more by reducing the married couple's ability to cooperate and by increasing the likelihood of a costly divorce.\footnote{An increased likelihood of divorce can reduce the ability of the couple to cooperate by itself.
+Yet it also directly affects the marriage surplus by reducing the possibility of losing assets upon divorce.
+For example, if there was no wage uncertainty and women always participated in the labor market, unilateral divorce would affect marriage gains via the direct effect only.} Since cohabiting couples that would have married under the older regime are better matched than the average cohabiting couple, the reform increases the stability and the duration of newly formed cohabitations.
+To further deepen our understanding of the mechanisms, we analyze the intra-household bargaining changes that followed the policy change.
 We find that the average Pareto weight of cohabiting women increases because men, fearing to lose most of their assets because of divorce, convince women to cohabit instead of marrying in exchange for more power in the couple.
-This mechanism is specific to community property regime: under a title-based regime men would not need to choose cohabitation to insure their assets.
-Consistently with empirical evidence, the impact of unilateral divorce on the likelihood to cohabit is lower in the model under a title-based regime.
+This mechanism is specific to the divorce regime where assets are split evenly.
+Instead, if spouses always keep owning their assets separately, men would not need to choose cohabitation to insure their property.
+Consistently with empirical evidence, the impact of unilateral divorce on cohabitation likelihood is lower in the model under separate ownership.
+% This paragraph is still long and can be split somehow
 
 The fourth and last part of the paper conducts a series of counterfactual experiments to understand the quantitative importance of the forces that contributed to the rise of cohabitation.
-To assess the role of unilateral divorce we perform a counterfactual experiment where unilateral divorce was never introduced.
+To assess the role of unilateral divorce, we perform a counterfactual experiment where the unilateral divorce was never introduced.
 We find that people on average would have spent 1.35 years cohabiting instead of 2.26, while only 26.7\% of people would have ever cohabited instead of 34.8\%.
-In a second series of counterfactual experiments we find that a 20\% increase in women wages and a 20\% drop in market prices of goods increase respectively by 1\% and 2\% the share of people that ever cohabited at age 39.
+In the second series of counterfactuals, we find that a 20\% increase in women wages and a 20\% drop in market prices of goods increase respectively by 1\% and 2\% the share of people that ever cohabited at age 39.
 Both effects are driven by a reduced scope for household specialization, which is better exploited within marriage.
-We also perform a welfare analysis of the introduction of unilateral divorce: the possibility to cohabit limits the welfare losses for men who can secure their assets, while women suffer more because couple-specific investments like children deteriorate their value of divorcing more that for men.
+We also study various channels of how unilateral divorce affects welfare.
+The possibility to cohabit limits the welfare losses for men who can secure their assets, while women suffer more because of couple-specific investments like children deteriorate their value of divorcing more than for men.
 
@@
 This policy change has been shown to affect the rate of divorce (\citealp{friedberg1998}, \citealp{wolfers2006}), female labor supply (\citealp{stevenson2008}, \citealp{voena2015}), savings (\citealp{voena2015}), marriage rates (\citealp{rasul2003,rasul2006}), children's well-being (\citealp{gruber2004}), family violence (\citealp{stevenson2006}), marriage-specific capital (\citealp{stevenson2007}), assortative mating (\citealp{reynoso2019}) and prostitution (\citealp{ciacci2017}), among the others.
-We complement the findings of \cite{rasul2003,rasul2006} by showing that the decrease in marriage rates after the introduction of unilateral divorce is not only driven by more people staying singles, but also by more people that choose to cohabit.
+We complement the findings of \cite{rasul2003,rasul2006} by showing that the decrease in marriage rates after the introduction of unilateral divorce is not only driven by more people staying single, but also by more people that choose to cohabit.
 This suggest that marriage and cohabitation are substitutes.\footnote{Cohabitation can also be a substitute for being single or dating, as \cite{rindfuss1990} point out.
-Moreover, \cite{blasutto2020} and \cite{brien2006} claim that cohabitation can also be a complement for marriage, which allows the couple to learn about its match quality before making the binding decision of getting married.} Our paper builds on \cite{voena2015}, that studies how the interaction of unilateral divorce with property rights upon divorce affected household behavior of married couples.
+Moreover, \cite{blasutto2020} and \cite{brien2006} claim that cohabitation can also be a complement for marriage, which allows the couple to learn about its match quality before making the binding decision of getting married.} Our paper builds on \cite{voena2015},  which studies how the interaction of unilateral divorce with property rights upon divorce affected married couples' household behavior.
 We extend her work both by considering cohabitation as an alternative relationship and by analyzing selection into partnership.
 This paper also extends the work of \cite{fernandez2017} by showing that not considering cohabitation as an alternative to marriage biases upwards the negative impact of unilateral divorce on men's welfare.
-The intuition is that men can limit the losses stemming from the increased risk of divorce by choosing to cohabit.
+The intuition is that men can limit the losses stemming from the increased risk of divorce by cohabiting.
 
@@
 A first subset thereof has focused on identifying the gains of marriage and cohabitation, highlighting the role of commitment \citep{matouschek2008}, specialization within the couple \citep{gemici2014}, learning about match quality \citep{brien2006}, income dynamics \citep{blasutto2020}, assets \citep{lafortune2017, lafortune2020} and investment in children \citep{lundberg2015}.
-We extend these works by showing how an increase in the easiness of divorce not only decreases the ability of the couple to cooperate, but it also makes divorce allocations more relevant for partnership choices, since the likelihood of divorce increases.
-Consequently, the relative power of potential partners and the rules about division of assets upon divorce become crucial.
-These results highlight a new role of partners' relative power and assets for partnership choices, which is analyzed within a framework that extends the theory of \cite{blasutto2020} and \cite{gemici2014} by including saving decisions.\footnote{\cite{lafortune2020} also highlight the role of assets: our model features their intuition that assets can act as act as a commitment technology, but our framework also allows assets to influence partnership choices via a direct effect of divorce's risk.
-Thanks to this mechanism we can explain why unilateral divorce caused cohabitation to increase more in community property states than in title-based ones.} A second set of papers studies the effect of changes in cohabitants' rights on partnership choices and cohabiting couples' behavior, highlighting the role of alimony rights (\citealp{chiappori2017,gousse2018}), taxation \cite{leturcq2012} and division of assets at breakup (\citealp{fisher2012,gousse2018,chigavazira2019}).
+We extend these works by showing how an increase in the easiness of divorce decreases the couple's ability to cooperate and makes divorce allocations more relevant for partnership choices, since the likelihood of divorce increases.
+Consequently, the relative power of potential partners and the rules about the division of assets upon divorce become crucial.
+These results highlight a new role of partners' relative power and assets for partnership choices, which is analyzed within a framework that extends the theory of \cite{blasutto2020} and \cite{gemici2014} by including saving decisions.\footnote{\cite{lafortune2020} also highlight the role of assets: our model features their intuition that assets can act as a commitment technology, but our framework also allows assets to influence partnership choices via a direct effect of divorce's risk.
+Thanks to this mechanism, we can explain why unilateral divorce caused cohabitation to increase more in community property states than in title-based ones.}
+
+Another subset of these papers studies the effect of changes in cohabitants' rights on partnership choices and cohabiting couples' behavior, highlighting the role of alimony rights  (\citealp{chiappori2017,gousse2018}), taxation \cite{leturcq2012} and division of assets at breakup (\citealp{fisher2012,gousse2018,chigavazira2019}).
 We extend this literature by showing that the introduction of unilateral divorce impacts both the choice to cohabit and cohabitation's stability, even though cohabitant's rights are not directly affected.\footnote{\cite{matouschek2008} study the effect of unilateral divorce on marriage rates using a framework where the choice between marriage and cohabitation is considered.
-Their framework does not predict changes to the propensity to cohabit.} Further, the effects on the choice to cohabit depends on property division rights, which indicates that partnership choices depend on divorce allocations.
+Their framework does not predict changes to the propensity to cohabit.} Further, the effects on the intention to cohabit depends on property division rights, which indicates that partnership choices depend on divorce allocations.
 This evidence suggests that changes in family law should be designed considering that marriage and cohabitation are substitutes.
@@
 
-Finally, this paper is tied to the large literature that studies the changes in the character of the American household over the last decades.
+Finally, this paper is tied to the extensive literature that studies the changes in the American household character over the last decades.
 Various studies explored the role of health improvements, wage distribution and dynamics, norms and technology on the rise in female labor force participation \citep{fernandez2004,greenwood2005,albanesi2016,greenwood2016}, the changes in household formation and dissolution \citep{greenwood2016,ciscato2019}, the rise in positive assortative mating \citep{fernandez2005,greenwood2016,ciscato2019} and the increase in the age at marriage \citep{santos2016}.
-We extend this literature by showing that the introduction of unilateral divorce implied an increase in cohabitation and that advances in the home production technology and the reduction in the gender wage gap also contributed to the rise in cohabitation.
+We extend this literature by showing that the introduction of unilateral divorce implied a rise in cohabitation.
+Advances in the home production technology and the reduction in the gender wage gap also contributed to the rise.
+
+Our modelling of the decision making in the couple builds on existing literature on limited commitment (\cite{kk1996},  \cite{ligon2002}, \cite{marcet2019} and \cite{pavoni2018}), which has been applied to dynamic collective models in the household by \cite{mazzocco2007}, \cite{mazzocco2013}, \cite{bayot2015}, \cite{rigas2015}, \cite{voena2015}, \cite{abraham2018}, \cite{lise2018}, \cite{low2018}, \cite{foerster2019} and \cite{reynoso2019} among others.
+The fact that couples cannot commit ex-ante to any possible division of marital surplus contributes to the creation of an imperfectly transferable utility environment, under which the Becker-Coase theorem does not hold (see \cite{galichon2019} and \cite{weber2018}, who applies the theorem to related environments).
+The imperfect transferability feature is important: according to \cite{becker1977}, divorce laws should not affect separation decisions \textit{``if all compensations between spouses were feasible and costless"}.
+\cite{chiappori2015} and \cite{fella2004} discuss the assumptions of the Becker-Coase theorem more.
 
@@
 Section 3 documents the effect of introducing unilateral divorce on partnership choices.
-Section 4 presents and develop the theoretical model.
-Section 5 describes the estimation of the model, while section 6 discusses the main mechanisms of the model.
+Section 4 presents and develops the theoretical model.
+Section 5 describes the model's estimation, while section 6 discusses the main mechanisms of the model.
 Section 7 reports the results of the welfare analysis.
-Section 8 performs a series of counterfactual experiments, while section 9 contains the conclusion.
+Section 8 performs a series of counterfactual experiments, while Section 9 contains the conclusion.
 
@@
 %\end{enumerate}
-\section{US Divorce and Cohabitation Laws: an Overview}
-\textbf{Divorce Laws.} Between late 1960s and early 1980s most U.S.
-states experienced fundamental changes in the divorce law, both regarding the right to initiate a divorce without the consent of the other spouse and about the laws that govern the division of assets upon divorce.
-
-Before the 1960s the vast majority of US states had a mutual consent divorce regime,\footnote{All the states apart from New Mexico, Oklahoma and Alaska.} where the agreement of both spouses was needed to obtain a divorce for mundane reasons (i.e.
-without misconduct by any spouse).
-Moreover, divorce was permitted for grounds showing guilt of misconduct by any of the two spouses: for those cases the agreement of the innocent party alone was enough for having a divorce granted.\footnote{Examples of guilt or misconduct are adultery or abandonment.}
-From the late 1960s and early 1980s most U.S.
-states switched to a unilateral divorce regime.\footnote{A list of the years at which unilateral divorce was introduced in different states can be found in table 1 of \cite{ciacci2017}.} Under this regime divorce can be filed by one spouse without the consent of the other.
-
-Another dimension along which divorce laws differs across states and over time is the one about property division regimes. In the United States there are three types of those:
+\section{US Divorce and Cohabitation Laws: an Overview} % This should be a subsection, otherwise it is a bit short...
+\textbf{Divorce Laws.} Between the late 1960s and early 1980s, most US states experienced fundamental changes in the divorce law.
+These changes affected both the right to initiate a divorce without the other spouse's consent and about the division of assets upon divorce.
+
+Before the 1960s the vast majority of US states had a mutual consent divorce regime.\footnote{All the states apart from New Mexico, Oklahoma and Alaska.} Both spouses' agreement was needed to obtain a divorce for mundane reasons (i.e., without misconduct by any spouse).
+Both spouses' agreement was needed to obtain a divorce for mundane reasons (i.e., without misconduct by any spouse).
+However, divorce was still permitted for grounds showing guilt of misconduct by any of the two spouses: for those cases, the innocent party's agreement alone was enough for having a divorce granted.
+Examples of guilt or misconduct are adultery or abandonment.
+
+From the late 1960s and early 1980s, most US states switched to a unilateral divorce regime.
+Under this regime divorce can be filed by one spouse without the consent of the other.
+More detailed chronology about the unilateral divorce introduction was in different states can be found in Table 1 of \cite{ciacci2017}% I think this needs an appendix
+
+Another dimension along which divorce laws differ across states and over time is property division regimes. In the United States, there are three types of these regimes:
 \begin{enumerate}
 \item \textit{Community Property}.
-Under this regime the couple are jointly owning family wealth, both that obtained during marriage and before.
-This implies that when divorce occurs, each spouse gets exactly half of the total family wealth.
+Under this regime the couple is jointly owning family wealth, both that obtained during the marriage and before.
+This implies that when divorce occurs, each spouse gets precisely half of the total family wealth.
 \item \textit{Equitable distribution}.
-Under this regime, it is the court that decides how to split family wealth between the two spouses.
-This decision is driven by the principle of equity, which is ambiguous: in some cases the wealth is divided exactly in half, while in others a larger share reserved to the party that contributed the most to its accumulation.
-\item \textit{Title Based Regime}. Under this regime wealth is split according to the title of ownership.	
+Under this regime, the court decides how to split family wealth between the two spouses.
+This decision is driven by the principle of equity, which is ambiguous.
+In some cases, the wealth is divided exactly in half; in others, a larger share reserved for the party that contributed the most to its accumulation.
+\item \textit{Title Based Regime}. Under this regime, wealth is split according to the title of ownership, as the spouses own their assets separately.
 \end{enumerate}
@@
 %\end{enumerate}
-\textbf{Breakup/Divorce laws compared.} The regulation of cohabitation in the US is limited, and small changes have been done since the 1960s, when “Cohabitation created no rights or obligations” \citep{garrison2008}.\footnote{\cite{garrison2008} explains that in to 1960s \textit{“Cohabitants could not agree to create rights or obligations based on their intimate relationship”}.
+\textbf{Breakup/Divorce laws compared.} The regulation of cohabitation in the US is limited, and small changes have been done since the 1960s, when “Cohabitation created no rights or obligations”, see \cite{garrison2008}.
+She argues that \textit{“Cohabitants could not agree to create rights or obligations based on their intimate relationship”}.
 She continues analyzing the effect of the \textit{Marvin vs.
-Marvin} case (year 1976), where a palimony---a compensation from one member of an unmarried couple to another after breakup--- was awarded to the female partner: \textit{“[the case] has not produced results markedly different from those permissible under pre-Marvin case law.”} Finally, she argues that claims for financial relief has rarely reached the courts because 1) cohabitation are usually very short and no committed 2) cohabitants are younger and poorer than marrieds and 3) cohabitants do not usually adopt sharing behavior, unlike in the Marvin cases.
-Similarly, \cite{bowman2004} claims that remedies based of contract had a limited application.} Hence, breakup resembles unilateral divorce because cohabitation can be ended by one partner without the consent of the other partner.
-Concerning property division rights, breakup de facto falls under the title-based property regime.
-One important difference between divorce and breakup is that the former requires the couple to undergo a legal process, which implies monetary and time costs, while the latter does not requires this procedure.\footnote{While \cite{garrison2008} argues that claims for financial reliefs after breakup are rare, breakup is treated like divorce under the doctrine of common-law marriage, a legal framework under which a couple is considered as married without having formally registered their relationship.
-\cite{goran2008} explains that the existence of the implied contract is presumed once continuous cohabitation and reputation (holding out as husband and wife) are proven, but it is still possible that the couple---even if cohabiting for many years---is not considered as being in a marriage agreement, with marital right and obligations.
-These rules creates uncertainty regarding the recognition of common-law marriage for some couples, especially those close to a breakdown, where the two partners might disagree about the existence of an implied marital agreement.} This fact is consistent with the findings of \cite{avellar2005}, who show that for women the drop in income following couple's breakdown is larger for divorce than breakup.
-To further support the claim that divorce is more costly than breakup, in appendix \ref{section:eventsa} we select from the PSID a sample of couples that divorced/broke up to study how their net-worth evolves after splitting.
-The point estimates of two event-studies indicates that the divorce of richer couples results in a loss of assets, while we could not observe the same pattern for the divorce of poorer couples and breakups.
+Marvin} case (1976), where palimony --- a compensation from one member of an unmarried couple to another after breakup --- was awarded to the female partner: \textit{“[the case] have not produced results markedly different from those permissible under pre-Marvin case law.”} Finally, she argues that claims for financial relief has rarely reached the courts because 1) cohabitation is usually very short and no committed 2) cohabitants are younger and poorer than marrieds and 3) cohabitants do not usually adopt sharing behavior, unlike in the Marvin cases.
+Similarly, \cite{bowman2004} claims that remedies based on the contract had a limited application.
+
+Hence, breakup resembles unilateral divorce because one partner can end cohabitation without the other partner's consent.
+Concerning property division rights, cohabitation de facto falls under the title-based property regime.
+One crucial difference between divorce and breakup is that the former requires the couple to undergo a legal process, which implies monetary and time costs, while the latter does not require this procedure.
+While \cite{garrison2008} argues that claims for financial reliefs after a breakup are rare, the breakup is treated like a divorce under the doctrine of common-law marriage, a legal framework under which a couple is considered as married without having formally registered their relationship.
+\cite{goran2008} explains that the existence of the implied contract is presumed once continuous cohabitation and reputation (holding out as husband and wife) are proven.
+However, it is still possible that the couple --- even if cohabiting for many years---is not considered to be in a marriage agreement, with marital rights and obligations.
+These rules create uncertainty regarding recognizing common-law marriage for some couples, especially those close to a breakup, where the two partners might disagree about the existence of an implied marital agreement.
+
+The lower costs of a breakup are consistent with the findings of \cite{avellar2005}, who show that for women the drop in income following the couple's breakdown is larger for divorce than for a breakup.
+To further support the claim that divorce is more costly than a breakup, in appendix \ref{section:eventsa} we select from the PSID a sample of couples that divorced/broke up to study how their net-worth evolves after splitting.
+The point estimates of two event-studies indicate that richer couples' divorce results in a loss of assets, while we could not observe the same pattern for the divorce of poorer couples and breakups.
+
 %When a child is born in the unmarried couple, where the situation started changing in the 1990s, when establishing paternity and the enforcement of child support became easier.\footnote{\cite{rossin2017} explains that in-hospital voluntary paternity establishments enabled all unmarried parents to voluntarily establish paternity.}
@@
 
-\bibliographystyle{achicago}
+%\bibliographystyle{achicago}
 \bibliography{mybibliography}

### 2020-10-01 draft_sub_con.tex
some modifications in intro and body (NO empirical part)

@@
 
-\title{The Rise of Cohabitation and Unilateral Divorce\thanks{The authors wish to thank David de la Croix, Matthias Doepke, Fabio Mariani, Jesús Fernández-Villaverde, Alessandra Voena and the Norhtwestern Macro group for their useful comments.
+\title{(Changing) Marriage and Cohabitation Patterns in the US: do Divorce Laws Matter?\thanks{The authors wish to thank David de la Croix, Matthias Doepke, Fabio Mariani, Jesús Fernández-Villaverde, Alessandra Voena and the Northwestern Macro group for their useful comments.
 Computational resources were provided by the supercomputing facilities of the Université catholique de Louvain (CISM/UCL) and Northwestern University.
@@
 	\footnotetext[1]{IRES/LIDAM, UCLouvain \& FNRS (Belgium). Email:  \tt{fabio.blasutto@uclouvain.be}}
-	\footnotetext[2]{Northwestern Univrsity. Email:  \tt{egorkozlov2020@u.northwestern.edu}.\\}
+	\footnotetext[2]{Northwestern University. Email:  \tt{egorkozlov2020@u.northwestern.edu}.\\}
 
@@
 As cohabiting couples formed after the reform are better matched, the average length of cohabitations increases.
-A counterfactual experiment reveals that the time spent cohabiting would have been halved if the divorce laws had never changed.
+A counterfactual experiment reveals that the time spent cohabiting would have been almost halved if the divorce laws had never changed.
 \end{abstract}
@@
 Fourth, we perform several counterfactual experiments to understand the overall role of unilateral divorce on the rise of cohabitation.
-We then quantify the welfare gains and losses of the reform for men and women.
 Thus, this paper consists of four parts, one for each contribution, which we now describe in more detail.
@@
 We use data from the National Survey of Family and the Household (NSFH) and from the National Survey of Family Growth (NSFG) to study the choice between marrying and cohabiting.
-Then, exploiting the exogenous variation coming from the staggered introduction of unilateral divorce over time across the US states, we estimate that newly formed couples are 5-7\% more likely to choose cohabitation over marriage than in the pre-reform period.
+Then, exploiting the exogenous variation coming from the staggered introduction of unilateral divorce over time across the US states, we estimate that couples formed after the policy change are 5-7\% more likely to choose cohabitation over marriage than in the pre-reform period.
 % Give some baseline numbers here?
@@
 We build a dynamic model of intra-household decision making and search in the mating market, where agents make decisions according to the realization of idiosyncratic permanent income shocks, their amount of wealth and couple-specific match quality.
-With some probability, single agents meet a potential partner with a random match quality, productivity, and wealth.
+With some probability, single agents meet a potential partner drawn from an exogenous distribution of match quality, productivity, and wealth.
 After the draw, they decide whether to marry, cohabit, or stay single.
@@
 To assess the role of unilateral divorce, we perform a counterfactual experiment where the unilateral divorce was never introduced.
-We find that people on average would have spent 1.35 years cohabiting instead of 2.26, while only 26.7\% of people would have ever cohabited instead of 34.8\%.
-In the second series of counterfactuals, we find that a 20\% increase in women wages and a 20\% drop in market prices of goods increase respectively by 1\% and 2\% the share of people that ever cohabited at age 39.
+We find that people on average would have spent 1.24 years cohabiting instead of 2.19, while only 29.1\% of people would have ever cohabited instead of 43.3\%.
+In the second series of counterfactuals, we find that a 20\% decrease in gender productivity gap and a 10\% drop in market prices of goods increase respectively by 9\% and 3\% the share of people that ever cohabited at age 39.
 Both effects are driven by a reduced scope for household specialization, which is better exploited within marriage.
@@
 They select a sample of marriages and cohabitation that stays intact at the end of the time span[this seems wrong to me].
-Then they claim that the effect is not due to selection, even tought they check that in a sloppy way without a duration model, which seems the thing to do.
+Then they claim that the effect is not due to selection, even thought they check that in a sloppy way without a duration model, which seems the thing to do.
 %\item \cite{chiappori2017}: what:  granting alimony rights to cohabiting couples in Canada.
@@
 %	\item \cite{waggoner2016} Textual words:\textit{As far as the law is concerned, the partners are complete strangers to each other}.
-He means short term relationship because longer-term cohabitations have already found their way into the legal system, even tough Contracts are unenforceable in some jurisdictions and, even if they are, the plaintiff cannot always prove the	existence of a contract.
+He means short term relationship because longer-term cohabitations have already found their way into the legal system, even though Contracts are unenforceable in some jurisdictions and, even if they are, the plaintiff cannot always prove the	existence of a contract.
 Other English-speaking jurisdictions have already enacted or introduced	legislation granting marital rights to cohabiting couples if their relationship meets specific criteria (Australia, Canada, Ireland,1 New Zealand,101 and Scotland1 and introduced in the United Kingdom for England and Wales.
@@
 \begin{equation}\label{eq:ols_baseline}
-\text{married}_{i,t,s}=\beta_0+\beta_1*\text{Unilatearal}_{t,s}+\mathbf{\gamma'}\mathbf{X}_i+\delta_s+\nu_t+\epsilon_{i,t,s}.
+\text{married}_{i,t,s}=\beta_0+\beta_1*\text{Unilateral}_{t,s}+\mathbf{\gamma'}\mathbf{X}_i+\delta_s+\nu_t+\epsilon_{i,t,s}.
 \end{equation}
@@
 \begin{split}
-\text{married}_{i,t,s}=\beta_0+&\beta_1*\text{Unilatearal*No Title Based}_{t,s}\\&+\beta_2*\text{Unilatearal*Title Based}_{t,s}+\\&\quad\quad\beta_3*\text{Title Based}_{t,s}+\mathbf{\gamma'}\mathbf{X_i}+\delta_s+\nu_t+\epsilon_{i,t,s},
+\text{married}_{i,t,s}=\beta_0+&\beta_1*\text{Unilateral*No Title Based}_{t,s}\\&+\beta_2*\text{Unilateral*Title Based}_{t,s}+\\&\quad\quad\beta_3*\text{Title Based}_{t,s}+\mathbf{\gamma'}\mathbf{X_i}+\delta_s+\nu_t+\epsilon_{i,t,s},
 \end{split}
@@
 \FloatBarrier
-The results show that the effect of unilateral divorce on the likelihood that a couples chooses marriage over cohabitation in non-title-based states is significant with a magnitude of $-6\%(-7\%)$ depending on specification, while it is non significant and much smaller in title-based states.
+The results show that the effect of unilateral divorce on the likelihood that a couples chooses marriage over cohabitation in non-title-based states is significant with a magnitude of $-6\%(-7\%)$ depending on specification, while it is not significant and much smaller in title-based states.
 These results suggest that having a sharing rule decided by the law is not enough to replace the mutual consent regime as an alternative commitment technology.
@@
 \begin{split}
-&Y_{i,s,t,d}^\text{Marry}=\beta^\text{Marry}*\text{Unilatearal}_{s,t}+\mathbf{\gamma^{\text{Marry'}}}\mathbf{X_i}+\alpha_d+\delta_s+\nu_t+\epsilon^{\text{Marry}}_{i,s,t,d},\\&
-Y_{i,s,t,d}^\text{Cohabit}=\beta^\text{Cohabit}*\text{Unilatearal}_{s,t}+\mathbf{\gamma^{\text{Cohabit'}}}\mathbf{X_i}+\alpha_d+\delta_s+\nu_t+\epsilon^{\text{Cohabit}}_{i,s,t,d},\\&
-Y_{i,s,t,d}^\text{Separate}=\beta^\text{Separate}*\text{Unilatearal}_{s,t}+\mathbf{\gamma^{\text{Separate'}}}\mathbf{X_i}+\alpha_d+\delta_s+\nu_t+\epsilon^{\text{Separate}}_{i,s,t,d},
+&Y_{i,s,t,d}^\text{Marry}=\beta^\text{Marry}*\text{Unilateral}_{s,t}+\mathbf{\gamma^{\text{Marry'}}}\mathbf{X_i}+\alpha_d+\delta_s+\nu_t+\epsilon^{\text{Marry}}_{i,s,t,d},\\&
+Y_{i,s,t,d}^\text{Cohabit}=\beta^\text{Cohabit}*\text{Unilateral}_{s,t}+\mathbf{\gamma^{\text{Cohabit'}}}\mathbf{X_i}+\alpha_d+\delta_s+\nu_t+\epsilon^{\text{Cohabit}}_{i,s,t,d},\\&
+Y_{i,s,t,d}^\text{Breakup}=\beta^\text{Breakup}*\text{Unilateral}_{s,t}+\mathbf{\gamma^{\text{Breakup'}}}\mathbf{X_i}+\alpha_d+\delta_s+\nu_t+\epsilon^{\text{Breakup}}_{i,s,t,d},
 \end{split}
@@
 \begin{equation}\label{eq:probit_error}
-\myvec{\epsilon_{i,s,t,d}^{\text{Marry}}\\\epsilon_{i,s,t,d}^{\text{Cohabit}}\\\epsilon_{i,s,t,d}^{\text{Separate}}}\sim\mathcal{N}(\mathbf{0},\mathbf{\Sigma}),
+\myvec{\epsilon_{i,s,t,d}^{\text{Marry}}\\\epsilon_{i,s,t,d}^{\text{Cohabit}}\\\epsilon_{i,s,t,d}^{\text{Breakup}}}\sim\mathcal{N}(\mathbf{0},\mathbf{\Sigma}),
 \end{equation}
@@
 \begin{cases}  	
-\text{Marry}\hspace{30pt}       \text{if}\hspace{10pt}Y_{i,s,t,d}^\text{Marry}>Y_{i,s,t,d}^\text{Cohabit}\hspace{5pt}\text{and}\hspace{5pt}\hspace{5pt}Y_{i,s,t,d}^\text{Marry}>Y_{i,s,t,d}^\text{Separate}\\
-\text{Cohabit}\hspace{23pt}   \text{if}\hspace{10pt}Y_{i,s,t,d}^\text{Cohabit}>Y_{i,s,t,d}^\text{Marry}\hspace{5pt}\text{and}\hspace{5pt}\hspace{5pt}Y_{i,s,t,d}^\text{Cohabit}>Y_{i,s,t,d}^\text{Separate}\\
-\text{Separate}\hspace{22pt}     \text{otherwise.}
+\text{Marry}\hspace{30pt}       \text{if}\hspace{10pt}Y_{i,s,t,d}^\text{Marry}>Y_{i,s,t,d}^\text{Cohabit}\hspace{5pt}\text{and}\hspace{5pt}\hspace{5pt}Y_{i,s,t,d}^\text{Marry}>Y_{i,s,t,d}^\text{Breakup}\\
+\text{Cohabit}\hspace{23pt}   \text{if}\hspace{10pt}Y_{i,s,t,d}^\text{Cohabit}>Y_{i,s,t,d}^\text{Marry}\hspace{5pt}\text{and}\hspace{5pt}\hspace{5pt}Y_{i,s,t,d}^\text{Cohabit}>Y_{i,s,t,d}^\text{Breakup}\\
+\text{Breakup}\hspace{22pt}     \text{otherwise.}
 \end{cases}
@@
 			\begin{tablenotes}[flushleft]
-				\footnotesize{\item \textsc{Notes}: the values reported in the table are the mean and the standard deviation (in parenthesis) of the posterior distribution of parameters obtained using the markov chain monte carlo estimation described by \cite{imai2005a}.
+				\footnotesize{\item \textsc{Notes}: the values reported in the table are the mean and the standard deviation (in parenthesis) of the posterior distribution of parameters obtained using the Markov chain Monte Carlo estimation described by \cite{imai2005a}.
 				Coefficients' distributions whose interpercentile range do not contain 0 are denoted by the following system: *90\%, **95\%  and ***99\%.}
@@
 \begin{equation}\label{eq:bcm}
-a_{t+1}=R a_t+w^m_t(1-\phi)+P^f_t w^f_t(1-\phi)-c^f_t-c^m_t-d_t, \text{ with }a_{t+1}\geq0,
+a^f_{t+1}+a^m_{t+1}=R a_t+w^m_t(1-\phi)+P^f_t w^f_t(1-\phi)-c^f_t-c^m_t-d_t, \text{ with }a_{t+1}\geq0,
 \end{equation}
@@
 Since we use data from community property states to estimate the model, this regime applies to divorce.
-Accordingly, upon divorce each spouse keeps half of the assets, while the division of asset upon breakup is a couple decision.
+Accordingly, upon divorce each spouse keeps half of the assets, while the division of asset upon breakup is a couple's decision.
 We describe the details of this choice in this section, where the problem of the cohabiting couple is presented.
@@
 Under mutual consent regime, marriage is denoted by $\hat{M}$.
-Couples solve a Pareto problem where the weight of the wife is $\theta^f$ and the one of the husband is $1-\theta^f$.\footnote{Later in this section we describe how initial Pareto weight are set.} The state vector is $\Omega^{\hat{M}}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f\}$, while the variables over which the couple maximizes are summarized by the vector $\mathbf{q}^M_t=\{a_{t+1},d_{t},c^m_{t},c^f_{t},P^f_t,D_t\}$, where $D_t$ is a dummy variable that takes value $1$ is divorce happens and $0$ otherwise.
+Couples solve a Pareto problem where the weight of the wife is $\theta^f$ and the one of the husband is $1-\theta^f$.\footnote{Later in this section we describe how initial Pareto weight are set.} The state vector is $\Omega^{\hat{M}}_t=\{a^m_t,a^f_t,z^f_t,z^m_t,\psi_t,\theta^f\}$, while the variables over which the couple maximizes are summarized by the vector $\mathbf{q}^M_t=\{a^f_{t+1},a^m_{t+1},d_{t},c^m_{t},c^f_{t},P^f_t,D_t\}$, where $D_t$ is a dummy variable that takes value $1$ is divorce happens and $0$ otherwise.
 The formal problem solved by a couple who enters period $t$ as married is:
@@
 \end{equation}
-where $\mathbf{q}^{\hat{M}}_t=\{\tilde{a}_{t+1},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$ is the $\argmax$ of problem \eqref{eq:v_mutual} conditionally on having chosen $D_t=0$.
+where $\mathbf{q}^{\hat{M}}_t=\{\tilde{a}^m_{t+1},\tilde{a}^f_{t+1},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$ is the $\argmax$ of problem \eqref{eq:v_mutual} conditionally on having chosen $D_t=0$.
 $V_{t+1}^{i\hat{M}}(\Omega^{\hat{M}}_{t+1})$ instead can be obtained by the expectation of the sum of the time utilities that the agent gets from $t+1$ to $T$, where the variables entering the utility function derive from the Pareto problem if the agent is in a relationship, otherwise they are the solution of \eqref{eq:v_single}, which represent the singles' problem.
@@
 Intuitively, the fact that Pareto weights stay constant allows for a functioning risk-sharing and the female labor force participation decisions are taken cooperatively, ruling out the possibility that women over-supply labor to increase their bargaining power.
-In this framework, the conditions for divorce are particularly stringent: the couple splits only if both partners are better off divorcing than staying together for a feasible allocation.
+In this framework, the conditions for divorce are particularly stringent: the couple splits only if both partners are better-off divorcing than staying together for a feasible allocation.
 More in particular, if one spouse only wishes to divorce under the divorce allocation dictated by the law where assets are split equally, she will ``bribe'' the other by offering a larger share of assets to make her indifferent between staying married and divorcing.\footnote{Note that if both partners are better off divorcing under the sharing rule dictated by the law, which corresponds to an equal division in community property states, no bribing happens.}
@@
 Note that, in opposition to the mutual consent regime, Pareto weights can vary over time.
-The state vector of this problem is $\Omega^{\overline{M}}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^M_t$.
+The state vector of this problem is $\Omega^{\overline{M}}_t=\{a^m_t,a^f_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^M_t$.
 The formal problem of a couple entering $t$ as married is:
@@
 First, there is no loss in assets upon breakup.
-Second, the choice set of the cohabiting couple $\mathbf{q}^C_t=\{a_{t+1},d_t,c^m_t,c^f_t,P^f_t,D_t,M_t,\chi_{t+1}\}$ and the state variables $\Omega^{C}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t,\chi_t\}$ are different.
+Second, the choice set of the cohabiting couple $\mathbf{q}^C_t=\{a^m_{t+1},a^f_{t+1},d_t,c^m_t,c^f_t,P^f_t,D_t,M_t,\chi_{t+1}\}$ and the state variables $\Omega^{C}_t=\{a^m_t,a^f_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t,\chi_t\}$ are different.
 Note that $M_t$ is dummy that indicates the choice of marrying and $\chi_t$ is the share of assets going to the women in case of breakup.\footnote{Note that while cohabiting couples can decide to marry, married couples cannot decide to cohabit.
@@
 Instead, the parameters relative to the production of public goods, $\nu$ and $\kappa$ match those in \cite{mcgrattan1997}.
-As far as the pensions are concerned, I follow \cite{heathcote2010}: they consider the progressive nature of the US pension system but they simplify it, assuming that only the last period before retirement is relevant for the amount of the pension that a person receives.
+As far as the pensions are concerned, I follow \cite{heathcote2010}: they consider the progressive nature of the US system but they simplify it, assuming that only the last period before retirement is relevant for the amount of the pension that a person receives.
 Parameter $\phi$ is set to 0.189 to reflect the relative time that singles spend on house works relative to the time spend on the labor market.\footnote{In the PSID the average yearly time spend on house works by singles is 465.5 hours.
@@
 We use the method of indirect inference \citep{gourieroux1993} to pin down the vector $\vartheta=(\alpha, \lambda, \sigma_\psi, \sigma_{\psi,I}, \delta, \mu, \xi, \gamma )$ of the 8 remaining parameters of the model.
-We use 32 moments and regression coefficients for the structural estimation, which capture the process of marriage and cohabitation creation and dissolution, as well the female labor force participation.
+We use 31 moments and regression coefficients for the structural estimation, which capture the process of marriage and cohabitation creation and dissolution, as well as female labor supply.
 More precisely, we include as targets the coefficient of unilateral divorce estimated through equation \ref{eq:ols_baseline},\footnote{Note that the sample used for estimating equation \ref{eq:ols_baseline} in the empirical section and in the structural estimation is different.
@@
 Alternatively, we could have targeted female labor force participation, picking a number of hours for full-time work such that female labor supply is also matched.
-Since the amount of part-time work is very different according to the status (married, cohabiting or single) of the women, the amount of hours for participating women should have been differed by status.
-The problem with this approach is that women would have chosen their partnership according to the artificially fixed working schedule that partnerships offer, and not only accolading to the mechanisms that our model generates.} differences in female labor force participation between marriage and cohabitation (2), ratio of the rate of divorce between households with male wage above and below the median (1) and differences in log wages between married and cohabiting men (1).
+Since the amount of part-time work is very different according to the status (married, cohabiting or single) of the women, the number of hours for participating women should have been differed by status.
+The problem with this approach is that women would have chosen their partnership according to the artificially fixed working schedule that partnerships offer, and not only accolading to the mechanisms that our model generates.} differences in female labor force participation between marriage and cohabitation (2) and differences in log wages between married and cohabiting men (1).
 We use the retrospective marital history data from the NSFH wave III to construct the moments linked to partnership choice, while we all the others are computed using the PSID.\footnote{NSFH wave III is conducted in 2001/2003 following the original respondents of wave 1.
@@
 Instead, $\sigma_{\psi,I}$ is identified by the hazard of breakup and marriage: when this parameter is small compared to the variance of the transitory shocks, agents are not \textit{picky} about sorting into cohabitation, but they move fast to a marriage or they separate within the first periods of the relationship, according to the evolution of the love and productivity shocks.
-Finally, the parameter $\xi$ influences the surplus of marriage and cohabitation by income.
+Finally, the parameter $\xi$ influences the surplus of marriage and cohabitation by wealth.
 In fact, when $\xi$ is small, wealthier agents find the consumption of the public good $Q$ relatively more attractive.
 Since marriage allows to consume a larger quantity of $Q$ because it protects women that devote time to its production, marriage becomes a relatively more interesting option for wealthier families.
-Hence, $\xi$ is identified by the difference in log wages of married and cohabiting men and by the ratio of the rate of divorce between the relatively richer and poorer households.
+Hence, $\xi$ is identified by the difference in log wages of married and cohabiting men.
 \subsection{Model Fit}
-Table \ref{table:structural_params} reports the results of the structural estimation together with asymptotic standard errors, computed following \cite{adda2003}.
-The estimated standard deviation $\sigma_{\psi}$ of the transitory match quality shock is $0.39$, while standard deviation $\sigma_{\psi,I}$ of the love shock at first meeting is higher with a value of $0.85$.
-Instead, the probability of meeting a partner $\lambda$ is $0.51$, while the share of assets left after divorce is $0.75$.
-The weight on the public good $\alpha$ is $1.01$, while the loss in productivity parameter $\mu$ is $0.04$.
-Finally, the penalty of cohabiting is $\gamma$, while the coefficient of relative risk aversion for the public good $\xi$ is $1.18$.
+Table \ref{table:structural_params} reports the results of the structural estimation.
+The estimated standard deviation $\sigma_{\psi}$ of the transitory match quality shock is $0.76$, while standard deviation $\sigma_{\psi,I}$ of the love shock at first meeting is higher with a value of $1.67$.
+Instead, the probability of meeting a partner $\lambda$ is $0.38$, while the share of assets left after divorce is $0.80$.
+The weight on the public good $\alpha$ is $1.20$, while the loss in productivity parameter $\mu$ is $0.07$.
+Finally, the penalty of cohabiting $\gamma$ is $0.15$, while the coefficient of relative risk aversion for the public good $\xi$ is $1.14$.
 
 The fit of the model is reported in table \ref{table:fit}.
-The model matches well the hazard of marriage, breakup and divorce over time: model moments rarely lie outside the 95\% confidence interval of data moments.
-One exception is that the hazard of divorce is not hump shaped over duration because our model abstracts from learning, which is necessary to match this pattern of the data \citep{blasutto2020} .
-The share of people that ever cohabited and married over time is well matched, even though in the model the people that cohabited are slightly smaller than in the data.
-The data about female labor supply is well matched and the differences in divorce by wage and the differences in log wages for married and cohabiting men are well matched.
-Finally, the coefficient of unilateral divorce estimated through equation (\ref{eq:ols_baseline}) is slightly too large.
-
-The model is validated according to its ability to reproduce the effects of unilateral divorce on cohabitation duration, the share of income earned by women over time and average wage earned by women over age.
-We run the same econometric models of section \ref{empirics} for cohabitation duration, both with the real data sample and with the simulated sample.
+The model matches generally well the hazard of marriage, breakup and divorce over time, even though lie outside the 95\% confidence interval of data moments.
+One exception is that the hazard of divorce and breakup are not hump shaped over duration because our model abstracts from learning, which is necessary to match these pattern of the data \citep{blasutto2020} .
+The share of people that ever cohabited and married over time is well matched.
+The data about female labor supply is well matched.
+Instead, the differences in log wages for married and cohabiting men is lower than in the data.
+Finally, the coefficient of unilateral divorce estimated through equation (\ref{eq:ols_baseline}) is slightly larger than in the data, but it lies within the 95\% confidence interval.
+
+The model is validated according to its ability to reproduce the effects of unilateral divorce on cohabitation duration, the share of income in the couple earned by married women, the average wage earned by women over their age and the ratio of hazard rates of richer over poorer men.\footnote{Richer men are those whose income is above the median, while poorer men are those whose income is below the median.} We run the same econometric models of section \ref{empirics} for cohabitation duration, both with the real data sample and with the simulated sample.
 The results, reported in table \ref{table:fit}, show that the size of the effects is well matched.
-Instead, women wages are a slightly too low in the simulation, as figure \ref{fig:datasimwage} suggest.
-Finally, the average share of income provided by the wife in the household is well matched.
-
-A further test is to check whether the effect of unilateral divorce on the propensity to cohabit is lower under title-based regime than under community property regime, as it is in the data.
-We solve the model assuming a title-based regime and we obtain that the coefficient of unilateral divorce of equation (\ref{eq:ols_baseline}) is -0.04, while it was -0.09 under community property.\footnote{Note that we do not expect to match exactly the empirical coefficient (\ref{eq:ols_baseline}) under the title-based regime because we did not re-estimate the model using a sample of residents in title-based states.
+Women's wages over age and the average share of income provided by the wife in the household match the data, which validates the selection of women into the labor force.
+The fact that the model matches that divorce rates are lower for richer men supports our assumptions regarding the cost of divorce, which influences both the allocation within divorce and the surplus of marriage.
+
+A further test for our model is to check whether the effect of unilateral divorce on the propensity to cohabit is lower under title-based regime than under community property regime, as it is in the data.
+We solve the model assuming a title-based regime and we obtain that the coefficient of unilateral divorce of equation (\ref{eq:ols_baseline}) is -0.09, while it was -0.16 under community property.\footnote{Note that we do not expect to match exactly the empirical coefficient (\ref{eq:ols_baseline}) under the title-based regime because we did not re-estimate the model using a sample of residents in title-based states.
 The parameters used for this exercise are those in table \ref{table:fit}.} This result is consistent with the idea that under community property regime the shift towards cohabitation is larger because men, who are those with most decisional power, start finding cohabitation attractive when the risk of divorce increases.
@@
 \begin{threeparttable}
-\begin{tabular}{@{\extracolsep{5pt}}lcccc}   % centered columns (4 columns)
+\begin{tabular}{@{\extracolsep{5pt}}lccc}   % centered columns (4 columns)
 \hline \hline%inserts single line
 \rule{-4pt}{2.5ex}
-Estimated Parameters &  & Value & Standard error &\\ [0.45ex] % inserts table
+Estimated Parameters &  & Value & \\ [0.45ex] % inserts table
 \hline
 \rule{-4pt}{2.5ex}
-Standard deviation of match quality shock         & $\sigma_{\psi}$  & 0.39 &  $0.58\cdot 10^{-3}$&\\[0.45ex]
-Standard deviation of initial match quality shock & $\sigma_{\psi,I}$         & 0.85  &  $1.32\cdot 10^{-3}$&\\[0.45ex]
-Probability of meeting a partner               & $\lambda$       & 0.51 & $1.53\cdot 10^{-3}$ &\\[0.45ex]
-Assets left upon divorce                                 & $\delta$             & 0.75  &  $4.22\cdot 10^{-3}$&\\[0.45ex]
-Weight of public good               & $\alpha$             & 1.01 &  $6.33\cdot 10^{-3}$&\\[0.45ex]
-Loss in productivity while not working               & $\mu$             & 0.04 &  $0.13\cdot 10^{-3}$&\\[0.45ex]
-Relative Risk Aversion public good          &$\xi$   & 1.18& $2.78\cdot 10^{-3}$&\\[0.45ex]
-Penalty of Cohabiting          &$\gamma$   & 0.09&  $0.09\cdot 10^{-3}$&\\[0.45ex]
+Standard deviation of match quality shock         & $\sigma_{\psi}$  & 0.76 &  \\[0.45ex]
+Standard deviation of initial match quality shock & $\sigma_{\psi,I}$         & 1.67  &  \\[0.45ex]
+Probability of meeting a partner               & $\lambda$       & 0.38 &\\[0.45ex]
+Assets left upon divorce                                 & $\delta$             & 0.80  &  \\[0.45ex]
+Weight of public good               & $\alpha$             & 1.20 & \\[0.45ex]
+Loss in productivity while not working               & $\mu$             & 0.07 &  \\[0.45ex]
+Relative Risk Aversion public good          &$\xi$   & 1.14& \\[0.45ex]
+Penalty of Cohabiting          &$\gamma$   & 0.15&  \\[0.45ex]
 \hline
 \end{tabular}
-\begin{tablenotes}[flushleft]
-\footnotesize{\item \textsc{Notes}: The parameters in the table are estimated by Indirect inference. Asymptotic standard errors are computed following \cite{adda2003}.}
-\end{tablenotes}
 \end{threeparttable}
@@
 Share Ever Cohabited and Married         & fig. \ref{fig:erel} &  fig. \ref{fig:erel} & fig. \ref{fig:erel} \\[0.15ex]
-FLS in a Couple (hours)                 & 1075 & 1016& [1001,1031] \\[0.15ex]
-FLS if Married/ FLS if Cohabiting ($<$35 yrs)                 & 0.95 & 0.86 & [0.77,0.95] \\[0.15ex]
-FLS if Married/ FLS if Cohabiting ($\ge$35 yrs)                 & 0.95 & 1.00 & [0.88,1.12] \\[0.15ex]
-Log wages Marriage-Log wages Cohabitation                  & 0.14 & 0.12 & [0.11,0.13] \\[0.15ex]
-Divorce Rate Rich/Divorce Rate Poor                  & 0.78 & 0.79 & [0.71,0.87] \\[0.15ex]
-Unilateral Divorce coefficient equation (\ref{eq:ols_baseline})     & -0.091  & -0.065 & [-0.12,+0.06] \\[0.15ex]
+FLS in a Couple (hours)                 & 1007 & 1016& [1002,1029] \\[0.15ex]
+FLS if Married/ FLS if Cohabiting ($<$35 yrs.)                 & 1.02 & 0.86 & [0.78,0.95] \\[0.15ex]
+FLS if Married/ FLS if Cohabiting ($\ge$35 yrs.)                 & 0.97 & 1.00 & [0.89,1.13] \\[0.15ex]
+Log wages Marriage-Log wages Cohabitation                  & -0.08 & 0.12 & [0.04,0.12] \\[0.15ex]
+Unilateral Divorce coefficient equation (\ref{eq:ols_baseline})     & -0.16  & -0.11 & [-0.21,-0.02] \\[0.15ex]
 \hline \hline%inserts single line
@@
 Unilateral Divorce on the relative Risk of Marriage      & 0.75 & 0.73 &   [0.60,0.86]\\[0.15ex]
-Unilateral Divorce on the relative Risk of Separation                   & 0.81 & 0.82 & [0.75,0.89] \\[0.15ex]
+Unilateral Divorce on the relative Risk of Breakup                   & 0.81 & 0.82 & [0.75,0.89] \\[0.15ex]
 Women wages by age           &  fig. \ref{fig:datasimwage} &  fig. \ref{fig:datasimwage} & fig. \ref{fig:datasimwage} \\[0.15ex]
+Divorce Rate Rich/Divorce Rate Poor                  & 0.74 & 0.79 & [0.75,0.84] \\[0.15ex]
 Share household income earned by women  &  0.34\% &  0.35\% & [0.36-0.38] \\[0.15ex]
+
 \hline
@@
 Marriage guarantees a better commitment and cooperation, but when the match quality is low the best option is to opt for cohabitation because breaking up is cheaper than divorcing.
-The results of the event study show that upon the introduction of unilateral divorce the match quality of newly formed cohabitations increases by a value that is around 30\% percent of its structural standard deviation.\footnote{Note that the observed and structural distributions of the initial match quality are different because couples are not formed when the match quality at meeting is too low.} This result is consistent with selection of relatively high match quality couples into cohabitation after the policy change.
-This happens because unilateral divorce increases the risk of dissolution of marriage and the spouses' ability cooperate.
-This result explains why the hazard of breakup of newly formed cohabiting couples decreases after the policy reform.
+The results of the event study show that upon the introduction of unilateral divorce the match quality of newly formed cohabitations increases by a value that is around 35\% percent of its structural standard deviation.\footnote{Note that the observed and structural distributions of the initial match quality are different because couples are not formed when the match quality at meeting is too low.} This result is consistent with selection of relatively high match quality couples into cohabitation after the policy change.
+This happens because unilateral divorce increases the risk of dissolution of marriage and the spouses' ability to cooperate.
+
+%This result explains why the hazard of breakup of newly formed cohabiting couples decreases after the policy reform.
 From panel \subref{sf:sub-first} we also observe that the match quality of newly formed marriages goes up, which happens because of the decreased gains from marriage.
@@
 
-\textbf{Women's bargaining power $\theta$.} Panel \subref{sf:sub-second} depicts the evolution of the women bargaining power $\theta$ for cohabitation and marriage around unilateral divorce.
-$\theta$ increases with respect to baseline for cohabitation after the policy change, while no detectable differences are observed for marriage.
-Therefore, the reform drastically reduces the differences in average $\theta$ that preceded the policy change.
+\textbf{Women's bargaining power $\theta$.} Panel \subref{sf:sub-second} depicts the evolution of the women bargaining power $\theta$ at meeting for cohabitation and marriage around unilateral divorce.
+$\theta$ increases with respect to baseline for cohabitation after the policy change, while it decreases for marriage.
 Under Mutual consent, marriage was protecting women from ending up divorced and poor, while cohabitation was chosen only by couples where the man was not able to commit for a long term relationship and the woman had little say about the decision.
-After the reform, men prefer cohabitation over marriage because it avoids splitting up assets equally upon divorce, but they have to promise a higher initial $\theta$ to convince women.\footnote{Note that upon breakup men receive on average around 65\% of the couple's wealth.}
+After the reform, men prefer cohabitation over marriage because it avoids splitting up assets equally upon divorce, but they have to promise a higher initial $\theta$ to convince women.\footnote{Note that upon breakup men receive on average around 65\% of the couple's wealth.} Similarly, the Pareto weight of women that marry goes down because men are willing to marry instead of cohabiting only if they can control more resources within the household.
 
@@
 Table \ref{table:welf} reports the results, which show that welfare under a unilateral divorce regime is lower than under mutual consent for both genders.
-The difference is larger for women, which would need to be given more than 17,000\$ in assets in $t=0$ to be indifferent between the two regimes, while men would need only \$9,023 to be indifferent between the two.
+The difference is larger for women, which would need to be given almost 13,000\$ in assets in $t=0$ to be indifferent between the two regimes, while men would need only \$3,244 to be indifferent between the two.
 To understand the role of cohabitation for the changes in well-being, we repeat the welfare analysis assuming that cohabitation in no longer a choice.\footnote{In practice, we increase the stigma parameter towards cohabitation $\gamma$ such that cohabitation is never chosen.} For ease of exposition, we refer to the model with cohabitation as model $A$, while model $B$ is the one without cohabitation.
@@
 Table \ref{table:counterfactual_exp} reports the share of people that cohabited at 39 and the average years spent cohabiting\footnote{We consider the number of years spent cohabiting between the age of 20 to the age of 55.} under the baseline scenario and the counterfactual.
-The results show that under the counterfactual only three fourth of the people would have cohabited by the age of 39, while the years spent into cohabitation would have moved from 2.26 to 1.35.
+The results show that under the counterfactual only 67\% of the people would have cohabited by the age of 39, while the years spent into cohabitation would have moved from 2.19 to 1.24.
 The latter effect is the strongest because it captures both changes in partnership choices of singles and in the duration of partnerships.
 
-\textbf{Shrinking gender wage gap.} Table \ref{table:counterfactual_exp} reports the results of another scenario where the gender wage gap is reduced, increasing women potential wages by 20\%:\footnote{More specifically, we increase women's productivity, which might not be realized if they decide not to participate in the labor market.} the share of people that ever cohabited increases from 34.8\% to 36.2\%, while the number of years spent cohabiting move from 2.26 to 2.45.
+\textbf{Shrinking gender wage gap.} Table \ref{table:counterfactual_exp} reports the results of another scenario where the gender productivity gap is reduced by increasing women potential wages by 10\% and men's productivity is reduced by 10\%:\footnote{More specifically, we increase women's productivity, which might not be realized if they decide not to participate in the labor market.} the share of people that ever cohabited increases from 43.3\% to 47.3\%, while the number of years spent cohabiting move from 2.19 to 2.65.
 In the counterfactual there is less room from specialization in the couple when the two partner's wages are more similar and the opportunity cost of not working for women rises.
@@
 
-\textbf{Decreasing the price of home appliances.} In table \ref{table:counterfactual_exp} we report one last counterfactual experiment that explores the effects of reducing by 20\% the relative price of goods $d$, used to produce public goods $Q$.
+\textbf{Decreasing the price of home appliances.} In table \ref{table:counterfactual_exp} we report one last counterfactual experiment that explores the effects of reducing by 10\% the relative price of goods $d$, used to produce public goods $Q$.
 This change is to be interpreted as a result of the improvement in home production technologies, such as the dish washer or the washing machine, which freed up women's time.
 Previous research already showed the impact of those changes of female labor supply \citep{greenwood2005}, the decline in marriage, the rise in divorce and assortative mating  \citep{greenwood2016}.
-The counterfactual experiment shows that the share of people that ever cohabited  increases by moved from 34.8\% to 37.1\%, while the years spent cohabiting stays almost identical.
+The counterfactual experiment shows that the share of people that ever cohabited  increases by moved from 43.3\% to 44.8\%, while the years spent cohabiting move from 2.19 to 2.27.
 Similarly to a reduction in the gender wage gap, improvements in the technology of home production decrease the need for labor specialization within the household and for a commitment technology to enforce it.
 Hence, improvements in the technology of home production not only caused a decline of marriage with respect to singleness, as \cite{greenwood2016} claim, but also a change in the relative convenience of partnership contracts.
+
+\textbf{No stigma on cohabitation.} Table \ref{table:counterfactual_exp} reports the results of one last counterfactual scenario where the gains stigma towards cohabitation $\gamma$ is set to zero.
+In the counterfactual, over 80\% of people have ever cohabited and agents spend on average more than 11 years cohabiting.
+These results suggest that norms have an important role for the rise of cohabitation over time.
+Finally, note that many people continue marrying: in this scenario 44\% of people have ever married, which suggest that the economic incentives alone are able to generate a positive surplus of marriage with respect to cohabitation for certain individuals.
 
@@
 \rule{-4pt}{2.5ex}
-Baseline         &  34.8 & 2.26 &  \\[0.45ex]
-No Unilateral Divorce &  26.7  & 1.35 &  \\[0.45ex]
-$\downarrow$ Wage gap      & 36.2 & 2.45 &  \\[0.45ex]
-$\downarrow$ Price of ``durable" good $d$     & 37.1  & 2.24 &  \\[0.45ex]
+Baseline         &  43.3 & 2.19 &  \\[0.45ex]
+No Unilateral Divorce &  29.1  & 1.24 &  \\[0.45ex]
+$\downarrow$ gender productivity gap      & 47.3 & 2.65 &  \\[0.45ex]
+$\downarrow$ 10\% Price of good $d$     & 44.8  & 2.27 &  \\[0.45ex]
+No stigma on Cohabitation ($\gamma=0$)     & 82.4  & 11.40 &  \\[0.45ex]
 \hline
@@
 The Baseline scenario reports the model output with the parameters reported in the previous section.
-The scenario ``No Unilateral divorce" assumes that all the agents live under a Mutual consent regime during all their life, while in the lower gender gap scenario women wages are increased by 20\%.
-Instead, under the lower price of public good scenario the relative price between goods $d$, used to produce the public good, and private consumption $c$ is reduced by 20\%.
+The scenario ``No Unilateral divorce" assumes that all the agents live under a Mutual consent regime during all their life, while in the lower productivity gender gap scenario women's productivity is increased by 10\%, while men's productivity is decreased by 10\%.
 The share of people that ever cohabited is measured at the simulated age of 39, while years spent cohabiting are computed between ages 20 and 55.}
@@
 The possibility to switch to cohabitation does not affect much men's welfare, while for women the welfare under unilateral divorce is much lower because.
-Finally, we show that the magnitude of the overall effect of unilateral divorce on cohabitation is large: a counterfactual experiment reveals that if the law never changed, time spent into cohabitation for the birth cohorts used in our estimation would have been 1.35 years instead of 2.26, while the share of people that eve cohabited would have moved from 34.8\% to 26.7\%.
+Finally, we show that the magnitude of the overall effect of unilateral divorce on cohabitation is large: a counterfactual experiment reveals that if the law never changed, time spent into cohabitation for the birth cohorts used in our estimation would have been 1.24 years instead of 2.19, while the share of people that eve cohabited would have moved from 43.3\% to 29.1\%.
 
@@
 Note that we included year, years since marriage/cohabitation and age fixed effects.
-We estimate this model separately for formerly married and cohabiting households and we further subdivide our sample considering wealthier/poorer households and men/women.\footnote{A household is considered wealthy if its net worth before couple disruption is above the $75^{th}$ percentile of the distribution and poor otherwise.d} Figure \ref{fig:assdiv} reports the results.
+We estimate this model separately for formerly married and cohabiting households and we further subdivide our sample considering wealthier/poorer households and men/women.\footnote{A household is considered wealthy if its net worth before couple disruption is above the $75^{th}$ percentile of the distribution and poor otherwise.} Figure \ref{fig:assdiv} reports the results.
 We normalize the coefficient estimates $\beta^{Split}_j$ by adding the average of net worth at divorce $E[\text{Net worth}|t = -1]$.
-In panel \subref{sf:assdiv1} we can see a decrease in net worth for richer households: the estimates indicate the year after the divorce the household is left with significantly less than half its original net worth, even tough the large standard errors do not allow us to identify clearly the amount of net worth lost because of the divorce.
+In panel \subref{sf:assdiv1} we can see a decrease in net worth for richer households: the estimates indicate the year after the divorce the household is left with significantly less than half its original net worth, even though the large standard errors do not allow us to identify clearly the amount of net worth lost because of the divorce.
 Instead, no clear decrease in net worth can be observed for poorer household.
@@
 \centering
-\caption{Hazard of Separation}
+\caption{Hazard of Breakup}
 \label{fig:hazs}
@@
 \begin{minipage}{0.99\textwidth} % choose width suitably
-{\footnotesize \textsc{Notes.} The figures display mean and variances of simulated log wages and assets of men and women in a couple over their age.
+{\footnotesize \textsc{Notes.} The figures display means and variances of simulated log wages and assets of men and women in a couple over their age.
 We label as ``main person" the variables that are computed from agents that are simulated and followed through their whole life-cycle, while we label as ``met person" the variables constructed using the partners met by the people whose behavior is simulated for their whole life-cycle.

### 2020-10-01 welfare.tex
some modifications in intro and body (NO empirical part)

@@
     \multicolumn{4}{c}{\textit{Life-Time utilities in $t=0$}}\\[3ex]
--352.16 &-355.06 &-338.88 &-340.62 \\
+     -364.62 &-368.13 &-351.53 &-351.88 \\
     \cmidrule(l){1-4}
     \multicolumn{4}{c}{\textit{Welfare Losses with Unilateral Divorce}}\\[3ex]
-\multicolumn{2}{c}{\Chartgirls{1.0}}& \multicolumn{2}{c}{\Chartguys{0.4307177814029403}}\\[-0.15ex]
-\multicolumn{2}{c}{17531.97 \$}& \multicolumn{2}{c}{9023.81 \$}\\
-    \hline\midrule
-    \multicolumn{4}{c}{\textit{Life-Time utilities in $t=0$ when cohabitation is not an option}}\\[3ex]
--351.47 &-354.68 &-339.59 &-340.74 \\
+    \multicolumn{2}{c}{\Chartgirls{1.0}}& \multicolumn{2}{c}{\Chartguys{0.2508214676889376}}\\[-0.15ex]
+    \multicolumn{2}{c}{12933.66 \$}& \multicolumn{2}{c}{3244.04 \$}\\
+     \hline\midrule\cmidrule(l){1-4} 
+      \multicolumn{4}{c}{\textit{Life-Time utilities in $t=0$ when cohabitation is not in the choice set}}\\[3ex]
+    -362.49 &-365.86 &-353.11 &-354.13 \\
     \cmidrule(l){1-4}
-\multicolumn{4}{c}{\textit{Welfare Losses with Unilateral Divorce when cohabitation is not an option}}\\[3ex]
-\multicolumn{2}{c}{\Chartgirls{1.0}}& \multicolumn{2}{c}{\Chartguys{0.6304128902316224}}\\[-0.15ex]
-\multicolumn{2}{c}{18287.03 \$}& \multicolumn{2}{c}{11528.38 \$}\\
+    \multicolumn{4}{c}{\textit{Welfare Losses with Unilateral Divorce}}\\[3ex]
+    \multicolumn{2}{c}{\Chartgirls{1.0}}& \multicolumn{2}{c}{\Chartguys{0.7564234326824255}}\\[-0.15ex]
+    \multicolumn{2}{c}{13783.62 \$}& \multicolumn{2}{c}{10426.25 \$}\\
     \hline\hline

### 2020-10-02 draft_sub_con.tex
taking into account Pauline's feedback

@@
 First, by documenting how divorce laws influence the choice between marriage and cohabitation, we add to the existing literature that studies the effects of unilateral divorce.
-This policy change has been shown to affect the rate of divorce (\citealp{friedberg1998}, \citealp{wolfers2006}), female labor supply (\citealp{stevenson2008}, \citealp{voena2015}), savings (\citealp{voena2015}), marriage rates (\citealp{rasul2003,rasul2006}), children's well-being (\citealp{gruber2004}), family violence (\citealp{stevenson2006}), marriage-specific capital (\citealp{stevenson2007}), assortative mating (\citealp{reynoso2019}) and prostitution (\citealp{ciacci2017}), among the others.
+This policy change has been shown to affect the rate of divorce (\citealp{friedberg1998}, \citealp{wolfers2006}), female labor supply (\citealp{stevenson2008}, \citealp{voena2015}), savings (\citealp{voena2015}), marriage rates (\citealp{rasul2003,rasul2006}), children's well-being (\citealp{gruber2004}), family violence (\citealp{stevenson2006}), marriage-specific capital (\citealp{stevenson2007}), assortative mating (\citealp{reynoso2019}), the rise in serial monogamy (\citealp{de2015}),  and prostitution (\citealp{ciacci2017}), among the others.
 We complement the findings of \cite{rasul2003,rasul2006} by showing that the decrease in marriage rates after the introduction of unilateral divorce is not only driven by more people staying single, but also by more people that choose to cohabit.
@@
 Another subset of these papers studies the effect of changes in cohabitants' rights on partnership choices and cohabiting couples' behavior, highlighting the role of alimony rights  (\citealp{chiappori2017,gousse2018}), taxation \cite{leturcq2012} and division of assets at breakup (\citealp{fisher2012,gousse2018,chigavazira2019}).
-We extend this literature by showing that the introduction of unilateral divorce impacts both the choice to cohabit and cohabitation's stability, even though cohabitant's rights are not directly affected.\footnote{\cite{matouschek2008} study the effect of unilateral divorce on marriage rates using a framework where the choice between marriage and cohabitation is considered.
-Their framework does not predict changes to the propensity to cohabit.} Further, the effects on the intention to cohabit depends on property division rights, which indicates that partnership choices depend on divorce allocations.
+We extend this literature by showing that the introduction of unilateral divorce impacts both the choice to cohabit and cohabitation's stability, even though cohabitant's rights are not directly affected.
+Further, the effects on the intention to cohabit depends on property division rights, which indicates that partnership choices depend on divorce allocations.
 This evidence suggests that changes in family law should be designed considering that marriage and cohabitation are substitutes.
@@
 \end{enumerate}
+The possibility of signing prenuptial agreements gives to the couple the possibility of splitting assets differently than it is dictated by the law, but legal scholars believe that their effect is quite limited.
+In fact, these contracts could not be enforced by courts until the 1970s.
+After the introduction of the Uniform Premarital Agreements Act of 1983, it has been easier to enforce these contracts even though today prenuptial agreements are signed in a minority of marriages (5-10\%) according to \cite{rainer2007}, which might be due to social stigma or lack of information on their benefits \citep{mahar2003}.\\
 %Rights of cohabitors,literature
@@
 We begin by describing our data.
-We use the National Survey of Family and the Household (NSFH) wave I, and the National survey of Family Growth, 1988 wave.
+We use the wave I (1987-1988) of the National Survey of Family and the Household (NSFH), and the National survey of Family Growth (NSFG), 1988 wave.
 Both surveys were designed to study the causes and consequences of changes happening in families and households within the United States.
@@
 \begin{table}[!htbp]\centering
-	\caption{\\Descriptive statistics, cohabitation sample}
+	\caption{\\Descriptive statistics, relationship sample}
 	\label{table:sum_rel}
@@
 \begin{table}[!htbp]\centering
-	\caption{\\Descriptive statistics, relationship sample}
+	\caption{\\Descriptive statistics, cohabitation sample}
 	\label{table:sum_coh}
@@
 \end{equation}
-Parameter $\mu$ is the loss in productivity that affects women that are not participating in the labor market.
+where $P^s_t$ is a dummy of labor force participation.
 Men and single women are always assumed to participate in the labor market, hence $P^m_t=1$.\footnote{The assumption that men, as opposed to women, always participate in the labor market is rather common in the literature (\citealp{ciscato2019,low2018,voena2015}) and it is in line with the gender roles typically observed in the period under analysis.
-In our PSID sample only 5\% of men between 20 and 60 do not supply working hours in the market.} It can be interpreted as a reduced form way of capturing both the missed opportunity to accumulate human capital while working and the skill atrophy from interruptions \citep{adda2017}.
+In our PSID sample only 5\% of men between 20 and 60 do not supply working hours in the market.} Parameter $\mu$ is the loss in productivity that affects women that are not participating in the labor market.
+It can be interpreted as a reduced form way of capturing both the missed opportunity to accumulate human capital while working and the skill atrophy from interruptions \citep{adda2017}.
 Modeling the loss in productivity for not working is an important feature of our model as it creates an incentive to join the labor force for women that expect to divorce or breakup soon.
@@
 \end{equation}
-where $P^f_t$ is a dummy of female labor force participation.
 When a couple divorces in $t$, we assume 
@@
 where $\delta$ is the fraction of total assets $a_t$ left after divorce.
-We assume $\delta=0$ for breakup.\footnote{The assumption that divorce erodes a fraction of wealth is common to \cite{cubeddu2003}.
+We assume $\delta=1$ for breakup.\footnote{The assumption that divorce erodes a fraction of wealth is common to \cite{cubeddu2003}.
 In appendix \ref{section:eventsa} we provide evidence that divorce results in a loss of net worth for rich but not for poor households.
@@
 The productivity and the assets of the potential partner depends on the single agent's characteristics.
-Formally, the assets of the potential partner are defined as:
+Formally, the assets of the potential partner $p$ are defined as:
 \begin{equation}\label{eq:mma}

### 2020-10-27 wmar_mlogit.tex
prepare for overleaf

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: dom, ott 25, 2020 - 09:33:20
\begingroup 
\footnotesize 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable: Relative risk of cohabiting wrt to marrying}} \\
\cline{2-5} \\[-1.5ex]
 & Full Sample & Resident & Full Sample & Resident \\[-1ex]
\\[-1.4ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 UnDiv    & 1.236$^{**}$ & 1.310$^{**}$ &   & \\ 
   & (0.106) & (0.141) &   &\\

 UnDiv*NoTit &   &   & 1.250$^{**}$ & 1.325$^{**}$ \\ 
  &   &  & (0.115) & (0.153) \\ 
  UnDiv*Tit &   &   & 1.130 & 1.313 \\ 
  &   &   & (0.179) & (0.273) \\ 
  Tit &   &   & 1.074 & 1.090 \\ 
  &  &  & (0.090) & (0.115) \\ 
 \hline \\[-1.8ex] 
State Fixed effects & Yes & Yes & Yes & Yes \\ 
Duration Polynomials & Yes & Yes & Yes & Yes \\ 
Demographic Controls & Yes & Yes & Yes & Yes \\ 
Observations & 112,697 & 70,882 & 112,697 & 70,882 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular} 
\endgroup

### 2020-10-27 mpc.tex
latest

@@
  \hline \\[-1.8ex]
- Unilateral Divorce &  -0.09  &  -0.07  &  -0.12  &  -0.13  \\ 
-  & ( 0.04 ) & ( 0.04 ) & ( 0.04 ) & ( 0.11 ) \\  
+ Unilateral Divorce &  $-0.24^{***}$  &  $-0.25^{***}$  &  $-0.28^{***}$  &  $-0.28^{***}$  \\ 
+  & ( 0.06 ) & ( 0.08 ) & ( 0.09 ) & ( 0.09 ) \\  
  \hline \\[-1.8ex]
- Average Relative Risk &  -0.12  &  -0.08  &  -0.2  &  -0.14  \\ 
+ Average Relative Risk &  0.64  &  0.63  &  0.59  &  0.6  \\ 
  \hline \\[-1.8ex]
- \\[-2.2ex] & \multicolumn{4}{c}{Risk of Separation relative to Cohabitation} \\  
+ \\[-2.2ex] & \multicolumn{4}{c}{Risk of Breakup relative to Cohabitation} \\  
  \hline \\[-1.8ex]
- Unilateral Divorce &  -0.04  &  -0.09  &  -0.05  &  -0.06  \\ 
-  & ( 0.02 ) & ( 0.02 ) & ( 0.02 ) & ( 0.1 ) \\  
+ Unilateral Divorce &  $-$0.19$^{***}$  &  $-$0.16$^{***}$  &  $-$0.08  &  $-$0.24$^{*}$  \\ 
+  & ( 0.07 ) & ( 0.06 ) & ( 0.05 ) & ( 0.14 ) \\  
  \hline \\[-1.8ex]
- Average Relative Risk &  -0.06  &  -0.18  &  -0.1  &  -0.06  \\ 
+ Average Relative Risk &  0.67  &  0.71  &  0.83  &  0.62  \\ 
  \hline \\[-1.8ex]
@@
 Age Polynomial & Yes & Yes & Yes & Yes \\
-Picewise Duration & Yes & Yes & Yes & Yes \\ 
+Pice-wise Duration & Yes & Yes & Yes & Yes \\ 
 \hline

### 2020-10-27 draft_sub_con.tex
BAU try for overleaf sync

@@
 
-\title{(Changing) Marriage and Cohabitation Patterns in the US: do Divorce Laws Matter?\thanks{The authors wish to thank David de la Croix, Matthias Doepke, Fabio Mariani, Jesús Fernández-Villaverde, Alessandra Voena and the Northwestern Macro group for their useful comments.
+\title{(Changing) Marriage and Cohabitation Patterns in the US: do Divorce Laws Matter?\thanks{The authors wish to thank Edoardo Ciscato, David de la Croix, Matthias Doepke, Philipp Kircher, Fabio Mariani, Jesús Fernández-Villaverde, Luca Pensieroso, Alessandra Voena, as well as all the participants at seminars that took place in Northwestern University, UCLouvain, KU Leuven and the University of Michigan.
 Computational resources were provided by the supercomputing facilities of the Université catholique de Louvain (CISM/UCL) and Northwestern University.
@@
 \begin{abstract}
-This paper analyzes the role of unilateral divorce for the rise of unmarried cohabitation.
+BAU BAU This paper analyzes the role of unilateral divorce for the rise of unmarried cohabitation.
 Exploiting the staggered introduction of unilateral divorce across the US states, we show that after the reform singles become more likely to cohabit than to marry, and newly formed cohabitations last longer.
@@
 The imperfect transferability feature is important: according to \cite{becker1977}, divorce laws should not affect separation decisions \textit{``if all compensations between spouses were feasible and costless"}.
-\cite{chiappori2015} and \cite{fella2004} discuss the assumptions of the Becker-Coase theorem more.
+The assumptions underlying the Becker-Coase theorem are discussed by \cite{chiappori2015} and \cite{fella2004}.
 
@@
 \section{Mechanisms}
-The aim of this section is to better understand the mechanisms underlying the introduction of unilateral divorce and the subsequent rise in cohabitation.
+The aim of this section is 1) to better understand the quantitative relevance of the mechanisms underlying the introduction of unilateral divorce and the subsequent rise of cohabitation and 2) quantify the gains of marriage with respect to cohabitation.
 
@@
 
+\textbf{Risk-Sharing and consumption insurance.}
+The veto over divorce in the mutual consent regime and the higher cost of divorce with respect to breakup are commitment technologies that enforce cooperation within marriage.
+What is the quantitative relevance of these mechanisms on the ability of married and cohabiting couples to share risk?
+To answer this question we study how income shocks affect the changes in consumption over time for men in a couple.\footnote{Results for women in a couple are displayed in table \ref{table:riskshf}.
+We chose to show the results for men in this section since changes in their productivity always translate into changes of disposable income.
+This does not happen for women who do not participate in the labor market: for this reason results in table \ref{table:riskshf} are largely driven by the different degree of female labor force participation under different divorce regimes and partnership types.} First, we obtain paths of consumption and labor earnings of men who are in their first relationship by simulating their choices under different divorce regimes.\footnote{First relationships correspond to the periods in which an agent spend time in a couple with his or her first partner without changing partnership type.
+This means that the first relationship of a men than first cohabited and then married his first partner is a cohabitation spell that stops when the couples gets married.
+We restrict our attention on first relationships only because this allow us to perform an exercise where we impose marriage to a couple that decided to cohabit.
+This exorcise allows to compare marriage and cohabitation controlling for selection.} Then, for each of these samples we estimate the below equation
+\[\Delta \log c_{it}=\alpha+\mu \Delta \log(w_{it})+\nu_{t}+\epsilon_{it},\]
+where $c_{it}$ and $w_{it}$ are the consumption and the labor earnings of men $i$ at age $t$.
+$\nu_{t}$ are age fixed effects.
+Coefficient $\mu$ is informative about how much of the changes in income translate into changes in consumption.
+Consequently, a low value of $\mu$ corresponds to a high degree of consumption insurance.
+The results displayed in table \ref{fig:divcons} provide important pieces of information about partnership types and consumption insurance.
+First, coefficient $\mu$ is the largest for cohabitation and the smallest for marriage under mutual consent divorce as reported in the first row.\footnote{We only consider individuals who spend their whole life-cycle under the same divorce regime.} This means that consumption insurance is the most effective within marriage with mutual consent divorce and the least effective within cohabitation.
+Does this happen because of a selection effect or because partnership rules directly affect the ability to share risk?
+Rows 2 and 3 of table \ref{fig:divcons} suggest that selection matters: marriages that were not preceded by cohabitation display a stronger degree of consumption insurance than those that were preceded by cohabitation.
+The reason is that the initial match quality of couples that married directly is higher compared to those who first cohabited.
+The fact that match quality is higher  implies that participation constraints bind more rarely, allowing for a smoother consumption path.
+Row 4 of table \ref{fig:divcons} shows that if we ``force" to marry men that had chosen to cohabit, we obtain that the amount of consumption insurance lies in between that of marriage and cohabitation.
+Since this experiment controls for selection, we conclude that partnership rules have a direct effect on couples' ability to share risk.
+The results relative to consumption insurance are partnership types are driven by the frequency at which Pareto weights are renegotiated.
+Consistently with these results, figure \ref{fig:thch} shows that the share of periods in which Pareto weights are renegotiated is higher for cohabitation than marriage, and that only some of this difference can be explained by selection.
+This suggest that consumption insurance is tightly link with the frequency at which the couples renegotiates the way resources are shared.\\
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%Table of risk sharing
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begingroup
+\renewcommand{\arraystretch}{1.3}
+\begin{table}[h]\centering
+	\caption{\\Partnership type and consumption insurance against income shocks}
+	\label{table:risksh}
+	\begin{threeparttable}[t]\centering
+		\begin{tabular}{@{\extracolsep{15pt}}lccc} 
+			\hline 
+			\hline 
+			& \multicolumn{3}{c}{Married and Cohabiting Men} \\
+			\cline{2-4} 
+			& \multicolumn{2}{c}{Married} & Cohabiting  \\ 
+			\cline{2-3} \cline{4-4} 
+			& M.C. & U.D. &  \\ 
+			\hline 
+			Baseline & 0.450 & 0.484 &  0.498 \\ 
+			Only marriages preceded by cohabitation  & 0.454 & 0.486 & -  \\
+			Only marriages not preceded by cohabitation  & 0.449 & 0.483 & -  \\
+			Marriages with cohabitation selection & 0.468 & 0.496 & -  \\
+			\hline \\[-1.8ex] 
+		\end{tabular}
+	    \vspace{-0.2cm} 
+		\begin{tablenotes}[flushleft]
+			\footnotesize{\item \textsc{Notes}: the table reports the estimates of coefficients $\mu$ obtained from regression
+			\[\Delta \log c_{it}=\alpha+\mu \Delta \log(w_{it})+\nu_{t}+\epsilon_{it}.\]
+		    The sample includes the whole duration of the first relationship of simulated men $i$.
+The last row is run on a sample of men who decided to cohabit but we imposed them to marry instead.
+This allow us to analyze the insurance within marriage controlling for selection into a relationship.
+	}
+		\end{tablenotes}
+	\end{threeparttable}
+\end{table}
+\FloatBarrier
+\endgroup
+\textbf{Consumption smoothing upon divorce/breakup.} Is there a link between partnership types and consumption smoothing upon divorce/breakup?
+To answer this question we analyze the evolution of log consumption around divorce/breakup using a standard event study on the simulated sample.
+Note that, after the relationship breakdown, we report the log consumption of the household of the partner that is simulated for her/his whole life-cycle.
+Specifically, we estimate the following regression model
+\begin{equation}\label{eq:ev_studa2}
+\log(c)_{i,a,t}=\sum_{j=-3}^{3}\beta^{Split}_j\cdot\mathcal{I}(t=j)+\alpha_{0}+\alpha_{a}+\epsilon_{i,a,t},
+\end{equation}
+where $a$ is age of the person observed after the couple chase to exist, $t$ is the year relative to to breakup/divorce ($t=-1$ is omitted) and $i$ is the household.
+Note that we included age fixed effects.
+We estimate this model separately for formerly married and cohabiting households under different divorce regimes, following either men or women after the divorce/breakup.
+Figure \ref{fig:divcons} report the results and shows two main facts.
+First, consumption drop more after divorce than breakup because the former is costly in terms of assets.
+Second, women lose more because they are less productive than men, especially if they devoted their time to produce the home good while they were in a couple.
 \section{Welfare}
@@
 \end{equation}
-where $a$ is age of the person observed after the couple chase to exist, $t$ if the year relative to switching to unilateral divorce ($t=-1$ is omitted), and $i$ is the household, $y$ is the year and $ma$ is the number of years since the start of the marriage/cohabitation.
+where $a$ is age of the person observed after the couple chase to exist, $t$ is the year relative to divorce/breakup ($t=-1$ is omitted), and $i$ is the household, $y$ is the year and $ma$ is the number of years since the start of the marriage/cohabitation.
 Note that we included year, years since marriage/cohabitation and age fixed effects.
@@
 \FloatBarrier
-\subsubsection*{Relationship Choice - Logit}
+
+\subsubsection*{Relationship Choice - California left out of sample}
 
@@
 \begin{table}[H]\centering
-	\caption{\\Logitstic regression. Observation: first and second relationships}
-	\label{table:wmar_logit}
+	\caption{\\OLS regression. Observation: first and second relationships. California dropped from initial sample}
+	\label{table:wmar_c}
 	\begin{threeparttable}[t]\centering
-	\input{wmar_logit.tex}
+		\input{wmar_c.tex}
 		\begin{tablenotes}[flushleft]
@@
 
-\newpage
+\subsubsection*{Relationship Choice - Heterogeneity by Property regime and California left out of sample}
+
+%RELATIONSHIP CHOICE
+\begin{table}[H]\centering
+	\caption{\\OLS regression. Observation: first and second relationships. California dropped from initial sample}
+	\label{table:wmarc_c}
+	\begin{threeparttable}[t]\centering
+		\input{wmarc_c.tex}
+		\begin{tablenotes}[flushleft]
+			\footnotesize{\item \textsc{Notes}: standard errors are clustered at the state level.
+				Coefficients that are significantly different from zero are denoted by the following system: *10\%, **5\%  and ***1\%.}
+		\end{tablenotes}
+	\end{threeparttable}
+\end{table}
+\FloatBarrier
+
+\subsubsection*{Relationship Choice - Multinomial Logit}
+The
+\begin{table}[H]\centering
+	\caption{\\Multinomial Logit. Observation: person month, the choices are: staying single, marry or cohabit}
+	\label{table:wmar_mlogit}
+	\begin{threeparttable}[t]\centering
+		\input{wmar_mlogit.tex}
+		\begin{tablenotes}[flushleft]
+			\footnotesize{\item \textsc{Notes}: standard errors are clustered at the state level.
+The numbers displayed in the table are the $exp$ of the coefficient of the multinomial logit and they indicate the relative risk of cohabiting with respect to marrying.
+When these number are larger than $1$ the regressor of interest is associated with an relative increase in the risk of cohabiting.
+				Relative risks that are significantly different from zero are denoted by the following system: *10\%, **5\%  and ***1\%.}
+		\end{tablenotes}
+	\end{threeparttable}
+\end{table}
+\FloatBarrier
+\subsubsection*{Relationship Choice - Event Study}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Symmetry in income and assets
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[ht]
+	\begin{center}
+		\caption{\\Event studies on share of couples choosing marriage instead of cohabitation, around the introduction of unilateral divorce}
+		\label{fig:estud}
+
+		\begin{subfigure}{.49\textwidth}
+			\centering
+			% include first image
+			\caption{Full sample}
+			\label{fig:ev1}
+			\scalebox{0.5}{\input{event_1.pgf} } 
+		\end{subfigure}
+		\begin{subfigure}{.49\textwidth}
+			\centering
+			% include second image
+			\caption{Resident}
+			\label{fig:ev2}
+			\scalebox{0.5}{\input{event_2.pgf} } 
+		\end{subfigure}
+	\end{center}
+
+	\hspace{20em}
+
+	\begin{center}
+		\begin{subfigure}{.49\textwidth}
+			\centering
+			% include second image
+			\caption{NSFH}
+			\label{fig:ev3}
+			\scalebox{0.5}{\input{event_3.pgf} } 
+		\end{subfigure}
+		\begin{subfigure}{.49\textwidth}
+			\centering
+			% include second image
+			\caption{NSFG}
+			\label{fig:ev4}
+			\scalebox{0.5}{\input{event_4.pgf} } 
+		\end{subfigure}
+	\end{center}
+
+	\begin{minipage}{0.99\textwidth} % choose width suitably
+		{\footnotesize \textsc{Notes.}. \par}
+	\end{minipage}
+\end{figure}
+\FloatBarrier
+
+\subsubsection*{Relationship Choice and Children}
+Is there a shift towards cohabitation for both childless couples and couples with children?
+Using the NSFH sample, in table \ref{table:wmarc_chil} below we shows that unilateral divorce is associated with a shift towards cohabitation both for couples whose respondent has some children, is childless or is childless and does not want to have children.
+The shift towards cohabitation is lower in absolute value for couples whose respondent has children.
+This can be due to the fact that marriage remains the best partnership for enhancing cooperation, one desirable feature for couples with children since they require large investments in terms of time and money.
+This heterogeneity will be captured by our model: couples with a high relationship quality will be less sensible to the changes in the law and are also more likely to produce large quantities of the public good, which also represents children.
+
+%RELATIONSHIP CHOICE
+\begin{table}[H]\centering
+	\caption{\\OLS regression. Observation: first and second relationships.}
+	\label{table:wmarc_chil}
+	\begin{threeparttable}[t]\centering
+		\input{wmar_chil.tex}
+		\begin{tablenotes}[flushleft]
+			\footnotesize{\item \textsc{Notes}: standard errors are clustered at the state level.
+				Coefficients that are significantly different from zero are denoted by the following system: *10\%, **5\%  and ***1\%.}
+		\end{tablenotes}
+	\end{threeparttable}
+\end{table}
+\FloatBarrier
+
+%\newpage
 
@@
 \end{figure}
-
-\begin{figure}[h!]
-\centering
-\caption{\\Distribution of women Pareto weight $\theta$---marriage and cohabitation}
-\label{fig:thetadist}
-\hspace*{-1.1cm} 
-\resizebox{0.8\textwidth}{!}{\input{thtdist.pgf}}
-\begin{minipage}{0.99\textwidth} % choose width suitably
-
-\hspace{30em}
-
-{\footnotesize \textsc{Notes.} This figure depicts the distribution women Pareto weight for married and cohabiting couples.
-The thick solid lines represent the distribution of this variable in the period the couple decides to get together, while the lighter areas depict the distribution of $\theta$ considering every relationship duration.\par}
-\end{minipage}
-\end{figure}
 \FloatBarrier
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Symmetry in income and assets
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[ht]
+	\caption{\\ Event studies of log consumption around divorce--simulated data}
+	\label{fig:divcons}
+
+	\begin{subfigure}{.49\textwidth}
+		\centering
+		% include second image
+		\caption{Log consumption---unilateral divorce regime}
+		\label{sf:cdivbil}
+		\scalebox{0.5}{\input{cdivbil.pgf} } 
+	\end{subfigure}
+	\begin{subfigure}{.49\textwidth}
+		\centering
+		% include first image
+		\caption{Log consumption--mutual consent regime}
+		\label{sf:cdivuni}
+		\scalebox{0.5}{\input{cdivuni.pgf} } 
+	\end{subfigure}
+
+	\hspace{20em}
+
+	\begin{minipage}{0.99\textwidth} % choose width suitably
+
+		\hspace{50em}
+
+		{\footnotesize \textsc{Notes.} The figures display the evolution of simulated consumption around divorce or breakup.
+The displayed patterns are normalized coefficients from event studies around divorce/breakup.)\par}
+	\end{minipage}
+\end{figure}
+\FloatBarrier
+
+\begin{figure}[h!]
+	\centering
+	\caption{\\$\%$ of periods $t$ for which $\theta_t\neq \theta_{t+1}$}
+	\vspace*{-0.5cm} 
+	\hspace*{-1.3cm} 
+	\label{fig:thch}
+	\resizebox{0.8\textwidth}{!}{\input{bartht.pgf}}
+		\hspace{20em}	
+	\begin{minipage}{0.99\textwidth} % choose width suitably
+		{\footnotesize \textsc{Notes.} The figures display the share of consecutive periods where the bargaining power in the couple changes.
+The abbreviation M.C.
+means Mutual Consent regime, the abbreviation U.D.
+stands for Unilateral Divorce regime.
+The values are computed using the first simulated partnership of individuals who spent their life under the same divorce regime.
+The asterisk $*$ means that these marriages are obtained by imposing marriage (under unilateral divorce regime) as a partnership to couples that had decided to cohabit.\par}
+	\end{minipage}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%Table of risk sharing
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begingroup
+\renewcommand{\arraystretch}{1.3}
+\begin{table}[h]\centering
+	\caption{\\Partnership type and consumption insurance against income shocks}
+	\label{table:riskshf}
+	\begin{threeparttable}[t]\centering
+		\begin{tabular}{@{\extracolsep{15pt}}lccc} 
+			\hline 
+			\hline 
+			& \multicolumn{3}{c}{Married and Cohabiting Women} \\
+			\cline{2-4} 
+			& \multicolumn{2}{c}{Married} & Cohabiting  \\ 
+			\cline{2-3} \cline{4-4} 
+			& M.C. & U.D. &  \\ 
+			\hline 
+			Baseline & 0.201 & 0.164 &  0.329 \\ 
+			Only marriages preceded by cohabitation  & 0.097 & 0.183 & -  \\
+			Only marriages not preceded by cohabitation  & 0.210 & 0.160 & -  \\
+			Marriages with cohabitation selection & 0.329 & 0.331 & -  \\
+			\hline \\[-1.8ex] 
+		\end{tabular}
+		\vspace{-0.2cm} 
+		\begin{tablenotes}[flushleft]
+			\footnotesize{\item \textsc{Notes}: the table reports the estimates of coefficients $\mu$ obtained from regression
+				\[\Delta \log c_{it}=\alpha+\mu \Delta \log(w_{it})+\nu_{t}+\epsilon_{it}.\]
+				The sample includes the whole duration of the first relationship of simulated women $i$.
+The last row is run on a sample of men who decided to cohabit but we imposed them to marry instead.
+This allow us to analyze the insurance within marriage controlling for selection into a relationship.
+			}
+		\end{tablenotes}
+	\end{threeparttable}
+\end{table}
+\FloatBarrier
+\endgroup
+
+\begin{figure}[ht]
+	\begin{center}
+		\caption{\\ Newly formed relationships (either married or cohabiting) and unilateral divorce (U.D.)}
+		\label{fig:events_raw}
+
+		\begin{subfigure}{.49\textwidth}
+			\centering
+			% include second image
+			\caption{{\color{blue}\% new couples choosing marriage instead of cohabitation} and {\color{red}\% relationships born under U.D.} }
+
+			\label{fig:years_raw}
+			\scalebox{0.5}{\input{years_raw.pgf} } 
+		\end{subfigure}
+		\begin{subfigure}{.49\textwidth}
+			\centering
+			% include first image
+			\caption{\% new couples choosing marriage instead of cohabitation around U.D.}
+			\label{fig:event_raw}
+			\scalebox{0.5}{\input{event_raw.pgf} } 
+		\end{subfigure}
+
+	\end{center}
+
+	\begin{minipage}{0.99\textwidth} % choose width suitably
+		{\footnotesize \textsc{Notes.} The left panel shows in blue the evolution over time of the \% of relationships born in year $t$ such that the couple chose marriage as opposed to informal cohabitation.
+The red line represents the \% of relationships born in $t$ in a state that already adopted unilateral divorce by year $t$.
+The right panel shows the \% of relationships where the couple chose to marry instead of cohabiting in an year whose distance in time from the introduction unilateral divorce in that state is equal to $d$ years.
+The red dotted lines are obtained running linear regressions on a dummy for marriage, using the event time as the only regressor.
+All the variables presented in this figure are constructed with a sample of first and second relationships (which can be either marriage or cohabitation) from the 1988 wave of the NSFH: we provide further details about the survey and the sample construction in section 3.
+All the variables depicted in the two figures are constructed using sample weights.
+\par}
+	\end{minipage}
+\end{figure}
+\FloatBarrier
 \end{document}

### 2020-11-05 draft_sub_con.tex
BAU no good
before Didi final check

@@
 \usepackage[margin=2cm]{geometry}
-%\usepackage[top=1.5in, bottom=1.5in, left=1.5in, right=1.5in]{geometry}
 \usepackage{blindtext} % to change the page dimensions
-%\geometry{a4paper} % or letterpaper (US) or a5paper or....
-%\geometry{margin=1.5in} % for example, change the margins to 2 inches all round
-% \geometry{landscape} % set up the page for landscape
-%   read geometry.pdf for detailed page layout information
+
+%Matthias style below
+\usepackage{palatino,amssymb,amsfonts,amsmath,amsthm,latexsym}
+\usepackage{graphicx,xcolor,booktabs,array,rotating}
+\usepackage[T1]{fontenc}
+\usepackage[detect-all]{siunitx}
+\usepackage{epstopdf}
+\usepackage{rotating}
+\usepackage{bm,subcaption}
 
@@
 \restylefloat{table}
-
-%%% PAGE DIMENSIONS
-%\usepackage[margin=2.5 cm]{geometry}
-%\usepackage{blindtext} % to change the page dimensions
-%\geometry{a4paper} % or letterpaper (US) or a5paper or....
-%\geometry{margin=1.5cm} % for example, change the margins to 2 inches all round
-% \geometry{landscape} % set up the page for landscape
-%   read geometry.pdf for detailed page layout information
 
@@
 \usepackage{pdfpages}
-\linespread{1.5}
+\linespread{1.39}%\linespread{1.37}
 \setlength{\footnotemargin}{4mm}
@@
 \newcommand*\Chart[1]{#1~\rlap{\textcolor{blue!20}{\rule{#1\MAX}{2ex}}}}
-%\newcommand*\Chartguys[1]{\rlap{\textcolor{blue!30}{\rule{6ex}{\MAX}}}{\textcolor{white!30}{\rule{6ex}{#1\MAX}}}}
-%\newcommand*\Chartgirls[1]{\rlap{\textcolor{red!30}{\rule{6ex}{\MAX}}}{\textcolor{white!30}{\rule{6ex}{#1\MAX}}}}
 \newcommand*\Chartguys[1]{{\textcolor{blue!30}{\rule{6ex}{#1\MAX}}}}
@@
 \setcounter{MaxMatrixCols}{10}
-%TCIDATA{OutputFilter=LATEX.DLL}
-%TCIDATA{Version=5.50.0.2960}
-%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
-%TCIDATA{BibliographyScheme=BibTeX}
-%TCIDATA{LastRevised=Monday, August 27, 2018 20:06:51}
-%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
-%TCIDATA{Language=American English}
-
-%\restylefloat{table}
-%\oddsidemargin  +0.18in
-%\evensidemargin +0.18in
-%\topmargin 40pt \textheight 8.1in \textwidth 6.5in
-%\linespread{1.5}\parskip .05in
 
@@
 \usepgflibrary[arrows] % ConTEXt and pure pgf
-\usetikzlibrary{arrows} % LATEX and plain TEX when using Tik Z
+\usetikzlibrary{arrows} % LATEX and plain TEX when using
+\usetikzlibrary{arrows,decorations.markings}
 \usetikzlibrary[arrows] % ConTEXt when using Tik Z
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Space between paragraphs
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\allowdisplaybreaks
+%\setlength{\parindent}{0em}
+\setlength{\parskip}{0.55ex plus0.5ex minus0.5ex}
+
+%%%%%%%%%%%%%%%%%%%5
+%Nicer start of paragraph
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+\makeatletter
+
+\renewcommand\section{\@startsection{section}{1}{0cm}{-1.5ex \@plus
+-.2ex \@minus -.2ex}%
+{.5ex \@plus.2ex} {\normalfont\large\bfseries}}
+
+\renewcommand\subsection{\@startsection{subsection}{1}{0cm}{-1.5ex \@plus
+-.2ex \@minus -.2ex}%
+{.5ex \@plus.2ex} {\normalfont\bfseries}}
+
+\renewcommand\subsubsection{\@startsection{subsubsection}{1}{0cm}{-1.5ex \@plus
+-.2ex \@minus -.2ex}%
+{.5ex \@plus.2ex} {\normalfont}}
+
+\makeatother
+
+%\makeatother
 %%% The "real" document content comes below...
@@
 %\parskip3mm\parindent0cm
-
-\title{(Changing) Marriage and Cohabitation Patterns in the US: do Divorce Laws Matter?\thanks{The authors wish to thank Edoardo Ciscato, David de la Croix, Matthias Doepke, Philipp Kircher, Fabio Mariani, Jesús Fernández-Villaverde, Luca Pensieroso, Alessandra Voena, as well as all the participants at seminars that took place in Northwestern University, UCLouvain, KU Leuven and the University of Michigan.
+\begin{document}
+\begin{onehalfspacing}
+\begin{titlepage}
+\title{\bf(Changing) Marriage and Cohabitation Patterns in the US: do Divorce Laws Matter?\thanks{The authors wish to thank Edoardo Ciscato, David de la Croix, Matthias Doepke, Jesús Fernández-Villaverde, Philipp Kircher, Fabio Mariani, Pauline Morault, Luca Pensieroso, Alessandra Voena, as well as all the participants at seminars that took place in Northwestern University, UCLouvain, KU Leuven and the University of Michigan.
 Computational resources were provided by the supercomputing facilities of the Université catholique de Louvain (CISM/UCL) and Northwestern University.
@@
 
-\begin{document}
 	 	\tikzstyle{block} = [draw, fill=white, rectangle, 
@@
 	% Bibliography style, important for biblatex functioning	
-	\bibliographystyle{apa}
+	\bibliographystyle{chicago}
 
@@
 
-\vspace{-2cm}
+\vspace{-2.3cm}
 \begin{center}\large	
@@
 
-%\begin{abstract}
-%	Marriage differs from informal cohabitation for its higher cost of breaking up.
-Moving from a mutual to a unilateral divorce regime drastically increases the risk of dissolution.
-We explore how this change affects partnership choice and the relative power within the couple.
-Exploiting the staggered introduction of unilateral divorce across the US states, we show that after the reform newly formed relationships are significantly more likely to be cohabitations instead of marriages, and that cohabitation spells last longer.
-To understand the drivers of these changes, we build and estimate a structural life cycle model with partnership choice, female labor supply and savings decisions, where the gains of marriage with respect to cohabitation come from a better risk sharing and specialization within the household, enforced through a costly divorce.
-In the model, the reform increases the risk of divorce, making cohabitation preferred by couples that would have had the highest risk of divorce under the mutual consent regime.
-Since the match quality of cohabitations is on average lower than that of marriages, the reform increases their length: we estimate that time spent cohabiting would have been four times lower if the law had never changed.
-In states where assets upon divorce are split equally, men would lose most of their wealth upon divorce: at equilibrium, many women accept to cohabit in exchange for a higher bargaining power.
-%\end{abstract}
-
-%\begin{abstract}
-%	This paper analyzes the role of unilateral divorce for the rise in cohabitation.
-Exploiting the staggered introduction of unilateral divorce across the US states, we show that after the reform singles become more likely to cohabit than to marry, and that newly formed cohabitation spells last longer.
-We then provide a theoretical rationale for these facts, building a life-cycle model with partnership choice, female labor supply and saving decisions.
-A structural estimation of the model suggests that the decline in marriage is due to an increased risk of divorce, while new cohabitation spells last longer for a selection effect.
-A counterfactual experiment reveals that time spent cohabiting would have been four times lower if divorce law had never changed.
-%\end{abstract}
-
-%\begin{abstract}
-%	This paper analyzes the role of unilateral divorce for the rise of cohabitation.
-Exploiting the staggered introduction of unilateral divorce across the US states, we show that after the reform singles become more likely to cohabit than to marry, and that newly formed cohabitation spells last longer.
-We then provide a theoretical rationale for these facts, building a life-cycle model with partnership choice, female labor supply and saving decisions.
-A structural estimation of the model suggests that unilateral divorce reduces the gains from marriage, making cohabitation preferred to couples that would have had the highest risk of divorce.
-Since married couples are on average better matched, the reform increases the length of newly formed cohabitations because of a selection effect.
-A counterfactual experiment reveals that time spent cohabiting would have been four times lower if divorce law had never changed.
-%\end{abstract}
-
 \begin{abstract}
-BAU BAU This paper analyzes the role of unilateral divorce for the rise of unmarried cohabitation.
-Exploiting the staggered introduction of unilateral divorce across the US states, we show that after the reform singles become more likely to cohabit than to marry, and newly formed cohabitations last longer.
-We then provide a theoretical rationale for these facts, building a life-cycle model with partnership choice, female labor force participation, and saving decisions.
-A structural estimation of the model suggests that unilateral divorce decreases couples’ stability, making cohabitation preferred to couples that would have been at high risk of divorce if they marry.
-As cohabiting couples formed after the reform are better matched, the average length of cohabitations increases.
-A counterfactual experiment reveals that the time spent cohabiting would have been almost halved if the divorce laws had never changed.
+What is the role of unilateral divorce in the rise of unmarried cohabitation?
+Exploiting the staggered introduction of unilateral divorce across the US states, we show that after the reform singles become more likely to cohabit than to marry, and that newly formed cohabitations last longer.
+To understand the mechanisms driving these outcomes, we build a life-cycle model with partnership choice, endogenous divorce/breakup, female labor force participation, and saving decisions.
+A structural estimation that matches the empirical findings suggests that unilateral divorce decreases marriage gains stemming from cooperation and risk-sharing.
+This makes cohabitation preferred to couples that would have likely faced a divorce, which is more expensive than breaking up.
+As cohabiting couples formed after the reform are better matched, the average length of cohabitations increases by 27\%.
+Consistent with data, the rise of cohabitation is larger in states that impose an equal division of property as men, fearing to lose most of their assets upon divorce, convince women to cohabit in exchange for more household resources.
+A counterfactual experiment reveals that the time spent cohabiting would have been halved if the divorce laws had never changed.
 \end{abstract}
-
 %\clearpage
-%\noindent \medskip{}
-\clearpage
+
+\thispagestyle{empty}
+\end{titlepage}
+
+\end{onehalfspacing}
 \section{Introduction}
-
-%Informal cohabitation is on the rise: the share of women that ever cohabited in the United States moved from 33\% in 1987 to 60\% in 2010 \citep{manning2013}.
-Since cohabiting couples display different outcomes than married ones, this rise definitely contributes to the overall changes in the structure and behavior of the American family.
-For example, \cite{bumpass2000} claim that the higher instability of cohabitation is responsible for the rise in the number of single mothers, which is linked to worse children's outcomes \citep{chetty2018}.
-The first step to find out why cohabitation is surging and why its outcomes differs from marriage is to better understand partnership choice, selection and cohabiting couples behavior.
-
-%Moreover, \cite{poortman2012} point out that couple specific investments of those who cohabit are lower than those who are married.
-%Since disadvantaged social classes are those who are more likely to cohabit instead of marrying, partnership choice can be an engine of economic inequality
-
 Unmarried cohabitation is on the rise: the share of women that ever cohabited in the United States moved from 33\% in 1987 to 60\% in 2010 \citep{manning2013}.
 This increase contributed to the overall changes in the structure and behavior of the American family.
-The higher instability of cohabitation plausibly contributes to the rise in the number of single mothers (\cite{bumpass2000}), which is associated with poor outcomes for children \citep{chetty2018,mclanahan2013}.
-Cohabiting people spend less money on relationship-specific investments % maybe any examples here?
+The higher instability of cohabitation contributes to the rise in the number of single mothers \citep{bumpass2000}, which is associated with poor outcomes for children \citep{chetty2018,mclanahan2013}.
+Cohabiting people are less likely to engage in relationship-specific investments, such as intra-household specialization or having joint accounts.
 \citep{poortman2012}.
 Finally, their children's well-being is worse even after controlling for parental resources \citep{brown2004}.
-However, it is not clear to what extent cohabitants' outcomes are due to selection % elaborate what kind of?
+However, it is not clear to what extent cohabitants' outcomes are due to selection
 versus the direct effect of the form of partnership on the couple's behavior.
-Quantifying these two mechanisms' relative importance can be done only by understanding the rationale for the partnerships choices.
+Quantifying these two mechanisms' relative importance can be done only by understanding the rationale for the partnership choices.
 Why do people cohabit instead of marrying?
-Why did cohabitation become more common over time?
+Why is cohabitation on the rise?
 
 Our paper addresses these questions by focusing on a major US policy change that took place mostly during the 1970s.
-During this period, most of the states have made divorce considerably easier by switching from the mutual consent divorce regime, requiring both spouses to agree to divorce, towards unilateral divorce, in which one spouse's decision was enough to initiate the procedure.
+During this period, most of the states have made divorce easier by switching from the mutual consent divorce regime, requiring both spouses to agree to divorce, towards unilateral divorce, in which one spouse's decision was enough to initiate the procedure.
 The paper explores what role does unilateral divorce have for the rise of cohabitation.
 Since marriage and cohabitation can be viewed as contracts whose attractiveness depends on their termination rights and costs, the switch from mutual consent to unilateral divorce represents a unique opportunity to learn about partnership choices.
-
-We answer the questions with four contributions.
-First, we offer a few pieces of empirical evidence.
-We show that under the unilateral divorce people prefer cohabitation to marriage more often.
-We also argue that the newly formed cohabitations last longer.
-Second, we propose a theory of partnership choice and endogenous breakup/divorce.
-In particular, in our model the policy makes cohabitation the preferred option to couples that would have experienced the highest risk of a costly divorce.
-Therefore, the average match quality of cohabiting couples increases, which causes cohabitation spells to last longer.
-% A theory professor asked me once if something I claim to be a result is generic or is it specific to my choice of parameters.
-This may be a useless thing, but maybe the wording can slightly be adjusted top.
-Third, we structurally estimate our model to match the empirical findings about the divorce regimes' transition.
-Fourth, we perform several counterfactual experiments to understand the overall role of unilateral divorce on the rise of cohabitation.
+Understanding these choices is relevant for policy design: for example, protecting the weaker partner by increasing her/his rights within marriage can backfire if this cause the couple to choose a less protective partnership as cohabitation.
+
+We answer the question with four contributions. First, we show that after
+the reform singles become more likely to cohabit than to marry, and newly formed cohabitations last longer. 
+Second, we propose a theory of partnership choice and endogenous breakup/divorce to understand the mechanisms underlying these facts.
+Third, we quantify the importance of each mechanism by structurally estimating our model to match the empirical findings of the divorce regimes' transition.
+Fourth, we perform several counterfactual experiments to understand the role of unilateral divorce on the rise of cohabitation and on changes in the pool of cohabiting couples.
 Thus, this paper consists of four parts, one for each contribution, which we now describe in more detail.
-
-%Since the seminal work of \cite{becker1981}, economists studied the incentives behind the decision to marry, among which the sharing of public goods, the division of labor to exploit comparative advantages (\citealp{chiappori1997}), and risk sharing (\citealp{voena2015} and \citealp{rigas2015}).
-These reasons tell us why couples live together, while they are actually silent about the choice between marriage and informal cohabitation.
-Those two partnerships can be viewed as contracts subject to different rules, which in particular regulate costs and rights to end these agreements.
-While the cost of divorce is higher than the one of just breaking up,\footnote{Henceforth we will refer to the separation from cohabitation as breakup to avoid confusion with the legal separation.}, the introduction of unilateral divorce during the 1970s shifted the property rights from the spouse who wished to stay married to the one who wished to divorce.
-Hence, the switch from mutual consent to unilateral divorce represents a unique opportunity to learn how people choose between marriage and cohabitation.
-%In particular, unilateral divorce might have eroded the gains from marriage, both increasing the likelihood of a costly divorce and hampering couples' ability to commit, thus making some couples willing to cohabit instead of marrying.
-In addition, shifting to a less committed relationship hampers couples' ability to specialize and it might affect the relative bargaining  power of partners.
-
-%In this paper, we study the role of unilateral divorce on the rise of cohabitation.
-Our main contribution is to show that the rate of cohabitation surged after the changes in the US law because the increased risk of divorce made marriage less attractive.
-In particular, cohabitation becomes the preferred choice to couples that would have experienced the highest risk of divorce.
-As a consequence, the average match quality of cohabiting couples increases, which cause cohabitation spells to last longer.
-Interestingly, men are those who wish to cohabit the most after the reform because they would lose a relatively higher share of their wealth upon divorce.
-This increases the bargaining power of women entering cohabitation.
 
@@
 We use data from the National Survey of Family and the Household (NSFH) and from the National Survey of Family Growth (NSFG) to study the choice between marrying and cohabiting.
-Then, exploiting the exogenous variation coming from the staggered introduction of unilateral divorce over time across the US states, we estimate that couples formed after the policy change are 5-7\% more likely to choose cohabitation over marriage than in the pre-reform period.
-% Give some baseline numbers here?
+Then, exploiting the exogenous variation coming from the staggered introduction of unilateral divorce over time across the US states, we estimate that couples formed after the policy change are 7-8\% less likely to choose marriage over cohabitation than in the pre-reform period.
+Among the couples formed in the year the law changed, 30\% chose cohabitation.
 Interestingly, the effect's size depends on how property is divided upon divorce, being strongest in states where each spouse gets half of the wealth and where the judge decides the assets' shares.
-This suggests that divorce allocations affect partnership choices.
-%This suggests that the result cannot be entirely driven by divorce being a less binding commitment technology,\footnote{This mechanism is highlighted by \cite{lafortune2020}, where the equal division of assets within marriage makes it possible to efficiently invest in children even after the rise of unilateral divorce.} since the egalitarian property division rule can act as a substitute for the mutual consent regime.
-Moreover, we analyze how unilateral divorce affected cohabitation spells duration: our estimates from a multinomial probit show that cohabitations formed after the reform last longer because people both marry less and break up less.\footnote{Hereafter we refer to the separation from cohabitation as a breakup to avoid confusion with legal separation.}
+This suggests that divorce settlements affect partnership choices when one spouse can divorce unilaterally.
+Moreover, we analyze how unilateral divorce affected cohabitation spells duration: our estimates show that cohabitations formed after the reform last longer because people both marry less and break up less.\footnote{Hereafter we refer to the separation from cohabitation as a breakup to avoid confusion with legal separation.}
 
 In the second part of the paper, we propose a theory to understand the mechanisms underlying the facts documented in the empirical part.
-We build a dynamic model of intra-household decision making and search in the mating market, where agents make decisions according to the realization of idiosyncratic permanent income shocks, their amount of wealth and couple-specific match quality.
+We build a dynamic collective model of intra-household decision making and search in the mating market, where agents make decisions according to the realization of idiosyncratic permanent income shocks, their amount of wealth and couple-specific match quality.
 With some probability, single agents meet a potential partner drawn from an exogenous distribution of match quality, productivity, and wealth.
@@
 Moreover, there is a stigma affecting cohabitations, which is modeled as an exogenous disutility flow.
-It can capture the shame towards out-out-wedlock births, premarital sex, and premarital cohabitation at the time of the divorce revolution.
+It captures the shame towards out-out-wedlock births and premarital sex.
 In the case of a breakup, assets are split according to individual property rights.
-In the case of divorce, we assume they are divided in half.
-We estimate the model using community property states data to be consistent with this assumption.
+In the case of divorce, we assume they are divided in half.\footnote{We estimate the model using community property states data to be consistent with this assumption.} Additionally, we assume that contrary to breakup, divorce is financially costly.
 Breakup (unilateral divorce) can be initiated unilaterally, as opposed to mutual consent divorce, which requires both partners' agreement.
-Following \cite{voena2015}, under mutual consent the couple always cooperates while married, which implies that the allocation of resources corresponds to the Pareto-efficient inter-temporal allocation.
-% Wait is this even true???
-Instead, the fact that just one spouse can decide to terminate the relationship results in a lack of commitment, making the intra-household allocation of decision power responsive to shocks.
-Hence, abandoning the mutual consent regime affects the risk of divorce and, in turn, the surplus of marriage.
-
-The divorce costs and rights affect the gains of marriage relative to cohabitation through three main channels.
-First, by acting as commitment technologies, they enforce a better risk sharing and a more efficient specialization in public goods production within marriage.
-We assume that public goods are produced with money and women's time.
-When a woman stops working to produce such a good, her potential productivity in the labor market decreases.
-Second, divorce costs increase the risk of being ``trapped" in a bad marriage.
-Third, they affect the expected value of marriage by modifying the risk and value of divorce.
+Following \cite{voena2015}, under mutual consent the couple always cooperates while married and the allocation of resources corresponds to the Pareto-efficient inter-temporal allocation.
+Instead, the fact that just one spouse (cohabitant) can decide to terminate the relationship results in a lack of commitment,\footnote{Our modelling of the decision making in the couple builds on existing literature on limited commitment (\cite{kk1996},  \cite{ligon2002}, \cite{marcet2019} and \cite{pavoni2018}), which has been applied to dynamic collective models in the household by \cite{mazzocco2007}, \cite{mazzocco2013}, \cite{bayot2015}, \cite{rigas2015}, \cite{voena2015}, \cite{abraham2018}, \cite{lise2018}, \cite{low2018}, \cite{foerster2019} and \cite{reynoso2019} among others.
+} making the intra-household decision power responsive to shocks, as spouses (cohabitants) can credibly exercise the threat of divorce (breakup).
+Because utility is imperfectly transferable, in our model the Becker-Coase theorem does not hold.
+Hence, abandoning the mutual consent regime affects the risk of divorce and, in turn, the surplus of marriage.\footnote{According to \cite{becker1977}, divorce laws should not affect separation decisions \textit{``if all compensations between spouses were feasible and costless"}.
+The assumptions underlying the Becker-Coase theorem are discussed by \cite{chiappori2015} and \cite{fella2004}.}
+
+The barriers to divorce---represented by its costs and the right to veto it---affect the gains of marriage relative to cohabitation through three main channels.
+First, by acting as commitment technologies, they enforce a better risk sharing and a more efficient household specialization.
+Second, they increase the risk of being ``trapped" in a bad marriage.
+Third, they affect the expected value of marriage by modifying the risk of divorce, as the intra-household allocation during marriage differs from the allocation of resources in divorce, which depends on the mandated equal division of property.
 The effects of tightening or relaxing the barriers to divorce depend on which channel prevails.
 For example, the introduction of unilateral divorce has an uncertain impact on the share of couples that cohabit and marry.
-The outcomes of cohabitation and marriage depend not only on the rules underlying these contracts but also on sorting on unobserved relationship quality.
-A cheap breakup is most attractive to couples whose match quality is low.
-The couples' ability to cooperate depends on the match quality itself through its effect on the couples' stability: making partnership-specific investments is more comfortable when the risk of splitting is low, which is when the match quality is high.
-
-%In our framework marriage gains depend on the quality of the match: for couples whose value is low cohabitation is the best choice because breaking up is cheaper and their risk of splitting is high.
-Interestingly, the ability of the couple to cooperate is directly affected by the quality of the match.
-For this reason, the outcomes of cohabitation and marriage depend not only of the rules underlying these contracts, but the ability of the couple to cooperate is directly affected by the quality of the match.
-
-%The gains of marriage with respect to cohabitation come from a better risk sharing and a more efficient specialization in the production of public goods,\footnote{We assume that public goods are produced with money and women's time.
-When women stop working for producing such a good their potential productivity in the labor market decreases.} which arise from a stronger commitment, enforced through the threat of a costly divorce and the mutual consent regime.
-On the other hand, couples facing the highest risk of splitting (i.e.
-because of a low match quality draw) are more likely to choose cohabitation, since breaking up is cheaper.
-Interestingly, the ability of the couple to cooperate is directly affected by the quality of the match.
-For this reason, the outcomes of cohabitation and marriage depend not only of the rules underlying these contracts, but also on sorting on match quality.
-
-% After unilateral divorce is introduced, the dissolution of marriage can be initiated by one spouse without the other spouse's consent.
-We model the decision making in the couple building on the literature on limited commitment (see for example \cite{kk1996},  \cite{ligon2002}, \cite{marcet2019} and \cite{pavoni2018}), which has been applied to dynamic collective models in the household by \cite{voena2015}, \cite{mazzocco2007}, \cite{foerster2019} and \cite{lise2018} among others.
-In this framework, when one member of the couple wishes to split, the couple rebargains such that the binding member is made indifferent between breakup and staying in a couple.\footnote{For particularly bad draws in the match quality or productivity shock this might not be possible and hence the couple would split.}
+The outcomes of cohabitation and marriage depend not only on the rules underlying these contracts but also on the match quality through its effect on the couples' stability.
+In fact, making partnership-specific investments is more comfortable when the risk of splitting is low, which is when the match quality is high.
+Since a cheap breakup is most attractive to couples whose match quality is low, selection on match quality amplifies the differences in the behavior between married and cohabiting couples.
 
 In the third part of the paper we structurally estimate the model to understand the quantitative relevance of the mechanisms that drive partnership choice.
-The model is estimated by indirect inference using to match the regression results from our empirical analysis, mating market moments (NSFH), and female labor supply moments (PSID).
+The model is estimated by indirect inference using as targets the regression results from our empirical analysis, mating market moments (NSFH), and female labor force participation moments (PSID).
 The introduction of unilateral divorce is modeled as an unexpected policy change.
 The estimated model closely replicates the targeted moments.
-Our over-identification checks support the estimation results: the model can match several non-targeted moments, for instance, the impact of unilateral divorce on cohabitation duration.
+Our over-identification checks support the estimation results by highlighting that the model can match several non-targeted moments, among which the impact of unilateral divorce on cohabitation duration.
 
@@
 For example, if there was no wage uncertainty and women always participated in the labor market, unilateral divorce would affect marriage gains via the direct effect only.} Since cohabiting couples that would have married under the older regime are better matched than the average cohabiting couple, the reform increases the stability and the duration of newly formed cohabitations.
-To further deepen our understanding of the mechanisms, we analyze the intra-household bargaining changes that followed the policy change.
-We find that the average Pareto weight of cohabiting women increases because men, fearing to lose most of their assets because of divorce, convince women to cohabit instead of marrying in exchange for more power in the couple.
+The possibility of cohabitation has been crucial to translate institutional change (unilateral divorce) into social change (female empowerment within the couple).
+In fact, we find that the average Pareto weight of cohabiting women at the time the couple meets increases because men, fearing to lose most of their assets upon divorce, convince women to cohabit instead of marrying in exchange for more power in the couple.
 This mechanism is specific to the divorce regime where assets are split evenly.
@@
 Consistently with empirical evidence, the impact of unilateral divorce on cohabitation likelihood is lower in the model under separate ownership.
-% This paragraph is still long and can be split somehow
 
 The fourth and last part of the paper conducts a series of counterfactual experiments to understand the quantitative importance of the forces that contributed to the rise of cohabitation.
-To assess the role of unilateral divorce, we perform a counterfactual experiment where the unilateral divorce was never introduced.
+To assess the role of unilateral divorce, we perform a counterfactual experiment where unilateral divorce was never introduced.
 We find that people on average would have spent 1.24 years cohabiting instead of 2.19, while only 29.1\% of people would have ever cohabited instead of 43.3\%.
-In the second series of counterfactuals, we find that a 20\% decrease in gender productivity gap and a 10\% drop in market prices of goods increase respectively by 9\% and 3\% the share of people that ever cohabited at age 39.
+In the second series of counterfactuals, we find that a decrease in gender productivity gap and a drop in market prices of home goods increase the share of people that ever cohabited.
 Both effects are driven by a reduced scope for household specialization, which is better exploited within marriage.
@@
 
-Another subset of these papers studies the effect of changes in cohabitants' rights on partnership choices and cohabiting couples' behavior, highlighting the role of alimony rights  (\citealp{chiappori2017,gousse2018}), taxation \cite{leturcq2012} and division of assets at breakup (\citealp{fisher2012,gousse2018,chigavazira2019}).
-We extend this literature by showing that the introduction of unilateral divorce impacts both the choice to cohabit and cohabitation's stability, even though cohabitant's rights are not directly affected.
-Further, the effects on the intention to cohabit depends on property division rights, which indicates that partnership choices depend on divorce allocations.
+Another subset of these papers studies the effect of changes in cohabitants' rights on partnership choices and cohabiting couples' behavior, highlighting the role of alimony rights  (\citealp{chiappori2017,gousse2018}), taxation \citep{leturcq2012} and division of assets at breakup (\citealp{fisher2012,gousse2018,chigavazira2019}).
+We extend this literature by showing that the introduction of unilateral divorce impacts both the choice to cohabit and cohabitation's stability, even though cohabitant's rights are not directly affected.\footnote{\cite{matouschek2008} study the effect of a decrease in the cost of divorce, proxied by unilateral divorce, on marriage and divorce rates using a framework where cohabitation is a choice.
+Since they abstract from intra-household bargaining, they cannot capture the effect of property rights upon divorce.} Further, the effects on the intention to cohabit depends on property division rights, which indicates that partnership choices depend on divorce allocations.
 This evidence suggests that changes in family law should be designed considering that marriage and cohabitation are substitutes.
-%\cite{chiappori2017},\cite{persson2020}, \cite{leturcq2012}, \cite{gousse2018}
-%Second, our paper expands the literature on cohabitation, showing how the risk of divorce is essential for understanding partnership choices.
-Different papers in the literature highlighted various gains of marriage with respect cohabitation: commitment \citep{matouschek2008}, labor specialization within the couple \citep{gemici2014}, learning about match quality \citep{brien2006}, income dynamics \citep{blasutto2020} and investment in children \citep{lafortune2020}.
-A paper closely related to ours is \cite{lafortune2020}, who highlight the role of assets as a collateral that enforces commitment and hence allows for optimal investment in children.
-While we think that their mechanism is important, it cannot be the whole story since we observe that the switch towards cohabitation is the strongest in states where assets are divided more equally, where their model would predict that the effect is the weakest.
-In this paper, we quantify how much of the shift is due to the erosion of marriage's collateral versus the role of the increased risk of divorce.
-We extend the work of \cite{gemici2014} and \cite{blasutto2020}, who develop collective dynamic models with limited commitment, introducing asset accumulation decisions, which are shown to play an important role for commitment and hence for partnership choice, especially when interacted with property rights upon divorce.
-Other papers highlighted how
 
@@
 Advances in the home production technology and the reduction in the gender wage gap also contributed to the rise.
-
-Our modelling of the decision making in the couple builds on existing literature on limited commitment (\cite{kk1996},  \cite{ligon2002}, \cite{marcet2019} and \cite{pavoni2018}), which has been applied to dynamic collective models in the household by \cite{mazzocco2007}, \cite{mazzocco2013}, \cite{bayot2015}, \cite{rigas2015}, \cite{voena2015}, \cite{abraham2018}, \cite{lise2018}, \cite{low2018}, \cite{foerster2019} and \cite{reynoso2019} among others.
-The fact that couples cannot commit ex-ante to any possible division of marital surplus contributes to the creation of an imperfectly transferable utility environment, under which the Becker-Coase theorem does not hold (see \cite{galichon2019} and \cite{weber2018}, who applies the theorem to related environments).
-The imperfect transferability feature is important: according to \cite{becker1977}, divorce laws should not affect separation decisions \textit{``if all compensations between spouses were feasible and costless"}.
-The assumptions underlying the Becker-Coase theorem are discussed by \cite{chiappori2015} and \cite{fella2004}.
 
@@
 
-%\begin{enumerate}
-%\item \cite{chigavazira2019}: What: extending  equitable  property  division  divorce  laws  to  unmarried cohabiting couples in Australia.
-Findings: men increase their employment and women increase time spent on housework.
-Couples have more children and are more likely  to  become  home  owners.
-Strategy: triple Diff-in-Diff: state-time-relationship(coh/mar).
-They select a sample of marriages and cohabitation that stays intact at the end of the time span[this seems wrong to me].
-Then they claim that the effect is not due to selection, even thought they check that in a sloppy way without a duration model, which seems the thing to do.
-%\item \cite{chiappori2017}: what:  granting alimony rights to cohabiting couples in Canada.
-Finsings: Among couples united before the reform, obtaining the right to petition for alimony led women to lower their labor force participation but not among newly formed cohabiting couples.
-Cool difference lead by selection+commitment
-%\item \cite{persson2020}: VERY IMPORTANT PAPER.
-Exploiting Sweden’ s elimin ation of s ur v ivors insur ance, I demon strate that severin g this link (1) affected entry into marriage up to 50 years before expected payout, (2) raised the divorce rate by 10pp, and (3) raised the assortativeness of matching (4) increased rate of cohabitation and of separation, consistent with selection along match quality
-%
-%\end{enumerate}
-\section{US Divorce and Cohabitation Laws: an Overview} % This should be a subsection, otherwise it is a bit short...
+\section{US Divorce and Cohabitation Laws: an Overview} 
 \textbf{Divorce Laws.} Between the late 1960s and early 1980s, most US states experienced fundamental changes in the divorce law.
@@
 Before the 1960s the vast majority of US states had a mutual consent divorce regime.\footnote{All the states apart from New Mexico, Oklahoma and Alaska.} Both spouses' agreement was needed to obtain a divorce for mundane reasons (i.e., without misconduct by any spouse).
-Both spouses' agreement was needed to obtain a divorce for mundane reasons (i.e., without misconduct by any spouse).
 However, divorce was still permitted for grounds showing guilt of misconduct by any of the two spouses: for those cases, the innocent party's agreement alone was enough for having a divorce granted.
@@
 Under this regime divorce can be filed by one spouse without the consent of the other.
-More detailed chronology about the unilateral divorce introduction was in different states can be found in Table 1 of \cite{ciacci2017}% I think this needs an appendix
+More detailed chronology about the unilateral divorce introduction was in different states can be found in table \ref{table:dlaws} in the appendix.
 
@@
 %\end{enumerate}
-\textbf{Breakup/Divorce laws compared.} The regulation of cohabitation in the US is limited, and small changes have been done since the 1960s, when “Cohabitation created no rights or obligations”, see \cite{garrison2008}.
-She argues that \textit{“Cohabitants could not agree to create rights or obligations based on their intimate relationship”}.
-She continues analyzing the effect of the \textit{Marvin vs.
-Marvin} case (1976), where palimony --- a compensation from one member of an unmarried couple to another after breakup --- was awarded to the female partner: \textit{“[the case] have not produced results markedly different from those permissible under pre-Marvin case law.”} Finally, she argues that claims for financial relief has rarely reached the courts because 1) cohabitation is usually very short and no committed 2) cohabitants are younger and poorer than marrieds and 3) cohabitants do not usually adopt sharing behavior, unlike in the Marvin cases.
+\textbf{Breakup/Divorce laws compared.} The regulation of cohabitation in the US is limited, and small changes have been done since the 1960s, when \textit{“Cohabitation created no rights or obligations”} \citep{garrison2008}.
+The research by \cite{garrison2008} also analyzes the effects of the \textit{Marvin vs.
+Marvin} case (1976), where palimony --- a compensation from one member of an unmarried couple to another after breakup --- was awarded to the female partner: \textit{“[the case] have not produced results markedly different from those permissible under pre-Marvin case law.”} Finally, she argues that claims for financial relief has rarely reached the courts because 1) cohabitation is usually very short and not committed 2) cohabitants are younger and poorer than marrieds and 3) cohabitants do not usually adopt sharing behavior, unlike in the Marvin cases.
 Similarly, \cite{bowman2004} claims that remedies based on the contract had a limited application.
@@
 Concerning property division rights, cohabitation de facto falls under the title-based property regime.
-One crucial difference between divorce and breakup is that the former requires the couple to undergo a legal process, which implies monetary and time costs, while the latter does not require this procedure.
-While \cite{garrison2008} argues that claims for financial reliefs after a breakup are rare, the breakup is treated like a divorce under the doctrine of common-law marriage, a legal framework under which a couple is considered as married without having formally registered their relationship.
+One crucial difference between divorce and breakup is that the former requires the couple to undergo a legal process, which implies monetary and time costs, while the latter does not require this procedure.\footnote{While \cite{garrison2008} argues that claims for financial reliefs after a breakup are rare, the breakup is treated like a divorce under the doctrine of common-law marriage, a legal framework under which a couple is considered as married without having formally registered their relationship.
 \cite{goran2008} explains that the existence of the implied contract is presumed once continuous cohabitation and reputation (holding out as husband and wife) are proven.
 However, it is still possible that the couple --- even if cohabiting for many years---is not considered to be in a marriage agreement, with marital rights and obligations.
-These rules create uncertainty regarding recognizing common-law marriage for some couples, especially those close to a breakup, where the two partners might disagree about the existence of an implied marital agreement.
-
-The lower costs of a breakup are consistent with the findings of \cite{avellar2005}, who show that for women the drop in income following the couple's breakdown is larger for divorce than for a breakup.
+These rules create uncertainty regarding recognizing common-law marriage for some couples, especially those close to a breakup, where the two partners might disagree about the existence of an implied marital agreement.} The lower costs of a breakup are consistent with the findings of \cite{avellar2005}, who show that for women the drop in income following the couple's breakdown is larger for a divorce than for a breakup.
 To further support the claim that divorce is more costly than a breakup, in appendix \ref{section:eventsa} we select from the PSID a sample of couples that divorced/broke up to study how their net-worth evolves after splitting.
-The point estimates of two event-studies indicate that richer couples' divorce results in a loss of assets, while we could not observe the same pattern for the divorce of poorer couples and breakups.
+The point estimates of several event studies indicate that richer couples' divorce results in a loss of assets, while we could not observe the same pattern for the divorce of poorer couples and breakups.
 
@@
 \section{Data and Empirical Evidence}
+Is the introduction of unilateral divorce related to the rise of cohabitation?
+Figure \ref{fig:events_raw} suggests that the link between these two events merits to be investigated.
+The left panel shows a negative correlation between the share of couples that decide to marry as opposed to cohabit, and the share of couples that are formed under a unilateral divorce regime.
+Even more interestingly, the right panel shows that the decrease in the share of couples that decide to marry instead of cohabiting over time accelerates once unilateral divorce is introduced.
+Since these two graphs do not control for possible confounders and do not provide a credible counterfactual, in this section we tackle these issues to offer more convincing evidence on the effect that unilateral divorce have on  i) partnership choices and on ii) the pool of people that cohabit.
+%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%GRAPH OF UNID ,MARRIAGE AND COHABITATION
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[ht]
+	\begin{center}
+		\caption{\\ Newly formed relationships (either married or cohabiting) and unilateral divorce (U.D.)}
+		\label{fig:events_raw}
+
+		\begin{subfigure}{.49\textwidth}
+			\centering
+			% include second image
+			\caption{{\color{blue}\% new couples choosing marriage instead of cohabitation} and {\color{red}\% relationships born under U.D.} }
+
+			\label{fig:years_raw}
+			\scalebox{0.5}{\input{years_raw.pgf} } 
+		\end{subfigure}
+		\begin{subfigure}{.49\textwidth}
+			\centering
+			% include first image
+			\caption{\% new couples choosing marriage instead of cohabitation around U.D.}
+			\label{fig:event_raw}
+			\scalebox{0.5}{\input{event_raw.pgf} } 
+		\end{subfigure}
+
+	\end{center}
+
+	\begin{minipage}{0.99\textwidth} % choose width suitably
+		{\footnotesize \textsc{Notes.} The left panel shows in blue the evolution over time of the \% of relationships born in year $t$ such that the couple chose marriage as opposed to unmarried cohabitation.
+The red line represents the \% of relationships born in $t$ in a state that already adopted unilateral divorce by year $t$.
+The right panel shows the \% of relationships where the couple chose to marry instead of cohabiting in an year whose distance in time from the introduction unilateral divorce in that state is equal to $d$ years.
+The red dotted lines are obtained running linear regressions on a dummy for marriage, using the event time as the only regressor.
+All the variables presented in this figure are constructed with a sample of first and second relationships (which can be either marriage or cohabitation) from the 1988 wave of the NSFH: we provide further details about the survey and the sample construction in section 3.
+All the variables depicted in the two figures are constructed using sample weights.
+\par}
+	\end{minipage}
+\end{figure}
+\FloatBarrier
 \subsection{Dataset}\label{dataset}
@@
 This is reflected in detailed questions regarding the retrospective family history of respondents, including information both about marriage and cohabitation.
-Moreover, primary respondents are asked a large set of questions regarding their socio economic background and the demographics of the household.\footnote{One adult per household was randomly selected as the primary respondent, while in the NSFG respondents are all women of 15-44 years of age.} While the NSFH I is the first of three longitudinal waves, NSFG is made of several repeated cross sectional samples.\footnote{We decided not to use the other two other waves of the NSFH because in the second wave all currently cohabiting households were dropped from the survey.
-Moreover, the 1988 wave of NSFG is the only one with publicly available information about the residence of the respondents, which is crucial to identify the divorce regime that applies to the respondent.} A drawback of using this data is that we know the state of residence of the respondents only at age 16 for the NSFH and at birth for the NSFG.\footnote{We do not have the choice of using other surveys for our analysis, since they either lack the State of residence variable, or they miss information about cohabitation history, or they do not cover people that were in a relationship age at the time the law changed.} Since we also know whether people lived all their life in the same state, we can overcome it and perform our empirical analysis both on the universe and of the subsample of never movers.
+Moreover, primary respondents are asked a large set of questions regarding their socio-economic background and the demographics of the household.\footnote{One adult per household was randomly selected as the primary respondent, while in the NSFG respondents are all women of 15-44 years of age.} While the NSFH I is the first of three longitudinal waves, NSFG is made of several repeated cross sectional samples.\footnote{We decided not to use the other two other waves of the NSFH because in the second wave all currently cohabiting households were dropped from the survey.
+Moreover, the 1988 wave of NSFG is the only one with publicly available information about the residence of the respondents, which is crucial to identify the divorce regime that applies to the respondent.} A drawback of using this data is that we know the state of residence of the respondents only at age 16 for the NSFH and at birth for the NSFG.\footnote{We do not have the choice of using other surveys for our analysis, since they either lack the state of residence variable, or they miss information about cohabitation history, or they do not cover people that were in a relationship age at the time the law changed.} Since we also know whether people lived all their life in the same state, we can overcome it and perform our empirical analysis both on the universe and of the subsample of never movers.
 We will show that point estimates turn out to be statistically not distinguishable between the two samples.
@@
 We did not consider third or higher order relationships for our analysis since these individuals would be further away from the age at which we knew their state of residence.
-Finally, we consider only relationships that started when the respondent was 20 years old or older.
+Finally, we consider only relationships that lasted at least one month and started when the respondent was 20 years old or older.
+Relationships that started before 1955  are dropped to minimize the recall bias.
 In table \ref{table:sum_rel} we report the descriptive statistics of this sample.
@@
 Does unilateral divorce affect the partnership choice of couples?
-We exploit the timing in the adoption of unilateral divorce as a source of exogenous variation in the right to divorce.\footnote{See table 1 in \cite{ciacci2017} for the timing of adoption of unilateral divorce.} This strategy has already been used several times by the literature\footnote{Among the others, see \cite{wolfers2006}, \cite{stevenson2008}, \cite{voena2015}, \cite{reynoso2019} and \cite{ciacci2017}.} to study the non-neutrality of the rights to divorce on various economic and demographic outcomes.
-According to \cite{gruber2004}, who reviews the legal literature about the topic, the introduction of unilateral divorce was not view as a tool of social policy, but rather a way to reduce the legal burden of divorce trials.
+We exploit the timing in the adoption of unilateral divorce as a source of exogenous variation in the right to divorce.\footnote{See table \ref{table:dlaws} for the timing of adoption of unilateral divorce.} This strategy has already been used several times by the literature to study the non-neutrality of the rights to divorce on various economic and demographic outcomes.\footnote{Among the others, see \cite{wolfers2006}, \cite{stevenson2008}, \cite{voena2015}, \cite{reynoso2019} and \cite{ciacci2017}.}  According to \cite{gruber2004}, who reviews the legal literature about the topic, the introduction of unilateral divorce was not view as a tool of social policy, but rather a way to reduce the legal burden of divorce trials.
 This reasoning is consistent with the fact that this change was not initiated by the most liberal states: New York was the last state to introduce unilateral divorce in October 2010, almost 40 years later than Kentucky.
@@
 \begin{equation}\label{eq:ols_baseline}
-\text{married}_{i,t,s}=\beta_0+\beta_1*\text{Unilateral}_{t,s}+\mathbf{\gamma'}\mathbf{X}_i+\delta_s+\nu_t+\epsilon_{i,t,s}.
-\end{equation}
-The dependent variable is a dummy take takes value $1$ if the couple $i$, started at time $t$ if state $s$ is a marriage, and 0 if it is cohabitation.
-The vector $\mathbf{X}_i$ instead includes a set of socio demographic controls, while $\delta_s$ are the state fixed effects and  $\nu_t$ are the time fixed effects.
+\text{married}_{i,t,s}=\beta_0+\beta_1\cdot\text{Unilateral}_{t,s}+\mathbf{\gamma'}\mathbf{X}_i+\delta_s+\nu_t+\epsilon_{i,t,s}.
+\end{equation}
+The dependent variable is a dummy take takes value $1$ if the couple $i$, started at time $t$ in state $s$ is a marriage, and 0 if it is cohabitation.
+The vector $\mathbf{X}_i$ instead includes a set of socio-demographic controls, while $\delta_s$ are the state fixed effects and  $\nu_t$ are the time fixed effects.
 The variable $\text{Unilateral}_{t,s}$ instead is a dummy that takes value $1$ if unilateral divorce wave in place in state $s$ at time $t$: $\beta_1$ instead is the coefficient that is informative about the effect of unilateral divorce on partnership choice.
@@
 \FloatBarrier
-The results reported in table \ref{table:ols_rel_standard} suggest that unilateral divorce decreased the share of couples that are married by $-5\%(6\%)$ depending on the specification.
-These results are robust to an alternative specification that includes state specific linear trends, whose results are reported in table \ref{table:wmarlin}, and to the use of a logistic regression, reported in table \ref{table:wmar_logit}.
+The results reported in table \ref{table:ols_rel_standard} suggest that unilateral divorce decreased the share of couples that are married by $7-8\%$ depending on the specification.
+These results are robust to an alternative specification that includes state specific linear trends (table \ref{table:wmarlin}), to the use of a multinomial logit that takes into account the triple choice between staying single, cohabiting and marrying (table \ref{table:wmar_mlogit}), and to dropping California from the sample (table \ref{table:wmar_c}).
+Moreover, table \ref{table:wmarc_chil} shows that the shift towards cohabitation holds both for households where the respondent has some children and where she/he is childless and does not want any children.
+The limitations of using two way fixed effects estimators is highlighted by a recent literature (\citealp{goodman2018} and \citealp{chaise2020}) that casts doubts on their validity when treatment effects are heterogeneous across time.
+We address these issues following the recommendation of \cite{goodman2018} and use an event study design as a robustness check.
+The results, reported in figure \ref{fig:estud}, show that the effect stays significant and it is even slightly larger in size.
 
@@
 \begin{split}
-\text{married}_{i,t,s}=\beta_0+&\beta_1*\text{Unilateral*No Title Based}_{t,s}\\&+\beta_2*\text{Unilateral*Title Based}_{t,s}+\\&\quad\quad\beta_3*\text{Title Based}_{t,s}+\mathbf{\gamma'}\mathbf{X_i}+\delta_s+\nu_t+\epsilon_{i,t,s},
+\text{married}_{i,t,s}=\beta_0+&\beta_1\cdot\text{Unilateral}_{t,s}\cdot\text{No Title Based}_{t,s}\\&+\beta_2\cdot\text{Unilateral}_{t,s}\cdot\text{Title Based}_{t,s}+\\&\quad\quad\beta_3\cdot\text{Title Based}_{t,s}+\mathbf{\gamma'}\mathbf{X_i}+\delta_s+\nu_t+\epsilon_{i,t,s},
 \end{split}
@@
 \FloatBarrier
-The results show that the effect of unilateral divorce on the likelihood that a couples chooses marriage over cohabitation in non-title-based states is significant with a magnitude of $-6\%(-7\%)$ depending on specification, while it is not significant and much smaller in title-based states.
+The results show that the effect of unilateral divorce on the likelihood that a couples chooses marriage over cohabitation in non-title-based states is significant with a magnitude between $-7\%$ and $-9\%$ depending on specification, while it is not significant and smaller in title-based states.
 These results suggest that having a sharing rule decided by the law is not enough to replace the mutual consent regime as an alternative commitment technology.
-Instead, these results are consistent with the view that the richest partner starts disliking marriage when divorce becomes unilateral, since she would risk losing most of her wealth upon divorce.
-This was not happening in mutual consent regime, since she could have exercised her right to veto divorce.
+Instead, these results are consistent with the view that the richest partner starts disliking marriage when divorce becomes unilateral, since they would risk losing most of her wealth upon divorce.
+This was not happening in mutual consent regime, since they could have exercised her right to veto divorce.
 In title-based state this threat for the richest member of the couple does not exist, hence marriage surplus with respect to cohabitation does not vary significantly.
-Table \ref{table:wmarlinc} shows that results are robust to the inclusion of state specific linear trends.
+These results are robust to an alternative specification that includes state specific linear trends (\ref{table:wmarlinc}), to the use of a multinomial logit that takes into account the triple choice between staying single, cohabiting and marrying (\ref{table:wmar_mlogit}), and to dropping California from the sample (\ref{table:wmarc_c}).
+
 \subsubsection*{Cohabitation Duration}
@@
 \begin{split}
-&Y_{i,s,t,d}^\text{Marry}=\beta^\text{Marry}*\text{Unilateral}_{s,t}+\mathbf{\gamma^{\text{Marry'}}}\mathbf{X_i}+\alpha_d+\delta_s+\nu_t+\epsilon^{\text{Marry}}_{i,s,t,d},\\&
-Y_{i,s,t,d}^\text{Cohabit}=\beta^\text{Cohabit}*\text{Unilateral}_{s,t}+\mathbf{\gamma^{\text{Cohabit'}}}\mathbf{X_i}+\alpha_d+\delta_s+\nu_t+\epsilon^{\text{Cohabit}}_{i,s,t,d},\\&
-Y_{i,s,t,d}^\text{Breakup}=\beta^\text{Breakup}*\text{Unilateral}_{s,t}+\mathbf{\gamma^{\text{Breakup'}}}\mathbf{X_i}+\alpha_d+\delta_s+\nu_t+\epsilon^{\text{Breakup}}_{i,s,t,d},
+&Y_{i,s,t,d}^\text{Marry}=\beta^\text{Marry}\cdot\text{Unilateral}_{s,t}+\mathbf{\gamma^{\text{Marry'}}}\mathbf{X_i}+\alpha_d+\delta_s+\nu_t+\epsilon^{\text{Marry}}_{i,s,t,d},\\&
+Y_{i,s,t,d}^\text{Cohabit}=\beta^\text{Cohabit}\cdot\text{Unilateral}_{s,t}+\mathbf{\gamma^{\text{Cohabit'}}}\mathbf{X_i}+\alpha_d+\delta_s+\nu_t+\epsilon^{\text{Cohabit}}_{i,s,t,d},\\&
+Y_{i,s,t,d}^\text{Breakup}=\beta^\text{Breakup}\cdot\text{Unilateral}_{s,t}+\mathbf{\gamma^{\text{Breakup'}}}\mathbf{X_i}+\alpha_d+\delta_s+\nu_t+\epsilon^{\text{Breakup}}_{i,s,t,d},
 \end{split}
@@
 	\caption{}
-	\hspace{0.3cm}
+	\hspace{0.15cm}
 	\resizebox{0.99\textwidth}{!}{\input{graph_transitions2.tex}}
@@
 This assumption fits the fact that for people born in 1940-1955 (whose behavior will be used to build the target moments for the structural estimation) conservative attitudes towards premarital sex were common.\footnote{The shame associated with an out-of-wedlock birth, whose interaction with technology is studied by \cite{fernandez2014}, can be a factor leading young women to prefer marriage over cohabitation even if the rules governing these two partnerships were identical.
-\cite{blasutto2020} can match closely marriage and cohabitation choices using a theoretical framework close to ours, without the need of introducing a stigma component towards cohabitation.
-This is possible because he analyzes the behavior of people born in 1980-1984, for whom the stigma towards premarital sex and premarital cohabitation was low.}
+\cite{blasutto2020} can match closely marriage and cohabitation choices using a theoretical framework close to ours, without the need of introducing a stigma towards cohabitation.
+This is possible because he analyzes the behavior of people born in 1980-1984, for whom the stigma towards premarital sex and premarital cohabitation is arguably lower lower than for those born in 1940-1955.}
 
@@
 However, these costs are common with divorce and hence they do not help explaining why couples should choose one partnership over the others.
-This reasoning is confirmed by the fact that when we tried estimating the model allowing for a positive cost of breakup, these parameters was not identified.}
+This reasoning is confirmed by the fact that when we tried estimating the model allowing for a positive cost of breakup, this parameter was not identified.}
 An important feature of our model is the role of property rights, which defines how assets are divided upon divorce/breakup.
@@
 Under mutual consent regime, marriage is denoted by $\hat{M}$.
-Couples solve a Pareto problem where the weight of the wife is $\theta^f$ and the one of the husband is $1-\theta^f$.\footnote{Later in this section we describe how initial Pareto weight are set.} The state vector is $\Omega^{\hat{M}}_t=\{a^m_t,a^f_t,z^f_t,z^m_t,\psi_t,\theta^f\}$, while the variables over which the couple maximizes are summarized by the vector $\mathbf{q}^M_t=\{a^f_{t+1},a^m_{t+1},d_{t},c^m_{t},c^f_{t},P^f_t,D_t\}$, where $D_t$ is a dummy variable that takes value $1$ is divorce happens and $0$ otherwise.
+Couples solve a Pareto problem where the weight of the wife is $\theta^f$ and the one of the husband is $1-\theta^f$.\footnote{Later in this section we describe how initial Pareto weight are set.} The state vector is $\Omega^{\hat{M}}_t=\{a^m_t,a^f_t,z^f_t,z^m_t,\psi_t,\theta^f\}$, while the variables over which the couple maximizes are summarized by the vector $\mathbf{q}^\hat{M}_t=\{a^f_{t+1},a^m_{t+1},d_{t},c^m_{t},c^f_{t},P^f_t,D_t\}$, where $D_t$ is a dummy variable that takes value $1$ is divorce happens and $0$ otherwise.
 The formal problem solved by a couple who enters period $t$ as married is:
@@
 \end{equation}
-where $\mathbf{q}^{\hat{M}}_t=\{\tilde{a}^m_{t+1},\tilde{a}^f_{t+1},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$ is the $\argmax$ of problem \eqref{eq:v_mutual} conditionally on having chosen $D_t=0$.
+where $\tilde{\mathbf{q}}^{\hat{M}}_t=\{\tilde{a}^m_{t+1},\tilde{a}^f_{t+1},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$ is the $\argmax$ of problem \eqref{eq:v_mutual} conditionally on having chosen $D_t=0$.
 $V_{t+1}^{i\hat{M}}(\Omega^{\hat{M}}_{t+1})$ instead can be obtained by the expectation of the sum of the time utilities that the agent gets from $t+1$ to $T$, where the variables entering the utility function derive from the Pareto problem if the agent is in a relationship, otherwise they are the solution of \eqref{eq:v_single}, which represent the singles' problem.
@@
 Note that, in opposition to the mutual consent regime, Pareto weights can vary over time.
-The state vector of this problem is $\Omega^{\overline{M}}_t=\{a^m_t,a^f_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^M_t$.
+The state vector of this problem is $\Omega^{\overline{M}}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^{\overline{M}}_t=\{\tilde{a}_{t+1},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$.
 The formal problem of a couple entering $t$ as married is:
@@
 First, there is no loss in assets upon breakup.
-Second, the choice set of the cohabiting couple $\mathbf{q}^C_t=\{a^m_{t+1},a^f_{t+1},d_t,c^m_t,c^f_t,P^f_t,D_t,M_t,\chi_{t+1}\}$ and the state variables $\Omega^{C}_t=\{a^m_t,a^f_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t,\chi_t\}$ are different.
-Note that $M_t$ is dummy that indicates the choice of marrying and $\chi_t$ is the share of assets going to the women in case of breakup.\footnote{Note that while cohabiting couples can decide to marry, married couples cannot decide to cohabit.
-This asymmetry is not relevant because married couples would never decide to divorce and start cohabiting, even if they could.} Third, the time utility of cohabiting couple is decreased by $\gamma$.
-%Cohabiting couples, denoted by $C$, solve a pareto problem where the weight of the wife is $\theta^f_t$ and the one of the husband is $\theta^m_t$.The state vector is $\Omega^{C}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t\}$, while the variables over which the couple maximize are summarized by the vector $\mathbf{q}^C_t=\{a_{t+1},d_t,c^m_t,c^f_t,P^f_t,S_t,MA_t\}$.
-$S_t$ and ${M}_t$ are dummy variable that take value $1$ is the couple respectively breackup or marry\footnote{We denote marriage by $M$, which might be fall under unilateral divorce regime $\overline{M}$ or mutual consent $\hat{M}$.} and 0 otherwise.
-The formal problem that a cohabiting couple at $t$ solves is:
-%\begin{equation}\label{eq:v_coh}
-%\begin{split}
-%V_t^{C}(\Omega^{C}_t)=&\max_{\mathbf{q}^C_t} (1-S_t)\{\theta^f_{t+1} u(c^f_t,Q_t)+\theta^m_{t+1} u(c^m_t,Q_t)+\psi_t-\gamma+\beta E_t V^{C}_{t+1}(\Omega^{C}_{t+1})\}
-%\\ &\quad\quad+MA_t\{\theta^f_{t+1} u(c^f_t,Q_t)+\theta^m_{t+1} u(c^m_t,Q_t)+\psi_t+\beta E_t V^{M}_{t+1}(\Omega^{M}_{t+1})\}\\ &\quad\quad\quad\quad+S_t \{\theta^f_{t}V^{fS}_{t}(\omega^{f}_{t+1})+\theta^m_{t} V^{mS}_{t}(\omega^{m}_{t}))\}
-%\\ &\text{if $S_t=0$:}\hspace{35pt}\text{s.t. \eqref{eq:bcm} and \eqref{eq:pfunction},}\\ &\hspace{80pt}
-%\theta^f_{t+1}=\theta^f_{t}+\mu^f_t,\\ &\hspace{80pt}
-%\theta^m_{t+1}=\theta^m_{t}+\mu^m_t,
-%\\ &\text{if $S_t=1$:}\hspace{35pt}\text{s.t. \eqref{eq:bcs}, \eqref{eq:pfunction} for $i\in\{f,m\}$,}\\ &
-%\hspace{80pt}a_t^m+a_t^f= a_t,	\\ &
-%\hspace{80pt}a_t^m,a_t^f\text{ determined as in the title-based regime},
-%\end{split}
-%\end{equation}
-%where $\theta^f_{t+1}$ and $\theta^m_{t+1}$ adjust such that the following participation constraints are satisfied:
-%\begin{equation}\label{eq:p_cons_coh}
-%\begin{split}
-%&
-%W^{fC}_{t}(\Omega^{C}_{t})\geq V_{t}^{fS}(\omega^f_{t}),\\ &
-%W^{mC}_{t}(\Omega^{C}_{t})\geq V_{t}^{mS}(\omega^m_{t}). 
-%\end{split}
-%\end{equation}
-%Note that $\mu^i_t$ are the Lagrange multipliers associated with spouses' participation constraints.
-%The individual value of cohabitation conditional on $S_t=$ is  $W_{t}^{iC}$ for $i\in\{f,m\}$, and it is defined as 
-%\begin{equation}
-%W_{t}^{iC}=u(\tilde{c}_t^{i},\tilde{Q}_t^{i})+\psi_t-\gamma+\beta E_t V_{t+1}^{iC}(\Omega^{C}_{t+1}),
-%\end{equation}
-%where
-%$\mathbf{\tilde{q}}^{C}_t=\{\tilde{a}_{t+1},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$ is the $\argmax$ of problem \eqref{eq:v_mutual} conditionally on having chosen $S_t=0$.
-$V_{t+1}^{iC}(\Omega^{C}_{t+1})$ instead can be obtained by the expectation of the sum of the time utilities that the agent get from $t+1$ to $T$, where the variables entering the utility function derive from the pareto problem if the agent is in a relationship, otherwise they are the solution of \eqref{eq:v_single}.
-Similarly to the unilateral divorce regime, we assume that the planner evaluates the welfare of the two members of the couple if a breakup happens with the current Pareto weights.
+Second, the choice set of the cohabiting couple $\mathbf{q}^C_t=\{a_{t+1},d_t,c^m_t,c^f_t,P^f_t,D_t,M_t,\chi_{t+1}\}$ and the state variables $\Omega^{C}_t=\{a_t,,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t,\chi_t\}$ are different.
+Note that $M_t$ is dummy that indicates the choice of marrying and $\chi_t$ is the share of assets going to the women in case of breakup.\footnote{The way we model the title-based follows \cite{bayot2015}.} Third, the time utility of cohabiting couple is decreased by $\gamma$.
+The complete problem of the cohabiting couple can be found in section \ref{section:cprob} of the appendix.
 
@@
 In each period $t$ singles have a probability $\lambda_t$ to meet a potential partner.
-The productivity and the assets of the potential partner depends on the single agent's characteristics.
+The productivity and the assets of the potential partner depend on the single agent's characteristics.
 Formally, the assets of the potential partner $p$ are defined as:
@@
 \begin{equation}\label{eq:mmz}
-z_t^p=f(\overline{z}^{s^*,i^*}_t,z^r_t,\epsilon^z),
-\end{equation}
-where $\overline{z}^{s^*,i^*}_t$ represents the average productivity of singles of gender $s^*$,  $z^r_t$ is the productivity of the agent net of the gender and education specific trend, while $\epsilon^z$ is a normally distributed shock.
+\ln(z_t^p)=\alpha(\ln(\overline{z}^{s^*,i^*}_t)+\epsilon_t^z)+(1-\alpha)\ln(z^r_t),
+\end{equation}
+where $\overline{z}^{s^*,i^*}_t$ represents the average productivity of singles of gender $s^*$,  $z^r_t$ is the productivity of the agent net of the gender and education specific trend, while $\epsilon_t^z$ is a normally distributed shock.
 These assumptions capture in a reduced from fashion that people are mating assortatively both within marriage and cohabitation.
@@
 \begin{equation}
-\Upsilon^J(\theta^f_t,\Omega^{J-1}_t,\omega^f_t,\omega^m_t)=\big[V_t^{fJ}(\Omega^{J-1}_t)- V_t^{fS}(\omega^f_t)\big]\times\big[ V_t^{mJ}(\Omega^{J-1}_t)- V_t^{mS}(\omega^m_t)\big].
+\Upsilon^J(\theta^f_t,\Omega^{J-1}_t,\omega^f_t,\omega^m_t)=\big[V_t^{fJ}(\Omega^{J-1}_t,\theta^f_t)- V_t^{fS}(\omega^f_t)\big]\times\big[ V_t^{mJ}(\Omega^{J-1}_t,1-\theta^f_t)- V_t^{mS}(\omega^m_t)\big].
 \end{equation}
@@
 \item $\Theta^M_t\neq\O\text{ and }\Theta^C_t\neq\O \Rightarrow$ The couple chooses the partnership that gives the largest Nash product.
-Formally, if $ \Upsilon^M(\Omega^M_t,\omega^f_t,\omega^m_t)\geq\Upsilon^C(\Omega^C_t,\omega^f_t,\omega^m_t)$ the couple chooses marriage, otherwise cohabitation.
+Formally, if $ \Upsilon^M(\theta^{M,f}_t,\Omega^M_t,\omega^f_t,\omega^m_t)\geq\Upsilon^C(\theta^{C,f}_t,\Omega^C_t,\omega^f_t,\omega^m_t)$ the couple chooses marriage, otherwise cohabitation.
 \end{itemize}
@@
 This correction is particularly relevant for the estimation of the income process of women, because their hours worked vary significantly over the life-cycle.
-
 The income process of men is estimated by fitting the following liner model:
 \begin{equation}\label{eq:male_earn}
-\ln(w^m_{i,t,s,sur})=\iota^m_0+\iota^m_1*t+\iota^m_2*t^2+\delta_s+\nu_{sur}+u_{i,t,s,sur}^m,
+\ln(w^m_{i,t,s,sur})=\iota^m_0+\iota^m_1\cdot t+\iota^m_2 \cdot t^2+\delta_s+\nu_{sur}+u_{i,t,s,sur}^m,
 \end{equation}
@@
 \begin{equation}\label{eq:femae_earn}
-\ln(w^f_{i,t,s,sur})=\iota^f_0+\iota^f_1*t+\iota^f_2*t^2+\delta_s+\nu_{sur}+\varphi_{i,t,s,sur}+u_{i,t,s,sur}^f,
+\ln(w^f_{i,t,s,sur})=\iota^f_0+\iota^f_1 \cdot t+\iota^f_2 \cdot t^2+\delta_s+\nu_{sur}+\varphi_{i,t,s,sur}+u_{i,t,s,sur}^f,
 \end{equation}
@@
 Couples are always formed by men who are 2 years older than women.
-Agents retire at the age of 62 and the number of periods in the model if $T=62$.
-The discount factor $\beta$, the annual interest rate and the relative risk aversion $\sigma$ of private goods match those in \cite{attanasio2008}.
+Agents retire at the age of 62 and the number of periods in the model is $T=62$.
+The discount factor $\beta$ and the relative risk aversion $\sigma$ of private goods match those in \cite{attanasio2008}.
+The annual interest rate is set to 2\%.
 Instead, the parameters relative to the production of public goods, $\nu$ and $\kappa$ match those in \cite{mcgrattan1997}.
@@
 We considered the 1940-1955 birth cohorts of the PSID for these computations because the moments that we will use in the structural estimation are based on the behavior of people born in those years.} Wages are normalized such that average log wages of male at age 30 is 0.
-The variance of male and female's earnings at age $20$ $\sigma_{\zeta,1}^{2_m}$ and $\sigma_{\zeta,1}^{2_f}$ are taken directly from the PSID data.
+The variance of male's(female's) earnings at age $20(18)$ $\sigma_{\zeta,1}^{2_m}(\sigma_{\zeta,1}^{2_f})$ is taken directly from the PSID data.
 The parameters regarding the mating market, contained in equations \ref{eq:mma} and \ref{eq:mmz}, are pinned down to obtain a realistic degree of assortative mating with respect to assets and wages.
@@
    Var. $m$'s productivity   $t=1$  &$\sigma_{\zeta,1}^{2_m}$       & 0.54 & PSID \\[0.45ex]
-    Interest rate            &$R-1$       & 1.5\% & \cite{attanasio2008}   \\[0.45ex]
+    Interest rate            &$R-1$       & 2\% &    \\[0.45ex]
  Relative Risk Aversion private good   &$\gamma$  & 1.5 &\cite{attanasio2008}  \\[0.45ex]
@@
 Instead $\mu$ affects the gap in female labor supply for married and cohabiting couples.
-When this parameter is large the gap increases, because specialization within cohabitation becomes relatively harder as this relationship lacks a commitment technology $\lambda$ is intuitively identified by the share of people in a relationship.
+When parameter $\mu$ is large the gap increases, because household specialization within cohabitation becomes relatively harder as this relationship lacks a commitment technology.
+Parameter $\lambda$ is intuitively identified by the share of people in a relationship.
 The parameter $\sigma_{\psi}$ has a role in identifying the stability of marriage and cohabitation by modifying the likelihood that marriage surplus becomes negative, but it is mostly identified by the share of people that are choosing marriage over cohabitation.
@@
 
-The model is validated according to its ability to reproduce the effects of unilateral divorce on cohabitation duration, the share of income in the couple earned by married women, the average wage earned by women over their age and the ratio of hazard rates of richer over poorer men.\footnote{Richer men are those whose income is above the median, while poorer men are those whose income is below the median.} We run the same econometric models of section \ref{empirics} for cohabitation duration, both with the real data sample and with the simulated sample.
-The results, reported in table \ref{table:fit}, show that the size of the effects is well matched.
+The model is validated according to its ability to reproduce the effects of unilateral divorce on cohabitation duration, the share of income in the couple earned by married women, the average wage earned by women over their age and the ratio of hazard rates of richer over poorer men.\footnote{Richer men are those whose income is above the median, while poorer men are those whose income is below the median.} We use two cox duration models \citep{cox1972} to study how the risk of breakup and marriage for cohabiting couples are affected by the introduction of unilateral divorce.\footnote{Since the aim of this exercise is to study how the pool of cohabiting couples changes after the reform, we exclude cohabitation spells that already started when the law changed.
+When the event of interest in marriage (breakup), breakup (marriage) is treated as if the spell was censored.} The results, reported in table \ref{table:fit}, show that both using the empirical and the simulated sample the policy decreases the risk of marriage and breakup.
+Overall, the length of cohabitation increases by 27\% in the simulated sample.
 Women's wages over age and the average share of income provided by the wife in the household match the data, which validates the selection of women into the labor force.
@@
 \rule{-4pt}{2.5ex}
-External Moments & Model  & Data       &      95\% CI                      \\ [0.05ex] % inserts table
+External Moments & Model  & Data       &                           \\ [0.05ex] % inserts table
 \hline 
 \rule{-4pt}{2.5ex}
-Unilateral Divorce on the relative Risk of Marriage      & 0.75 & 0.73 &   [0.60,0.86]\\[0.15ex]
-Unilateral Divorce on the relative Risk of Breakup                   & 0.81 & 0.82 & [0.75,0.89] \\[0.15ex]
+Unilateral Divorce on the relative Risk of Marriage      & 0.72 & 0.42 &   [0.20,0.85]\\[0.15ex]
+Unilateral Divorce on the relative Risk of Breakup                   & 0.92 & 0.26 & [0.10,0.67] \\[0.15ex]
 Women wages by age           &  fig. \ref{fig:datasimwage} &  fig. \ref{fig:datasimwage} & fig. \ref{fig:datasimwage} \\[0.15ex]
@@
 See figure \ref{fig:psidist}.} This fact is consistent with a strong selection on marriage and cohabitation with respect to match quality.
-Marriage guarantees a better commitment and cooperation, but when the match quality is low the best option is to opt for cohabitation because breaking up is cheaper than divorcing.
+Marriage guarantees a better commitment and cooperation, but when the match quality is low the best option is to choose cohabitation because breaking up is cheaper than divorcing.
 The results of the event study show that upon the introduction of unilateral divorce the match quality of newly formed cohabitations increases by a value that is around 35\% percent of its structural standard deviation.\footnote{Note that the observed and structural distributions of the initial match quality are different because couples are not formed when the match quality at meeting is too low.} This result is consistent with selection of relatively high match quality couples into cohabitation after the policy change.
@@
 \textbf{Women's bargaining power $\theta$.} Panel \subref{sf:sub-second} depicts the evolution of the women bargaining power $\theta$ at meeting for cohabitation and marriage around unilateral divorce.
-$\theta$ increases with respect to baseline for cohabitation after the policy change, while it decreases for marriage.
-Under Mutual consent, marriage was protecting women from ending up divorced and poor, while cohabitation was chosen only by couples where the man was not able to commit for a long term relationship and the woman had little say about the decision.
-After the reform, men prefer cohabitation over marriage because it avoids splitting up assets equally upon divorce, but they have to promise a higher initial $\theta$ to convince women.\footnote{Note that upon breakup men receive on average around 65\% of the couple's wealth.} Similarly, the Pareto weight of women that marry goes down because men are willing to marry instead of cohabiting only if they can control more resources within the household.
+The average initial Pareto weight $\theta$ increases with respect to baseline for cohabitation after the policy change, while it decreases for marriage.
+Under mutual consent, marriage was protecting women from ending up divorced and poor, while cohabitation was chosen only by couples where the man was not able to commit for a long term relationship and the woman had little say about the decision.
+After the reform, men prefer cohabitation over marriage because the former avoids splitting up assets equally upon breakup, but in exchange women obtains a higher initial Pareto weight $\theta$.\footnote{Note that upon breakup men receive on average around 65\% of the couple's wealth.} Similarly, the Pareto weight of women that marry goes down because men are willing to marry instead of cohabiting only if they can control more resources within the household.
 
@@
 We restrict our attention on first relationships only because this allow us to perform an exercise where we impose marriage to a couple that decided to cohabit.
-This exorcise allows to compare marriage and cohabitation controlling for selection.} Then, for each of these samples we estimate the below equation
+This exercise allows to compare marriage and cohabitation controlling for selection.} Then, for each of these samples we estimate the equation below
 \[\Delta \log c_{it}=\alpha+\mu \Delta \log(w_{it})+\nu_{t}+\epsilon_{it},\]
@@
 Consequently, a low value of $\mu$ corresponds to a high degree of consumption insurance.
-The results displayed in table \ref{fig:divcons} provide important pieces of information about partnership types and consumption insurance.
+The results displayed in table \ref{table:risksh} provide important pieces of information about partnership types and consumption insurance.
 First, coefficient $\mu$ is the largest for cohabitation and the smallest for marriage under mutual consent divorce as reported in the first row.\footnote{We only consider individuals who spend their whole life-cycle under the same divorce regime.} This means that consumption insurance is the most effective within marriage with mutual consent divorce and the least effective within cohabitation.
 Does this happen because of a selection effect or because partnership rules directly affect the ability to share risk?
-Rows 2 and 3 of table \ref{fig:divcons} suggest that selection matters: marriages that were not preceded by cohabitation display a stronger degree of consumption insurance than those that were preceded by cohabitation.
+Rows 2 and 3 of table \ref{table:risksh} suggest that selection matters: marriages that were not preceded by cohabitation display a stronger degree of consumption insurance than those that were preceded by cohabitation.
 The reason is that the initial match quality of couples that married directly is higher compared to those who first cohabited.
 The fact that match quality is higher  implies that participation constraints bind more rarely, allowing for a smoother consumption path.
-Row 4 of table \ref{fig:divcons} shows that if we ``force" to marry men that had chosen to cohabit, we obtain that the amount of consumption insurance lies in between that of marriage and cohabitation.
+Row 4 of table \ref{table:risksh} shows that if we ``force" to marry men that had chosen to cohabit, we obtain that the amount of consumption insurance lies in between that of marriage and cohabitation.
 Since this experiment controls for selection, we conclude that partnership rules have a direct effect on couples' ability to share risk.
-The results relative to consumption insurance are partnership types are driven by the frequency at which Pareto weights are renegotiated.
+The results relative to consumption insurance and partnership types are driven by the frequency at which Pareto weights are renegotiated.
 Consistently with these results, figure \ref{fig:thch} shows that the share of periods in which Pareto weights are renegotiated is higher for cohabitation than marriage, and that only some of this difference can be explained by selection.
-This suggest that consumption insurance is tightly link with the frequency at which the couples renegotiates the way resources are shared.\\
+This suggest that consumption insurance is tightly link to the frequency at which the couples renegotiates the way resources are shared.\\
 
@@
 \section{Welfare}
-Previous research already studied the welfare effects of the introduction of unilateral divorce: both \cite{reynoso2019} and \cite{fernandez2017} find that this policy change decreases welfare for both genders, but more so for women.
+Previous research already studied the welfare effects of the introduction of unilateral divorce: both \cite{reynoso2019} and \cite{fernandez2017} find that this policy change decreases welfare for both genders and that the loss for women is larger than for men.
 While we find a similar effect, in this section we claim that accounting for cohabitation results in an even stronger difference by gender.
@@
 Here we assess its quantitative relevance by performing an experiment where unilateral divorce is never introduced.
-Table \ref{table:counterfactual_exp} reports the share of people that cohabited at 39 and the average years spent cohabiting\footnote{We consider the number of years spent cohabiting between the age of 20 to the age of 55.} under the baseline scenario and the counterfactual.
-The results show that under the counterfactual only 67\% of the people would have cohabited by the age of 39, while the years spent into cohabitation would have moved from 2.19 to 1.24.
+Table \ref{table:counterfactual_exp} reports the share of people that cohabited at 39 and the average years spent cohabiting under the baseline scenario and the counterfactual.\footnote{We consider the number of years spent cohabiting between the age of 20 to the age of 55.} The results show that under the counterfactual only 67\% of the people would have cohabited by the age of 39, while the years spent into cohabitation would have moved from 2.19 to 1.24.
 The latter effect is the strongest because it captures both changes in partnership choices of singles and in the duration of partnerships.
@@
 In the counterfactual there is less room from specialization in the couple when the two partner's wages are more similar and the opportunity cost of not working for women rises.
-Hence, in the counterfactual the couple's need for commitment decreases: cohabitation becomes relatively more interesting as it comes with a lower cost of breakup.
+Hence, in the counterfactual the couple's need for commitment decreases: cohabitation becomes relatively more interesting as it implies no cost of splitting.
 This result is consistent with the work of \cite{anelli2019}, who find that exposure to robots causes both a decline in market opportunities of men with respect to women and a decrease (increase) in the likelihood of being married (cohabiting).
@@
 Previous research already showed the impact of those changes of female labor supply \citep{greenwood2005}, the decline in marriage, the rise in divorce and assortative mating  \citep{greenwood2016}.
-The counterfactual experiment shows that the share of people that ever cohabited  increases by moved from 43.3\% to 44.8\%, while the years spent cohabiting move from 2.19 to 2.27.
+The counterfactual experiment shows that the share of people that ever cohabited  increases from 43.3\% to 44.8\%, while the years spent cohabiting move from 2.19 to 2.27.
 Similarly to a reduction in the gender wage gap, improvements in the technology of home production decrease the need for labor specialization within the household and for a commitment technology to enforce it.
@@
 In this paper, we show that partnership choices depend on the rights to divorce: the introduction of unilateral divorce in most US states influenced selection into marriage and cohabitation as well as the duration of these relationships and women's bargaining power.
-Using NSFH and NSFG data, we show that the introduction of unilateral divorce is responsible for a 5\% increase in the likelihood that singles choose cohabitation over marriage, and that newly formed cohabitations last longer.
+Using NSFH and NSFG data, we show that the introduction of unilateral divorce is responsible for a 7-8\% increase in the likelihood that singles choose cohabitation over marriage, and that newly formed cohabitations last longer.
 To understand the mechanisms that underlie those changes, as well its welfare effect for the two genders, we build a dynamic structural model where agents can choose to marry, cohabit and when to end these relationships.
@@
 Women are convinced to enter this relationship in exchange for a higher bargaining power, even though this makes them worse off if the couple subsequently breaks up.
-The possibility to switch to cohabitation does not affect much men's welfare, while for women the welfare under unilateral divorce is much lower because.
 Finally, we show that the magnitude of the overall effect of unilateral divorce on cohabitation is large: a counterfactual experiment reveals that if the law never changed, time spent into cohabitation for the birth cohorts used in our estimation would have been 1.24 years instead of 2.19, while the share of people that eve cohabited would have moved from 43.3\% to 29.1\%.
@@
 In fact, children raised by single mothers are likely outcomes of unwanted births that happen within cohabitation.
-This situation might happen less frequently within marriage, since it is a more stable relationship than cohabitation.
-
-%\section{Stuff to be Done}
-%\begin{itemize}
-%\item Check literature of rights of cohabitors in Family Law Quarterly
-%\item Read and Understand well Bayot-Voena, then provide a robustness check that incorporates their view of title-based breakup
-%\item Robustness check on comomn-law marriage: cohabitations with some probability $p$ should turn into marriages.
-Consider p varying with female labor supply, as cohabitation is more likely to be considered as common law marriage if children are present
-%\item Revise the empirical part, making the choice between cohabitation and marriage a duration model---better if a multinomial probit.
-%\item Robustness checks for the empirical part: eliminate california from the sample, do an event study.
-%\end{itemize}
+This situation might happen less frequently within marriage, since it is a more stable and committed relationship than cohabitation.
 
@@
 \counterwithin{table}{section}
+
+\section{History of US divorce Laws}
+%%%%%%%%%%%%
+%Table of UD
+%%%%%%%%%%%
+%Table of deep parameters
+\begin{table}[H]
+\caption{\\Year Unilateral Divorce was Introduced} % title of Table
+\label{table:dlaws}
+\centering % used for centering table
+\begin{threeparttable}
+\input{dlaws.tex}
+\begin{tablenotes}[flushleft]
+\footnotesize{\item \textsc{Notes}: The data of this table is taken from table 1, column (1) in \cite{ciacci2017}
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+\FloatBarrier
+
 \section{Net worth around divorce/breakup}\label{section:eventsa}
@@
 In the parallel version of TikTak, $Z^*_{j}$ is defined as the minimum among the outcomes  of the local minimizers  that already converged, while at the end of step 3 the global iteration number is updated to $j^*$, which stands for the number of global minimization that already started, without necessarily having converged already.
+
+\section{Problem of the cohabiting couple}\label{section:cprob}
+Cohabiting couples, denoted by $C$, solve a Pareto problem where the weight of the wife is $\theta^f_t$ and the one of the husband is $\theta^m_t$.The state vector is $\Omega^{C}_t=\{a_t,z^f_t,z^m_t,\psi_t,\theta^f_t,\theta^m_t,\chi_t\}$,  where $\chi_{t}$ is the share of assets going to the women in case of breakup.
+The variables over which the couple maximize are summarized by the vector $\mathbf{q}^C_t=\{a_{t+1},d_t,c^m_t,c^f_t,P^f_t,S_t,M_t,\chi_{t+1}\}$.
+$S_t$ and ${M}_t$ are dummy variable that take value $1$ is the couple respectively breakup or marry and 0 otherwise.\footnote{We denote marriage by $M$, which might be fall under unilateral divorce regime $\overline{M}$ or mutual consent $\hat{M}$.} The formal problem that a cohabiting couple at $t$ solves is:
+\begin{equation}\label{eq:v_coh}
+\begin{split}
+V_t^{C}(\Omega^{C}_t)=&\max_{\mathbf{q}^C_t} (1-S_t)\{\theta^f_{t} u(c^f_t,Q_t)+\theta^m_{t} u(c^m_t,Q_t)+\psi_t-\gamma+\beta E_t V^{C}_{t+1}(\Omega^{C}_{t+1})\}
+%\\ &\quad\quad+MA_t\{\theta^f_{t+1} u(c^f_t,Q_t)+\theta^m_{t+1} u(c^m_t,Q_t)+\psi_t+\beta E_t V^{M}_{t+1}(\Omega^{M}_{t+1})\}\\ &\quad\quad\quad\quad+S_t \{\theta^f_{t}V^{fS}_{t}(\omega^{f}_{t+1})+\theta^m_{t} V^{mS}_{t}(\omega^{m}_{t}))\}
+\\ &\text{if $S_t=0$:}\hspace{35pt}\text{s.t. \eqref{eq:bcm} and \eqref{eq:pfunction},}\\ &\hspace{80pt}
+\theta^f_{t+1}=\theta^f_{t}+\mu^f_t,\\ &\hspace{80pt}
+\theta^m_{t+1}=\theta^m_{t}+\mu^m_t,
+\\ &\text{if $S_t=1$:}\hspace{35pt}\text{s.t. \eqref{eq:bcs}, \eqref{eq:pfunction} for $i\in\{f,m\}$,}\\ &
+\hspace{80pt}a_t^m+a_t^f= a_t,	\\ &
+\hspace{80pt}a_t^f=\chi_t a_t,
+\end{split}
+\end{equation}
+where $\theta^f_{t+1}$ and $\theta^m_{t+1}$ adjust such that the following participation constraints are satisfied:
+\begin{equation}\label{eq:p_cons_coh}
+\begin{split}
+&
+W^{fC}_{t}(\Omega^{C}_{t})\geq V_{t}^{fS}(\omega^f_{t}),\\ &
+W^{mC}_{t}(\Omega^{C}_{t})\geq V_{t}^{mS}(\omega^m_{t}). 
+\end{split}
+\end{equation}
+Note that $\mu^i_t$ are the Lagrange multipliers associated with spouses' participation constraints.
+The individual value of cohabitation conditional on $S_t=$ is  $W_{t}^{iC}$ for $i\in\{f,m\}$, and it is defined as 
+\begin{equation}
+W_{t}^{iC}=u(\tilde{c}_t^{i},\tilde{Q}_t^{i})+\psi_t-\gamma+\beta E_t V_{t+1}^{iC}(\Omega^{C}_{t+1}),
+\end{equation}
+where
+$\mathbf{\tilde{q}}^{C}_t=\{\tilde{a}_{t+1},\tilde{\chi_{t+1}},\tilde{d}_{t},\tilde{c}^{m}_{t},\tilde{c}^{f}_{t},\tilde{P}^{f}_t\}$ is the $\argmax$ of problem \eqref{eq:v_coh} conditionally on having chosen $S_t=0$.
+$V_{t+1}^{iC}(\Omega^{C}_{t+1})$ instead can be obtained by the expectation of the sum of the time utilities that the agent get from $t+1$ to $T$, where the variables entering the utility function derive from the Pareto problem if the agent is in a relationship, otherwise they are the solution of \eqref{eq:v_single}.
+Similarly to the unilateral divorce regime, we assume that the planner evaluates the welfare of the two members of the couple if a breakup happens with the current Pareto weights.
 \section{Estimation of Income Processes}
@@
 \FloatBarrier
-\section{Robustness Checks - Empirical Analysis}
+\section{More evidence on the impact of unilateral
+divorce on partnership choices}
 \subsubsection*{Relationship Choice - Linear State Trends}
@@
 \subsubsection*{Relationship Choice - Multinomial Logit}
-The
+The empirical analysis on relationship choice that we conducted so far relied on a sample of newly formed partnerships.
+This implies that we studied the choice between marriage and cohabitation \textit{conditionally} on starting a partnership.
+Here we provide a more complete analysis by studying the choice of singles, who can decide every month to stay single, cohabit or to marry.
+We do so estimating a multinomial logit model on person month data, constructed using the first relationships of respondents of the NSFH and NSFG surveys.
+We construct the singleness spells by reporting individual choices from age 15 until the moment the first relationship (if it exists) begins.
+The results are reported in table \ref{table:wmar_mlogit} show how the introduction of unilateral divorce impacts the relative risk of cohabiting with respect to marrying.
+The results confirm that unilateral divorce increased the likelihood that individuals cohabit as opposed to marrying, and that the effect is larger in non title based states.
+Moreover, the size of the effect is also similar to the results presented in the main text.
+In fact, an increase in the relative risk of cohabitation with respect to marriage of 30\% (equivalent to a relative risk of 1.3) starting from an average number of first relationships that are cohabitation when the law changes of 30\%, is equivalent to a decrease in the number of marriages of 9\%.
+Interestingly, the estimated multinomial logits implies a smaller (2\%-6\%, not reported in the table) and non significant increase in the risk of staying single with respect to marrying.
 \begin{table}[H]\centering
@@
 \subsubsection*{Relationship Choice - Event Study}
-
+Two-way fixed effect regression have been widely used in the literature on the effects of unilateral divorce on economic outcomes.
+Yet, a recent work by \cite{goodman2018} shows that this technique is problematic for recovering causal effects when treatments effects are heterogeneous across time.
+We follow his recommendation to use an event study design as a robustness check for the results in the main text.
+Specifically, we restrict the sample to states that passed the unilateral divorce law before 1988 to estimate the following equation
+\begin{equation}\label{eq:ev_stude}
+\text{married}_{i,s,y,b}=\sum_{j=-32}^{55}\beta^{Unid}_j\cdot\mathcal{I}(t=j)+\alpha_{0}+\alpha_{b}+\alpha_{y}+\alpha_{s}+\mathbf{\gamma'Z_{i}}+\epsilon_{i,s,y,b},
+\end{equation}
+where $i$ stands for the respondent/household, $y$ for the month the relationship starts, $s$ is the state related to the household, $b$ is the age at birth of the respondent and $\textbf{Z}_i$ contains some characteristics of the respondent.
+Figure  \ref{fig:estud} plots $\beta^{Unid}_j$ for the different samples used for the estimation, where $j=-3$ is used as the reference.
+The results show no pretends and a significant reduction in the share of couples that cohabit after unilateral divorce is introduced: the size of the effect is larger than the one that comes from the two way fixed effect estimates.
+This might be due to the fact that the two weight fixed effect estimates over-weights observations that are closer to the policy change, as \cite{goodman2018} notice.
+This matter for our case as individuals might not recall the exact date at which the couple started living together.
+This is confirmed by the fact that the results reported in figure \ref{fig:estud} show that $\beta^{Unid}_j$ are negative (even though not significant) 1/2 years before the policy changes.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %Symmetry in income and assets
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[ht]
@@
 	\begin{minipage}{0.99\textwidth} % choose width suitably
-		{\footnotesize \textsc{Notes.}. \par}
+		{\footnotesize \textsc{Notes.} The figure plots the coefficients $\beta^{Unid}_j$  obtained from equation  \ref{eq:ev_stude}.
+Each panels shows the estimates obtained using one of our four samples.
+The red area around the lines indicates the 95\% confidence iterval, while the dotted line indicates the 90\% confidence interval.
+\par}
 	\end{minipage}
@@
 The shift towards cohabitation is lower in absolute value for couples whose respondent has children.
-This can be due to the fact that marriage remains the best partnership for enhancing cooperation, one desirable feature for couples with children since they require large investments in terms of time and money.
-This heterogeneity will be captured by our model: couples with a high relationship quality will be less sensible to the changes in the law and are also more likely to produce large quantities of the public good, which also represents children.
+This can be due to the fact that marriage is the best partnership for enhancing cooperation, which is a desirable feature for couples with children since these require large investments in terms of time and money.
+This heterogeneity is captured by our model: couples with a high relationship quality will be less sensible to the changes in the law and are also more likely to produce large quantities of the public good, which also represents children.
 
@@
 
-\section{Figures}
-
 %%%%%%%%%%%%%%%%%%%%%%%%5
@@
 
-\subsection{Model Fit}
+\section{Model Fit}
 
@@
 \FloatBarrier
-%%%%%%%%%%%%%%%%%%%%
-%MECHANISM
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Mechanisms}
-\begin{figure}[h!]
-\centering
-\caption{\\Cumulative distribution of love shock $\psi$ at meeting}
-\hspace*{-1.3cm} 
-\label{fig:psidist}
-\resizebox{0.8\textwidth}{!}{\input{psidist.pgf}}
-
-\end{figure}
-\FloatBarrier
+\section{Additional Figures and Tables}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Simulations-Symmetry}
+
 \begin{figure}[ht]
@@
 \FloatBarrier
+%%%%%%%%%%%%%%%%%%%%
+%MECHANISM
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[h!]
+\centering
+\caption{\\Cumulative distribution of love shock $\psi$ at meeting}
+\hspace*{-1.3cm} 
+\label{fig:psidist}
+\resizebox{0.8\textwidth}{!}{\input{psidist.pgf}}
+
+\end{figure}
+\FloatBarrier
 
@@
 
-		{\footnotesize \textsc{Notes.} The figures display the evolution of simulated consumption around divorce or breakup.
+		{\footnotesize \textsc{Notes.} The figures display the evolution of simulated consumption around divorce and breakup.
 The displayed patterns are normalized coefficients from event studies around divorce/breakup.)\par}
@@
 	\caption{\\$\%$ of periods $t$ for which $\theta_t\neq \theta_{t+1}$}
-	\vspace*{-0.5cm} 
+	\vspace*{-0.2cm} 
 	\hspace*{-1.3cm} 
@@
 The abbreviation M.C.
-means Mutual Consent regime, the abbreviation U.D.
-stands for Unilateral Divorce regime.
+means mutual consent regime, the abbreviation U.D.
+stands for unilateral divorce regime.
 The values are computed using the first simulated partnership of individuals who spent their life under the same divorce regime.
@@
 				The sample includes the whole duration of the first relationship of simulated women $i$.
-The last row is run on a sample of men who decided to cohabit but we imposed them to marry instead.
+The last row is run on a sample of women who decided to cohabit but we imposed them to marry instead.
 This allow us to analyze the insurance within marriage controlling for selection into a relationship.
@@
 
-\begin{figure}[ht]
-	\begin{center}
-		\caption{\\ Newly formed relationships (either married or cohabiting) and unilateral divorce (U.D.)}
-		\label{fig:events_raw}
-
-		\begin{subfigure}{.49\textwidth}
-			\centering
-			% include second image
-			\caption{{\color{blue}\% new couples choosing marriage instead of cohabitation} and {\color{red}\% relationships born under U.D.} }
-
-			\label{fig:years_raw}
-			\scalebox{0.5}{\input{years_raw.pgf} } 
-		\end{subfigure}
-		\begin{subfigure}{.49\textwidth}
-			\centering
-			% include first image
-			\caption{\% new couples choosing marriage instead of cohabitation around U.D.}
-			\label{fig:event_raw}
-			\scalebox{0.5}{\input{event_raw.pgf} } 
-		\end{subfigure}
-
-	\end{center}
-
-	\begin{minipage}{0.99\textwidth} % choose width suitably
-		{\footnotesize \textsc{Notes.} The left panel shows in blue the evolution over time of the \% of relationships born in year $t$ such that the couple chose marriage as opposed to informal cohabitation.
-The red line represents the \% of relationships born in $t$ in a state that already adopted unilateral divorce by year $t$.
-The right panel shows the \% of relationships where the couple chose to marry instead of cohabiting in an year whose distance in time from the introduction unilateral divorce in that state is equal to $d$ years.
-The red dotted lines are obtained running linear regressions on a dummy for marriage, using the event time as the only regressor.
-All the variables presented in this figure are constructed with a sample of first and second relationships (which can be either marriage or cohabitation) from the 1988 wave of the NSFH: we provide further details about the survey and the sample construction in section 3.
-All the variables depicted in the two figures are constructed using sample weights.
-\par}
-	\end{minipage}
-\end{figure}
-\FloatBarrier
 \end{document}

### 2020-11-05 graph_transitions2.tex
before Didi final check

@@
 \begin{tikzpicture}[domain=0:1,scale=1]
-\node [block, name=input,align=center] (sum) {\large Single};
-\node [block, above right=1.5cm and 7.449cm of sum ] (controller) {\large Separation};
-\node [block, below right=1.5cm and 7.449cm of controller,align=center] (system) {\large Cohabitation};
-\draw [<-,  thick, latex-] (controller) -- node[above left,yshift=0.3cm]{\large }(system);
+\node [ellipse,fill=blue!20,minimum height=2.5cm,minimum width=7.8cm,draw, name=input,align=center] (sum) {\huge\bf Single};
+\node [ellipse,fill=none,minimum height=0.5cm,minimum width=7.8cm, above right=1.5cm and 7.449cm of sum ] (controller) {\\ \huge \bf Breakup};
+\node [ellipse,fill=blue!20,minimum height=2.5cm,minimum width=7.8cm,draw, below right=1.5cm and 7.449cm of controller,align=center] (system) {\huge \bf Cohabitation};
+\draw [decoration={markings,mark=at position -0.95 with
+    {\arrow[scale=5,>=stealth]{<}}},postaction={decorate}] (controller) --  node[above left,yshift=0.3cm]{\huge \bf}(system);
 \node [output, right of=system] (output) {fe};
-\node [block, below left=1.5cm and 7.449cm of system,align=center] (measurements) {\large Marriage };
-\node [block, left of=measurements, node distance=10.05cm,align=left] (divorce) {\large Divorces};
-\draw [<-,  thick, latex-] (sum) -- node[above right,yshift=0.3cm]{\large } (controller);
-\draw [->,  thick, -latex] (sum) -- node[above]{\large} (system);
-\draw [->,  thick, -latex] (system) --node[above left]{\large } (measurements);
-\draw [->,  thick, -latex] (measurements) --node[above]{\large } (divorce);
-\draw [->,  thick, -latex] (sum) --node[above right]{\large } (measurements);
-\draw [->,  thick, -latex] (divorce) --node[right]{\large } (sum);
+\node [ellipse,fill=blue!20,minimum height=2.5cm,minimum width=7.8cm,draw, below left=1.5cm and 7.449cm of system,align=center] (measurements) {\huge \bf {\color{blue!20}a}Marriage };
+\node [ellipse,fill=none,minimum height=1.5cm,minimum width=4.2cm, left of=measurements, node distance=12.98cm,align=left] (divorce) {\huge \bf Divorce};
+\draw [decoration={markings,mark=at position -0.92 with
+    {\arrow[scale=5,>=stealth]{<}}},postaction={decorate}] (sum) -- node[above right,yshift=0.3cm]{\huge \bf } (controller);
+\draw [decoration={markings,mark=at position 1 with
+    {\arrow[scale=5,>=stealth]{>}}},postaction={decorate}] (sum) -- node[above]{\huge\bf} (system);
+\draw [decoration={markings,mark=at position 0.99 with
+    {\arrow[scale=5,>=stealth]{>}}},postaction={decorate}] (system) --node[above left]{\huge\bf } (measurements);
+\draw [decoration={markings,mark=at position 0.99 with
+    {\arrow[scale=5,>=stealth]{>}}},postaction={decorate}] (measurements) --node[above]{\huge\bf } (divorce);
+\draw [decoration={markings,mark=at position 1 with
+    {\arrow[scale=5,>=stealth]{>}}},postaction={decorate}] (sum) --node[above right]{\huge } (measurements);
+\draw [decoration={markings,mark=at position 1 with
+    {\arrow[scale=5,>=stealth]{>}}},postaction={decorate}] (divorce) --node[right]{\huge } (sum);
 node [near end] {$$} (sum);
